---
title: "LSB_DS_GLOBE"
output: html_document
---

# Connecting with Opal data server
## Login to server and assign study data
```{r, echo=FALSE}
#Load Opal R library
library(opal)
# Create an opal object with the login information
erasmus_opal <- opal.login()
#Login to Opal server and assign the content of the GLOBE table(s) to your RStudio environment
# GLOBE1991
opal.assign.table.tibble(erasmus_opal, 'GLOBE1991', 'GLOBE.GLOBE1991', variables= list("v137","v135","v139","v138","v136","v150","v145","SEGVv429","v147","v151","v153","SEVMv168","v140","v141","v240","v131")) 
GLOBE1991 <- opal.execute(erasmus_opal,'GLOBE1991')
# GLOBE1997
opal.assign.table.tibble(erasmus_opal, 'GLOBE1997', 'GLOBE.GLOBE1997',variables=list("v8d","v8b","v7","v8c","v8a","v9b","v9a","v9c","g13","v10e","v10b4","v10a","v10b3","v10b1","v10c","v10b2","v5")) 
GLOBE1997 <- opal.execute(erasmus_opal,'GLOBE1997')
# GLOBE2004
opal.assign.table.tibble(erasmus_opal, 'GLOBE2004', 'GLOBE.GLOBE2004', variables=list("w075","w074","w253","w078","w076","w077","w073","w099","w089","w090","w091","w093","w094","w095","w097","w098","w099","w101","w102","w103","w105","w106","w107","w139","w140","w141","w142","w143","w144","w180","w183")) 
GLOBE2004 <- opal.execute(erasmus_opal,'GLOBE2004')
# GLOBE2011
opal.assign.table.tibble(erasmus_opal, 'GLOBE2011', 'GLOBE.GLOBE2011', variables =list("v12_alc_freq","v13_alc_hv","v16_alcsoort_ra","v15_alcsoort","v16_alcsoort_r","v14_alc_binge","v17_rook_freq","v17_sig_pw","v17_sig_pd","v17_sigaar_pd","v18_rook_add","v19_a_wada","v19_a_waur","v19_a_wamin","v19_b_fida","v19_b_fiur","v19_b_fimin","v19_c_tuda","v19_c_tuur","v19_c_tumin","v21_a_hhda","v21_a_hhur","v21_a_hhmin","v21_b_zhda","v21_b_zhur","v21_b_zhmin","v32_a_ffq_groe","v32_b_ffq_rgro","v32_c_ffq_frui","v32_d_ffq_vifi","v23_b_wfda","v23_b_wfur","v23_b_wfmin")) 
GLOBE2011 <- opal.execute(erasmus_opal,'GLOBE2011')
# GLOBE2014
opal.assign.table.tibble(erasmus_opal, 'GLOBE2014', 'GLOBE.GLOBE2014', variables =list("G14v26","G14v27","G14v25","G14v25freq2","G14v23_d","G14v23freqd","G14v28_a_dag","G14v28_a_uur","G14v28_a_min","G14v28_b_dag","G14v28_b_uur","G14v28_b_min","G14v29_a_dag","G14v29_a_uur","G14v29_a_min","G14v29_b_dag","G14v29_b_uur","G14v29_b_min","G14v29_c_dag","G14v29_c_uur","G14v29_c_min","G14v32_a_dag","G14v32_a_uur","G14v32_a_min","G14v32_b_dag","G14v32_b_uur","G14v32_b_min")) 
GLOBE2014 <- opal.execute(erasmus_opal,'GLOBE2014')
```
## Assign participant id as first column of your harmonized dataframes
```{r, echo=FALSE}
lsb_GLOBE_0 <- data.frame(id = GLOBE1991$id)
lsb_GLOBE_1 <- data.frame(id = GLOBE1997$id)
lsb_GLOBE_2 <- data.frame(id = GLOBE2004$id)
lsb_GLOBE_3 <- data.frame(id = GLOBE2011$id)
lsb_GLOBE_4 <- data.frame(id = GLOBE2014$id)
```

## When you are done with your work, logout of Opal server
```{r, echo=FALSE}
opal.logout(erasmus_opal) 
```

# Table of Contents
1. [Alcohol consumption subdomain](#alcohol-consumption-subdomain)
2. [Tobacco consumption subdomain](#tobacco-consumption-subdomain)
3. [Physical activity subdomain](#physical-activity-subdomain)
4. [Diet and nutrition subdomain](#diet-and-nutrition-subdomain)
5. [Sleep quality subdomain](#sleep-quality-subdomain)

# Alcohol consumption subdomain

### **Variable label**:  Current consumption of alcohol  
**Variable name**: lsb_alc_cur_0  
**Variable description**:  Indicator of whether the participant currently consumes alcohol or has consumed alcohol in the past 12 months.  
**Value type**: integer  
**Variable unit**: N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 |  Does not currently consume alcohol   
1 |  Currently consumes alcohol  

**Harmonization status**:  complete     
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
lsb_GLOBE_0$lsb_alc_cur_0<-ifelse(GLOBE1991$v135<6,1L,
                                   ifelse(GLOBE1991$v135==6,0L,NA))

```  
**Validation script**:  
```{r, echo=TRUE}
attributes(GLOBE1991$v135)

A<-addmargins(table(lsb_GLOBE_0$lsb_alc_cur_0,GLOBE1991$v135,useNA = "always"))
colnames(A)<-c(names(attributes(GLOBE1991$v135)[[10]][1:6]),'NA','SUM')
as.data.frame.array(A,row.names = c('Does not currently consume alcohol','Currently consumes alcohol',"NA","SUM"))
```  
### **Variable label**:  Current consumption of alcohol  
**Variable name**: lsb_alc_cur_1  
**Variable description**:  Indicator of whether the participant currently consumes alcohol or has consumed alcohol in the past 12 months.  
**Value type**: integer  
**Variable unit**: N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 |  Does not currently consume alcohol   
1 |  Currently consumes alcohol   

**Harmonization status**:  complete  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
lsb_GLOBE_1$lsb_alc_cur_1<-recode(as.integer(GLOBE1997$v7),"1"=1L,"2"=1L,"3"=1L,"4"=1L,"5"=1L,"6"=0L)
```  
**Validation script**:  
```{r, echo=TRUE}
attributes(GLOBE1997$v7)

A<-addmargins(table(lsb_GLOBE_1$lsb_alc_cur_1,GLOBE1997$v7,useNA = "always"))
colnames(A)<-c(names(attributes(GLOBE1997$v7)[[10]][3:8]),'NA','SUM')
as.data.frame.array(A,row.names = c('Does not currently consume alcohol','Currently consumes alcohol',"NA","SUM"))
```  
### **Variable label**:  Current consumption of alcohol  
**Variable name**: lsb_alc_cur_2  
**Variable description**:  Indicator of whether the participant currently consumes alcohol or has consumed alcohol in the past 12 months.  
**Value type**: integer  
**Variable unit**: N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 |  Does not currently consume alcohol   
1 |  Currently consumes alcohol  

**Harmonization status**:  impossible  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}

```  
### **Variable label**:  Current consumption of alcohol  
**Variable name**: lsb_alc_cur_3  
**Variable description**:  Indicator of whether the participant currently consumes alcohol or has consumed alcohol in the past 12 months.  
**Value type**: integer  
**Variable unit**: N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 |  Does not currently consume alcohol   
1 |  Currently consumes alcohol  

**Harmonization status**:  complete  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
lsb_GLOBE_3$lsb_alc_cur_3<-recode(as.integer(GLOBE2011$v12_alc_freq),"1"=1L,"2"=1L,"3"=1L,"4"=1L,"5"=0L)
```  
**Validation script**:  
```{r, echo=TRUE}
attributes(GLOBE2011$v12_alc_freq)

A<-addmargins(table(lsb_GLOBE_3$lsb_alc_cur_3,GLOBE2011$v12_alc_freq,useNA = "always"))
colnames(A)<-c(names(attributes(GLOBE2011$v12_alc_freq)[[10]][1:5]),'NA','SUM')
as.data.frame.array(A,row.names = c('Does not currently consume alcohol','Currently consumes alcohol',"NA","SUM"))
```  
### **Variable label**:  Current consumption of alcohol  
**Variable name**: lsb_alc_cur_4  
**Variable description**:  Indicator of whether the participant currently consumes alcohol or has consumed alcohol in the past 12 months.  
**Value type**: integer  
**Variable unit**: N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 |  Does not currently consume alcohol   
1 |  Currently consumes alcohol  

**Harmonization status**:  complete  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
lsb_GLOBE_4$lsb_alc_cur_4<-recode(as.integer(GLOBE2014$G14v26),"1"=0L,"2"=1L,"3"=1L,"4"=1L,"5"=1L,"6"=1L)
```  
**Validation script**:  
```{r, echo=TRUE}
attributes(GLOBE2014$G14v26)

A<-addmargins(table(lsb_GLOBE_4$lsb_alc_cur_4,GLOBE2014$G14v26,useNA = "always"))
colnames(A)<-c(names(attributes(GLOBE2014$G14v26)[[10]][1:6]),'NA','SUM')
as.data.frame.array(A,row.names = c('Does not currently consume alcohol','Currently consumes alcohol',"NA","SUM"))
```  
### **Variable label**:  Current consumption of alcohol  
**Variable name**: lsb_alc_cur_5  
**Variable description**:  Indicator of whether the participant currently consumes alcohol or has consumed alcohol in the past 12 months.  
**Value type**: integer  
**Variable unit**: N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 |  Does not currently consume alcohol   
1 |  Currently consumes alcohol  

**Harmonization status**:  impossible  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
#This is where the R-script will be written

```  
**Correction script**:  
```{r, echo=TRUE}

```
### **Variable label**:  Current consumption of alcohol  
**Variable name**: lsb_alc_cur_6  
**Variable description**:  Indicator of whether the participant currently consumes alcohol or has consumed alcohol in the past 12 months.  
**Value type**: integer  
**Variable unit**: N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 |  Does not currently consume alcohol   
1 |  Currently consumes alcohol  

**Harmonization status**:  impossible  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}

```  

### **Variable label**:   Ever consumption of alcohol  
**Variable name**: lsb_alc_ever_0    
**Variable description**:  Indicator of whether the participant has ever consumed alcohol.  
**Value type**: integer  
**Variable unit**: N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 |   Never consumed alcohol  
1 |   Ever consumed alcohol  

**Harmonization status**:  impossible  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}

```  
### **Variable label**:   Ever consumption of alcohol  
**Variable name**: lsb_alc_ever_1    
**Variable description**:  Indicator of whether the participant has ever consumed alcohol.  
**Value type**: integer  
**Variable unit**: N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 |   Never consumed alcohol  
1 |   Ever consumed alcohol  

**Harmonization status**:  complete  
**Harmonization comment**:   
**Validation comment**:   the harmonized variable "Current consumption of alcohol" was combined with the study-specific variable "Have you had drinks containing alcohol in the past?" to create "Ever consumption of alcohol".  
**R script**:  
```{r, echo=TRUE}
lsb_GLOBE_1$lsb_alc_ever_1<-ifelse(lsb_GLOBE_1$lsb_alc_cur_1==1,1L,recode(as.integer(GLOBE1997$v9b),"1"=1L,"2"=0L))
```  
**Validation script**:  
```{r, echo=TRUE}
attributes(GLOBE1997$v9b)

A<-addmargins(table(lsb_GLOBE_1$lsb_alc_ever_1,GLOBE1997$v9b,useNA = "always"))
colnames(A)<-c(names(attributes(GLOBE1997$v9b)[[10]][3:4]),'NA','SUM')
as.data.frame.array(A,row.names = c('Does not currently consume alcohol','Currently consumes alcohol',"NA","SUM"))
```  
### **Variable label**:   Ever consumption of alcohol  
**Variable name**: lsb_alc_ever_2    
**Variable description**:  Indicator of whether the participant has ever consumed alcohol.  
**Value type**: integer  
**Variable unit**: N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 |   Never consumed alcohol  
1 |   Ever consumed alcohol  

**Harmonization status**:  impossible  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}

```  
### **Variable label**:   Ever consumption of alcohol  
**Variable name**: lsb_alc_ever_3    
**Variable description**:  Indicator of whether the participant has ever consumed alcohol.  
**Value type**: integer  
**Variable unit**: N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 |   Never consumed alcohol  
1 |   Ever consumed alcohol  

**Harmonization status**:  impossible   
**Harmonization comment**:   Study specific variable doesn't permits to know whether the participant never consumed alcohol or not.  
**R script**:  
```{r, echo=TRUE}

```  
### **Variable label**:   Ever consumption of alcohol  
**Variable name**: lsb_alc_ever_4    
**Variable description**:  Indicator of whether the participant has ever consumed alcohol.  
**Value type**: integer  
**Variable unit**: N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 |   Never consumed alcohol  
1 |   Ever consumed alcohol  

**Harmonization status**:  impossible   
**Harmonization comment**:   Study specific variable doesn't permits to know whether the participant never consumed alcohol or not .  
**R script**:  
```{r, echo=TRUE}

```  
### **Variable label**:   Ever consumption of alcohol  
**Variable name**: lsb_alc_ever_5    
**Variable description**:  Indicator of whether the participant has ever consumed alcohol.  
**Value type**: integer  
**Variable unit**: N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 |   Never consumed alcohol  
1 |   Ever consumed alcohol  

**Harmonization status**:  impossible  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}

```  
### **Variable label**:   Ever consumption of alcohol  
**Variable name**: lsb_alc_ever_6    
**Variable description**:  Indicator of whether the participant has ever consumed alcohol.  
**Value type**: integer  
**Variable unit**: N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 |   Never consumed alcohol  
1 |   Ever consumed alcohol  

**Harmonization status**:  impossible  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}

```  

### **Variable label**:   Frequency of binge drinking  
**Variable name**: lsb_alc_binge_0  
**Variable description**:  Frequency of drinking 4 or more drinks in one day.  
**Value type**: integer  
**Variable unit**: N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
1 |  0 to 3 times a month  
2 |  1 to 3 times a week   
3 |  3 times a week or more  

**Harmonization status**:  complete  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
lsb_GLOBE_0$lsb_alc_binge_0<-ifelse(lsb_GLOBE_0$lsb_alc_cur_0==0,1L,recode(as.integer(GLOBE1991$v137),"1"=3L,"2"=3L,"3"=3L,"4"=2L,"5"=1L,"6"=1L,"7"=1L))
```  
**Validation script**:  
```{r, echo=TRUE}
attributes(GLOBE1991$v137)

A<-addmargins(table(lsb_GLOBE_0$lsb_alc_binge_0,GLOBE1991$v137,useNA = "always"))
colnames(A)<-c(names(attributes(GLOBE1991$v137)[[10]][2:8]),'NA','SUM')
as.data.frame.array(A,row.names = c('Does not currently consume alcohol','Currently consumes alcohol',"NA","SUM"))
``` 
### **Variable label**:   Frequency of binge drinking  
**Variable name**: lsb_alc_binge_1  
**Variable description**:  Frequency of drinking 4 or more drinks in one day.  
**Value type**: integer  
**Variable unit**: N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
1 |  0 to 3 times a month  
2 |  1 to 3 times a week   
3 |  3 times a week or more  

**Harmonization status**:  complete  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
lsb_GLOBE_1$lsb_alc_binge_1<-ifelse(lsb_GLOBE_1$lsb_alc_cur_1==0,1L,recode(as.integer(GLOBE1997$v8b),"1"=3,"2"=3,"3"=3,"4"=2,"5"=1,"6"=1,"7"=1))

```  
### **Variable label**:   Frequency of binge drinking  
**Variable name**: lsb_alc_binge_2  
**Variable description**:  Frequency of drinking 4 or more drinks in one day.  
**Value type**: integer  
**Variable unit**: N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
1 |  0 to 3 times a month  
2 |  1 to 3 times a week   
3 |  3 times a week or more  

**Harmonization status**:  impossible  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}


```  
### **Variable label**:   Frequency of binge drinking  
**Variable name**: lsb_alc_binge_3  
**Variable description**:  Frequency of drinking 4 or more drinks in one day.  
**Value type**: integer  
**Variable unit**: N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
1 |  0 to 3 times a month  
2 |  1 to 3 times a week   
3 |  3 times a week or more  

**Harmonization status**:  complete  
**Harmonization comment**:   Category "2 to 4 times a momth" was recoded to "0 to 3 times a month".  
**R script**:  
```{r, echo=TRUE}
lsb_GLOBE_3$lsb_alc_binge_3<-ifelse(lsb_GLOBE_3$lsb_alc_cur_3==0,1L,recode(as.integer(GLOBE2011$v14_alc_binge),"1"=3,"2"=3,"3"=2,"4"=1,"5"=1,"6"=1,"7"=1))

```  
### **Variable label**:   Frequency of binge drinking  
**Variable name**: lsb_alc_binge_4  
**Variable description**:  Frequency of drinking 4 or more drinks in one day.  
**Value type**: integer  
**Variable unit**: N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
1 |  0 to 3 times a month  
2 |  1 to 3 times a week   
3 |  3 times a week or more  

**Harmonization status**:  impossible  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}

```  
### **Variable label**:   Frequency of binge drinking  
**Variable name**: lsb_alc_binge_5  
**Variable description**:  Frequency of drinking 4 or more drinks in one day.  
**Value type**: integer  
**Variable unit**: N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
1 |  0 to 3 times a month  
2 |  1 to 3 times a week   
3 |  3 times a week or more  

**Harmonization status**:  impossible  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}

```  
### **Variable label**:   Frequency of binge drinking  
**Variable name**: lsb_alc_binge_6  
**Variable description**:  Frequency of drinking 4 or more drinks in one day.  
**Value type**: integer  
**Variable unit**: N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
1 |  0 to 3 times a month  
2 |  1 to 3 times a week   
3 |  3 times a week or more  

**Harmonization status**:  impossible  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}

```  

### **Variable label**:   Current quantity of alcohol consumed per week (total)      
**Variable name**: lsb_alc_total_0  
**Variable description**:  Current quantity of wine, beer and liquor consumed per week.    
**Value type**: decimal    
**Variable unit**: drinks/week  
**Category coding**:  N/A  

**Harmonization status**:  impossible  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}

```  
### **Variable label**:   Current quantity of alcohol consumed per week (total)  
**Variable name**: lsb_alc_total_1  
**Variable description**:  Current quantity of wine, beer and liquor consumed per week.    
**Value type**: decimal    
**Variable unit**: drinks/week  
**Category coding**:  N/A  

**Harmonization status**:  impossible  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}

```  
### **Variable label**:   Current quantity of alcohol consumed per week (total)  
**Variable name**: lsb_alc_total_2  
**Variable description**:  Current quantity of wine, beer and liquor consumed per week.    
**Value type**: decimal    
**Variable unit**: drinks/week  
**Category coding**:  N/A  

**Harmonization status**:  impossible  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}

```  
### **Variable label**:   Current quantity of alcohol consumed per week (total)  
**Variable name**: lsb_alc_total_3  
**Variable description**:  Current quantity of wine, beer and liquor consumed per week.    
**Value type**: decimal    
**Variable unit**: drinks/week  
**Category coding**:  N/A  

**Harmonization status**:  impossible  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}

```  

### **Variable label**:   Current quantity of wine consumed per week  
**Variable name**: lsb_alc_wine_0  
**Variable description**:  Current quantity of wine consumed per week.    
**Value type**: decimal    
**Variable unit**: drinks/week  
**Category coding**:  N/A  

**Harmonization status**:  impossible  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}

```  
### **Variable label**:   Current quantity of wine consumed per week  
**Variable name**: lsb_alc_wine_1  
**Variable description**:  Current quantity of wine consumed per week.    
**Value type**: decimal    
**Variable unit**: drinks/week  
**Category coding**:  N/A  

**Harmonization status**:  impossible  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}

```  
### **Variable label**:   Current quantity of wine consumed per week  
**Variable name**: lsb_alc_wine_2  
**Variable description**:  Current quantity of wine consumed per week.    
**Value type**: decimal    
**Variable unit**: drinks/week  
**Category coding**:  N/A  

**Harmonization status**:  impossible  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}

```  
### **Variable label**:   Current quantity of wine consumed per week  
**Variable name**: lsb_alc_wine_3  
**Variable description**:  Current quantity of wine consumed per week.    
**Value type**: decimal    
**Variable unit**: drinks/week  
**Category coding**:  N/A  

**Harmonization status**:  impossible 
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}

```  

### **Variable label**:   Current quantity of beer consumed per week  
**Variable name**: lsb_alc_beer_0  
**Variable description**:  Current quantity of beer consumed per week.   
**Value type**: decimal    
**Variable unit**: drinks/week  
**Category coding**:  N/A  
 

**Harmonization status**:  impossible  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}

```  
### **Variable label**:   Current quantity of beer consumed per week  
**Variable name**: lsb_alc_beer_1  
**Variable description**:  Current quantity of beer consumed per week.    
**Value type**: decimal    
**Variable unit**: drinks/week  
**Category coding**:  N/A  
 

**Harmonization status**:  impossible  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}

```  
### **Variable label**:   Current quantity of beer consumed per week  
**Variable name**: lsb_alc_beer_2  
**Variable description**:  Current quantity of beer consumed per week.    
**Value type**: decimal    
**Variable unit**: drinks/week  
**Category coding**:  N/A  
 

**Harmonization status**:  impossible  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}

```  
### **Variable label**:   Current quantity of beer consumed per week  
**Variable name**: lsb_alc_beer_3  
**Variable description**:  Current quantity of beer consumed per week.    
**Value type**: decimal    
**Variable unit**: drinks/week  
**Category coding**:  N/A  
 

**Harmonization status**:  impossible  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}

```  

### **Variable label**:   Current quantity of liquor consumed per week  
**Variable name**: lsb_alc_liq_0  
**Variable description**:  Current quantity of liquor consumed per week.    
**Value type**: decimal    
**Variable unit**: drinks/week  
**Category coding**:  N/A  
 

**Harmonization status**:  impossible  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}

```  
### **Variable label**:   Current quantity of liquor consumed per week  
**Variable name**: lsb_alc_liq_1  
**Variable description**:  Current quantity of liquor consumed per week.   
**Value type**: decimal    
**Variable unit**: drinks/week  
**Category coding**:  N/A  
 

**Harmonization status**:  impossible  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}

```  
### **Variable label**:   Current quantity of liquor consumed per week  
**Variable name**: lsb_alc_liq_2  
**Variable description**:  Current quantity of liquor consumed per week.    
**Value type**: decimal    
**Variable unit**: drinks/week  
**Category coding**:  N/A  
 

**Harmonization status**:  impossible  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}

```  
### **Variable label**:   Current quantity of liquor consumed per week  
**Variable name**: lsb_alc_liq_3  
**Variable description**:  Current quantity of liquor consumed per week.   
**Value type**: decimal    
**Variable unit**: drinks/week  
**Category coding**:  N/A  
 

**Harmonization status**:  impossible  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}

```  

# Tobacco consumption subdomain

### **Variable label**:  Current tobacco smoking  
**Variable name**:  lsb_smk_cur_0  
**Variable description**:  Indicator of whether the participant currently smokes any tobacco product.  
**Value type**:  integer  
**Variable unit**:  N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 |   Currently does not smoke any tobacco product  
1 |   Currently smokes any tobacco product  

**Harmonization status**:  complete  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
lsb_GLOBE_0$lsb_smk_cur_0<-recode(as.integer(GLOBE1991$v140),"1"=1L,"2"=0L,"3"=0L)
```  
**Validation script**:  
```{r, echo=TRUE}
attributes(GLOBE1991$v140)

A<-addmargins(table(lsb_GLOBE_0$lsb_smk_cur_0,GLOBE1991$v140,useNA = "always"))
colnames(A)<-c(names(attributes(GLOBE1991$v140)[[10]][1:3]),'NA','SUM')
as.data.frame.array(A,row.names = c('Currently does not smoke any tobacco product','Currently smokes any tobacco product',"NA","SUM"))
``` 
### **Variable label**:  Current tobacco smoking  
**Variable name**:  lsb_smk_cur_1  
**Variable description**:  Indicator of whether the participant currently smokes any tobacco product.  
**Value type**:  integer  
**Variable unit**:  N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 |   Currently does not smoke any tobacco product  
1 |   Currently smokes any tobacco product  

**Harmonization status**:  complete  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
lsb_GLOBE_1$lsb_smk_cur_1<-recode(as.integer(GLOBE1997$v10a),"1"=1L,"2"=0L,"3"=0L)
```  
**Validation script**:  
```{r, echo=TRUE}
attributes(GLOBE1997$v10a)

A<-addmargins(table(lsb_GLOBE_1$lsb_smk_cur_1,GLOBE1997$v10a,useNA = "always"))
colnames(A)<-c(names(attributes(GLOBE1997$v10a)[[10]][3:5]),'NA','SUM')
as.data.frame.array(A,row.names = c('Currently does not smoke any tobacco product','Currently smokes any tobacco product',"NA","SUM"))
```
### **Variable label**:  Current tobacco smoking  
**Variable name**:  lsb_smk_cur_2  
**Variable description**:  Indicator of whether the participant currently smokes any tobacco product.  
**Value type**:  integer  
**Variable unit**:  N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 |   Currently does not smoke any tobacco product  
1 |   Currently smokes any tobacco product  

**Harmonization status**:  complete  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
lsb_GLOBE_2$lsb_smk_cur_2<-recode(as.integer(GLOBE2004$w073),"1"=1L,"2"=1L,"3"=1L,"4"=0L,"5"=0L)
```  
**Validation script**:  
```{r, echo=TRUE}
attributes(GLOBE2004$w073)

A<-addmargins(table(lsb_GLOBE_2$lsb_smk_cur_2,GLOBE2004$w073,useNA = "always"))
colnames(A)<-c(names(attributes(GLOBE2004$w073)[[10]][1:5]),'NA','SUM')
as.data.frame.array(A,row.names = c('Currently does not smoke any tobacco product','Currently smokes any tobacco product',"NA","SUM"))
```
### **Variable label**:  Current tobacco smoking  
**Variable name**:  lsb_smk_cur_3  
**Variable description**:  Indicator of whether the participant currently smokes any tobacco product.  
**Value type**:  integer  
**Variable unit**:  N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 |   Currently does not smoke any tobacco product  
1 |   Currently smokes any tobacco product  

**Harmonization status**:  complete  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
lsb_GLOBE_3$lsb_smk_cur_3<-recode(as.integer(GLOBE2011$v17_rook_freq),"1"=1L,"2"=1L,"3"=1L,"4"=0L,"5"=0L)
```
**Validation script**:  
```{r, echo=TRUE}
attributes(GLOBE2011$v17_rook_freq)

A<-addmargins(table(lsb_GLOBE_3$lsb_smk_cur_3,GLOBE2011$v17_rook_freq,useNA = "always"))
colnames(A)<-c(names(attributes(GLOBE2011$v17_rook_freq)[[10]][1:5]),'NA','SUM')
as.data.frame.array(A,row.names = c('Currently does not smoke any tobacco product','Currently smokes any tobacco product',"NA","SUM"))
```
### **Variable label**:  Current tobacco smoking  
**Variable name**:  lsb_smk_cur_4  
**Variable description**:  Indicator of whether the participant currently smokes any tobacco product.  
**Value type**:  integer  
**Variable unit**:  N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 |   Currently does not smoke any tobacco product  
1 |   Currently smokes any tobacco product  

**Harmonization status**:  complete  
**Harmonization comment**:   Participants that reported smoking e-cigarettes were recoded to NA.
**R script**:  
```{r, echo=TRUE}
lsb_GLOBE_4$lsb_smk_cur_4<-recode(as.integer(GLOBE2014$G14v25),"1"=1L,"2"=1L,"4"=1L,"5"=0L,"6"=0L,"7"=0L,.default=NA_integer_)
``` 
**Validation script**:  
```{r, echo=TRUE}
attributes(GLOBE2014$G14v25)
summ(as.factor(lsb_GLOBE_4$lsb_smk_cur_4))
A<-addmargins(table(lsb_GLOBE_4$lsb_smk_cur_4,GLOBE2014$G14v25,useNA = "always"))
colnames(A)<-c(names(attributes(GLOBE2014$G14v25)[[10]][1:7]),'NA','SUM')
as.data.frame.array(A,row.names = c('Currently does not smoke any tobacco product','Currently smokes any tobacco product',"NA","SUM"))
```
### **Variable label**:  Current tobacco smoking  
**Variable name**:  lsb_smk_cur_5  
**Variable description**:  Indicator of whether the participant currently smokes any tobacco product.  
**Value type**:  integer  
**Variable unit**:  N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 |   Currently does not smoke any tobacco product  
1 |   Currently smokes any tobacco product  

**Harmonization status**:  impossible  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}

```  
### **Variable label**:  Current tobacco smoking  
**Variable name**:  lsb_smk_cur_6  
**Variable description**:  Indicator of whether the participant currently smokes any tobacco product.  
**Value type**:  integer  
**Variable unit**:  N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 |   Currently does not smoke any tobacco product  
1 |   Currently smokes any tobacco product  

**Harmonization status**:  impossible  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}

```  

### **Variable label**:  Smoking status  
**Variable name**:  lsb_smk_status_0  
**Variable description**:  Smoking status of the participant.  
**Value type**:  integer  
**Variable unit**:  N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 |   Never smoker  
1 |   Former smoker  
2 |   Current smoker  

**Harmonization status**:  complete  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
lsb_GLOBE_0$lsb_smk_status_0<-recode(as.integer(GLOBE1991$v140),"1"=2L,"2"=1L,"3"=0L)
```  
**Validation script**:  
```{r, echo=TRUE}
attributes(GLOBE1991$v140)
summ(as.factor(lsb_GLOBE_0$lsb_smk_status_0))
A<-addmargins(table(lsb_GLOBE_0$lsb_smk_status_0,GLOBE1991$v140,useNA = "always"))
colnames(A)<-c(names(attributes(GLOBE1991$v140)[[10]][1:3]),'NA','SUM')
as.data.frame.array(A,row.names = c('Never smoker','Former smoker','Current smoker',"NA","SUM"))
```
### **Variable label**:  Smoking status  
**Variable name**:  lsb_smk_status_1  
**Variable description**:  Smoking status of the participant.  
**Value type**:  integer  
**Variable unit**:  N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 |   Never smoker  
1 |   Former smoker  
2 |   Current smoker  

**Harmonization status**:  complete  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
lsb_GLOBE_1$lsb_smk_status_1<-recode(as.integer(GLOBE1997$v10a),"1"=2L,"2"=1L,"3"=0L)
```  
**Validation script**:  
```{r, echo=TRUE}
attributes(GLOBE1997$v10a)

A<-addmargins(table(lsb_GLOBE_1$lsb_smk_status_1,GLOBE1997$v10a,useNA = "always"))
colnames(A)<-c(names(attributes(GLOBE1997$v10a)[[10]][3:5]),"NA","SUM")
as.data.frame.array(A,row.names = c("Never smoker","Former smoker","Current smoker","NA","SUM"))
``` 
### **Variable label**:  Smoking status  
**Variable name**:  lsb_smk_status_2  
**Variable description**:  Smoking status of the participant.  
**Value type**:  integer  
**Variable unit**:  N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 |   Never smoker  
1 |   Former smoker  
2 |   Current smoker  

**Harmonization status**:  complete  
**Harmonization comment**:  
**Validatioln comment**: Add Harmo comment "Study-specific variable considers daily smokers"
**R script**:  
```{r, echo=TRUE}
lsb_GLOBE_2$lsb_smk_status_2<-recode(as.integer(GLOBE2004$w073),"1"=2L,"2"=2L,"3"=2L,"4"=1L,"5"=0L)
``` 
**Validation script**: 
```{r, echo=TRUE}
attributes(GLOBE2004$w073)

A<-addmargins(table(lsb_GLOBE_2$lsb_smk_status_2,GLOBE2004$w073,useNA = "always"))
colnames(A)<-c(names(attributes(GLOBE2004$w073)[[10]][1:5]),"NA","SUM")
as.data.frame.array(A,row.names = c("Never smoker","Former smoker","Current smoker","NA","SUM"))
``` 
### **Variable label**:  Smoking status  
**Variable name**:  lsb_smk_status_3  
**Variable description**:  Smoking status of the participant.  
**Value type**:  integer  
**Variable unit**:  N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 |   Never smoker  
1 |   Former smoker  
2 |   Current smoker  

**Harmonization status**:  complete  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
lsb_GLOBE_3$lsb_smk_status_3<-recode(as.integer(GLOBE2011$v17_rook_freq),"1"=2L,"2"=2L,"3"=2L,"4"=1L,"5"=0L)
```  
**Validation script**: 
```{r, echo=TRUE}
attributes(GLOBE2011$v17_rook_freq)

A<-addmargins(table(lsb_GLOBE_3$lsb_smk_status_3,GLOBE2011$v17_rook_freq,useNA = "always"))
colnames(A)<-c(names(attributes(GLOBE2011$v17_rook_freq)[[10]][1:5]),"NA","SUM")
as.data.frame.array(A,row.names = c("Never smoker","Former smoker","Current smoker","NA","SUM"))
``` 
### **Variable label**:  Smoking status  
**Variable name**:  lsb_smk_status_4  
**Variable description**:  Smoking status of the participant.  
**Value type**:  integer  
**Variable unit**:  N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 |   Never smoker  
1 |   Former smoker  
2 |   Current smoker  

**Harmonization status**:  complete  
**Harmonization comment**:   Participants that reported smoking e-cigarettes were recoded to NA.
**Validation comment**: In harmo comment add "Never smokers are respondents who never smoked daily"
**R script**:  
```{r, echo=TRUE}
lsb_GLOBE_4$lsb_smk_status_4<-recode(as.integer(GLOBE2014$G14v25),"1"=2L,"2"=2L,"4"=2L,"5"=1L,"6"=1L,"7"=0L,.default=NA_integer_)
```  
**Validation script**: 
```{r, echo=TRUE}
attributes(GLOBE2014$G14v25)

A<-addmargins(table(lsb_GLOBE_4$lsb_smk_status_4,GLOBE2014$G14v25,useNA = "always"))
colnames(A)<-c(names(attributes(GLOBE2014$G14v25)[[10]][1:7]),"NA","SUM")
as.data.frame.array(A,row.names = c("Never smoker","Former smoker","Current smoker","NA","SUM"))
``` 
 
### **Variable label**:  Smoking status  
**Variable name**:  lsb_smk_status_5  
**Variable description**:  Smoking status of the participant.  
**Value type**:  integer  
**Variable unit**:  N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 |   Never smoker  
1 |   Former smoker  
2 |   Current smoker  

**Harmonization status**:  impossible  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}

```  
### **Variable label**:  Smoking status  
**Variable name**:  lsb_smk_status_6  
**Variable description**:  Smoking status of the participant.  
**Value type**:  integer  
**Variable unit**:  N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 |   Never smoker  
1 |   Former smoker  
2 |   Current smoker  

**Harmonization status**:  impossible  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}

```  

### **Variable label**:  Ever tobacco smoking  
**Variable name**:  lsb_smk_ever_0    
**Variable description**:  Indicator of whether the participant has ever smoked any tobacco product.  
**Value type**:  integer  
**Variable unit**:  N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 |   Never smoked tobacco  
1 |   Ever smoked tobacco  

**Harmonization status**:  complete  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
#Merging the raw tables 
MyMerge <- function(x,y){
  df <- merge(x,y, by="id",all=TRUE)
  return(df)
}
#Reducing the table to the variables needed
smk_table <- Reduce(MyMerge, list(GLOBE1991,GLOBE1997,GLOBE2004,GLOBE2011,GLOBE2014))
smk_table<- smk_table[,c("id","v140","v10a","w073","v17_rook_freq","G14v25")]
#Harmonization scripts to create "ever smoke" for all participants in all waves
smk_table$lsb_smk_ever_0 <- recode(as.integer(smk_table$v140),"1"=1L,"2"=0L,"3"=0L)
#Direct mapping to harmonized tables keeping correct participants for each wave
lsb_GLOBE_0 <- merge(lsb_GLOBE_0, smk_table[,c("id","lsb_smk_ever_0")],by="id",all.x=TRUE)
``` 
**Validation script**: 
```{r, echo=TRUE}
attributes(GLOBE1991$v140)

A<-addmargins(table(lsb_GLOBE_0$lsb_smk_ever_0,GLOBE1991$v140,useNA = "always"))
colnames(A)<-c(names(attributes(GLOBE1991$v140)[[10]][1:3]),"NA","SUM")
as.data.frame.array(A,row.names = c("Never smoked tobacco","Ever smoked tobacco","NA","SUM"))
``` 
### **Variable label**:  Ever tobacco smoking  
**Variable name**:  lsb_smk_ever_1    
**Variable description**:  Indicator of whether the participant has ever smoked any tobacco product.  
**Value type**:  integer  
**Variable unit**:  N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 |   Never smoked tobacco  
1 |   Ever smoked tobacco  

**Harmonization status**:  complete  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
#Harmonization scripts to create "ever smoke" for all participants in all waves
smk_table$lsb_smk_ever_1 <- ifelse(smk_table$lsb_smk_ever_0 ==1,1L,recode(as.integer(smk_table$v10a),"1"=1L,"2"=1L,"3"=0L))
#Direct mapping to harmonized tables keeping correct participants for each wave
lsb_GLOBE_1 <- merge(lsb_GLOBE_1, smk_table[,c("id","lsb_smk_ever_1")],by="id",all.x=TRUE)
```  
**Validation script**: 
```{r, echo=TRUE}
attributes(GLOBE1997$v10a)

A<-addmargins(table(lsb_GLOBE_1$lsb_smk_ever_1,GLOBE1997$v10a,useNA = "always"))
colnames(A)<-c(names(attributes(GLOBE1997$v10a)[[10]][3:5]),"NA","SUM")
as.data.frame.array(A,row.names = c("Never smoked tobacco","Ever smoked tobacco","NA","SUM"))
``` 
### **Variable label**:  Ever tobacco smoking  
**Variable name**:  lsb_smk_ever_2    
**Variable description**:  Indicator of whether the participant has ever smoked any tobacco product.  
**Value type**:  integer  
**Variable unit**:  N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 |   Never smoked tobacco  
1 |   Ever smoked tobacco  

**Harmonization status**:  complete  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
#Harmonization scripts to create "ever smoke" for all participants in all waves
smk_table$lsb_smk_ever_2 <- ifelse(smk_table$lsb_smk_ever_1 ==1 ,1L,recode(as.integer(smk_table$w073),"1"=1L,"2"=1L,"3"=1L,"4"=1L,"5"=0L))
#Direct mapping to harmonized tables keeping correct participants for each wave
lsb_GLOBE_2 <- merge(lsb_GLOBE_2, smk_table[,c("id","lsb_smk_ever_2")],by="id",all.x=TRUE)
```  
**Validation script**: 
```{r, echo=TRUE}
attributes(GLOBE2004$w073)

A<-addmargins(table(lsb_GLOBE_2$lsb_smk_ever_2,GLOBE2004$w073,useNA = "always"))
colnames(A)<-c(names(attributes(GLOBE2004$w073)[[10]][1:5]),"NA","SUM")
as.data.frame.array(A,row.names = c("Never smoked tobacco","Ever smoked tobacco","NA","SUM"))
``` 
### **Variable label**:  Ever tobacco smoking  
**Variable name**:  lsb_smk_ever_3    
**Variable description**:  Indicator of whether the participant has ever smoked any tobacco product.  
**Value type**:  integer  
**Variable unit**:  N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 |   Never smoked tobacco  
1 |   Ever smoked tobacco  

**Harmonization status**:  complete  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
#Harmonization scripts to create "ever smoke" for all participants in all waves
smk_table$lsb_smk_ever_3 <- ifelse(smk_table$lsb_smk_ever_2 ==1 ,1L,recode(as.integer(smk_table$v17_rook_freq),"1"=1L,"2"=1L,"3"=1L,"4"=1L,"5"=0L))
#Direct mapping to harmonized tables keeping correct participants for each wave
lsb_GLOBE_3 <- merge(lsb_GLOBE_3, smk_table[,c("id","lsb_smk_ever_3")],by="id",all.x=TRUE)
```  
**Validation script**: 
```{r, echo=TRUE}
attributes(GLOBE2011$v17_rook_freq)

A<-addmargins(table(lsb_GLOBE_3$lsb_smk_ever_3,GLOBE2011$v17_rook_freq,useNA = "always"))
colnames(A)<-c(names(attributes(GLOBE2011$v17_rook_freq)[[10]][1:5]),"NA","SUM")
as.data.frame.array(A,row.names = c("Never smoked tobacco","Ever smoked tobacco","NA","SUM"))
``` 
### **Variable label**:  Ever tobacco smoking  
**Variable name**:  lsb_smk_ever_4    
**Variable description**:  Indicator of whether the participant has ever smoked any tobacco product.  
**Value type**:  integer  
**Variable unit**:  N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 |   Never smoked tobacco  
1 |   Ever smoked tobacco  

**Harmonization status**:  complete  
**Harmonization comment**:   Participants that reported smoking e-cigarettes are recoded to NA.
**R script**:  
```{r, echo=TRUE}
#Harmonization scripts to create "ever smoke" for all participants in all waves
smk_table$lsb_smk_ever_4 <- ifelse(smk_table$lsb_smk_ever_3 ==1 ,1L,recode(as.integer(smk_table$G14v25),"1"=1L,"2"=1L,"4"=1L,"5"=1L,"6"=1L,"7"=0L,.default=NA_integer_))
#Direct mapping to harmonized tables keeping correct participants for each wave
lsb_GLOBE_4 <- merge(lsb_GLOBE_4, smk_table[,c("id","lsb_smk_ever_4")],by="id",all.x=TRUE)
```  
**Validation script**: 
```{r, echo=TRUE}
attributes(GLOBE2014$G14v25)

A<-addmargins(table(lsb_GLOBE_4$lsb_smk_ever_4,GLOBE2014$G14v25,useNA = "always"))
colnames(A)<-c(names(attributes(GLOBE2014$G14v25)[[10]][1:7]),"NA","SUM")
as.data.frame.array(A,row.names = c("Never smoked tobacco","Ever smoked tobacco","NA","SUM"))
``` 
### **Variable label**:  Ever tobacco smoking  
**Variable name**:  lsb_smk_ever_5    
**Variable description**:  Indicator of whether the participant has ever smoked any tobacco product.  
**Value type**:  integer  
**Variable unit**:  N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 |   Never smoked tobacco  
1 |   Ever smoked tobacco  

**Harmonization status**:  impossible  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
#This is where the R-script will be written

``` 
**Validation script**:  
```{r, echo=TRUE}

```  
### **Variable label**:  Ever tobacco smoking  
**Variable name**:  lsb_smk_ever_6    
**Variable description**:  Indicator of whether the participant has ever smoked any tobacco product.  
**Value type**:  integer  
**Variable unit**:  N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 |   Never smoked tobacco  
1 |   Ever smoked tobacco  

**Harmonization status**:  impossible  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}

```  

### **Variable label**:  Quantity cigarettes smoked    
**Variable name**:  lsb_cig_qty_0   
**Variable description**:  Current average number of cigarettes smoked per day.  
**Value type**:  integer  
**Variable unit**:  cigarettes/day  
**Category coding**:  

**Harmonization status**:  complete  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
lsb_GLOBE_0$lsb_cig_qty_0<-ifelse(lsb_GLOBE_0$lsb_smk_cur_0==0,0,
                                  ifelse(lsb_GLOBE_0$lsb_smk_cur_0==1,GLOBE1991$v141,NA))
```  
**Validation script**: 
```{r, echo=TRUE}
summary(lsb_GLOBE_0$lsb_cig_qty_0)
summary(GLOBE1991$v141)

table(lsb_GLOBE_0$lsb_smk_cur_0,!is.na(GLOBE1991$v141),useNA='always')
```
**Correction script**: 
```{r, echo=TRUE}
lsb_GLOBE_0$lsb_cig_qty_0<-ifelse(lsb_GLOBE_0$lsb_smk_cur_0==0,0,GLOBE1991$v141)
```
### **Variable label**:  Quantity cigarettes smoked    
**Variable name**:  lsb_cig_qty_1   
**Variable description**:  Current average number of cigarettes smoked per day.  
**Value type**:  integer  
**Variable unit**:  cigarettes/day  
**Category coding**:  

**Harmonization status**:  complete  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
lsb_GLOBE_1$lsb_cig_qty_1<-ifelse(lsb_GLOBE_1$lsb_smk_cur_1==0,0,
                                  ifelse(lsb_GLOBE_1$lsb_smk_cur_1==1,GLOBE1997$v10b1,NA))
```  
**Validation script**:  
```{r, echo=TRUE}
summary(lsb_GLOBE_1$lsb_cig_qty_1)
summary(GLOBE1997$v10b1)

table(lsb_GLOBE_1$lsb_smk_cur_1,!is.na(GLOBE1997$v10b1),useNA='always')
```  
### **Variable label**:  Quantity cigarettes smoked    
**Variable name**:  lsb_cig_qty_2   
**Variable description**:  Current average number of cigarettes smoked per day.  
**Value type**:  integer  
**Variable unit**:  cigarettes/day  
**Category coding**:  

**Harmonization status**:  complete  
**Harmonization comment**:   How many cigarettes/shags do you approximately smoke a day?
**R script**:  
```{r, echo=TRUE}
lsb_GLOBE_2$lsb_cig_qty_2<-ifelse(lsb_GLOBE_2$lsb_smk_cur_2==0,0,
                                  ifelse(lsb_GLOBE_2$lsb_smk_cur_2==1,GLOBE2004$w074,NA))

```  
### **Variable label**:  Quantity cigarettes smoked    
**Variable name**:  lsb_cig_qty_3   
**Variable description**:  Current average number of cigarettes smoked per day.  
**Value type**:  integer  
**Variable unit**:  cigarettes/day  
**Category coding**:  

**Harmonization status**:  complete  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
lsb_GLOBE_3$lsb_cig_qty_3<-ifelse(lsb_GLOBE_3$lsb_smk_cur_3==0,0,
                                  ifelse(lsb_GLOBE_3$lsb_smk_cur_3==1,GLOBE2011$v17_sig_pd,NA))

```  
### **Variable label**:  Quantity cigarettes smoked    
**Variable name**:  lsb_cig_qty_4   
**Variable description**:  Current average number of cigarettes smoked per day.  
**Value type**:  integer  
**Variable unit**:  cigarettes/day  
**Category coding**:  

**Harmonization status**:  complete  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
lsb_GLOBE_4$lsb_cig_qty_4<-ifelse(lsb_GLOBE_4$lsb_smk_cur_4==0,0,
                                  ifelse(lsb_GLOBE_4$lsb_smk_cur_4==1,GLOBE2011$v17_sig_pd,NA))

```  
### **Variable label**:  Quantity cigarettes smoked    
**Variable name**:  lsb_cig_qty_5   
**Variable description**:  Current average number of cigarettes smoked per day.  
**Value type**:  integer  
**Variable unit**:  cigarettes/day  
**Category coding**:  

**Harmonization status**:  impossible  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}

```  
### **Variable label**:  Quantity cigarettes smoked    
**Variable name**:  lsb_cig_qty_6   
**Variable description**:  Current average number of cigarettes smoked per day.  
**Value type**:  integer  
**Variable unit**:  cigarettes/day  
**Category coding**:  

**Harmonization status**:  impossible  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}

```  

### **Variable label**:  Smoking initiation age    
**Variable name**:  lsb_smk_start_0    
**Variable description**:  Age at which the participant started smoking any tobacco product.  
**Value type**:  integer  
**Variable unit**:  years  
**Category coding**:  

**Harmonization status**:  complete  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
lsb_GLOBE_0$lsb_smk_start_0<-as.integer(GLOBE1991$v151)
```  
**Validation script**:  
```{r, echo=TRUE}
summary(lsb_GLOBE_0$lsb_smk_start_0)
summary(GLOBE1991$v151)
```  
### **Variable label**:  Smoking initiation age    
**Variable name**:  lsb_smk_start_1    
**Variable description**:  Age at which the participant started smoking any tobacco product.  
**Value type**:  integer  
**Variable unit**:  years  
**Category coding**:  

**Harmonization status**:  impossible  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}

```  
### **Variable label**:  Smoking initiation age    
**Variable name**:  lsb_smk_start_2    
**Variable description**:  Age at which the participant started smoking any tobacco product.  
**Value type**:  integer  
**Variable unit**:  years  
**Category coding**:  

**Harmonization status**:  complete  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
lsb_GLOBE_2$lsb_smk_start_2<-as.integer(GLOBE2004$w077)

```  
### **Variable label**:  Smoking initiation age    
**Variable name**:  lsb_smk_start_3    
**Variable description**:  Age at which the participant started smoking any tobacco product.  
**Value type**:  integer  
**Variable unit**:  years  
**Category coding**:  

**Harmonization status**:  impossible  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}


```  
### **Variable label**:  Smoking initiation age    
**Variable name**:  lsb_smk_start_4    
**Variable description**:  Age at which the participant started smoking any tobacco product.  
**Value type**:  integer  
**Variable unit**:  years  
**Category coding**:  

**Harmonization status**:  impossible  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}


```  
### **Variable label**:  Smoking initiation age    
**Variable name**:  lsb_smk_start_5    
**Variable description**:  Age at which the participant started smoking any tobacco product.  
**Value type**:  integer  
**Variable unit**:  years  
**Category coding**:  

**Harmonization status**:  impossible  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
#This is where the R-script will be written

```  
**Correction script**:  
```{r, echo=TRUE}

```  
### **Variable label**:  Smoking initiation age    
**Variable name**:  lsb_smk_start_6    
**Variable description**:  Age at which the participant started smoking any tobacco product.  
**Value type**:  integer  
**Variable unit**:  years  
**Category coding**:  

**Harmonization status**:  impossible  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}

```  

### **Variable label**:  Smoking cessation age  
**Variable name**:  lsb_smk_stop_0   
**Variable description**:  Age at which the participant last smoked any tobacco product.  
**Value type**:  integer  
**Variable unit**:  years  
**Category coding**:  

**Harmonization status**:  impossible  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}

```  
### **Variable label**:  Smoking cessation age  
**Variable name**:  lsb_smk_stop_1   
**Variable description**:  Age at which the participant last smoked any tobacco product.  
**Value type**:  integer  
**Variable unit**:  years  
**Category coding**:  

**Harmonization status**:  complete  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
lsb_GLOBE_1$lsb_smk_stop_1<-as.integer(GLOBE1997$v10e)
```  
**Validation script**:  
```{r, echo=TRUE}
summary(lsb_GLOBE_1$lsb_smk_stop_1)
summary(GLOBE1997$v10e)
```  
### **Variable label**:  Smoking cessation age  
**Variable name**:  lsb_smk_stop_2   
**Variable description**:  Age at which the participant last smoked any tobacco product.  
**Value type**:  integer  
**Variable unit**:  years  
**Category coding**:  

**Harmonization status**:  impossible  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}

```  
### **Variable label**:  Smoking cessation age  
**Variable name**:  lsb_smk_stop_3   
**Variable description**:  Age at which the participant last smoked any tobacco product.  
**Value type**:  integer  
**Variable unit**:  years  
**Category coding**:  

**Harmonization status**:  impossible  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}

```  
### **Variable label**:  Smoking cessation age  
**Variable name**:  lsb_smk_stop_4   
**Variable description**:  Age at which the participant last smoked any tobacco product.  
**Value type**:  integer  
**Variable unit**:  years  
**Category coding**:  

**Harmonization status**:  impossible  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}

```  
### **Variable label**:  Smoking cessation age  
**Variable name**:  lsb_smk_stop_5   
**Variable description**:  Age at which the participant last smoked any tobacco product.  
**Value type**:  integer  
**Variable unit**:  years  
**Category coding**:  

**Harmonization status**:  impossible  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}

```  
### **Variable label**:  Smoking cessation age  
**Variable name**:  lsb_smk_stop_6   
**Variable description**:  Age at which the participant last smoked any tobacco product.  
**Value type**:  integer  
**Variable unit**:  years  
**Category coding**:  

**Harmonization status**:  impossible  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}

```  

### **Variable label**:  Pack years  
**Variable name**:  lsb_smk_py_0    
**Variable description**:  Number of estimated pack years of the participant.   
**Value type**:  decimal    
**Variable unit**:  pack-years    
**Category coding**:  

**Harmonization status**:  complete    
**Harmonization comment**:   20 cigarettes per pack was considered.
**R script**:  
```{r, echo=TRUE}
lsb_GLOBE_0$lsb_smk_py_0<-ifelse(lsb_GLOBE_0$lsb_smk_ever_0==0,0,(lsb_GLOBE_0$lsb_cig_qty_0/20)*GLOBE1991$v153)
```  
**Validation script**:  
```{r, echo=TRUE}
summary(lsb_GLOBE_0$lsb_smk_py_0)
class(lsb_GLOBE_0$lsb_smk_py_0)
``` 
### **Variable label**:  Pack years  
**Variable name**:  lsb_smk_py_1    
**Variable description**:  Number of estimated pack years of the participant.     
**Value type**:  decimal    
**Variable unit**:  pack-years    
**Category coding**:  

**Harmonization status**:  complete    
**Harmonization comment**:   20 cigarettes per pack was considered
**R script**:  
```{r, echo=TRUE}
lsb_GLOBE_1$lsb_smk_py_1<-ifelse(lsb_GLOBE_1$lsb_smk_ever_1==0,0,(lsb_GLOBE_1$lsb_cig_qty_1/20)*GLOBE1997$v10c)
```  
**Validation script**:  
```{r, echo=TRUE}
summary(lsb_GLOBE_1$lsb_smk_py_1)
summary(GLOBE1997$v10c)
``` 
### **Variable label**:  Pack years  
**Variable name**:  lsb_smk_py_2    
**Variable description**:  Number of estimated pack years of the participant.     
**Value type**:  decimal    
**Variable unit**:  pack-years    
**Category coding**:  

**Harmonization status**:  complete    
**Harmonization comment**:   20 cigarettes per pack was considered.
**R script**:  
```{r, echo=TRUE}
lsb_GLOBE_2$lsb_smk_py_2<-ifelse(lsb_GLOBE_2$lsb_smk_ever_2==0,0,(lsb_GLOBE_2$lsb_cig_qty_2/20)*GLOBE2004$w078)
```  

# Physical activity subdomain

### **Variable label**: Frequency of walking    
**Variable name**:    lsb_pa_walk_freq_0    
**Variable description**:  Number of times the participant went for a walk in last week.    
**Value type**:  integer  
**Variable unit**:  N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 |  Never  
1 |  Seldom (1-2 days)  
2 |  Sometimes (3-4 days)  
3 |  Often (5-7 days)  

**Harmonization status**:  impossible  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}

```  
### **Variable label**: Frequency of walking    
**Variable name**:    lsb_pa_walk_freq_1    
**Variable description**:  Number of times the participant went for a walk in last week.    
**Value type**:  integer  
**Variable unit**:  N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 |  Never  
1 |  Seldom (1-2 days)  
2 |  Sometimes (3-4 days)  
3 |  Often (5-7 days)  

**Harmonization status**:  impossible  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}

```  
### **Variable label**: Frequency of walking    
**Variable name**:    lsb_pa_walk_freq_2    
**Variable description**:  Number of times the participant went for a walk in last week.    
**Value type**:  integer  
**Variable unit**:  N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 |  Never  
1 |  Seldom (1-2 days)  
2 |  Sometimes (3-4 days)  
3 |  Often (5-7 days)    

**Harmonization status**:  impossible    
**Harmonization comment**:   There are 2 study-specific variables that can be used ("How many days in an average week in the past months did you walk to and from work or school?" and "How many days in an average week in the past months did you walk (in leisure time)?), but it's impossible to determine whether the participant walked the same days or not for leisure or transportation.  
**R script**:  
```{r, echo=TRUE}

```  
### **Variable label**: Frequency of walking    
**Variable name**:    lsb_pa_walk_freq_3    
**Variable description**:  Number of times the participant went for a walk in last week.    
**Value type**:  integer  
**Variable unit**:  N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 |  Never  
1 |  Seldom (1-2 days)  
2 |  Sometimes (3-4 days)  
3 |  Often (5-7 days)    

**Harmonization status**:  impossible  
**Harmonization comment**:   There are 2 study-specific variables that can be used ("How many days in an average week in the past months did you walk to and from work or school?" and "How many days in an average week in the past months did you walk (in leisure time)?), but it's impossible to determine whether the participant walked the same days or not for leisure or transportation.  
**R script**:  
```{r, echo=TRUE}

```  
### **Variable label**: Frequency of walking    
**Variable name**:    lsb_pa_walk_freq_4    
**Variable description**:  Number of times the participant went for a walk in last week.    
**Value type**:  integer  
**Variable unit**:  N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 |  Never  
1 |  Seldom (1-2 days)  
2 |  Sometimes (3-4 days)  
3 |  Often (5-7 days)    

**Harmonization status**:  impossible  
**Harmonization comment**:   There are 2 study-specific variables that can be used ("How many days in an average week in the past months did you walk to and from work or school?" and "How many days in an average week in the past months did you walk (in leisure time)?), but it's impossible to determine whether the participant walked the same days or not for leisure or transportation.  
**R script**:  
```{r, echo=TRUE}

```  
### **Variable label**: Frequency of walking    
**Variable name**:    lsb_pa_walk_freq_5    
**Variable description**:  Number of times the participant went for a walk in last week.    
**Value type**:  integer  
**Variable unit**:  N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 |  Never  
1 |  Seldom (1-2 days)  
2 |  Sometimes (3-4 days)  
3 |  Often (5-7 days)    

**Harmonization status**:  impossible  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}

```  
### **Variable label**: Frequency of walking    
**Variable name**:    lsb_pa_walk_freq_6    
**Variable description**:  Number of times the participant went for a walk in last week.    
**Value type**:  integer  
**Variable unit**:  N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 |  Never  
1 |  Seldom (1-2 days)  
2 |  Sometimes (3-4 days)  
3 |  Often (5-7 days)    

**Harmonization status**:  impossible  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}

```  

### **Variable label**:  Average walking time     
**Variable name**:   lsb_pa_walk_time_0  
**Variable description**:  Average time the participant spends walking per day.    
**Value type**:  integer  
**Variable unit**:  N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 |  Less than 30 minutes  
1 |  30 minutes but less than 1 hour  
2 |  1 hour but less than 2 hours
3 |  2 hours but less than 4 hours  
4 |  4 hours or more  

**Harmonization status**:  impossible  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}

```  
### **Variable label**:  Average walking time   
**Variable name**:   lsb_pa_walk_time_1  
**Variable description**:  Average time the participant spends walking per day.    
**Value type**:  integer  
**Variable unit**:  N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 |  Less than 30 minutes  
1 |  30 minutes but less than 1 hour  
2 |  1 hour but less than 2 hours
3 |  2 hours but less than 4 hours  
4 |  4 hours or more   

**Harmonization status**:  impossible  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}

```  
### **Variable label**:  Average walking time    
**Variable name**:   lsb_pa_walk_time_2  
**Variable description**:  Average time the participant spends walking per day.    
**Value type**:  integer  
**Variable unit**:  N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 |  Less than 30 minutes  
1 |  30 minutes but less than 1 hour  
2 |  1 hour but less than 2 hours
3 |  2 hours but less than 4 hours  
4 |  4 hours or more   

**Harmonization status**:  impossible  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}

```  
### **Variable label**:  Average walking time     
**Variable name**:   lsb_pa_walk_time_3  
**Variable description**:  Average time the participant spends walking per day.    
**Value type**:  integer  
**Variable unit**:  N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 |  Less than 30 minutes  
1 |  30 minutes but less than 1 hour  
2 |  1 hour but less than 2 hours
3 |  2 hours but less than 4 hours  
4 |  4 hours or more   

**Harmonization status**:  impossible  
**Harmonization comment**:      
**R script**:  
```{r, echo=TRUE}

```  
### **Variable label**:  Average walking time    
**Variable name**:   lsb_pa_walk_time_4  
**Variable description**:  Average time the participant spends walking per day.    
**Value type**:  integer  
**Variable unit**:  N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 |  Less than 30 minutes  
1 |  30 minutes but less than 1 hour  
2 |  1 hour but less than 2 hours
3 |  2 hours but less than 4 hours  
4 |  4 hours or more     

**Harmonization status**:  impossible  
**Harmonization comment**:     
**R script**:  
```{r, echo=TRUE}

```  
### **Variable label**:  Average walking time     
**Variable name**:   lsb_pa_walk_time_5  
**Variable description**:  Average time the participant spends walking per day.    
**Value type**:  integer  
**Variable unit**:  N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 |  Less than 30 minutes  
1 |  30 minutes but less than 1 hour  
2 |  1 hour but less than 2 hours
3 |  2 hours but less than 4 hours  
4 |  4 hours or more     

**Harmonization status**:  impossible  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}

```  
### **Variable label**:  Average walking time     
**Variable name**:   lsb_pa_walk_time_6  
**Variable description**:  Average time the participant spends walking per day.    
**Value type**:  integer  
**Variable unit**:  N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 |  Less than 30 minutes  
1 |  30 minutes but less than 1 hour  
2 |  1 hour but less than 2 hours
3 |  2 hours but less than 4 hours  
4 |  4 hours or more    

**Harmonization status**:  impossible  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}

```  

### **Variable label**:  Average walking time for transportation  
**Variable name**:  lsb_pa_walk_trans_0    
**Variable description**:  Minutes per week the participant spent on walking for transportation (utilitarian walking) in the last week.  
**Value type**:  integer  
**Variable unit**:  minutes/week  
**Category coding**:  N/A  

**Harmonization status**:  impossible  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}

```  
### **Variable label**:  Average walking time for transportation    
**Variable name**:  lsb_pa_walk_trans_1    
**Variable description**: Minutes per week the participant spent on walking for transportation (utilitarian walking) in the last week.    
**Value type**:  integer  
**Variable unit**:  minutes/week  
**Category coding**:  N/A  

**Harmonization status**:  impossible  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}

```  
### **Variable label**:  Average walking time for transportation    
**Variable name**:  lsb_pa_walk_trans_2    
**Variable description**:  Minutes per week the participant spent on walking for transportation (utilitarian walking) in the last week.  
**Value type**:  integer  
**Variable unit**:  minutes/week  
**Category coding**:  N/A  

**Harmonization status**:  complete  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
lsb_GLOBE_2$lsb_pa_walk_trans_2<-GLOBE2004$w089*(GLOBE2004$w090*60+GLOBE2004$w091)
```  
### **Variable label**:  Average walking time for transportation    
**Variable name**:  lsb_pa_walk_trans_3    
**Variable description**:  Minutes per week the participant spent on walking for transportation (utilitarian walking) in the last week.  
**Value type**:  decimal      
**Variable unit**:  minutes/week  
**Category coding**:  N/A  

**Harmonization status**:  impossible  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}

```  
### **Variable label**:  Average walking time for transportation    
**Variable name**:  lsb_pa_walk_trans_4    
**Variable description**:  Minutes per week the participant spent on walking for transportation (utilitarian walking) in the last week.    
**Value type**:  integer  
**Variable unit**:  minutes/week  
**Category coding**:  N/A  

**Harmonization status**:  complete  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
lsb_GLOBE_4$lsb_pa_walk_trans_4<-GLOBE2014$G14v28_a_dag*(GLOBE2014$G14v28_a_uur*60+GLOBE2014$G14v28_a_min)
```  

### **Variable label**:  Average walking time for leisure  
**Variable name**:  lsb_pa_walk_leis_0    
**Variable description**:  Minutes per week the participant spent on walking for leisure in the last week.  
**Value type**:  integer  
**Variable unit**:  minutes/week  
**Category coding**:  N/A  

**Harmonization status**:  impossible  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}

```  
### **Variable label**:  Average walking time for leisure  
**Variable name**:  lsb_pa_walk_leis_1    
**Variable description**:  Minutes per week the participant spent on walking for leisure in the last week.  
**Value type**:  decimal      
**Variable unit**:  minutes/week  
**Category coding**:  N/A  

**Harmonization status**:  impossible  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}

```  
### **Variable label**:  Average walking time for leisure  
**Variable name**:  lsb_pa_walk_leis_2    
**Variable description**:  Minutes per week the participant spent on walking for leisure in the last week.  
**Value type**:  integer  
**Variable unit**:  minutes/week  
**Category coding**:  N/A  

**Harmonization status**:  complete  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
lsb_GLOBE_2$lsb_pa_walk_leis_2<-GLOBE2004$w097*(GLOBE2004$w098*60+GLOBE2004$w099)
```  
### **Variable label**:  Average walking time for leisure  
**Variable name**:  lsb_pa_walk_leis_3    
**Variable description**:  Minutes per week the participant spent on walking for leisure in the last week.  
**Value type**:  integer  
**Variable unit**:  minutes/week  
**Category coding**:  N/A  

**Harmonization status**:  complete  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
lsb_GLOBE_3$lsb_pa_walk_leis_3<-GLOBE2011$v19_a_wada*(GLOBE2011$v19_a_waur*60+GLOBE2011$v19_a_wamin)
```  
### **Variable label**:  Average walking time for leisure  
**Variable name**:  lsb_pa_walk_leis_4    
**Variable description**:  Minutes per week the participant spent on walking for leisure in the last week.  
**Value type**:  integer  
**Variable unit**:  minutes/week  
**Category coding**:  N/A  

**Harmonization status**:  complete  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
lsb_GLOBE_4$lsb_pa_walk_leis_4<-GLOBE2014$G14v29_a_dag*(GLOBE2014$G14v29_a_uur*60+GLOBE2014$G14v29_a_min)
```  

### **Variable label**:  Average cycling time    
**Variable name**:  lsb_pa_cycle_0  
**Variable description**:  Average minutes per week the participant spent on cycling in the last week.  
**Value type**:  integer  
**Variable unit**:  minutes/week  
**Category coding**:  N/A  

**Harmonization status**:  impossible  
**Harmonization comment**:    
**R script**:  
```{r, echo=TRUE}

```  
### **Variable label**:  Average cycling time    
**Variable name**:  lsb_pa_cycle_1  
**Variable description**:  Average minutes per week the participant spent on cycling in the last week.    
**Value type**:  integer  
**Variable unit**:  minutes/week  
**Category coding**:  N/A  

**Harmonization status**:    impossible  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}

```  
### **Variable label**:  Average cycling time    
**Variable name**:  lsb_pa_cycle_2  
**Variable description**:  Average minutes per week the participant spent on cycling in the last week.    
**Value type**:  integer  
**Variable unit**:  minutes/week  
**Category coding**:  N/A  

**Harmonization status**:  complete   
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
GLOBE2004$lsb_pa_cycle_2<-GLOBE2004$w093*(GLOBE2004$w094*60+GLOBE2004$w095)+GLOBE2004$w101*(GLOBE2004$w102*60+GLOBE2004$w103)
```  
### **Variable label**:  Average cycling time    
**Variable name**:  lsb_pa_cycle_3  
**Variable description**:  Average minutes per week the participant spent on cycling in the last week.    
**Value type**:  integer  
**Variable unit**:  minutes/week  
**Category coding**:  N/A  

**Harmonization status**:  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
lsb_GLOBE_3$lsb_pa_cycle_3<-GLOBE2011$v19_b_fida*(GLOBE2011$v19_b_fiur*60+GLOBE2011$v19_b_fimin)+GLOBE2011$v23_b_wfda*(GLOBE2011$v23_b_wfur*60+GLOBE2011$v23_b_wfmin)
```  
### **Variable label**:  Average cycling time    
**Variable name**:  lsb_pa_cycle_4  
**Variable description**:  Average minutes per week the participant spent on cycling in the last week.    
**Value type**:  integer  
**Variable unit**:  minutes/week  
**Category coding**:  N/A  

**Harmonization status**:  complete  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
lsb_GLOBE_4$lsb_pa_cycle_4<-GLOBE2014$G14v28_b_dag*(GLOBE2014$G14v28_b_uur*60+GLOBE2014$G14v28_b_min)+GLOBE2014$G14v29_b_dag*(GLOBE2014$G14v29_b_uur*60+GLOBE2014$G14v29_b_min)
```  
### **Variable label**:  Average cycling time    
**Variable name**:  lsb_pa_cycle_5  
**Variable description**:  Average minutes per week the participant spent on cycling in the last week.    
**Value type**:  integer  
**Variable unit**:  minutes/week  
**Category coding**:  N/A  

**Harmonization status**:  impossible  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}

```  
### **Variable label**:  Average cycling time    
**Variable name**:  lsb_pa_cycle_6  
**Variable description**:  Average minutes per week the participant spent on cycling in the last week.    
**Value type**:  integer  
**Variable unit**:  minutes/week  
**Category coding**:  N/A  

**Harmonization status**:  impossible  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}

```  

### **Variable label**:  Gardening   
**Variable name**:  lsb_pa_garden_0  
**Variable description**:  Indicator of whether the participant does any gardening activities.  
**Value type**:  integer  
**Variable unit**:  N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 |   Does not do any gardening activities  
1 |   Does any gardeing activities  

**Harmonization status**:  impossible  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}

```  
### **Variable label**:  Gardening    
**Variable name**:  lsb_pa_garden_1  
**Variable description**:  Indicator of whether the participant does any gardening activities.  
**Value type**:  integer  
**Variable unit**:  N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 |   Does not do any gardening activities  
1 |   Does any gardeing activities  

**Harmonization status**:  impossible  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}

```  
### **Variable label**:  Gardening    
**Variable name**:  lsb_pa_garden_2  
**Variable description**:  Indicator of whether the participant does any gardening activities.  
**Value type**:  integer  
**Variable unit**:  N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 |   Does not do any gardening activities  
1 |   Does any gardeing activities  

**Harmonization status**:  complete  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
lsb_GLOBE_2$lsb_pa_garden_2<-ifelse(GLOBE2004$w105==0,0L,
                                    ifelse(GLOBE2004$w105>0L,1,NA))
```  
### **Variable label**:  Gardening    
**Variable name**:  lsb_pa_garden_3  
**Variable description**:  Indicator of whether the participant does any gardening activities.  
**Value type**:  integer  
**Variable unit**:  N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 |   Does not do any gardening activities  
1 |   Does any gardeing activities  

**Harmonization status**:  complete  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
lsb_GLOBE_3$lsb_pa_garden_3<-ifelse(GLOBE2011$v19_c_tuda==0,0L,
                                    ifelse(GLOBE2011$v19_c_tuda>0,1L,NA))
```  
### **Variable label**:  Gardening    
**Variable name**:  lsb_pa_garden_4  
**Variable description**:  Indicator of whether the participant does any gardening activities.  
**Value type**:  integer  
**Variable unit**:  N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 |   Does not do any gardening activities  
1 |   Does any gardeing activities  

**Harmonization status**:  complete  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
lsb_GLOBE_4$lsb_pa_garden_4<-ifelse(GLOBE2014$G14v29_c_dag==0,0L,
                                    ifelse(GLOBE2014$G14v29_c_dag>0,1L,NA))
```  
### **Variable label**:  Gardening    
**Variable name**:  lsb_pa_garden_5  
**Variable description**:  Indicator of whether the participant does any gardening activities.  
**Value type**:  integer  
**Variable unit**:  N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 |   Does not do any gardening activities  
1 |   Does any gardeing activities  

**Harmonization status**:  impossible  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}

```  
### **Variable label**:  Gardening    
**Variable name**:  lsb_pa_garden_6  
**Variable description**:  Indicator of whether the participant does any gardening activities.  
**Value type**:  integer  
**Variable unit**:  N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 |   Does not do any gardening activities  
1 |   Does any gardeing activities  

**Harmonization status**:  impossible  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}

```  
### **Variable label**:  Average gardening time    
**Variable name**:  lsb_pa_garden_time_0    
**Variable description**:  Average minutes per week the participant spent on gardening activities in the last week.    
**Value type**:  integer  
**Variable unit**:  minutes/week  
**Category coding**:  N/A  

**Harmonization status**:  impossible  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}

```  
### **Variable label**:  Average gardening time    
**Variable name**:  lsb_pa_garden_time_1    
**Variable description**:  Average minutes per week the participant spent on gardening activities in the last week.       
**Value type**:  integer  
**Variable unit**:  minutes/week    
**Category coding**:  N/A  

**Harmonization status**:  impossible  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}

```  
### **Variable label**:  Average gardening time    
**Variable name**:  lsb_pa_garden_time_2    
**Variable description**:  Average minutes per week the participant spent on gardening activities in the last week.       
**Value type**:  integer  
**Variable unit**:  minutes/week    
**Category coding**:  N/A  

**Harmonization status**:  complete  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
lsb_GLOBE_2$lsb_pa_garden_time_2<-GLOBE2004$w105*(GLOBE2004$w106*60+GLOBE2004$w107)
```  
### **Variable label**:  Average gardening time    
**Variable name**:  lsb_pa_garden_time_3    
**Variable description**:  Average minutes per week the participant spent on gardening activities in the last week.       
**Value type**:  integer  
**Variable unit**:  minutes/week    
**Category coding**:  N/A  

**Harmonization status**:  complete  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
lsb_GLOBE_3$lsb_pa_garden_time_3<-GLOBE2011$v19_c_tuda*(GLOBE2011$v19_c_tuur*60+GLOBE2011$v19_c_tumin)
```  
### **Variable label**:  Average gardening time    
**Variable name**:  lsb_pa_garden_time_4    
**Variable description**:  Average minutes per week the participant spent on gardening activities in the last week.       
**Value type**:  integer  
**Variable unit**:  minutes/week    
**Category coding**:  N/A  

**Harmonization status**:  complete  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
lsb_GLOBE_4$lsb_pa_garden_time_4<-GLOBE2014$G14v29_c_dag*(GLOBE2014$G14v29_c_uur*60+GLOBE2014$G14v29_c_min)
```  
### **Variable label**:  Average gardening time    
**Variable name**:  lsb_pa_garden_time_5    
**Variable description**:  Average minutes per week the participant spent on gardening activities in the last week.       
**Value type**:  integer  
**Variable unit**:  minutes/week    
**Category coding**:  N/A  

**Harmonization status**:  impossible  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}

```  
### **Variable label**:  Average gardening time    
**Variable name**:  lsb_pa_garden_time_6    
**Variable description**:  Average minutes per week the participant spent on gardening activities in the last week.       
**Value type**:  integer  
**Variable unit**:  minutes/week    
**Category coding**:  N/A  

**Harmonization status**:  impossible  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}

```  

### **Variable label**:  Household activities  
**Variable name**:  lsb_pa_house_0  
**Variable description**:  Indicator of whether the participant does any household activities (light, moderate or vigorous).     
**Value type**:  integer  
**Variable unit**:  N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 |   Does not do any household activities  
1 |   Does any household activities  

**Harmonization status**:  impossible  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}

```  
### **Variable label**:  Household activities  
**Variable name**:  lsb_pa_house_1  
**Variable description**:  Indicator of whether the participant does any household activities (light, moderate or vigorous).     
**Value type**:  integer  
**Variable unit**:  N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 |   Does not do any household activities  
1 |   Does any household activities  

**Harmonization status**:  impossible  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}

```  
### **Variable label**:  Household activities  
**Variable name**:  lsb_pa_house_2  
**Variable description**:  Indicator of whether the participant does any household activities (light, moderate or vigorous).     
**Value type**:  integer  
**Variable unit**:  N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 |   Does not do any household activities  
1 |   Does any household activities  

**Harmonization status**:  complete  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
lsb_GLOBE_2$lsb_pa_house_2<-ifelse(GLOBE2004$w139>0 | GLOBE2004$w139>0, 1L,
                                   ifelse(GLOBE2004$w139==0 & GLOBE2004$w139==0,0L,NA)) 
```  
### **Variable label**:  Household activities  
**Variable name**:  lsb_pa_house_3  
**Variable description**:  Indicator of whether the participant does any household activities (light, moderate or vigorous).     
**Value type**:  integer  
**Variable unit**:  N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 |   Does not do any household activities  
1 |   Does any household activities  

**Harmonization status**:  complete  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
lsb_GLOBE_3$lsb_pa_house_3<-ifelse(GLOBE2011$v21_a_hhda>0 | GLOBE2011$v21_b_zhda>0, 1L,
                                   ifelse(GLOBE2011$v21_a_hhda==0 & GLOBE2011$v21_b_zhda==0,0L,NA))
```  
### **Variable label**:  Household activities  
**Variable name**:  lsb_pa_house_4  
**Variable description**:  Indicator of whether the participant does any household activities (light, moderate or vigorous).     
**Value type**:  integer  
**Variable unit**:  N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 |   Does not do any household activities  
1 |   Does any household activities  

**Harmonization status**:  complete  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
lsb_GLOBE_4$lsb_pa_house_4<-ifelse(GLOBE2014$G14v32_a_dag >0 | GLOBE2014$G14v32_b_dag>0, 1L,
                                   ifelse(GLOBE2014$G14v32_a_dag==0 & GLOBE2014$G14v32_b_dag ==0,0L,NA))
```  
### **Variable label**:  Household activities  
**Variable name**:  lsb_pa_house_5  
**Variable description**:  Indicator of whether the participant does any household activities (light, moderate or vigorous).     
**Value type**:  integer  
**Variable unit**:  N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 |   Does not do any household activities  
1 |   Does any household activities  

**Harmonization status**:  impossible  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}

```  
### **Variable label**:  Household activities  
**Variable name**:  lsb_pa_house_6  
**Variable description**:  Indicator of whether the participant does any household activities (light, moderate or vigorous).     
**Value type**:  integer  
**Variable unit**:  N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 |   Does not do any household activities  
1 |   Does any household activities  

**Harmonization status**:  impossible  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}

```  

### **Variable label**:  Average household activities time      
**Variable name**:  lsb_pa_house_time_0  
**Variable description**:  Average minutes per week the participant spent doing household activities in last week.  
**Value type**:  integer  
**Variable unit**:  minutes/week  
**Category coding**:  N/A  

**Harmonization status**:  impossible  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}

```  
### **Variable label**:  Average household activities time      
**Variable name**:  lsb_pa_house_time_1  
**Variable description**:  Average minutes per week the participant spent doing household activities in last week.  
**Value type**:  integer  
**Variable unit**:  minutes/week  
**Category coding**:  N/A  

**Harmonization status**:  impossible  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}

```  
### **Variable label**:  Average household activities time      
**Variable name**:  lsb_pa_house_time_2  
**Variable description**:  Average minutes per week the participant spent doing household activities in last week.  
**Value type**:  integer  
**Variable unit**:  minutes/week  
**Category coding**:  N/A  

**Harmonization status**:  complete  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
lsb_GLOBE_2$lsb_pa_garden_time_2<-GLOBE2004$w139*(GLOBE2004$w140*60+GLOBE2004$w141)+GLOBE2004$w142*(GLOBE2004$w143*60+GLOBE2004$w144)
```  
### **Variable label**:  Average household activities time      
**Variable name**:  lsb_pa_house_time_3  
**Variable description**:  Average minutes per week the participant spent doing household activities in last week.  
**Value type**:  integer  
**Variable unit**:  minutes/week  
**Category coding**:  N/A  

**Harmonization status**:  complete  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
lsb_GLOBE_3$lsb_pa_garden_time_3<-GLOBE2011$v21_a_hhda*(GLOBE2011$v21_a_hhur*60+GLOBE2011$v21_a_hhmin)+GLOBE2011$v21_b_zhda*(GLOBE2011$v21_b_zhur*60+GLOBE2011$v21_b_zhmin)
```  
### **Variable label**:  Average household activities time      
**Variable name**:  lsb_pa_house_time_4  
**Variable description**:  Average minutes per week the participant spent doing household activities in last week.  
**Value type**:  integer  
**Variable unit**:  minutes/week  
**Category coding**:  N/A  

**Harmonization status**:  complete  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
lsb_GLOBE_4$lsb_pa_garden_time_4<-GLOBE2014$G14v32_a_dag*(GLOBE2014$G14v32_a_uur*60+GLOBE2014$G14v32_a_min)+GLOBE2014$G14v32_b_dag*(GLOBE2014$G14v32_b_uur*60+GLOBE2014$G14v32_b_min)
```  
### **Variable label**:  Average household activities time      
**Variable name**:  lsb_pa_house_time_5  
**Variable description**:  Average minutes per week the participant spent doing household activities in last week.  
**Value type**:  integer  
**Variable unit**:  minutes/week  
**Category coding**:  N/A  

**Harmonization status**:  impossible  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}

```  
### **Variable label**:  Average household activities time      
**Variable name**:  lsb_pa_house_time_6  
**Variable description**:  Average minutes per week the participant spent doing household activities in last week.  
**Value type**:  integer  
**Variable unit**:  minutes/week  
**Category coding**:  N/A  

**Harmonization status**:  impossible  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}

```  
### **Variable label**: Sports or exercise      
**Variable name**:  lsb_pa_sport_0  
**Variable description**:  Indicator of whether the participant does any sports or exercise.  
**Value type**:  integer  
**Variable unit**:  N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 |  Does not do any sports or exercise   
1 |  Does any sports or exercise

**Harmonization status**:  complete  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
lsb_GLOBE_0$lsb_pa_sport_0<-recode(as.integer(GLOBE1991$v240),"1"=0L,"2"=1L,"3"=1L,"4"=1L)
```  
**Validation script**:  
```{r, echo=TRUE}
attributes(GLOBE1991$v240)

A<- addmargins(table(lsb_GLOBE_0$lsb_pa_sport_0,GLOBE1991$v240,useNA='always'))
colnames(A)<- c(names(attributes(GLOBE1991$v240)[[10]][1:4]),'NA','SUM')
as.data.frame.array(A,row.names = c('Does not do any sports or exercise','Does any sports or exercise','NA','SUM'))
```  
### **Variable label**: Sports or exercise      
**Variable name**:  lsb_pa_sport_1  
**Variable description**:  Indicator of whether the participant does any sports or exercise.  
**Value type**:  integer  
**Variable unit**:  N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 |  Does not do any sports or exercise   
1 |  Does any sports or exercise

**Harmonization status**:  complete  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
lsb_GLOBE_1$lsb_pa_sport_1<-recode(as.integer(GLOBE1997$v5),"1"=0L,"2"=1L,"3"=1L,"4"=1L)
```   
**Validation script**:  
```{r, echo=TRUE}
attributes(GLOBE1997$v5)

A<- addmargins(table(lsb_GLOBE_1$lsb_pa_sport_1,GLOBE1997$v5,useNA='always'))
colnames(A)<- c(names(attributes(GLOBE1991$v240)[[10]][1:4]),'NA','SUM')
as.data.frame.array(A,row.names = c('Does not do any sports or exercise','Does any sports or exercise','NA','SUM'))
``` 
### **Variable label**: Sports or exercise      
**Variable name**:  lsb_pa_sport_2  
**Variable description**:  Indicator of whether the participant does any sports or exercise.  
**Value type**:  integer  
**Variable unit**:  N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 |  Does not do any sports or exercise   
1 |  Does any sports or exercise

**Harmonization status**:  impossible  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}

```   
### **Variable label**: Sports or exercise      
**Variable name**:  lsb_pa_sport_3  
**Variable description**:  Indicator of whether the participant does any sports or exercise.  
**Value type**:  integer  
**Variable unit**:  N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 |  Does not do any sports or exercise   
1 |  Does any sports or exercise

**Harmonization status**:  impossible  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}

```   
### **Variable label**: Sports or exercise      
**Variable name**:  lsb_pa_sport_4  
**Variable description**:  Indicator of whether the participant does any sports or exercise.  
**Value type**:  integer  
**Variable unit**:  N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 |  Does not do any sports or exercise   
1 |  Does any sports or exercise

**Harmonization status**:  impossible  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}

```   
### **Variable label**: Sports or exercise      
**Variable name**:  lsb_pa_sport_5  
**Variable description**:  Indicator of whether the participant does any sports or exercise.  
**Value type**:  integer  
**Variable unit**:  N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 |  Does not do any sports or exercise   
1 |  Does any sports or exercise

**Harmonization status**:  impossible  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}

```   
### **Variable label**: Sports or exercise      
**Variable name**:  lsb_pa_sport_6  
**Variable description**:  Indicator of whether the participant does any sports or exercise.  
**Value type**:  integer  
**Variable unit**:  N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 |  Does not do any sports or exercise   
1 |  Does any sports or exercise

**Harmonization status**:  impossible  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}

```   

### **Variable label**:  Average sports or exercise time       
**Variable name**:  lsb_pa_sport_time_0  
**Variable description**:  Average time a week the participant spent on sports or exercise.    
**Value type**: integer  
**Variable unit**:  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 |  never   
1 |  less than 1 hour a week   
2 |  between 1 and 2 hours a week   
3 |  more than 2 hours a week  

**Harmonization status**:  complete  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
lsb_GLOBE_0$lsb_pa_sport_time_0<-recode(as.integer(GLOBE1991$v240),"1"=0L,"2"=1L,"3"=2L,"4"=3L)
```  
**Validation script**:  
```{r, echo=TRUE}
attributes(GLOBE1991$v240)

A<- addmargins(table(lsb_GLOBE_0$lsb_pa_sport_time_0,GLOBE1991$v240,useNA='always'))
colnames(A)<- c(names(attributes(GLOBE1991$v240)[[10]][1:4]),'NA','SUM')
as.data.frame.array(A,row.names = c('never','less than 1 hour a week','between 1 and 2 hours a week','more than 2 hours a week','NA','SUM'))
```
### **Variable label**:  Average sports or exercise time       
**Variable name**:  lsb_pa_sport_time_1  
**Variable description**:  Average time a week the participant spent on sports or exercise.    
**Value type**: integer    
**Variable unit**:  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 |  never   
1 |  less than 1 hour a week   
2 |  between 1 and 2 hours a week   
3 |  more than 2 hours a week   

**Harmonization status**:  complete  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
lsb_GLOBE_1$lsb_pa_sport_time_1<-recode(as.integer(GLOBE1997$v5),"1"=0L,"2"=1L,"3"=2L,"4"=3L)
```  
**Validation script**:  
```{r, echo=TRUE}
attributes(GLOBE1997$v5)

A<- addmargins(table(lsb_GLOBE_1$lsb_pa_sport_time_1,GLOBE1997$v5,useNA='always'))
colnames(A)<- c(names(attributes(GLOBE1997$v5)[[10]][3:6]),'NA','SUM')
as.data.frame.array(A,row.names = c('never','less than 1 hour a week','between 1 and 2 hours a week','more than 2 hours a week','NA','SUM'))
```
### **Variable label**:  Average sports or exercise time       
**Variable name**:  lsb_pa_sport_time_2  
**Variable description**:  Average time a week the participant spent on sports or exercise.    
**Value type**: integer   
**Variable unit**:  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 |  never   
1 |  less than 1 hour a week   
2 |  between 1 and 2 hours a week   
3 |  more than 2 hours a week    

**Harmonization status**:  impossible  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}

```  
### **Variable label**:  Average sports or exercise time       
**Variable name**:  lsb_pa_sport_time_3  
**Variable description**:  Average time a week the participant spent on sports or exercise.    
**Value type**: integer    
**Variable unit**:  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 |  never   
1 |  less than 1 hour a week   
2 |  between 1 and 2 hours a week   
3 |  more than 2 hours a week    

**Harmonization status**:  impossible  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}

```  
### **Variable label**:  Average sports or exercise time       
**Variable name**:  lsb_pa_sport_time_4  
**Variable description**:  Average time a week the participant spent on sports or exercise.    
**Value type**: integer   
**Variable unit**:  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 |  never   
1 |  less than 1 hour a week   
2 |  between 1 and 2 hours a week   
3 |  more than 2 hours a week    

**Harmonization status**:  impossible  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}

```  
### **Variable label**:  Average sports or exercise time       
**Variable name**:  lsb_pa_sport_time_5  
**Variable description**:  Average time a week the participant spent on sports or exercise.    
**Value type**: integer   
**Variable unit**:  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 |  never   
1 |  less than 1 hour a week   
2 |  between 1 and 2 hours a week   
3 |  more than 2 hours a week    

**Harmonization status**:  impossible  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}

```  
### **Variable label**:  Average sports or exercise time       
**Variable name**:  lsb_pa_sport_time_6  
**Variable description**:  Average time a week the participant spent on sports or exercise.    
**Value type**: integer   
**Variable unit**:  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 |  never   
1 |  less than 1 hour a week   
2 |  between 1 and 2 hours a week   
3 |  more than 2 hours a week    

**Harmonization status**:  impossible  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}

```  

# Diet and nutrition subdomain

### **Variable label**:  Daily vegetable consumption  
**Variable name**:  lsb_veg_0    
**Variable description**:  Indicator of whether the participant currently consumes vegetables on a daily basis.   
**Value type**:  integer  
**Variable unit**:  N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 |   Does not consume vegetables on a daily basis  
1 |   Consumes vegetables on a daily basis  

**Harmonization status**:  impossible  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}

```  
### **Variable label**:  Daily vegetable consumption  
**Variable name**:  lsb_veg_1    
**Variable description**:  Indicator of whether the participant currently consumes vegetables on a daily basis.   
**Value type**:  integer  
**Variable unit**:  N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 |   Does not consume vegetables on a daily basis  
1 |   Consumes vegetables on a daily basis  

**Harmonization status**:  impossible  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}

```  
### **Variable label**:  Daily vegetable consumption  
**Variable name**:  lsb_veg_2    
**Variable description**:  Indicator of whether the participant currently consumes vegetables on a daily basis.   
**Value type**:  integer  
**Variable unit**:  N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 |   Does not consume vegetables on a daily basis  
1 |   Consumes vegetables on a daily basis  

**Harmonization status**:  impossible  
**Harmonization comment**:   The 2 variables for study specific don't permit us to determine whether the participant consumes vegetables in a daily basis.
**R script**:  
```{r, echo=TRUE}

```  

### **Variable label**:  Daily fruit consumption  
**Variable name**:  lsb_fruit_0  
**Variable description**:  Indicator of whether the participant currently consumes fruit on a daily basis.   
**Value type**:  integer  
**Variable unit**:  N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 |   Does not consume fruit on a daily basis
1 |   Consumes fruit on a daily basis  

**Harmonization status**:  impossible  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}

```  
### **Variable label**:  Daily fruit consumption  
**Variable name**:  lsb_fruit_1  
**Variable description**:  Indicator of whether the participant currently consumes fruit on a daily basis.   
**Value type**:  integer  
**Variable unit**:  N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 |   Does not consume fruit on a daily basis
1 |   Consumes fruit on a daily basis  

**Harmonization status**:  impossible  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}

```  
### **Variable label**:  Daily fruit consumption  
**Variable name**:  lsb_fruit_2  
**Variable description**:  Indicator of whether the participant currently consumes fruit on a daily basis.   
**Value type**:  integer  
**Variable unit**:  N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 |   Does not consume fruit on a daily basis
1 |   Consumes fruit on a daily basis  

**Harmonization status**:  impossible  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}

```  

### **Variable label**:  Daily water consumption  
**Variable name**:  lsb_water_0    
**Variable description**:  Indicator of whether the participant drinks water on a daily basis.   
**Value type**:  integer  
**Variable unit**:  N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 |   Does not drinks water on a daily basis
1 |   Drinks water on a daily basis

**Harmonization status**:  impossible  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}

```  
### **Variable label**:  Daily water consumption  
**Variable name**:  lsb_water_1    
**Variable description**:  Indicator of whether the participant drinks water on a daily basis.   
**Value type**:  integer  
**Variable unit**:  N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 |   Does not drinks water on a daily basis
1 |   Drinks water on a daily basis

**Harmonization status**:  impossible  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}

```  
### **Variable label**:  Daily water consumption  
**Variable name**:  lsb_water_2    
**Variable description**:  Indicator of whether the participant drinks water on a daily basis.   
**Value type**:  integer  
**Variable unit**:  N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 |   Does not drinks water on a daily basis
1 |   Drinks water on a daily basis

**Harmonization status**:  impossible  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}

```  
### **Variable label**:  Daily water consumption  
**Variable name**:  lsb_water_3    
**Variable description**:  Indicator of whether the participant drinks water on a daily basis.   
**Value type**:  integer  
**Variable unit**:  N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 |   Does not drinks water on a daily basis
1 |   Drinks water on a daily basis

**Harmonization status**:  impossible  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}

```  
### **Variable label**:  Daily water consumption  
**Variable name**:  lsb_water_4    
**Variable description**:  Indicator of whether the participant drinks water on a daily basis.   
**Value type**:  integer  
**Variable unit**:  N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 |   Does not drinks water on a daily basis
1 |   Drinks water on a daily basis

**Harmonization status**:  complete  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
lsb_GLOBE_4$lsb_water_4<-recode(as.integer(GLOBE2014$G14v23_d),"1"=0L,"2"=0L,"3"=0L,"4"=0L,"5"=0L,"6"=1L)
```  
**Validation script**:  
```{r, echo=TRUE}
lsb_GLOBE_4$lsb_water_4<-recode(as.integer(GLOBE2014$G14v23_d),"1"=0L,"2"=0L,"3"=0L,"4"=0L,"5"=0L,"6"=1L)
```

### **Variable label**:  Quantity daily coffee  
**Variable name**:  lsb_coffee_qty_0  
**Variable description**:  Current quantity of coffee the participant consumes per day.   
**Value type**:  integer  
**Variable unit**:  cups/day  
**Category coding**:  N/A  

**Harmonization status**:  complete  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
lsb_GLOBE_0$lsb_coffee_qty_0<-GLOBE1991$v131
```  
### **Variable label**:  Quantity daily coffee  
**Variable name**:  lsb_coffee_qty_1  
**Variable description**:  Current quantity of coffee the participant consumes per day.   
**Value type**:  integer  
**Variable unit**:  cups/day 
**Category coding**:  N/A  

**Harmonization status**:  impossible  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}

```  
### **Variable label**:  Quantity daily coffee  
**Variable name**:  lsb_coffee_qty_2  
**Variable description**:  Current quantity of coffee the participant consumes per day.   
**Value type**:  integer  
**Variable unit**:  cups/day  
**Category coding**:  N/A  

**Harmonization status**:  impossible  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}

```  
### **Variable label**:  Quantity daily coffee  
**Variable name**:  lsb_coffee_qty_3  
**Variable description**:  Current quantity of coffee the participant consumes per day.   
**Value type**:  integer  
**Variable unit**:  cups/day 
**Category coding**:  N/A  

**Harmonization status**:  impossible  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}

```  
### **Variable label**:  Quantity daily coffee  
**Variable name**:  lsb_coffee_qty_4  
**Variable description**:  Current quantity of coffee the participant consumes per day.   
**Value type**:  integer  
**Variable unit**:  cups/day  
**Category coding**:  N/A  

**Harmonization status**:  impossible  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}

```  

# Sleep quality subdomain

### **Variable label**:  Average sleep hours  
**Variable name**:  lsb_sleep_hours_0  
**Variable description**:  Average number of hours the participant sleeps per night.  
**Value type**:  integer  
**Variable unit**:  hours/night  
**Category coding**:  N/A  

**Harmonization status**:  impossible  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}

```  
### **Variable label**:  Average sleep hours  
**Variable name**:  lsb_sleep_hours_1  
**Variable description**:  Average number of hours the participant sleeps per night.  
**Value type**:  integer  
**Variable unit**:  hours/night   
**Category coding**:  N/A  

**Harmonization status**:  impossible  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}


```  
### **Variable label**:  Average sleep hours  
**Variable name**:  lsb_sleep_hours_2  
**Variable description**:  Average number of hours the participant sleeps per night.  
**Value type**:  integer  
**Variable unit**:  hours/night 
**Category coding**:  N/A  

**Harmonization status**:  impossible  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}

```  
### **Variable label**:  Average sleep hours  
**Variable name**:  lsb_sleep_hours_3  
**Variable description**:  Average number of hours the participant sleeps per night.  
**Value type**:  integer  
**Variable unit**:  hours/night
**Category coding**:  N/A  

**Harmonization status**:  impossible  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}

```  
### **Variable label**:  Average sleep hours  
**Variable name**:  lsb_sleep_hours_4    
**Variable description**:  Average number of hours the participant sleeps per night.  
**Value type**:  integer  
**Variable unit**:  hours/night   
**Category coding**:  N/A  

**Harmonization status**:  impossible  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}

```  
### **Variable label**:  Average sleep hours  
**Variable name**:  lsb_sleep_hours_5  
**Variable description**:  Average number of hours the participant sleeps per night.  
**Value type**:  integer  
**Variable unit**:  hours/night    
**Category coding**:  N/A  

**Harmonization status**:  impossible  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}

```  

### **Variable label**:  Difficulty falling asleep  
**Variable name**:  lsb_sleep_diff_0  
**Variable description**:  Indicator of whether the participant ever has any diffulty falling asleep.  
**Value type**:  integer  
**Variable unit**:  N/A  
**Category coding**:    

**Code** | **Category Label**  
------------- | -------------  
0 |  Never has difficulty falling asleep
1 |  Sometimes has difficulty falling asleep

**Harmonization status**:  impossible  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}

```  
### **Variable label**:  Difficulty falling asleep  
**Variable name**:  lsb_sleep_diff_1  
**Variable description**:  Indicator of whether the participant ever has any diffulty falling asleep.  
**Value type**:  integer  
**Variable unit**:  N/A  
**Category coding**:    

**Code** | **Category Label**  
------------- | -------------  
0 |  Never has difficulty falling asleep
1 |  Sometimes has difficulty falling asleep

**Harmonization status**:  impossible  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
   
```  
### **Variable label**:  Difficulty falling asleep  
**Variable name**:  lsb_sleep_diff_2    
**Variable description**:  Indicator of whether the participant ever has any diffulty falling asleep.  
**Value type**:  integer  
**Variable unit**:  N/A  
**Category coding**:    

**Code** | **Category Label**  
------------- | -------------  
0 |  Never has difficulty falling asleep
1 |  Sometimes has difficulty falling asleep

**Harmonization status**:     impossible  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}

```  
### **Variable label**:  Difficulty falling asleep  
**Variable name**:  lsb_sleep_diff_3  
**Variable description**:  Indicator of whether the participant ever has any diffulty falling asleep.  
**Value type**:  integer  
**Variable unit**:  N/A  
**Category coding**:    

**Code** | **Category Label**  
------------- | -------------  
0 |  Never has difficulty falling asleep
1 |  Sometimes has difficulty falling asleep

**Harmonization status**:  impossible  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}

```  
### **Variable label**:  Difficulty falling asleep  
**Variable name**:  lsb_sleep_diff_4  
**Variable description**:  Indicator of whether the participant ever has any diffulty falling asleep.  
**Value type**:  integer  
**Variable unit**:  N/A  
**Category coding**:    

**Code** | **Category Label**  
------------- | -------------  
0 |  Never has difficulty falling asleep
1 |  Sometimes has difficulty falling asleep

**Harmonization status**:  impossible  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}

```  
### **Variable label**:  Difficulty falling asleep  
**Variable name**:  lsb_sleep_diff_5  
**Variable description**:  Indicator of whether the participant ever has any diffulty falling asleep.  
**Value type**:  integer  
**Variable unit**:  N/A  
**Category coding**:    

**Code** | **Category Label**  
------------- | -------------  
0 |  Never has difficulty falling asleep
1 |  Sometimes has difficulty falling asleep

**Harmonization status**:  impossible  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
   
```  

### **Variable label**:  Quality of sleep  
**Variable name**:  lsb_sleep_qlty_0  
**Variable description**:  Indicator of the quality of sleep of the participant.    
**Value type**:  integer  
**Variable unit**:  N/A  
**Category coding**:    

**Code** | **Category Label**  
------------- | -------------  
0 |  Very bad 
1 |  Fairly bad
2 |  Fairly good
3 |  Very good  

**Harmonization status**:  impossible  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}

```  

### **Variable label**:  Quality of sleep  
**Variable name**:  lsb_sleep_qlty_1  
**Variable description**:  Indicator of the quality of sleep of the participant.    
**Value type**:  integer  
**Variable unit**:  N/A  
**Category coding**:    

**Code** | **Category Label**  
------------- | -------------  
0 |  Very bad 
1 |  Fairly bad
2 |  Fairly good
3 |  Very good  

**Harmonization status**:  impossible  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}

``` 

### **Variable label**:  Quality of sleep  
**Variable name**:  lsb_sleep_qlty_2  
**Variable description**:  Indicator of the quality of sleep of the participant.    
**Value type**:  integer  
**Variable unit**:  N/A  
**Category coding**:    

**Code** | **Category Label**  
------------- | -------------  
0 |  Very bad 
1 |  Fairly bad
2 |  Fairly good
3 |  Very good  

**Harmonization status**:  impossible  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}

``` 
### **Variable label**:  Quality of sleep  
**Variable name**:  lsb_sleep_qlty_3  
**Variable description**:  Indicator of the quality of sleep of the participant.    
**Value type**:  integer  
**Variable unit**:  N/A  
**Category coding**:    

**Code** | **Category Label**  
------------- | -------------  
0 |  Very bad 
1 |  Fairly bad
2 |  Fairly good
3 |  Very good  

**Harmonization status**:  impossible  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}

```  
### **Variable label**:  Quality of sleep  
**Variable name**:  lsb_sleep_qlty_4  
**Variable description**:  Indicator of the quality of sleep of the participant.    
**Value type**:  integer  
**Variable unit**:  N/A  
**Category coding**:    

**Code** | **Category Label**  
------------- | -------------  
0 |  Very bad 
1 |  Fairly bad
2 |  Fairly good
3 |  Very good  

**Harmonization status**:  impossible  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}

```  
### **Variable label**:  Quality of sleep  
**Variable name**:  lsb_sleep_qlty_5  
**Variable description**:  Indicator of the quality of sleep of the participant.    
**Value type**:  integer  
**Variable unit**:  N/A  
**Category coding**:    

**Code** | **Category Label**  
------------- | -------------  
0 |  Very bad 
1 |  Fairly bad
2 |  Fairly good
3 |  Very good  

**Harmonization status**:  impossible  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}

```  



