---
title: "Lifestyle and behaviours DataSchema"
output: html_document
---

# Connecting with Opal data server
## Login to server and assign study data
```{r, echo=FALSE}
#Load R libraries
library(opalr)
# Create an opal object with the login information
erasmus_opal <- opal.login()

#Login to Opal server and assign the content of the GLOBE table(s) to your RStudio environment
opal.assign.table.tibble(erasmus_opal, 'RSII_MINDMAP_13082019_visit0','ROTTERDAM.RSII_MINDMAP_13082019_visit0', variables =NULL)

ROTTERDAM_0 <- opal.execute(erasmus_opal,'RSII_MINDMAP_13082019_visit0')


opal.assign.table.tibble(erasmus_opal, 'RSII_MINDMAP_13082019_visit1','ROTTERDAM.RSII_MINDMAP_13082019_visit1', variables =NULL)

ROTTERDAM_1 <- opal.execute(erasmus_opal,'RSII_MINDMAP_13082019_visit1')


opal.assign.table.tibble(erasmus_opal, 'RSII_MINDMAP_18102019_visit2','ROTTERDAM.RSII_MINDMAP_18102019_visit2', variables =NULL)

ROTTERDAM_2 <- opal.execute(erasmus_opal,'RSII_MINDMAP_18102019_visit2')

opal.assign.table.tibble(erasmus_opal, 'RSII_MINDMAP_18102019_visit3','ROTTERDAM.RSII_MINDMAP_18102019_visit3', variables =NULL)

ROTTERDAM_3 <- opal.execute(erasmus_opal,'RSII_MINDMAP_18102019_visit3')

opal.logout(erasmus_opal)

```
## Assign participant id as first column of your harmonized dataframes
```{r, echo=FALSE}
lsb_ROTTERDAM_0 <- data.frame(id = ROTTERDAM_0$id)
lsb_ROTTERDAM_1 <- data.frame(id = ROTTERDAM_1$id)
lsb_ROTTERDAM_2 <- data.frame(id = ROTTERDAM_2$id)
lsb_ROTTERDAM_3 <- data.frame(id = ROTTERDAM_3$id)

```

# Table of Contents
1. [Alcohol consumption subdomain](#alcohol-consumption-subdomain)
2. [Tobacco consumption subdomain](#tobacco-consumption-subdomain)
3. [Physical activity subdomain](#physical-activity-subdomain)
4. [Diet and nutrition subdomain](#diet-and-nutrition-subdomain)
5. [Sleep quality subdomain](#sleep-quality-subdomain)

# Alcohol consumption subdomain

### **Variable label**:  Current consumption of alcohol  
**Variable name**: lsb_alc_cur_0  
**Variable description**:  Indicator of whether the participant currently consumes alcohol or has consumed alcohol in the past 12 months.  
**Value type**: integer  
**Variable unit**: N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 |  Does not currently consume alcohol   
1 |  Currently consumes alcohol  

**Harmonization status**:  complete      
**Harmonization comment**:   The study-specific variable is "Do you ever drink alcoholic beverages?" is used in harmonization. People who are currently at the same age as their answer to the question "How old were you when you stopped drinking alcoholic beverages?" were also coded as having consumed alcohol in the last 12 months. 
**R script**:  
```{r, echo=TRUE}
table(ROTTERDAM_0$ep_lf3, ROTTERDAM_0$ep_lf3b!=888, useNA="always")
table((ROTTERDAM_0$ep_page- ROTTERDAM_0$ep_lf3b)==0, ROTTERDAM_0$ep_lf3,useNA="always")
table(ROTTERDAM_0$ep_lf3, ROTTERDAM_0$ep_lf3a, useNA="always")
table(ROTTERDAM_0$ep_lf3)
lsb_ROTTERDAM_0$lsb_alc_cur_0<-ifelse(ROTTERDAM_0$ep_lf3==0 &(ROTTERDAM_0$ep_page- ROTTERDAM_0$ep_lf3b==0), 1L,
                                      ifelse(ROTTERDAM_0$ep_lf3==0, 0L,ifelse(ROTTERDAM_0$ep_lf3==1, 1L, NA)))

table(lsb_ROTTERDAM_0$lsb_alc_cur_0, useNA="always")

```  
### **Variable label**:  Current consumption of alcohol  
**Variable name**: lsb_alc_cur_1  
**Variable description**:  Indicator of whether the participant currently consumes alcohol or has consumed alcohol in the past 12 months.  
**Value type**: integer  
**Variable unit**: N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 |  Does not currently consume alcohol   
1 |  Currently consumes alcohol   

**Harmonization status**:  complete      
**Harmonization comment**:  The study-specific variable is "Do you ever drink alcoholic beverages?" is used in harmonization. 
**R script**:  
```{r, echo=TRUE}
 
table(ROTTERDAM_1$e4_didalc, useNA="always")

#table(ROTTERDAM_1$e4_didalc,ROTTERDAM_1$e4_didalcpl , useNA="always")
lsb_ROTTERDAM_1$lsb_alc_cur_1<-ifelse(ROTTERDAM_1$e4_didalc==0, 0L, ifelse(ROTTERDAM_1$e4_didalc==1, 1L, NA))
table(lsb_ROTTERDAM_1$lsb_alc_cur_1, useNA="always")

```  
### **Variable label**:  Current consumption of alcohol  
**Variable name**: lsb_alc_cur_2  
**Variable description**:  Indicator of whether the participant currently consumes alcohol or has consumed alcohol in the past 12 months.  
**Value type**: integer  
**Variable unit**: N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 |  Does not currently consume alcohol   
1 |  Currently consumes alcohol  

**Harmonization status**:  complete      
**Harmonization comment**:   The study-specific variable asks "How often did you have a drink containing alcohol in the past year?"
**R script**:  
```{r, echo=TRUE}
 
table(ROTTERDAM_2$e5_EIAUDIT1, useNA = "always")
lsb_ROTTERDAM_2$lsb_alc_cur_2<- ifelse(ROTTERDAM_2$e5_EIAUDIT1==0, 0L, ifelse(is.na(ROTTERDAM_2$e5_EIAUDIT1), NA, 1L ))
table(lsb_ROTTERDAM_2$lsb_alc_cur_2, useNA = "always")
```  
### **Variable label**:  Current consumption of alcohol  
**Variable name**: lsb_alc_cur_3  
**Variable description**:  Indicator of whether the participant currently consumes alcohol or has consumed alcohol in the past 12 months.  
**Value type**: integer  
**Variable unit**: N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 |  Does not currently consume alcohol   
1 |  Currently consumes alcohol  

**Harmonization status**:  complete  
**Harmonization comment**:   The study-specific variable asks "How often did you have a drink containing alcohol in the past year?"
**R script**:  
```{r, echo=TRUE}
table(ROTTERDAM_3$e6_EIAUDIT1, useNA= "always")
lsb_ROTTERDAM_3$lsb_alc_cur_3<- ifelse(ROTTERDAM_3$e6_EIAUDIT1==0, 0L, ifelse(is.na(ROTTERDAM_3$e6_EIAUDIT1), NA, 1L))
table(lsb_ROTTERDAM_3$lsb_alc_cur_3, useNA="always")
```  
### **Variable label**:  Current consumption of alcohol  
**Variable name**: lsb_alc_cur_4  
**Variable description**:  Indicator of whether the participant currently consumes alcohol or has consumed alcohol in the past 12 months.  
**Value type**: integer  
**Variable unit**: N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 |  Does not currently consume alcohol   
1 |  Currently consumes alcohol  

**Harmonization status**:  impossible    
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
 

```  
### **Variable label**:  Current consumption of alcohol  
**Variable name**: lsb_alc_cur_5  
**Variable description**:  Indicator of whether the participant currently consumes alcohol or has consumed alcohol in the past 12 months.  
**Value type**: integer  
**Variable unit**: N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 |  Does not currently consume alcohol   
1 |  Currently consumes alcohol  

**Harmonization status**:  impossible    
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
 

```  
### **Variable label**:  Current consumption of alcohol  
**Variable name**: lsb_alc_cur_6  
**Variable description**:  Indicator of whether the participant currently consumes alcohol or has consumed alcohol in the past 12 months.  
**Value type**: integer  
**Variable unit**: N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 |  Does not currently consume alcohol   
1 |  Currently consumes alcohol  

**Harmonization status**:  impossible    
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
 

```  

### **Variable label**:   Ever consumption of alcohol  
**Variable name**: lsb_alc_ever_0    
**Variable description**:  Indicator of whether the participant has ever consumed alcohol.  
**Value type**: integer  
**Variable unit**: N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 |   Never consumed alcohol  
1 |   Ever consumed alcohol  

**Harmonization status**:  complete      
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
MyMerge <- function(x,y){
  df <- merge(x,y, by="id",all=TRUE)
  return(df)
}
#Reducing the table to the variables needed
alc_table_rotterdam <- Reduce(MyMerge, list(ROTTERDAM_0, ROTTERDAM_1, ROTTERDAM_2, ROTTERDAM_3))
                                         
table(ROTTERDAM_0$ep_lf3a, useNA="always")

alc_table_rotterdam$lsb_alc_ever_0 <- ifelse(ROTTERDAM_0$ep_lf3a==0, 0L, ifelse(ROTTERDAM_0$ep_lf3a==1, 1L, NA))
lsb_ROTTERDAM_0<- merge(lsb_ROTTERDAM_0,alc_table_rotterdam[,c("id","lsb_alc_ever_0")],by = "id", all.x = TRUE)
table(lsb_ROTTERDAM_0$lsb_alc_ever_0 )

```  
### **Variable label**:   Ever consumption of alcohol  
**Variable name**: lsb_alc_ever_1    
**Variable description**:  Indicator of whether the participant has ever consumed alcohol.  
**Value type**: integer  
**Variable unit**: N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 |   Never consumed alcohol  
1 |   Ever consumed alcohol  

**Harmonization status**:  complete     
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
table(ROTTERDAM_1$e4_didalcp, useNA="always")
alc_table_rotterdam$lsb_alc_ever_1 <- ifelse(alc_table_rotterdam$lsb_alc_ever_0 ==1 | alc_table_rotterdam$e4_didalcp==1,1L,
                                      ifelse(alc_table_rotterdam$e4_didalcp==0      & alc_table_rotterdam$lsb_alc_ever_0 ==0, 0L,NA))

lsb_ROTTERDAM_1<- merge(lsb_ROTTERDAM_1,alc_table_rotterdam[,c("id","lsb_alc_ever_1")],by = "id", all.x = TRUE)

table(lsb_ROTTERDAM_1$lsb_alc_ever_1)

# this code creates fewer NAs but merged tables were used in the other studies
# lsb_ROTTERDAM_1$lsb_alc_ever_1 <- ifelse(ROTTERDAM_1$e4_didalcp==0, 0L, ifelse(ROTTERDAM_1$e4_didalcp==1, 1L, NA))

```  
### **Variable label**:   Ever consumption of alcohol  
**Variable name**: lsb_alc_ever_2    
**Variable description**:  Indicator of whether the participant has ever consumed alcohol.  
**Value type**: integer  
**Variable unit**: N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 |   Never consumed alcohol  
1 |   Ever consumed alcohol  

**Harmonization status**:  impossible  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
 

```  
### **Variable label**:   Ever consumption of alcohol  
**Variable name**: lsb_alc_ever_3    
**Variable description**:  Indicator of whether the participant has ever consumed alcohol.  
**Value type**: integer  
**Variable unit**: N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 |   Never consumed alcohol  
1 |   Ever consumed alcohol  

**Harmonization status**:  impossible    
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
 

```  
### **Variable label**:   Ever consumption of alcohol  
**Variable name**: lsb_alc_ever_4    
**Variable description**:  Indicator of whether the participant has ever consumed alcohol.  
**Value type**: integer  
**Variable unit**: N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 |   Never consumed alcohol  
1 |   Ever consumed alcohol  

**Harmonization status**:  impossible    
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
 

```  
### **Variable label**:   Ever consumption of alcohol  
**Variable name**: lsb_alc_ever_5    
**Variable description**:  Indicator of whether the participant has ever consumed alcohol.  
**Value type**: integer  
**Variable unit**: N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 |   Never consumed alcohol  
1 |   Ever consumed alcohol  

**Harmonization status**:  impossible    
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
 

```  
### **Variable label**:   Ever consumption of alcohol  
**Variable name**: lsb_alc_ever_6    
**Variable description**:  Indicator of whether the participant has ever consumed alcohol.  
**Value type**: integer  
**Variable unit**: N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 |   Never consumed alcohol  
1 |   Ever consumed alcohol  

**Harmonization status**:  impossible    
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
 

```  

### **Variable label**:   Frequency of binge drinking  
**Variable name**: lsb_alc_binge_0  
**Variable description**:  Frequency of drinking 4 or more drinks in one day.  
**Value type**: integer  
**Variable unit**: N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
1 |  0 to 3 times a month  
2 |  1 to 2 times a week   
3 |  3 times a week or more  

**Harmonization status**:  impossible    
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}

```  
### **Variable label**:   Frequency of binge drinking  
**Variable name**: lsb_alc_binge_1  
**Variable description**:  Frequency of drinking 4 or more drinks in one day.  
**Value type**: integer  
**Variable unit**: N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
1 |  0 to 3 times a month  
2 |  1 to 2 times a week   
3 |  3 times a week or more  

**Harmonization status**:  impossible    
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
 
```  
### **Variable label**:   Frequency of binge drinking  
**Variable name**: lsb_alc_binge_2  
**Variable description**:  Frequency of drinking 4 or more drinks in one day.  
**Value type**: integer  
**Variable unit**: N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
1 |  0 to 3 times a month  
2 |  1 to 2 times a week   
3 |  3 times a week or more  

**Harmonization status**:  impossible    
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
 

```  
### **Variable label**:   Frequency of binge drinking  
**Variable name**: lsb_alc_binge_3  
**Variable description**:  Frequency of drinking 4 or more drinks in one day.  
**Value type**: integer  
**Variable unit**: N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
1 |  0 to 3 times a month  
2 |  1 to 2 times a week   
3 |  3 times a week or more  

**Harmonization status**:  complete     
**Harmonization comment**:   The study-specific variable is "How often do you have six or more drinks on one occasion?". The study specific category "weekly 1 to 3 times per week" is coded under category 2| 1 to 2 times a week, of the harmonized variable.  

**R script**:  
```{r, echo=TRUE}
table(ROTTERDAM_3$e6_EIAUDIT3)

lsb_ROTTERDAM_3$lsb_alc_binge_3<- dplyr::recode(as.character(ROTTERDAM_3$e6_EIAUDIT3), "0"=1L, "1"=1L, "2"=1L, "3"=2L, "4"=3L,
                                         .default =NA_integer_)
# 0 = 'never'
# 1 = 'less than monthly'
# 2 = 'monthly 1to 3 times per month'
# 3 = 'weekly 1to 3 times per week'
# 4 = 'daily or almost daily 4 or more times per week'
# 7 = 'dont know'
# 9 = 'missing '
# e6_EIAUDIT1
# 0 = 'never'
# 1 = 'monthly or less'
# 2 = '2 to 4 times a month'
# 3 = '2 to 3 times a week'
# 4 = '4 or more times a week'
# 7 = 'dont know'
# 9 = 'missing '
# e6_EIAUDIT2
# 0 = '1 or 2'
# 1 = '3 or 4'
# 2 = '5 or 6'
# 3 = '7, 8 or 9'
# 4 = '10 or more'
# 7 = 'dont know'
# 9 = 'missing '

table(lsb_ROTTERDAM_3$lsb_alc_binge_3)
```  
### **Variable label**:   Frequency of binge drinking  
**Variable name**: lsb_alc_binge_4  
**Variable description**:  Frequency of drinking 4 or more drinks in one day.  
**Value type**: integer  
**Variable unit**: N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
1 |  0 to 3 times a month  
2 |  1 to 2 times a week   
3 |  3 times a week or more  

**Harmonization status**:  impossible    
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
 

```  
### **Variable label**:   Frequency of binge drinking  
**Variable name**: lsb_alc_binge_5  
**Variable description**:  Frequency of drinking 4 or more drinks in one day.  
**Value type**: integer  
**Variable unit**: N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
1 |  0 to 3 times a month  
2 |  1 to 2 times a week   
3 |  3 times a week or more  

**Harmonization status**:  impossible    
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
 

```  
### **Variable label**:   Frequency of binge drinking  
**Variable name**: lsb_alc_binge_6  
**Variable description**:  Frequency of drinking 4 or more drinks in one day.  
**Value type**: integer  
**Variable unit**: N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
1 |  0 to 3 times a month  
2 |  1 to 2 times a week   
3 |  3 times a week or more  

**Harmonization status**:  impossible    
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
 

```  

### **Variable label**:   Current quantity of alcohol consumed per week (total)      
**Variable name**: lsb_alc_total_0  
**Variable description**:  Current quantity of wine, beer and liquor consumed per week.    
**Value type**: decimal    
**Variable unit**: drinks/week  
**Category coding**:  N/A  

**Harmonization status**:  complete         
**Harmonization comment**:  The study-specific variable "Do you drink other moderately strong alcoholic beverages like advocaat, berry jenever, campari, liqueur, vermouth or martini?" has not been used in the harmonization of this data schema variable.  


**R script**:  
```{r, echo=TRUE}
table(ROTTERDAM_0$ep_lf3nd, useNA="always")

table(ROTTERDAM_0$ep_lf3l,useNA="always")

ROTTERDAM_0$nb_beer     <-ifelse(ROTTERDAM_0$ep_lf3d==1, ROTTERDAM_0$ep_lf3e, ifelse(ROTTERDAM_0$ep_lf3d==0, 0L, NA))
ROTTERDAM_0$nb_whitewine<-ifelse(ROTTERDAM_0$ep_lf3f==1, ROTTERDAM_0$ep_lf3g, ifelse(ROTTERDAM_0$ep_lf3f==0, 0L, NA))
ROTTERDAM_0$nb_redwine  <-ifelse(ROTTERDAM_0$ep_lf3h==1, ROTTERDAM_0$ep_lf3i, ifelse(ROTTERDAM_0$ep_lf3h==0, 0L, NA))
# ROTTERDAM_0$nb_modstrong<-ifelse(ROTTERDAM_0$ep_lf3l==1, ROTTERDAM_0$ep_lf3m, ifelse(ROTTERDAM_0$ep_lf3l==0, 0L, NA))
ROTTERDAM_0$nb_liq      <-ifelse(ROTTERDAM_0$ep_lf3n==1, ROTTERDAM_0$ep_lf3o, ifelse(ROTTERDAM_0$ep_lf3n==0, 0L, NA))
  
lsb_ROTTERDAM_0$lsb_alc_total_0 <- rowSums(ROTTERDAM_0[,278:281])
  

table(lsb_ROTTERDAM_0$lsb_alc_total_0, useNA="always")

# ep_lf3d
# Do you drink beer?
# 
# ep_lf3e
# How many glasses of beer do you drink per week?
# 
# ep_lf3f
# Do you drink white wine?
# 
# ep_lf3g
# How many glasses of white wine do you drink per week?
# 
# ep_lf3h
# Do you drink red wine?
# 
# ep_lf3i
# How many glasses of red wine do you drink per week?
# 
# ep_lf3j
# Do you drink sherry, port, vermouth or Martini?
#  

#to check the study-specific variable 
ROTTERDAM_0$lsb_alc_total_0<-lsb_ROTTERDAM_0$lsb_alc_total_0
table(ROTTERDAM_0$ep_lf3nd, useNA="always")
as.integer(ROTTERDAM_0$ep_lf3nd)>as.integer(ROTTERDAM_0$lsb_alc_total_0)


```  
### **Variable label**:   Current quantity of alcohol consumed per week (total)  
**Variable name**: lsb_alc_total_1  
**Variable description**:  Current quantity of wine, beer and liquor consumed per week.    
**Value type**: decimal    
**Variable unit**: drinks/week  
**Category coding**:  N/A  

**Harmonization status**:        
**Harmonization comment**:   The study specific variable "Do you drink moderately strong alcoholic beverages like sherry, port, advocaat, bessenjenever, campari, liqueur, vermouth or martini?" has not been used in the harmonization of this data schema variable.  

**R script**:  
```{r, echo=TRUE}

ROTTERDAM_1$nb_beer     <-ifelse(ROTTERDAM_1$e4_didbe==1, ROTTERDAM_1$e4_didbefr, ifelse(ROTTERDAM_1$e4_didbe==0, 0L, NA))
ROTTERDAM_1$nb_whitewine<-ifelse(ROTTERDAM_1$e4_didwwi==1, ROTTERDAM_1$e4_didwwifr, ifelse(ROTTERDAM_1$e4_didwwi==0, 0L, NA))
ROTTERDAM_1$nb_redwine  <-ifelse(ROTTERDAM_1$e4_didrwi==1, ROTTERDAM_1$e4_didrwifr, ifelse(ROTTERDAM_1$e4_didrwi==0, 0L, NA))
# ROTTERDAM_1$nb_modstrong<-ifelse(ROTTERDAM_1$e4_didsh==1, ROTTERDAM_1$e4_didshfr, ifelse(ROTTERDAM_1$e4_didsh==0, 0L, NA))
ROTTERDAM_1$nb_liq      <-ifelse(ROTTERDAM_1$e4_didli==1, ROTTERDAM_1$e4_didlifr, ifelse(ROTTERDAM_1$e4_didli==0, 0L, NA))
  
table(ROTTERDAM_1$e4_didwwifr)
lsb_ROTTERDAM_1$lsb_alc_total_1 <- rowSums(ROTTERDAM_1[,289:292])
  
# ROTTERDAM_1$e4_didwwi
# ROTTERDAM_1$e4_didwwifr
# ROTTERDAM_1$e4_didrwi
# ROTTERDAM_1$e4_didrwifr
# ROTTERDAM_1$e4_didsh
# ROTTERDAM_1$e4_didshfr
# ROTTERDAM_1$e4_didli
# ROTTERDAM_1$e4_didlifr
table(lsb_ROTTERDAM_1$lsb_alc_total_1, useNA="always")
```  
### **Variable label**:   Current quantity of alcohol consumed per week (total)  
**Variable name**: lsb_alc_total_2  
**Variable description**:  Current quantity of wine, beer and liquor consumed per week.    
**Value type**: decimal    
**Variable unit**: drinks/week  
**Category coding**:  N/A  

**Harmonization status**:  impossible    
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
 
# e5_EIAUDIT2, e5_EIAUDIT1
```  
### **Variable label**:   Current quantity of alcohol consumed per week (total)  
**Variable name**: lsb_alc_total_3  
**Variable description**:  Current quantity of wine, beer and liquor consumed per week.    
**Value type**: decimal    
**Variable unit**: drinks/week  
**Category coding**:  N/A  

**Harmonization status**:  impossible    
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
 # e6_EIAUDIT1, e6_EIAUDIT2
# How many drinks containing alcohol do you have on a typical day when you are drinking?
# How often did you have a drink containing alcohol in the past year?
# but if we use these variables, we can't specificy whether wine, beer, liquor or other type

```  

### **Variable label**:   Current quantity of wine consumed per week  
**Variable name**: lsb_alc_wine_0  
**Variable description**:  Current quantity of wine consumed per week.    
**Value type**: decimal    
**Variable unit**: drinks/week  
**Category coding**:  N/A  

**Harmonization status**:  complete      
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
table(ROTTERDAM_0$ep_lf3g, useNA = "always")
table(ROTTERDAM_0$ep_lf3i, useNA = "always")

lsb_ROTTERDAM_0$lsb_alc_wine_0<-ROTTERDAM_0$ep_lf3g+ 	ROTTERDAM_0$ep_lf3i
table(lsb_ROTTERDAM_0$lsb_alc_wine_0, useNA = "always")

```  
### **Variable label**:   Current quantity of wine consumed per week  
**Variable name**: lsb_alc_wine_1  
**Variable description**:  Current quantity of wine consumed per week.    
**Value type**: decimal    
**Variable unit**: drinks/week  
**Category coding**:  N/A  

**Harmonization status**:  complete      
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
table(ROTTERDAM_1$e4_didwwifr, useNA="always")

table(ROTTERDAM_1$e4_didrwifr, useNA="always")

lsb_ROTTERDAM_1$lsb_alc_wine_1<-ROTTERDAM_1$e4_didwwifr+ 	ROTTERDAM_1$e4_didrwifr
table(lsb_ROTTERDAM_1$lsb_alc_wine_1, useNA="always")
```  
### **Variable label**:   Current quantity of wine consumed per week  
**Variable name**: lsb_alc_wine_2  
**Variable description**:  Current quantity of wine consumed per week.    
**Value type**: decimal    
**Variable unit**: drinks/week  
**Category coding**:  N/A  

**Harmonization status**:  impossible    
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
 

```  
### **Variable label**:   Current quantity of wine consumed per week  
**Variable name**: lsb_alc_wine_3  
**Variable description**:  Current quantity of wine consumed per week.    
**Value type**: decimal    
**Variable unit**: drinks/week  
**Category coding**:  N/A  

**Harmonization status**:  impossible    
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
 

```  

### **Variable label**:   Current quantity of beer consumed per week  
**Variable name**: lsb_alc_beer_0  
**Variable description**:  Current quantity of beer consumed per week.   
**Value type**: decimal    
**Variable unit**: drinks/week  
**Category coding**:  N/A  
 

**Harmonization status**:  complete      
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
table(ROTTERDAM_0$ep_lf3d, useNA="always")
 
lsb_ROTTERDAM_0$lsb_alc_beer_0<- ifelse(ROTTERDAM_0$ep_lf3d==0|ROTTERDAM_0$ep_lf3d==8 , 0, ifelse(!is.na(ROTTERDAM_0$ep_lf3e), as.numeric(ROTTERDAM_0$ep_lf3e),NA))
table(ROTTERDAM_0$ep_lf3e, useNA="always")
table(lsb_ROTTERDAM_0$lsb_alc_beer_0, useNA = "always")

```  
### **Variable label**:   Current quantity of beer consumed per week  
**Variable name**: lsb_alc_beer_1  
**Variable description**:  Current quantity of beer consumed per week.    
**Value type**: decimal    
**Variable unit**: drinks/week  
**Category coding**:  N/A  
 

**Harmonization status**:  complete      
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}

table(ROTTERDAM_1$e4_didbe,ROTTERDAM_1$e4_didbefr, useNA="always")
lsb_ROTTERDAM_1$lsb_alc_total_1<-ifelse(ROTTERDAM_1$e4_didbe==0|ROTTERDAM_1$e4_didbe==8 , 0,as.numeric(ROTTERDAM_1$e4_didbefr)) 
table(lsb_ROTTERDAM_1$lsb_alc_total_1)

```  
### **Variable label**:   Current quantity of beer consumed per week  
**Variable name**: lsb_alc_beer_2  
**Variable description**:  Current quantity of beer consumed per week.    
**Value type**: decimal    
**Variable unit**: drinks/week  
**Category coding**:  N/A  
 

**Harmonization status**:  impossible    
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
 

```  
### **Variable label**:   Current quantity of beer consumed per week  
**Variable name**: lsb_alc_beer_3  
**Variable description**:  Current quantity of beer consumed per week.    
**Value type**: decimal    
**Variable unit**: drinks/week  
**Category coding**:  N/A  
 

**Harmonization status**:  impossible    
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
 

```  

### **Variable label**:   Current quantity of liquor consumed per week  
**Variable name**: lsb_alc_liq_0  
**Variable description**:  Current quantity of liquor consumed per week.    
**Value type**: decimal    
**Variable unit**: drinks/week  
**Category coding**:  N/A  
 

**Harmonization status**:      
**Harmonization comment**:    The study specific variable "Do you drink moderately strong alcoholic beverages like sherry, port, advocaat, bessenjenever, campari, liqueur, vermouth or martini?" and "Do you drink sherry, port, vermouth or Martini?" have not been used in the harmonization of this data schema variable.  "How many glasses of strong alcoholic beverages do you drink per week?" has been used in the harmonization of the DataSchema variable.  

**R script**:  
```{r, echo=TRUE}
table(ROTTERDAM_0$ep_lf3n, useNA="always")
table(ROTTERDAM_0$ep_lf3o, useNA="always")

lsb_ROTTERDAM_0$lsb_alc_liq_0<-ifelse(ROTTERDAM_0$ep_lf3n==0|ROTTERDAM_0$ep_lf3n==8 , 0,as.numeric(ROTTERDAM_0$ep_lf3o)) 
table(lsb_ROTTERDAM_0$lsb_alc_liq_0, useNA="always")

```  
### **Variable label**:   Current quantity of liquor consumed per week  
**Variable name**: lsb_alc_liq_1  
**Variable description**:  Current quantity of liquor consumed per week.   
**Value type**: decimal    
**Variable unit**: drinks/week  
**Category coding**:  N/A  
 

**Harmonization status**:      
**Harmonization comment**:    The study specific variable "Do you drink moderately strong alcoholic beverages like sherry, port, advocaat, bessenjenever, campari, liqueur, vermouth or martini?" has not been used in the harmonization of this variable. "Do you drink strong alcoholic beverages like Beerenburg, Brandy, lemon jenever, cognac, rum, jenever, Jagermeister, vieux or whisky?"" has been used in the harmonization of the DataSchema variable.  
**R script**:  
```{r, echo=TRUE}
table(ROTTERDAM_1$e4_didli, useNA="always")
table(ROTTERDAM_1$e4_didlifr, useNA="always")

lsb_ROTTERDAM_1$lsb_alc_liq_1<-ifelse(ROTTERDAM_1$e4_didli==0|ROTTERDAM_1$e4_didli==8 , 0,as.numeric(ROTTERDAM_1$e4_didlifr)) 
table(lsb_ROTTERDAM_1$lsb_alc_liq_1, useNA="always")
 

# e4_didli   "Do you drink strong alcoholic beverages like Beerenburg, Brandy, lemon jenever, cognac, rum, jenever, Jägermeister, vieux or whisky?
# 
# e4_didlifr  How many glasses do you drink per week?
#   
```  
### **Variable label**:   Current quantity of liquor consumed per week  
**Variable name**: lsb_alc_liq_2  
**Variable description**:  Current quantity of liquor consumed per week.    
**Value type**: decimal    
**Variable unit**: drinks/week  
**Category coding**:  N/A  
 

**Harmonization status**:  impossible    
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
 

```  
### **Variable label**:   Current quantity of liquor consumed per week  
**Variable name**: lsb_alc_liq_3  
**Variable description**:  Current quantity of liquor consumed per week.   
**Value type**: decimal    
**Variable unit**: drinks/week  
**Category coding**:  N/A  
 

**Harmonization status**:  impossible    
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
 

```  

# Tobacco consumption subdomain

### **Variable label**:  Current tobacco smoking  
**Variable name**:  lsb_smk_cur_0  
**Variable description**:  Indicator of whether the participant currently smokes any tobacco product.  
**Value type**:  integer  
**Variable unit**:  N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 |   Currently does not smoke any tobacco product  
1 |   Currently smokes any tobacco product  

**Harmonization status**:  complete    
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}

table(ROTTERDAM_0$ep_lf6)

lsb_ROTTERDAM_0$lsb_smk_cur_0<- as.integer(ROTTERDAM_0$ep_lf6==1)
table(lsb_ROTTERDAM_0$lsb_smk_cur_0)
 
```  
### **Variable label**:  Current tobacco smoking  
**Variable name**:  lsb_smk_cur_1  
**Variable description**:  Indicator of whether the participant currently smokes any tobacco product.  
**Value type**:  integer  
**Variable unit**:  N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 |   Currently does not smoke any tobacco product  
1 |   Currently smokes any tobacco product  

**Harmonization status**:  complete      
**Harmonization comment**:    
**R script**:  
```{r, echo=TRUE}

table(ROTTERDAM_1$e4_dict)


lsb_ROTTERDAM_1$lsb_smk_cur_1<- ifelse(ROTTERDAM_1$e4_dict==1, 1L,
                                ifelse(ROTTERDAM_1$e4_dict==0|ROTTERDAM_1$e4_dict==2|
                                       ROTTERDAM_1$e4_dict==3, 0L,NA))

table(lsb_ROTTERDAM_1$lsb_smk_cur_1)
```  
### **Variable label**:  Current tobacco smoking  
**Variable name**:  lsb_smk_cur_2  
**Variable description**:  Indicator of whether the participant currently smokes any tobacco product.  
**Value type**:  integer  
**Variable unit**:  N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 |   Currently does not smoke any tobacco product  
1 |   Currently smokes any tobacco product  

**Harmonization status**:  complete      
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}

table(ROTTERDAM_2$e5_EILF6)
lsb_ROTTERDAM_2$lsb_smk_cur_2<- as.integer(ROTTERDAM_2$e5_EILF6) 
table(lsb_ROTTERDAM_2$lsb_smk_cur_2, useNA="always")


```  
### **Variable label**:  Current tobacco smoking  
**Variable name**:  lsb_smk_cur_3  
**Variable description**:  Indicator of whether the participant currently smokes any tobacco product.  
**Value type**:  integer  
**Variable unit**:  N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 |   Currently does not smoke any tobacco product  
1 |   Currently smokes any tobacco product  

**Harmonization status**:  complete      
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
table(ROTTERDAM_3$e6_EILF6)

lsb_ROTTERDAM_3$lsb_smk_cur_3<-ifelse(ROTTERDAM_3$e6_EILF6==1, 1L, 
                               ifelse(ROTTERDAM_3$e6_EILF6==0,0L,NA))

table(lsb_ROTTERDAM_3$lsb_smk_cur_3, useNA="always")

```  
### **Variable label**:  Current tobacco smoking  
**Variable name**:  lsb_smk_cur_4  
**Variable description**:  Indicator of whether the participant currently smokes any tobacco product.  
**Value type**:  integer  
**Variable unit**:  N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 |   Currently does not smoke any tobacco product  
1 |   Currently smokes any tobacco product  

**Harmonization status**:  impossible    
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
 

```  
### **Variable label**:  Current tobacco smoking  
**Variable name**:  lsb_smk_cur_5  
**Variable description**:  Indicator of whether the participant currently smokes any tobacco product.  
**Value type**:  integer  
**Variable unit**:  N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 |   Currently does not smoke any tobacco product  
1 |   Currently smokes any tobacco product  

**Harmonization status**:  impossible    
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
 

```  
### **Variable label**:  Current tobacco smoking  
**Variable name**:  lsb_smk_cur_6  
**Variable description**:  Indicator of whether the participant currently smokes any tobacco product.  
**Value type**:  integer  
**Variable unit**:  N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 |   Currently does not smoke any tobacco product  
1 |   Currently smokes any tobacco product  

**Harmonization status**:  impossible    
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
 

```  

### **Variable label**:  Smoking status  
**Variable name**:  lsb_smk_status_0  
**Variable description**:  Smoking status of the participant.  
**Value type**:  integer  
**Variable unit**:  N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 |   Never smoker  
1 |   Former smoker  
2 |   Current smoker  

**Harmonization status**:  complete      
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
table(ROTTERDAM_0$ep_lf6)
table(ROTTERDAM_0$ep_lf6e)

lsb_ROTTERDAM_0$lsb_smk_status_0 <-  ifelse(ROTTERDAM_0$ep_lf6==1, 2L, 
                                     ifelse(ROTTERDAM_0$ep_lf6==0 & ROTTERDAM_0$ep_lf6e==0, 0L, 
                                     ifelse(ROTTERDAM_0$ep_lf6==0 & ROTTERDAM_0$ep_lf6e==1, 1L, NA)))
table(lsb_ROTTERDAM_0$lsb_smk_status_0, useNA="always")
```  
### **Variable label**:  Smoking status  
**Variable name**:  lsb_smk_status_1  
**Variable description**:  Smoking status of the participant.  
**Value type**:  integer  
**Variable unit**:  N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 |   Never smoker  
1 |   Former smoker  
2 |   Current smoker  

**Harmonization status**:  complete      
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
 
table(ROTTERDAM_1$e4_dict)
lsb_ROTTERDAM_1$lsb_smk_status_1<- ifelse(ROTTERDAM_1$e4_dict==0, 0L, 
                                   ifelse(ROTTERDAM_1$e4_dict==1, 2L, 
                                   ifelse(ROTTERDAM_1$e4_dict==2|ROTTERDAM_1$e4_dict==3, 1L, NA)))

table(lsb_ROTTERDAM_1$lsb_smk_status_1)
```  
### **Variable label**:  Smoking status  
**Variable name**:  lsb_smk_status_2  
**Variable description**:  Smoking status of the participant.  
**Value type**:  integer  
**Variable unit**:  N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 |   Never smoker  
1 |   Former smoker  
2 |   Current smoker  

**Harmonization status**:  complete      
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}

table(ROTTERDAM_2$e5_EILF6)
table(ROTTERDAM_2$e5_EILFE)
# table(ROTTERDAM_2$e5_EILFE, ROTTERDAM_2$e5_EILF6)

lsb_ROTTERDAM_2$lsb_smk_status_2 <- ifelse(ROTTERDAM_2$e5_EILF6==1, 2L,
                                    ifelse(ROTTERDAM_2$e5_EILFE==1 & ROTTERDAM_2$e5_EILF6==0, 1L,
                                    ifelse(ROTTERDAM_2$e5_EILF6==0 & ROTTERDAM_2$e5_EILFE==0, 0L, NA)))

table(lsb_ROTTERDAM_2$lsb_smk_status_2)
```  
### **Variable label**:  Smoking status  
**Variable name**:  lsb_smk_status_3  
**Variable description**:  Smoking status of the participant.  
**Value type**:  integer  
**Variable unit**:  N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 |   Never smoker  
1 |   Former smoker  
2 |   Current smoker  

**Harmonization status**:  complete      
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
table(ROTTERDAM_3$e6_EILSE5, useNA="always")
table(ROTTERDAM_3$e6_EILF6, useNA="always")
table(ROTTERDAM_3$e6_EILSE5,ROTTERDAM_3$e6_EILF6, useNA="always")

table(ROTTERDAM_3$e6_EILFHE5, useNA="always")

# table(ROTTERDAM_3$e5_EILFE, ROTTERDAM_2$e5_EILF6)

lsb_ROTTERDAM_3$lsb_smk_status_3 <- ifelse(ROTTERDAM_3$e6_EILF6==1, 2L,
                                    ifelse(ROTTERDAM_3$e6_EILF6==0 & 
                                          (ROTTERDAM_3$e6_EILSE5==1|ROTTERDAM_3$e6_EILSE5==2), 1L,
                                    ifelse(ROTTERDAM_3$e6_EILF6==0&ROTTERDAM_3$e6_EILSE5==0, 0L, NA)))

table(lsb_ROTTERDAM_3$lsb_smk_status_3, useNA="always")


```  
### **Variable label**:  Smoking status  
**Variable name**:  lsb_smk_status_4  
**Variable description**:  Smoking status of the participant.  
**Value type**:  integer  
**Variable unit**:  N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 |   Never smoker  
1 |   Former smoker  
2 |   Current smoker  

**Harmonization status**:  impossible    
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
 

```  
### **Variable label**:  Smoking status  
**Variable name**:  lsb_smk_status_5  
**Variable description**:  Smoking status of the participant.  
**Value type**:  integer  
**Variable unit**:  N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 |   Never smoker  
1 |   Former smoker  
2 |   Current smoker  

**Harmonization status**:  impossible    
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
 

```  
### **Variable label**:  Smoking status  
**Variable name**:  lsb_smk_status_6  
**Variable description**:  Smoking status of the participant.  
**Value type**:  integer  
**Variable unit**:  N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 |   Never smoker  
1 |   Former smoker  
2 |   Current smoker  

**Harmonization status**:  impossible    
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
 

```  

### **Variable label**:  Ever tobacco smoking  
**Variable name**:  lsb_smk_ever_0    
**Variable description**:  Indicator of whether the participant has ever smoked any tobacco product.  
**Value type**:  integer  
**Variable unit**:  N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 |   Never smoked tobacco  
1 |   Ever smoked tobacco  

**Harmonization status**:  complete      
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}
table(ROTTERDAM_0$ep_lf6e,ROTTERDAM_0$ep_lf6 ) 
table(ROTTERDAM_0$ep_lf6,ROTTERDAM_0$ep_lf6e, useNA = "always")
table(ROTTERDAM_0$ep_lf6,ROTTERDAM_0$ep_lf6k, useNA = "always")
table(ROTTERDAM_0$ep_lf6e,ROTTERDAM_0$ep_lf6k, useNA = "always")

alc_table_rotterdam$lsb_smk_ever_0<- ifelse(ROTTERDAM_0$ep_lf6e==1,1L,
                                     ifelse(ROTTERDAM_0$ep_lf6e==0,0L,NA))

#merging to harmonized table
lsb_ROTTERDAM_0<- merge(lsb_ROTTERDAM_0,alc_table_rotterdam[,c("id","lsb_smk_ever_0")],by = "id", all.x = TRUE)


table(lsb_ROTTERDAM_0$lsb_smk_ever_0,useNA = "always")
```  
### **Variable label**:  Ever tobacco smoking  
**Variable name**:  lsb_smk_ever_1    
**Variable description**:  Indicator of whether the participant has ever smoked any tobacco product.  
**Value type**:  integer  
**Variable unit**:  N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 |   Never smoked tobacco  
1 |   Ever smoked tobacco  

**Harmonization status**:  complete      
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
table(ROTTERDAM_1$e4_dicg, useNA="always")
table(ROTTERDAM_1$e4_dipi, useNA="always")
table(ROTTERDAM_1$e4_dict, useNA="always")

alc_table_rotterdam$lsb_smk_ever_1<- ifelse(alc_table_rotterdam$lsb_smk_ever_0==1| ROTTERDAM_1$e4_dict==1|ROTTERDAM_1$e4_dict==2|ROTTERDAM_1$e4_dict==3,1L,
                                         ifelse(alc_table_rotterdam$e4_dict==0&alc_table_rotterdam$lsb_smk_ever_0==0, 0L, NA ))
                                         
                                         
                                  
#merging to harmonized table
lsb_ROTTERDAM_1<- merge(lsb_ROTTERDAM_1,alc_table_rotterdam[,c("id","lsb_smk_ever_1")],by = "id", all.x = TRUE)

table(lsb_ROTTERDAM_1$lsb_smk_ever_1, useNA="always")

```  
### **Variable label**:  Ever tobacco smoking  
**Variable name**:  lsb_smk_ever_2    
**Variable description**:  Indicator of whether the participant has ever smoked any tobacco product.  
**Value type**:  integer  
**Variable unit**:  N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 |   Never smoked tobacco  
1 |   Ever smoked tobacco  

**Harmonization status**:  complete      
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}
table(ROTTERDAM_2$e5_EILF6, useNA="always")
table(ROTTERDAM_2$e5_EILFE, useNA="always")


alc_table_rotterdam$lsb_smk_ever_2<- ifelse(alc_table_rotterdam$lsb_smk_ever_0==1| alc_table_rotterdam$lsb_smk_ever_1==1|
                                              alc_table_rotterdam$e5_EILFE==1,1L,
                                         ifelse(alc_table_rotterdam$e5_EILFE==0&alc_table_rotterdam$lsb_smk_ever_0==0
                                               &alc_table_rotterdam$lsb_smk_ever_1==0, 0L, NA ))
                                         
                                         
                                  
#merging to harmonized table
lsb_ROTTERDAM_2<- merge(lsb_ROTTERDAM_2,alc_table_rotterdam[,c("id","lsb_smk_ever_2")],by = "id", all.x = TRUE)

                                        
table(lsb_ROTTERDAM_2$lsb_smk_ever_2, useNA="always")                                         
```  
### **Variable label**:  Ever tobacco smoking  
**Variable name**:  lsb_smk_ever_3    
**Variable description**:  Indicator of whether the participant has ever smoked any tobacco product.  
**Value type**:  integer  
**Variable unit**:  N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 |   Never smoked tobacco  
1 |   Ever smoked tobacco  

**Harmonization status**:  complete      
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
 
table(ROTTERDAM_3$e6_EILF6, ROTTERDAM_3$e6_EILSE5, useNA="always")
table(ROTTERDAM_3$e6_EILF6, ROTTERDAM_3$e6_EILF6C, useNA="always")
table(ROTTERDAM_3$e6_EILSE5, ROTTERDAM_3$e6_EILF6C, useNA="always")
table(ROTTERDAM_3$e6_EILF6, useNA="always")
table(ROTTERDAM_3$e6_EILF6C, useNA="always")
table(ROTTERDAM_3$e6_EILSE5, ROTTERDAM_3$e6_EILF6,useNA="always")

alc_table_rotterdam$lsb_smk_ever_3<- ifelse(alc_table_rotterdam$lsb_smk_ever_0==1| alc_table_rotterdam$lsb_smk_ever_1==1|
                                              alc_table_rotterdam$lsb_smk_ever_2==1|
                                              alc_table_rotterdam$e6_EILF6==1|alc_table_rotterdam$e6_EILSE5==2,1L,
                                         ifelse(alc_table_rotterdam$e6_EILF6==0 & 
                                                  alc_table_rotterdam$lsb_smk_ever_0==0 &
                                                  alc_table_rotterdam$lsb_smk_ever_1==0 &
                                               alc_table_rotterdam$lsb_smk_ever_2==0, 0L, NA ))
                                         
lsb_ROTTERDAM_3<- merge(lsb_ROTTERDAM_3,alc_table_rotterdam[,c("id","lsb_smk_ever_3")],by = "id", all.x = TRUE)

table(lsb_ROTTERDAM_3$lsb_smk_ever_3,useNA="always")


```  
### **Variable label**:  Ever tobacco smoking  
**Variable name**:  lsb_smk_ever_4    
**Variable description**:  Indicator of whether the participant has ever smoked any tobacco product.  
**Value type**:  integer  
**Variable unit**:  N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 |   Never smoked tobacco  
1 |   Ever smoked tobacco  

**Harmonization status**:  impossible    
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
 

```  
### **Variable label**:  Ever tobacco smoking  
**Variable name**:  lsb_smk_ever_5    
**Variable description**:  Indicator of whether the participant has ever smoked any tobacco product.  
**Value type**:  integer  
**Variable unit**:  N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 |   Never smoked tobacco  
1 |   Ever smoked tobacco  

**Harmonization status**:  impossible    
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
 

```  
### **Variable label**:  Ever tobacco smoking  
**Variable name**:  lsb_smk_ever_6    
**Variable description**:  Indicator of whether the participant has ever smoked any tobacco product.  
**Value type**:  integer  
**Variable unit**:  N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 |   Never smoked tobacco  
1 |   Ever smoked tobacco  

**Harmonization status**:  impossible    
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
 

```  

### **Variable label**:  Quantity cigarettes smoked    
**Variable name**:  lsb_cig_qty_0   
**Variable description**:  Current average number of cigarettes smoked per day.  
**Value type**:  integer  
**Variable unit**:  cigarettes/day  
**Category coding**:  

**Harmonization status**:  complete      
**Harmonization comment**:   The study-specific category 'incidental less than 1 per day' is coded as 0.
**R script**:  
```{r, echo=TRUE}
class(ROTTERDAM_0$ep_lf6a) 
table(ROTTERDAM_0$ep_lf6a, ROTTERDAM_0$ep_lf6, useNA="always")
table(ROTTERDAM_0$ep_lf6a,  useNA="always")

table(lsb_ROTTERDAM_0$lsb_smk_cur_0, useNA="always")
lsb_ROTTERDAM_0$lsb_cig_qty_0 <-ifelse(lsb_ROTTERDAM_0$lsb_smk_cur_0==0, 0L, ifelse(ROTTERDAM_0$ep_lf6a<76,ROTTERDAM_0$ep_lf6a,
                                                                                    ifelse(ROTTERDAM_0$ep_lf6a==76, 0L,NA)))
table(lsb_ROTTERDAM_0$lsb_cig_qty_0 , useNA="always")
```  
### **Variable label**:  Quantity cigarettes smoked    
**Variable name**:  lsb_cig_qty_1   
**Variable description**:  Current average number of cigarettes smoked per day.  
**Value type**:  integer  
**Variable unit**:  cigarettes/day  
**Category coding**:  

**Harmonization status**:  complete      
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
 
table(lsb_ROTTERDAM_1$lsb_smk_cur_1, useNA="always")
lsb_ROTTERDAM_1$lsb_cig_qty_1 <-ifelse(lsb_ROTTERDAM_1$lsb_smk_cur_1==0, 0L,
                                ifelse(ROTTERDAM_1$e4_dictn<76,ROTTERDAM_1$e4_dictn,NA))
table(lsb_ROTTERDAM_1$lsb_cig_qty_1, useNA="always")
table(ROTTERDAM_1$e4_dictn, useNA="always")
```  
### **Variable label**:  Quantity cigarettes smoked    
**Variable name**:  lsb_cig_qty_2   
**Variable description**:  Current average number of cigarettes smoked per day.  
**Value type**:  integer  
**Variable unit**:  cigarettes/day  
**Category coding**:  

**Harmonization status**:  complete      
**Harmonization comment**:   The study-specific category 'incidental less than 1 per day' is coded as 0.
**R script**:  
```{r, echo=TRUE}
table(lsb_ROTTERDAM_2$lsb_smk_cur_2, useNA="always") 

lsb_ROTTERDAM_2$lsb_cig_qty_2 <-ifelse(lsb_ROTTERDAM_2$lsb_smk_cur_2==0, 0L, 
                                ifelse(ROTTERDAM_2$e5_EILF6A<76,ROTTERDAM_2$e5_EILF6A,
                                ifelse(ROTTERDAM_2$e5_EILF6A==76, 0L,NA)))
table(lsb_ROTTERDAM_2$lsb_cig_qty_2, useNA="always")
```  
### **Variable label**:  Quantity cigarettes smoked    
**Variable name**:  lsb_cig_qty_3   
**Variable description**:  Current average number of cigarettes smoked per day.  
**Value type**:  integer  
**Variable unit**:  cigarettes/day  
**Category coding**:  

**Harmonization status**:  complete     
**Harmonization comment**:   The study-specific category 'incidental less than 1 per day' is coded as 0.
**R script**:  
```{r, echo=TRUE}
table(ROTTERDAM_3$e6_EILF6A, useNA="always")
 
lsb_ROTTERDAM_3$lsb_cig_qty_3 <-ifelse(lsb_ROTTERDAM_3$lsb_smk_cur_3==0, 0L, 
                                ifelse(ROTTERDAM_3$e6_EILF6A<76,ROTTERDAM_3$e6_EILF6A,
                                ifelse(ROTTERDAM_3$e6_EILF6A==76, 0L,NA)))
table(lsb_ROTTERDAM_3$lsb_cig_qty_3, useNA="always")

```  
### **Variable label**:  Quantity cigarettes smoked    
**Variable name**:  lsb_cig_qty_4   
**Variable description**:  Current average number of cigarettes smoked per day.  
**Value type**:  integer  
**Variable unit**:  cigarettes/day  
**Category coding**:  

**Harmonization status**:  impossible    
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
 

```  
### **Variable label**:  Quantity cigarettes smoked    
**Variable name**:  lsb_cig_qty_5   
**Variable description**:  Current average number of cigarettes smoked per day.  
**Value type**:  integer  
**Variable unit**:  cigarettes/day  
**Category coding**:  

**Harmonization status**:  impossible    
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
 

```  
### **Variable label**:  Quantity cigarettes smoked    
**Variable name**:  lsb_cig_qty_6   
**Variable description**:  Current average number of cigarettes smoked per day.  
**Value type**:  integer  
**Variable unit**:  cigarettes/day  
**Category coding**:  

**Harmonization status**:  impossible    
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
 

```  

### **Variable label**:  Smoking initiation age    
**Variable name**:  lsb_smk_start_0    
**Variable description**:  Age at which the participant started smoking any tobacco product.  
**Value type**:  integer  
**Variable unit**:  years  
**Category coding**:  

**Harmonization status**:      
**Harmonization comment**:   The study-specific questions are : How old were you when you first started smoking?  
**R script**:  
```{r, echo=TRUE}
 
table(ROTTERDAM_0$ep_lf6b)	
lsb_ROTTERDAM_0$lsb_smk_start_0 <- ifelse(ROTTERDAM_0$ep_lf6b<777, ROTTERDAM_0$ep_lf6b, ifelse(ROTTERDAM_0$ep_lf6g<777,  ROTTERDAM_0$ep_lf6g, NA ))
table(lsb_ROTTERDAM_0$lsb_smk_start_0)
```  
### **Variable label**:  Smoking initiation age    
**Variable name**:  lsb_smk_start_1    
**Variable description**:  Age at which the participant started smoking any tobacco product.  
**Value type**:  integer  
**Variable unit**:  years  
**Category coding**:  

**Harmonization status**:  impossible    
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
 


```  
### **Variable label**:  Smoking initiation age    
**Variable name**:  lsb_smk_start_2    
**Variable description**:  Age at which the participant started smoking any tobacco product.  
**Value type**:  integer  
**Variable unit**:  years  
**Category coding**:  

**Harmonization status**:  complete      
**Harmonization comment**:   The study-specific questions are : How old were you when you first started smoking?  
**R script**:  
```{r, echo=TRUE}
 #From the order of the questions, e5_EILF6B must be for current, and e5_EILFG must be for former smokers. Added to the excel notes sheet
table(ROTTERDAM_2$e5_EILF6B)	
table(ROTTERDAM_2$e5_EILFG)	

lsb_ROTTERDAM_2$lsb_smk_start_2 <- ifelse(ROTTERDAM_2$e5_EILF6B<777, ROTTERDAM_2$e5_EILF6B, ifelse(ROTTERDAM_2$e5_EILFG<777, ROTTERDAM_2$e5_EILFG, NA ))
table(lsb_ROTTERDAM_2$lsb_smk_start_2) 

```  
### **Variable label**:  Smoking initiation age    
**Variable name**:  lsb_smk_start_3    
**Variable description**:  Age at which the participant started smoking any tobacco product.  
**Value type**:  integer  
**Variable unit**:  years  
**Category coding**:  

**Harmonization status**:  impossible    
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
 

```  
### **Variable label**:  Smoking initiation age    
**Variable name**:  lsb_smk_start_4    
**Variable description**:  Age at which the participant started smoking any tobacco product.  
**Value type**:  integer  
**Variable unit**:  years  
**Category coding**:  

**Harmonization status**:  impossible    
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
 

```  
### **Variable label**:  Smoking initiation age    
**Variable name**:  lsb_smk_start_5    
**Variable description**:  Age at which the participant started smoking any tobacco product.  
**Value type**:  integer  
**Variable unit**:  years  
**Category coding**:  

**Harmonization status**:  impossible    
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
 

```  
### **Variable label**:  Smoking initiation age    
**Variable name**:  lsb_smk_start_6    
**Variable description**:  Age at which the participant started smoking any tobacco product.  
**Value type**:  integer  
**Variable unit**:  years  
**Category coding**:  

**Harmonization status**:  impossible    
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
 

```  

### **Variable label**:  Smoking cessation age  
**Variable name**:  lsb_smk_stop_0   
**Variable description**:  Age at which the participant last smoked any tobacco product.  
**Value type**:  integer  
**Variable unit**:  years  
**Category coding**:  

**Harmonization status**:  complete    
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
table(ROTTERDAM_0$ep_lf6h) 
lsb_ROTTERDAM_0$lsb_smk_stop_0 <- ifelse(ROTTERDAM_0$ep_lf6h<777, ROTTERDAM_0$ep_lf6h, NA )
table(lsb_ROTTERDAM_0$lsb_smk_stop_0)

```  
### **Variable label**:  Smoking cessation age  
**Variable name**:  lsb_smk_stop_1   
**Variable description**:  Age at which the participant last smoked any tobacco product.  
**Value type**:  integer  
**Variable unit**:  years  
**Category coding**:  

**Harmonization status**:  complete      
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
table(ROTTERDAM_1$e4_dictlps) 
lsb_ROTTERDAM_1$lsb_smk_stop_1 <- ifelse(ROTTERDAM_1$e4_dictlps<777, ROTTERDAM_1$e4_dictlps, NA )
table(lsb_ROTTERDAM_1$lsb_smk_stop_1)


```  
### **Variable label**:  Smoking cessation age  
**Variable name**:  lsb_smk_stop_2   
**Variable description**:  Age at which the participant last smoked any tobacco product.  
**Value type**:  integer  
**Variable unit**:  years  
**Category coding**:  

**Harmonization status**:  complete      
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
 

table(ROTTERDAM_2$e5_EILFH) 
lsb_ROTTERDAM_2$lsb_smk_stop_2 <- ifelse(ROTTERDAM_2$e5_EILFH<777, ROTTERDAM_2$e5_EILFH, NA )
table(lsb_ROTTERDAM_2$lsb_smk_stop_2)


```  
### **Variable label**:  Smoking cessation age  
**Variable name**:  lsb_smk_stop_3   
**Variable description**:  Age at which the participant last smoked any tobacco product.  
**Value type**:  integer  
**Variable unit**:  years  
**Category coding**:  

**Harmonization status**:  complete      
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
 	

table(ROTTERDAM_3$e6_EILFHE5) 
lsb_ROTTERDAM_3$lsb_smk_stop_3 <- ifelse(ROTTERDAM_3$e6_EILFHE5<777, ROTTERDAM_3$e6_EILFHE5, NA )
table(lsb_ROTTERDAM_3$lsb_smk_stop_3)



```  
### **Variable label**:  Smoking cessation age  
**Variable name**:  lsb_smk_stop_4   
**Variable description**:  Age at which the participant last smoked any tobacco product.  
**Value type**:  integer  
**Variable unit**:  years  
**Category coding**:  

**Harmonization status**:  impossible    
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
 

```  
### **Variable label**:  Smoking cessation age  
**Variable name**:  lsb_smk_stop_5   
**Variable description**:  Age at which the participant last smoked any tobacco product.  
**Value type**:  integer  
**Variable unit**:  years  
**Category coding**:  

**Harmonization status**:  impossible    
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
 

```  
### **Variable label**:  Smoking cessation age  
**Variable name**:  lsb_smk_stop_6   
**Variable description**:  Age at which the participant last smoked any tobacco product.  
**Value type**:  integer  
**Variable unit**:  years  
**Category coding**:  

**Harmonization status**:  impossible    
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
 

```  

### **Variable label**:  Pack years  
**Variable name**:  lsb_smk_py_0    
**Variable description**:  Number of estimated pack years of the participant.   
**Value type**:  decimal    
**Variable unit**:  pack-years    
**Category coding**:  

**Harmonization status**:  impossible    
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
 

```  
### **Variable label**:  Pack years  
**Variable name**:  lsb_smk_py_1    
**Variable description**:  Number of estimated pack years of the participant.     
**Value type**:  decimal    
**Variable unit**:  pack-years    
**Category coding**:  

**Harmonization status**:  impossible    
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
 

```  
### **Variable label**:  Pack years  
**Variable name**:  lsb_smk_py_2    
**Variable description**:  Number of estimated pack years of the participant.     
**Value type**:  decimal    
**Variable unit**:  pack-years    
**Category coding**:  

**Harmonization status**:  impossible    
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
 

```  

# Physical activity subdomain

### **Variable label**: Frequency of walking    
**Variable name**:    lsb_pa_walk_freq_0    
**Variable description**:  Number of times the participant went for a walk in last week.    
**Value type**:  integer  
**Variable unit**:  N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 |  Never  
1 |  Seldom (1-2 days)  
2 |  Sometimes (3-4 days)  
3 |  Often (5-7 days)  

**Harmonization status**:  impossible    
**Harmonization comment**:   The study-specific variable asks the minutes the participants spent walking during the week, instead of the number of times. 
**R script**:  
```{r, echo=TRUE}
# ROTTERDAM_0$ep_piwalksm 
# ROTTERDAM_0$ep_piwalkwm

```  
### **Variable label**: Frequency of walking    
**Variable name**:    lsb_pa_walk_freq_1    
**Variable description**:  Number of times the participant went for a walk in last week.    
**Value type**:  integer  
**Variable unit**:  N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 |  Never  
1 |  Seldom (1-2 days)  
2 |  Sometimes (3-4 days)  
3 |  Often (5-7 days)  

**Harmonization status**:  impossible    
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
 

```  
### **Variable label**: Frequency of walking    
**Variable name**:    lsb_pa_walk_freq_2    
**Variable description**:  Number of times the participant went for a walk in last week.    
**Value type**:  integer  
**Variable unit**:  N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 |  Never  
1 |  Seldom (1-2 days)  
2 |  Sometimes (3-4 days)  
3 |  Often (5-7 days)    

**Harmonization status**:  impossible    
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
 

```  
### **Variable label**: Frequency of walking    
**Variable name**:    lsb_pa_walk_freq_3    
**Variable description**:  Number of times the participant went for a walk in last week.    
**Value type**:  integer  
**Variable unit**:  N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 |  Never  
1 |  Seldom (1-2 days)  
2 |  Sometimes (3-4 days)  
3 |  Often (5-7 days)    

**Harmonization status**:  impossible    
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
 

```  
### **Variable label**: Frequency of walking    
**Variable name**:    lsb_pa_walk_freq_4    
**Variable description**:  Number of times the participant went for a walk in last week.    
**Value type**:  integer  
**Variable unit**:  N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 |  Never  
1 |  Seldom (1-2 days)  
2 |  Sometimes (3-4 days)  
3 |  Often (5-7 days)    

**Harmonization status**:  impossible    
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
 

```  
### **Variable label**: Frequency of walking    
**Variable name**:    lsb_pa_walk_freq_5    
**Variable description**:  Number of times the participant went for a walk in last week.    
**Value type**:  integer  
**Variable unit**:  N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 |  Never  
1 |  Seldom (1-2 days)  
2 |  Sometimes (3-4 days)  
3 |  Often (5-7 days)    

**Harmonization status**:  impossible    
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
 

```  
### **Variable label**: Frequency of walking    
**Variable name**:    lsb_pa_walk_freq_6    
**Variable description**:  Number of times the participant went for a walk in last week.    
**Value type**:  integer  
**Variable unit**:  N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 |  Never  
1 |  Seldom (1-2 days)  
2 |  Sometimes (3-4 days)  
3 |  Often (5-7 days)    

**Harmonization status**:  impossible    
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
 

```  

### **Variable label**:  Average walking time     
**Variable name**:   lsb_pa_walk_time_0  
**Variable description**:  Average time the participant spends walking per day.    
**Value type**:  integer  
**Variable unit**:  N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 |  Less than 30 minutes  
1 |  30 minutes but less than 1 hour  
2 |  1 hour but less than 2 hours
3 |  2 hours but less than 4 hours  
4 |  4 hours or more  

**Harmonization status**:  complete      
**Harmonization comment**: Two study-specific variables: "How much time do you usually spend walking per week in the winter? With walking we mean all kind of walking, including walking to go shopping." and "How much time do you usually spend walking per week in the summer? With walking we mean all kind of walking, including walking to go shopping." were used to harmonize the DataSchema variable. The average of these study-specific variables were taken. 
**R script**:  
```{r, echo=TRUE}
#99.99 is not listed as missing. Is it correct?

table(ROTTERDAM_0$ep_piwalksm, useNA="always" )
summary(ROTTERDAM_0$ep_piwalksm)
table(ROTTERDAM_0$ep_piwalkwm, useNA="always" )
table(ROTTERDAM_0$ep_piwalkwm+ROTTERDAM_0$ep_piwalksm, useNA="always" )

ROTTERDAM_0$ep_piwalkwm1<-ifelse(ROTTERDAM_0$ep_piwalkwm==99.99, NA, ROTTERDAM_0$ep_piwalkwm)
ROTTERDAM_0$ep_piwalksm1<-ifelse(ROTTERDAM_0$ep_piwalksm==99.99, NA, ROTTERDAM_0$ep_piwalksm)

ROTTERDAM_0$lsb_pa_walk_time_0 <-(ROTTERDAM_0$ep_piwalkwm1+ROTTERDAM_0$ep_piwalksm1)/2  
table(ROTTERDAM_0$lsb_pa_walk_time_0)
lsb_ROTTERDAM_0$lsb_pa_walk_time_0<-ifelse(ROTTERDAM_0$lsb_pa_walk_time_0<0.5, 0L,
                                       ifelse(ROTTERDAM_0$lsb_pa_walk_time_0>=0.5 &ROTTERDAM_0$lsb_pa_walk_time_0<1,1L,
                                           ifelse(ROTTERDAM_0$lsb_pa_walk_time_0>=1 &ROTTERDAM_0$lsb_pa_walk_time_0<2,2L,
                                                  ifelse(ROTTERDAM_0$lsb_pa_walk_time_0>=2 &ROTTERDAM_0$lsb_pa_walk_time_0<4,3L,
                                                         ifelse(ROTTERDAM_0$lsb_pa_walk_time_0>4,4L, NA)))))
table(lsb_ROTTERDAM_0$lsb_pa_walk_time_0, useNA = "always")
```  
### **Variable label**:  Average walking time   
**Variable name**:   lsb_pa_walk_time_1  
**Variable description**:  Average time the participant spends walking per day.    
**Value type**:  integer  
**Variable unit**:  N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 |  Less than 30 minutes  
1 |  30 minutes but less than 1 hour  
2 |  1 hour but less than 2 hours
3 |  2 hours but less than 4 hours  
4 |  4 hours or more   

**Harmonization status**:  impossible    
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
 

```  
### **Variable label**:  Average walking time    
**Variable name**:   lsb_pa_walk_time_2  
**Variable description**:  Average time the participant spends walking per day.    
**Value type**:  integer  
**Variable unit**:  N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 |  Less than 30 minutes  
1 |  30 minutes but less than 1 hour  
2 |  1 hour but less than 2 hours
3 |  2 hours but less than 4 hours  
4 |  4 hours or more   

**Harmonization status**:  impossible    
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
 

```  
### **Variable label**:  Average walking time     
**Variable name**:   lsb_pa_walk_time_3  
**Variable description**:  Average time the participant spends walking per day.    
**Value type**:  integer  
**Variable unit**:  N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 |  Less than 30 minutes  
1 |  30 minutes but less than 1 hour  
2 |  1 hour but less than 2 hours
3 |  2 hours but less than 4 hours  
4 |  4 hours or more   

**Harmonization status**:  impossible    
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
 

```  
### **Variable label**:  Average walking time    
**Variable name**:   lsb_pa_walk_time_4  
**Variable description**:  Average time the participant spends walking per day.    
**Value type**:  integer  
**Variable unit**:  N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 |  Less than 30 minutes  
1 |  30 minutes but less than 1 hour  
2 |  1 hour but less than 2 hours
3 |  2 hours but less than 4 hours  
4 |  4 hours or more     

**Harmonization status**:  impossible    
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
 

```  
### **Variable label**:  Average walking time     
**Variable name**:   lsb_pa_walk_time_5  
**Variable description**:  Average time the participant spends walking per day.    
**Value type**:  integer  
**Variable unit**:  N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 |  Less than 30 minutes  
1 |  30 minutes but less than 1 hour  
2 |  1 hour but less than 2 hours
3 |  2 hours but less than 4 hours  
4 |  4 hours or more     

**Harmonization status**:  impossible    
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
 

```  
### **Variable label**:  Average walking time     
**Variable name**:   lsb_pa_walk_time_6  
**Variable description**:  Average time the participant spends walking per day.    
**Value type**:  integer  
**Variable unit**:  N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 |  Less than 30 minutes  
1 |  30 minutes but less than 1 hour  
2 |  1 hour but less than 2 hours
3 |  2 hours but less than 4 hours  
4 |  4 hours or more    

**Harmonization status**:  impossible    
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
 

```  

### **Variable label**:  Average walking time for transportation  
**Variable name**:  lsb_pa_walk_trans_0    
**Variable description**:  Minutes per week the participant spent on walking for transportation (utilitarian walking) in the last week.  
**Value type**:  decimal    
**Variable unit**:  minutes/week  
**Category coding**:  N/A  

**Harmonization status**:  impossible    
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
 

```  
### **Variable label**:  Average walking time for transportation    
**Variable name**:  lsb_pa_walk_trans_1    
**Variable description**: Minutes per week the participant spent on walking for transportation (utilitarian walking) in the last week.    
**Value type**:  decimal      
**Variable unit**:  minutes/week  
**Category coding**:  N/A  

**Harmonization status**:  impossible    
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
 

```  
### **Variable label**:  Average walking time for transportation    
**Variable name**:  lsb_pa_walk_trans_2    
**Variable description**:  Minutes per week the participant spent on walking for transportation (utilitarian walking) in the last week.  
**Value type**:  decimal      
**Variable unit**:  minutes/week  
**Category coding**:  N/A  

**Harmonization status**:  impossible    
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
 

```  
### **Variable label**:  Average walking time for transportation    
**Variable name**:  lsb_pa_walk_trans_3    
**Variable description**:  Minutes per week the participant spent on walking for transportation (utilitarian walking) in the last week.  
**Value type**:  decimal      
**Variable unit**:  minutes/week  
**Category coding**:  N/A  

**Harmonization status**:  impossible    
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
 

```  
### **Variable label**:  Average walking time for transportation    
**Variable name**:  lsb_pa_walk_trans_4    
**Variable description**:  Minutes per week the participant spent on walking for transportation (utilitarian walking) in the last week.    
**Value type**:  decimal      
**Variable unit**:  minutes/week  
**Category coding**:  N/A  

**Harmonization status**:  impossible    
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
 

```  

### **Variable label**:  Average walking time for leisure  
**Variable name**:  lsb_pa_walk_leis_0    
**Variable description**:  Minutes per week the participant spent on walking for leisure in the last week.  
**Value type**:  decimal      
**Variable unit**:  minutes/week  
**Category coding**:  N/A  

**Harmonization status**:  impossible    
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
 

```  
### **Variable label**:  Average walking time for leisure  
**Variable name**:  lsb_pa_walk_leis_1    
**Variable description**:  Minutes per week the participant spent on walking for leisure in the last week.  
**Value type**:  decimal      
**Variable unit**:  minutes/week  
**Category coding**:  N/A  

**Harmonization status**:  impossible    
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
 

```  
### **Variable label**:  Average walking time for leisure  
**Variable name**:  lsb_pa_walk_leis_2    
**Variable description**:  Minutes per week the participant spent on walking for leisure in the last week.  
**Value type**:  decimal      
**Variable unit**:  minutes/week  
**Category coding**:  N/A  

**Harmonization status**:  impossible    
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
 

```  
### **Variable label**:  Average walking time for leisure  
**Variable name**:  lsb_pa_walk_leis_3    
**Variable description**:  Minutes per week the participant spent on walking for leisure in the last week.  
**Value type**:  decimal      
**Variable unit**:  minutes/week  
**Category coding**:  N/A  

**Harmonization status**:  impossible    
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
 

```  
### **Variable label**:  Average walking time for leisure  
**Variable name**:  lsb_pa_walk_leis_4    
**Variable description**:  Minutes per week the participant spent on walking for leisure in the last week.  
**Value type**:  decimal      
**Variable unit**:  minutes/week  
**Category coding**:  N/A  

**Harmonization status**:  impossible    
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
 

```  

### **Variable label**:  Average cycling time    
**Variable name**:  lsb_pa_cycle_0  
**Variable description**:  Average minutes per week the participant spent on cycling in the last week.  
**Value type**:  decimal      
**Variable unit**:  minutes/week  
**Category coding**:  N/A  

**Harmonization status**:  impossible    
**Harmonization comment**:    Two study-specific variables: "How many times do you cycle per week in the summer?" and "How many times do you cycle per week in the winter?" averaged to harmonize this variable
**R script**:  
```{r, echo=TRUE}
table(ROTTERDAM_0$ep_picyclsm)
table(ROTTERDAM_0$ep_picyclwm)

table(ROTTERDAM_0$ep_picyclsm, useNA="always" )
table(ROTTERDAM_0$ep_picyclwm, useNA="always" )

ROTTERDAM_0$ep_picyclsm1<-ifelse(ROTTERDAM_0$ep_picyclsm==99.99, NA, ROTTERDAM_0$ep_picyclsm)
ROTTERDAM_0$ep_picyclsm1<-ifelse(ROTTERDAM_0$ep_picyclsm==99.99, NA, ROTTERDAM_0$ep_picyclsm)

lsb_ROTTERDAM_0$lsb_pa_cycle_0 <-(ROTTERDAM_0$ep_picyclsm1+ROTTERDAM_0$ep_picyclsm1)*60/2  

table(lsb_ROTTERDAM_0$lsb_pa_cycle_0)

table(lsb_ROTTERDAM_0$lsb_pa_cycle_0 , useNA = "always")
```  
### **Variable label**:  Average cycling time    
**Variable name**:  lsb_pa_cycle_1  
**Variable description**:  Average minutes per week the participant spent on cycling in the last week.    
**Value type**:  decimal      
**Variable unit**:  minutes/week  
**Category coding**:  N/A  

**Harmonization status**:  impossible    
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
 

```  
### **Variable label**:  Average cycling time    
**Variable name**:  lsb_pa_cycle_2  
**Variable description**:  Average minutes per week the participant spent on cycling in the last week.    
**Value type**:  decimal      
**Variable unit**:  minutes/week  
**Category coding**:  N/A  

**Harmonization status**:  impossible    
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
 

```  
### **Variable label**:  Average cycling time    
**Variable name**:  lsb_pa_cycle_3  
**Variable description**:  Average minutes per week the participant spent on cycling in the last week.    
**Value type**:  decimal      
**Variable unit**:  minutes/week  
**Category coding**:  N/A  

**Harmonization status**:  impossible    
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
 

```  
### **Variable label**:  Average cycling time    
**Variable name**:  lsb_pa_cycle_4  
**Variable description**:  Average minutes per week the participant spent on cycling in the last week.    
**Value type**:  decimal      
**Variable unit**:  minutes/week  
**Category coding**:  N/A  

**Harmonization status**:  impossible    
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
 

```  
### **Variable label**:  Average cycling time    
**Variable name**:  lsb_pa_cycle_5  
**Variable description**:  Average minutes per week the participant spent on cycling in the last week.    
**Value type**:  decimal      
**Variable unit**:  minutes/week  
**Category coding**:  N/A  

**Harmonization status**:  impossible    
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
 

```  
### **Variable label**:  Average cycling time    
**Variable name**:  lsb_pa_cycle_6  
**Variable description**:  Average minutes per week the participant spent on cycling in the last week.    
**Value type**:  decimal      
**Variable unit**:  minutes/week  
**Category coding**:  N/A  

**Harmonization status**:  impossible    
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
 

```  

### **Variable label**:  Gardening   
**Variable name**:  lsb_pa_garden_0  
**Variable description**:  Indicator of whether the participant does any gardening activities.  
**Value type**:  integer  
**Variable unit**:  N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 |   Does not do any gardening activities  
1 |   Does any gardening activities  

**Harmonization status**:  complete      
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
table(ROTTERDAM_0$ep_pigardsd)
table(ROTTERDAM_0$ep_pigardwd)


lsb_ROTTERDAM_0$lsb_pa_garden_0 <-ifelse(ROTTERDAM_0$ep_pigardsd==0&ROTTERDAM_0$ep_pigardwd==0, 0L,
                                         ifelse((ROTTERDAM_0$ep_pigardsd>0 & ROTTERDAM_0$ep_pigardsd<77)|
                                                  (ROTTERDAM_0$ep_pigardwd>0&ROTTERDAM_0$ep_pigardsd<77),1L, NA))

table(lsb_ROTTERDAM_0$lsb_pa_garden_0, useNA="always")

```  
### **Variable label**:  Gardening    
**Variable name**:  lsb_pa_garden_1  
**Variable description**:  Indicator of whether the participant does any gardening activities.  
**Value type**:  integer  
**Variable unit**:  N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 |   Does not do any gardening activities  
1 |   Does any gardening activities  

**Harmonization status**:  impossible    
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
 

```  
### **Variable label**:  Gardening    
**Variable name**:  lsb_pa_garden_2  
**Variable description**:  Indicator of whether the participant does any gardening activities.  
**Value type**:  integer  
**Variable unit**:  N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 |   Does not do any gardening activities  
1 |   Does any gardening activities  

**Harmonization status**:  impossible    
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
 

```  
### **Variable label**:  Gardening    
**Variable name**:  lsb_pa_garden_3  
**Variable description**:  Indicator of whether the participant does any gardening activities.  
**Value type**:  integer  
**Variable unit**:  N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 |   Does not do any gardening activities  
1 |   Does any gardening activities  

**Harmonization status**:  impossible    
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
 

```  
### **Variable label**:  Gardening    
**Variable name**:  lsb_pa_garden_4  
**Variable description**:  Indicator of whether the participant does any gardening activities.  
**Value type**:  integer  
**Variable unit**:  N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 |   Does not do any gardening activities  
1 |   Does any gardening activities  

**Harmonization status**:  impossible    
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
 

```  
### **Variable label**:  Gardening    
**Variable name**:  lsb_pa_garden_5  
**Variable description**:  Indicator of whether the participant does any gardening activities.  
**Value type**:  integer  
**Variable unit**:  N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 |   Does not do any gardening activities  
1 |   Does any gardening activities  

**Harmonization status**:  impossible    
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
 

```  
### **Variable label**:  Gardening    
**Variable name**:  lsb_pa_garden_6  
**Variable description**:  Indicator of whether the participant does any gardening activities.  
**Value type**:  integer  
**Variable unit**:  N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 |   Does not do any gardening activities  
1 |   Does any gardening activities  

**Harmonization status**:  impossible    
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
 

```  
### **Variable label**:  Average gardening time    
**Variable name**:  lsb_pa_garden_time_0    
**Variable description**:  Average minutes per week the participant spent on gardening activities in the last week.    
**Value type**:  decimal      
**Variable unit**:  minutes/week  
**Category coding**:  N/A  

**Harmonization status**:  impossible    
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
 

```  
### **Variable label**:  Average gardening time    
**Variable name**:  lsb_pa_garden_time_1    
**Variable description**:  Average minutes per week the participant spent on gardening activities in the last week.       
**Value type**:  decimal      
**Variable unit**:  minutes/week    
**Category coding**:  N/A  

**Harmonization status**:  impossible    
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
 

```  
### **Variable label**:  Average gardening time    
**Variable name**:  lsb_pa_garden_time_2    
**Variable description**:  Average minutes per week the participant spent on gardening activities in the last week.       
**Value type**:  decimal      
**Variable unit**:  minutes/week    
**Category coding**:  N/A  

**Harmonization status**:  impossible    
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
 

```  
### **Variable label**:  Average gardening time    
**Variable name**:  lsb_pa_garden_time_3    
**Variable description**:  Average minutes per week the participant spent on gardening activities in the last week.       
**Value type**:  decimal      
**Variable unit**:  minutes/week    
**Category coding**:  N/A  

**Harmonization status**:  impossible    
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}

 
```  
### **Variable label**:  Average gardening time    
**Variable name**:  lsb_pa_garden_time_4    
**Variable description**:  Average minutes per week the participant spent on gardening activities in the last week.       
**Value type**:  decimal      
**Variable unit**:  minutes/week    
**Category coding**:  N/A  

**Harmonization status**:  impossible    
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
 

```  
### **Variable label**:  Average gardening time    
**Variable name**:  lsb_pa_garden_time_5    
**Variable description**:  Average minutes per week the participant spent on gardening activities in the last week.       
**Value type**:  decimal      
**Variable unit**:  minutes/week    
**Category coding**:  N/A  

**Harmonization status**:  impossible    
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
 

```  
### **Variable label**:  Average gardening time    
**Variable name**:  lsb_pa_garden_time_6    
**Variable description**:  Average minutes per week the participant spent on gardening activities in the last week.       
**Value type**:  decimal      
**Variable unit**:  minutes/week    
**Category coding**:  N/A  

**Harmonization status**:  impossible    
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
 

```  

### **Variable label**:  Household activities  
**Variable name**:  lsb_pa_house_0  
**Variable description**:  Indicator of whether the participant does any household activities (light, moderate or vigorous).     
**Value type**:  integer  
**Variable unit**:  N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 |   Does not do any household activities  
1 |   Does any household activities  

**Harmonization status**:  complete     
**Harmonization comment**:   The study-specific variables 
"How much time per week do you usually spend on window cleaning?", "How much time per week do you usually spend light household tasks?",
"How much time per week do you usually spend on moderately heavy household tasks?" were used to harmonize the DataSchema variable. 

**R script**:  
```{r, echo=TRUE}

table(ROTTERDAM_0$ep_picdome1,useNA="always")
table(ROTTERDAM_0$ep_picdome2,useNA="always")
table(ROTTERDAM_0$ep_picdome3,useNA="always")

 	
lsb_ROTTERDAM_0$lsb_pa_garden_0 <-ifelse(ROTTERDAM_0$ep_picdome1==0&ROTTERDAM_0$ep_picdome2==0&ROTTERDAM_0$ep_picdome3==0, 0L,
                                         ifelse((ROTTERDAM_0$ep_picdome1>0 & ROTTERDAM_0$ep_picdome1<99)|
                                                  (ROTTERDAM_0$ep_picdome2>0&ROTTERDAM_0$ep_picdome2<99)|
                                                  (ROTTERDAM_0$ep_picdome3>0&ROTTERDAM_0$ep_picdome3<99),1L, NA))
table(lsb_ROTTERDAM_0$lsb_pa_garden_0, useNA="always")
```  
### **Variable label**:  Household activities  
**Variable name**:  lsb_pa_house_1  
**Variable description**:  Indicator of whether the participant does any household activities (light, moderate or vigorous).     
**Value type**:  integer  
**Variable unit**:  N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 |   Does not do any household activities  
1 |   Does any household activities  

**Harmonization status**:  impossible    
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
 

```  
### **Variable label**:  Household activities  
**Variable name**:  lsb_pa_house_2  
**Variable description**:  Indicator of whether the participant does any household activities (light, moderate or vigorous).     
**Value type**:  integer  
**Variable unit**:  N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 |   Does not do any household activities  
1 |   Does any household activities  

**Harmonization status**:  impossible    
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
 

```  
### **Variable label**:  Household activities  
**Variable name**:  lsb_pa_house_3  
**Variable description**:  Indicator of whether the participant does any household activities (light, moderate or vigorous).     
**Value type**:  integer  
**Variable unit**:  N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 |   Does not do any household activities  
1 |   Does any household activities  

**Harmonization status**:  impossible    
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
 

```  
### **Variable label**:  Household activities  
**Variable name**:  lsb_pa_house_4  
**Variable description**:  Indicator of whether the participant does any household activities (light, moderate or vigorous).     
**Value type**:  integer  
**Variable unit**:  N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 |   Does not do any household activities  
1 |   Does any household activities  

**Harmonization status**:  impossible    
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
 

```  
### **Variable label**:  Household activities  
**Variable name**:  lsb_pa_house_5  
**Variable description**:  Indicator of whether the participant does any household activities (light, moderate or vigorous).     
**Value type**:  integer  
**Variable unit**:  N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 |   Does not do any household activities  
1 |   Does any household activities  

**Harmonization status**:  impossible    
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
 

```  
### **Variable label**:  Household activities  
**Variable name**:  lsb_pa_house_6  
**Variable description**:  Indicator of whether the participant does any household activities (light, moderate or vigorous).     
**Value type**:  integer  
**Variable unit**:  N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 |   Does not do any household activities  
1 |   Does any household activities  

**Harmonization status**:  impossible    
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
 

```  

### **Variable label**:  Average household activities time      
**Variable name**:  lsb_pa_house_time_0  
**Variable description**:  Average minutes per week the participant spent doing household activities in last week.  
**Value type**:  decimal      
**Variable unit**:  minutes/week  
**Category coding**:  N/A  

**Harmonization status**:  complete     
**Harmonization comment**: "How much time per week do you usually spend on window cleaning?", "How much time per week do you usually spend light 
household tasks?",
"How much time per week do you usually spend on moderately heavy household tasks?" were used to harmonize the DataSchema variable.   
**R script**:  
```{r, echo=TRUE}
 
table(ROTTERDAM_0$ep_picdome1,useNA="always")
table(ROTTERDAM_0$ep_picdome2,useNA="always")
table(ROTTERDAM_0$ep_picdome3,useNA="always")


ROTTERDAM_0$ep_picdome1.<-ifelse(ROTTERDAM_0$ep_picdome1==99.99, NA, ROTTERDAM_0$ep_picdome1)
ROTTERDAM_0$ep_picdome2.<-ifelse(ROTTERDAM_0$ep_picdome2==99.99, NA, ROTTERDAM_0$ep_picdome2)
ROTTERDAM_0$ep_picdome3.<-ifelse(ROTTERDAM_0$ep_picdome3==99.99, NA, ROTTERDAM_0$ep_picdome3)

lsb_ROTTERDAM_0$lsb_pa_house_time_0 <-(ROTTERDAM_0$ep_picdome1.+ROTTERDAM_0$ep_picdome2.+ROTTERDAM_0$ep_picdome3.)*60/3  
table(lsb_ROTTERDAM_0$lsb_pa_house_time_0)
 	
table(lsb_ROTTERDAM_0$lsb_pa_house_time_0, useNA="always")

```  
### **Variable label**:  Average household activities time      
**Variable name**:  lsb_pa_house_time_1  
**Variable description**:  Average minutes per week the participant spent doing household activities in last week.  
**Value type**:  decimal      
**Variable unit**:  minutes/week  
**Category coding**:  N/A  

**Harmonization status**:  impossible    
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
 

```  
### **Variable label**:  Average household activities time      
**Variable name**:  lsb_pa_house_time_2  
**Variable description**:  Average minutes per week the participant spent doing household activities in last week.  
**Value type**:  decimal      
**Variable unit**:  minutes/week  
**Category coding**:  N/A  

**Harmonization status**:  impossible    
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
 

```  
### **Variable label**:  Average household activities time      
**Variable name**:  lsb_pa_house_time_3  
**Variable description**:  Average minutes per week the participant spent doing household activities in last week.  
**Value type**:  decimal      
**Variable unit**:  minutes/week  
**Category coding**:  N/A  

**Harmonization status**:  impossible    
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
 

```  
### **Variable label**:  Average household activities time      
**Variable name**:  lsb_pa_house_time_4  
**Variable description**:  Average minutes per week the participant spent doing household activities in last week.  
**Value type**:  decimal      
**Variable unit**:  minutes/week  
**Category coding**:  N/A  

**Harmonization status**:  impossible    
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
 

```  
### **Variable label**:  Average household activities time      
**Variable name**:  lsb_pa_house_time_5  
**Variable description**:  Average minutes per week the participant spent doing household activities in last week.  
**Value type**:  decimal      
**Variable unit**:  minutes/week  
**Category coding**:  N/A  

**Harmonization status**:  impossible    
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
 

```  
### **Variable label**:  Average household activities time      
**Variable name**:  lsb_pa_house_time_6  
**Variable description**:  Average minutes per week the participant spent doing household activities in last week.  
**Value type**:  decimal      
**Variable unit**:  minutes/week  
**Category coding**:  N/A  

**Harmonization status**:  impossible    
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
 

```  
### **Variable label**: Sports or exercise      
**Variable name**:  lsb_pa_sport_0  
**Variable description**:  Indicator of whether the participant does any sports or exercise.  
**Value type**:  integer  
**Variable unit**:  N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 |  Does not do any sports or exercise   
1 |  Does any sports or exercise

**Harmonization status**:  complete     
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
table(ROTTERDAM_0$ep_pisport, useNA = "always")
table(ROTTERDAM_0$ep_piball)
table(ROTTERDAM_0$ep_pisport, ROTTERDAM_0$ep_piball)

lsb_ROTTERDAM_0$lsb_pa_sport_0 <- ifelse(ROTTERDAM_0$ep_pisport==1,1L, ifelse(ROTTERDAM_0$ep_pisport==0,0L,NA))
table(lsb_ROTTERDAM_0$lsb_pa_sport_0, useNA="always")

```   
### **Variable label**: Sports or exercise      
**Variable name**:  lsb_pa_sport_1  
**Variable description**:  Indicator of whether the participant does any sports or exercise.  
**Value type**:  integer  
**Variable unit**:  N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 |  Does not do any sports or exercise   
1 |  Does any sports or exercise

**Harmonization status**:  impossible    
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
 

```   
### **Variable label**: Sports or exercise      
**Variable name**:  lsb_pa_sport_2  
**Variable description**:  Indicator of whether the participant does any sports or exercise.  
**Value type**:  integer  
**Variable unit**:  N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 |  Does not do any sports or exercise   
1 |  Does any sports or exercise

**Harmonization status**:  impossible    
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
 

```   
### **Variable label**: Sports or exercise      
**Variable name**:  lsb_pa_sport_3  
**Variable description**:  Indicator of whether the participant does any sports or exercise.  
**Value type**:  integer  
**Variable unit**:  N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 |  Does not do any sports or exercise   
1 |  Does any sports or exercise

**Harmonization status**:  impossible    
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
 

```   
### **Variable label**: Sports or exercise      
**Variable name**:  lsb_pa_sport_4  
**Variable description**:  Indicator of whether the participant does any sports or exercise.  
**Value type**:  integer  
**Variable unit**:  N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 |  Does not do any sports or exercise   
1 |  Does any sports or exercise

**Harmonization status**:  impossible    
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
 

```   
### **Variable label**: Sports or exercise      
**Variable name**:  lsb_pa_sport_5  
**Variable description**:  Indicator of whether the participant does any sports or exercise.  
**Value type**:  integer  
**Variable unit**:  N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 |  Does not do any sports or exercise   
1 |  Does any sports or exercise

**Harmonization status**:  impossible    
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
 

```   
### **Variable label**: Sports or exercise      
**Variable name**:  lsb_pa_sport_6  
**Variable description**:  Indicator of whether the participant does any sports or exercise.  
**Value type**:  integer  
**Variable unit**:  N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 |  Does not do any sports or exercise   
1 |  Does any sports or exercise

**Harmonization status**:  impossible    
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
 

```   

### **Variable label**:  Average sports or exercise time       
**Variable name**:  lsb_pa_sport_time_0  
**Variable description**:  Average time a week the participant spent on sports or exercise.    
**Value type**: integer  
**Variable unit**:  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 |  never   
1 |  less than 1 hour a week   
2 |  between 1 and 2 hours a week   
3 |  more than 2 hours a week  

**Harmonization status**:  complete      
**Harmonization comment**: The study-specific variables about whether the participant participate in one of the listed forms of sport or exercise and how many hours they spent doing it are used. The-study specific variables ask about the following exercises:
a ball game,  moving to music, Playing billiards, Dancing, Gymnastics, Stretching exercises, Rowing, Ice skating, Playing shuffleboard, Tennis, Swimming, Another sport.
If a participant reported that he participates in any 2 of these exercises for less than an hour a week each, they are coded under the DataSchema category "between 1 and 2 hours a week".  

**R script**:  
```{r, echo=TRUE}
table(ROTTERDAM_0$ep_piball)
table(ROTTERDAM_0$ep_piballd., useNA= "always")


sprt_ROTTERDAM_0 <- data.frame(id = ROTTERDAM_0$id)

sprt_ROTTERDAM_0$ep_piballd.<- ifelse(ROTTERDAM_0$ep_pisport==0|ROTTERDAM_0$ep_piball==0, 0, 
                                      ifelse(ROTTERDAM_0$ep_piballd==0, 0.5, 
                                             ifelse(ROTTERDAM_0$ep_piballd>77, NA, ROTTERDAM_0$ep_piballd)))

sprt_ROTTERDAM_0$ep_pimoved.<- ifelse(ROTTERDAM_0$ep_pisport==0|ROTTERDAM_0$ep_pimove==0, 0,
                                      ifelse(ROTTERDAM_0$ep_pimoved==0, 0.5, 
                                             ifelse(ROTTERDAM_0$ep_pimoved>=77, NA, ROTTERDAM_0$ep_pimoved)))

sprt_ROTTERDAM_0$ep_pidancd.<- ifelse(ROTTERDAM_0$ep_pisport==0|ROTTERDAM_0$ep_pidanc==0, 0, 
                                      ifelse(ROTTERDAM_0$ep_pidancd==0, 0.5,
                                             ifelse(ROTTERDAM_0$ep_pidancd>=77, NA,  ROTTERDAM_0$ep_pidancd)))

sprt_ROTTERDAM_0$ep_pibilld.<- ifelse(ROTTERDAM_0$ep_pisport==0|ROTTERDAM_0$ep_pibill==0, 0,
                                      ifelse(ROTTERDAM_0$ep_pibilld==0, 0.5,
                                             ifelse(ROTTERDAM_0$ep_pibilld>=77, NA, ROTTERDAM_0$ep_pibilld)))

sprt_ROTTERDAM_0$ep_pigymd. <- ifelse(ROTTERDAM_0$ep_pisport==0|ROTTERDAM_0$ep_pigym== 0, 0,
                                      ifelse(ROTTERDAM_0$ep_pigymd==0, 0.5,
                                             ifelse(ROTTERDAM_0$ep_pigymd >=77, NA, ROTTERDAM_0$ep_pigymd)))

sprt_ROTTERDAM_0$ep_pistred.<- ifelse(ROTTERDAM_0$ep_pisport==0|ROTTERDAM_0$ep_pistre==0, 0,
                                      ifelse(ROTTERDAM_0$ep_pistred==0, 0.5,
                                             ifelse(ROTTERDAM_0$ep_pistred>=77, NA, ROTTERDAM_0$ep_pistred)))

sprt_ROTTERDAM_0$ep_pirowd. <- ifelse(ROTTERDAM_0$ep_pisport==0|ROTTERDAM_0$ep_pirow== 0, 0, 
                                      ifelse(ROTTERDAM_0$ep_pirowd==0, 0.5,
                                             ifelse(ROTTERDAM_0$ep_pirowd >=77, NA, ROTTERDAM_0$ep_pirowd)))

sprt_ROTTERDAM_0$ep_piskatd.<- ifelse(ROTTERDAM_0$ep_pisport==0|ROTTERDAM_0$ep_piskat==0, 0, 
                                      ifelse(ROTTERDAM_0$ep_piskatd==0, 0.5,
                                             ifelse(ROTTERDAM_0$ep_piskatd>=77, NA, ROTTERDAM_0$ep_piskatd)))

sprt_ROTTERDAM_0$ep_pishovd.<- ifelse(ROTTERDAM_0$ep_pisport==0|ROTTERDAM_0$ep_pishov==0, 0, 
                                      ifelse(ROTTERDAM_0$ep_pishovd==0, 0.5,
                                             ifelse(ROTTERDAM_0$ep_pishovd>=77, NA, ROTTERDAM_0$ep_pishovd)))

sprt_ROTTERDAM_0$ep_pitennd.<- ifelse(ROTTERDAM_0$ep_pisport==0|ROTTERDAM_0$ep_pitenn==0, 0,
                                      ifelse(ROTTERDAM_0$ep_pitennd==0, 0.5,
                                             ifelse(ROTTERDAM_0$ep_pitennd>=77, NA, ROTTERDAM_0$ep_pitennd)))

sprt_ROTTERDAM_0$ep_piswimd.<- ifelse(ROTTERDAM_0$ep_pisport==0|ROTTERDAM_0$ep_piswim==0, 0,
                                      ifelse(ROTTERDAM_0$ep_piswimd==0, 0.5,
                                             ifelse(ROTTERDAM_0$ep_piswimd>=77, NA, ROTTERDAM_0$ep_piswimd)))

sprt_ROTTERDAM_0$ep_pispotd.<- ifelse(ROTTERDAM_0$ep_pisport==0|ROTTERDAM_0$ep_pispot==0, 0, 
                                      ifelse(ROTTERDAM_0$ep_pispotd==0, 0.5,
                                             ifelse(ROTTERDAM_0$ep_pispotd>=77, NA, ROTTERDAM_0$ep_pispotd)))


sprt_ROTTERDAM_0$sport_time <- rowSums(sprt_ROTTERDAM_0[,2:13])

table(sprt_ROTTERDAM_0$sport_time, useNA = "always")

lsb_ROTTERDAM_0$lsb_pa_sport_time_0 <- ifelse(sprt_ROTTERDAM_0$sport_time==0,0L, 
                                              ifelse(sprt_ROTTERDAM_0$sport_time==0.5,1L, 
                                                     ifelse(sprt_ROTTERDAM_0$sport_time>=1& sprt_ROTTERDAM_0$sport_time<=2, 2L,
                                                            ifelse(sprt_ROTTERDAM_0$sport_time>2, 3L, NA))))

table(lsb_ROTTERDAM_0$lsb_pa_sport_time_0, useNA="always")                                              
                                              

```  
### **Variable label**:  Average sports or exercise time       
**Variable name**:  lsb_pa_sport_time_1  
**Variable description**:  Average time a week the participant spent on sports or exercise.    
**Value type**: integer    
**Variable unit**:  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 |  never   
1 |  less than 1 hour a week   
2 |  between 1 and 2 hours a week   
3 |  more than 2 hours a week   

**Harmonization status**:  impossible    
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
 

```  
### **Variable label**:  Average sports or exercise time       
**Variable name**:  lsb_pa_sport_time_2  
**Variable description**:  Average time a week the participant spent on sports or exercise.    
**Value type**: integer   
**Variable unit**:  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 |  never   
1 |  less than 1 hour a week   
2 |  between 1 and 2 hours a week   
3 |  more than 2 hours a week    

**Harmonization status**:  impossible    
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
 

```  
### **Variable label**:  Average sports or exercise time       
**Variable name**:  lsb_pa_sport_time_3  
**Variable description**:  Average time a week the participant spent on sports or exercise.    
**Value type**: integer    
**Variable unit**:  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 |  never   
1 |  less than 1 hour a week   
2 |  between 1 and 2 hours a week   
3 |  more than 2 hours a week    

**Harmonization status**:  impossible    
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
 

```  
### **Variable label**:  Average sports or exercise time       
**Variable name**:  lsb_pa_sport_time_4  
**Variable description**:  Average time a week the participant spent on sports or exercise.    
**Value type**: integer   
**Variable unit**:  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 |  never   
1 |  less than 1 hour a week   
2 |  between 1 and 2 hours a week   
3 |  more than 2 hours a week    

**Harmonization status**:  impossible    
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
 

```  
### **Variable label**:  Average sports or exercise time       
**Variable name**:  lsb_pa_sport_time_5  
**Variable description**:  Average time a week the participant spent on sports or exercise.    
**Value type**: integer   
**Variable unit**:  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 |  never   
1 |  less than 1 hour a week   
2 |  between 1 and 2 hours a week   
3 |  more than 2 hours a week    

**Harmonization status**:  impossible    
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
 

```  
### **Variable label**:  Average sports or exercise time       
**Variable name**:  lsb_pa_sport_time_6  
**Variable description**:  Average time a week the participant spent on sports or exercise.    
**Value type**: integer   
**Variable unit**:  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 |  never   
1 |  less than 1 hour a week   
2 |  between 1 and 2 hours a week   
3 |  more than 2 hours a week    

**Harmonization status**:  impossible    
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
 

```  

# Diet and nutrition subdomain

### **Variable label**:  Daily vegetable consumption  
**Variable name**:  lsb_veg_0    
**Variable description**:  Indicator of whether the participant currently consumes vegetables on a daily basis.   
**Value type**:  integer  
**Variable unit**:  N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 |   Does not consume vegetables on a daily basis  
1 |   Consumes vegetables on a daily basis  

**Harmonization status**:  impossible    
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
 

```  
### **Variable label**:  Daily vegetable consumption  
**Variable name**:  lsb_veg_1    
**Variable description**:  Indicator of whether the participant currently consumes vegetables on a daily basis.   
**Value type**:  integer  
**Variable unit**:  N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 |   Does not consume vegetables on a daily basis  
1 |   Consumes vegetables on a daily basis  

**Harmonization status**:  impossible    
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
 

```  
### **Variable label**:  Daily vegetable consumption  
**Variable name**:  lsb_veg_2    
**Variable description**:  Indicator of whether the participant currently consumes vegetables on a daily basis.   
**Value type**:  integer  
**Variable unit**:  N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 |   Does not consume vegetables on a daily basis  
1 |   Consumes vegetables on a daily basis  

**Harmonization status**:  impossible    
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
 

```  

### **Variable label**:  Daily fruit consumption  
**Variable name**:  lsb_fruit_0  
**Variable description**:  Indicator of whether the participant currently consumes fruit on a daily basis.   
**Value type**:  integer  
**Variable unit**:  N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 |   Does not consume fruit on a daily basis
1 |   Consumes fruit on a daily basis  

**Harmonization status**:  impossible    
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
 

```  
### **Variable label**:  Daily fruit consumption  
**Variable name**:  lsb_fruit_1  
**Variable description**:  Indicator of whether the participant currently consumes fruit on a daily basis.   
**Value type**:  integer  
**Variable unit**:  N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 |   Does not consume fruit on a daily basis
1 |   Consumes fruit on a daily basis  

**Harmonization status**:  impossible    
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
 

```  
### **Variable label**:  Daily fruit consumption  
**Variable name**:  lsb_fruit_2  
**Variable description**:  Indicator of whether the participant currently consumes fruit on a daily basis.   
**Value type**:  integer  
**Variable unit**:  N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 |   Does not consume fruit on a daily basis
1 |   Consumes fruit on a daily basis  

**Harmonization status**:  impossible    
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
 

```  

### **Variable label**:  Daily water consumption  
**Variable name**:  lsb_water_0    
**Variable description**:  Indicator of whether the participant drinks water on a daily basis.   
**Value type**:  integer  
**Variable unit**:  N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 |   Does not drink water on a daily basis
1 |   Drinks water on a daily basis

**Harmonization status**:  impossible    
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
 
# table(ROTTERDAM_0$WATER_TOT_sum_RS_II1)
```  
### **Variable label**:  Daily water consumption  
**Variable name**:  lsb_water_1    
**Variable description**:  Indicator of whether the participant drinks water on a daily basis.   
**Value type**:  integer  
**Variable unit**:  N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 |   Does not drink water on a daily basis
1 |   Drinks water on a daily basis

**Harmonization status**:  impossible    
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
 

```  
### **Variable label**:  Daily water consumption  
**Variable name**:  lsb_water_2    
**Variable description**:  Indicator of whether the participant drinks water on a daily basis.   
**Value type**:  integer  
**Variable unit**:  N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 |   Does not drink water on a daily basis
1 |   Drinks water on a daily basis

**Harmonization status**:  impossible    
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
 

```  
### **Variable label**:  Daily water consumption  
**Variable name**:  lsb_water_3    
**Variable description**:  Indicator of whether the participant drinks water on a daily basis.   
**Value type**:  integer  
**Variable unit**:  N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 |   Does not drink water on a daily basis
1 |   Drinks water on a daily basis

**Harmonization status**:  impossible    
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
 

```  
### **Variable label**:  Daily water consumption  
**Variable name**:  lsb_water_4    
**Variable description**:  Indicator of whether the participant drinks water on a daily basis.   
**Value type**:  integer  
**Variable unit**:  N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 |   Does not drink water on a daily basis
1 |   Drinks water on a daily basis

**Harmonization status**:  impossible    
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
 

```  

### **Variable label**:  Quantity daily coffee  
**Variable name**:  lsb_coffee_qty_0  
**Variable description**:  Current quantity of coffee the participant consumes per day.   
**Value type**:  integer  
**Variable unit**:  cups/day  
**Category coding**:  N/A  

**Harmonization status**:  impossible    
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}

table(ROTTERDAM_0$ep_lf1, ROTTERDAM_0$ep_lf1a, useNA = "always")
lsb_ROTTERDAM_0$lsb_coffee_qty_0  <- ifelse(ROTTERDAM_0$ep_lf1==0, 0L, ROTTERDAM_0$ep_lf1a)
table(lsb_ROTTERDAM_0$lsb_coffee_qty_0, useNA="always")

(ROTTERDAM_0$ep_coftot_RS2_1/ROTTERDAM_0$ep_lf1a)
```  
### **Variable label**:  Quantity daily coffee  
**Variable name**:  lsb_coffee_qty_1  
**Variable description**:  Current quantity of coffee the participant consumes per day.   
**Value type**:  integer  
**Variable unit**:  cups/day 
**Category coding**:  N/A  

**Harmonization status**:  impossible    
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
 
	
table(ROTTERDAM_1$e4_didcof, ROTTERDAM_1$e4_didcofn, useNA="always")
lsb_ROTTERDAM_1$lsb_coffee_qty_1 <- ifelse(ROTTERDAM_1$e4_didcof==0, 0L, ROTTERDAM_1$e4_didcofn)
table(lsb_ROTTERDAM_1$lsb_coffee_qty_1)


ROTTERDAM_1$e4_coftot_RS1_4/ROTTERDAM_1$e4_didcofn
ROTTERDAM_1$e4_coftot_RS1_4/125
```  
### **Variable label**:  Quantity daily coffee  
**Variable name**:  lsb_coffee_qty_2  
**Variable description**:  Current quantity of coffee the participant consumes per day.   
**Value type**:  integer  
**Variable unit**:  cups/day  
**Category coding**:  N/A  

**Harmonization status**:  complete    
**Harmonization comment**:  For this wave, only grams of coffee per day was available in the study. Looking at the previous waves for which both the grams/day and cups/day were available, the average cup size is taken to be 125 grams. The study-specific variable of grams of coffee per day for this wave was divided by 125 and rounded to calculate the cups of coffee the participant consumed per day.  
**R script**:  
```{r, echo=TRUE}
 
table(ROTTERDAM_2$e5_coftot, useNA="always")
(ROTTERDAM_2$e5_coftot/125)
table(round(ROTTERDAM_2$e5_coftot/125), useNA="always")
lsb_ROTTERDAM_2$lsb_coffee_qty_2<-round(ROTTERDAM_2$e5_coftot/125)

```  
### **Variable label**:  Quantity daily coffee  
**Variable name**:  lsb_coffee_qty_3  
**Variable description**:  Current quantity of coffee the participant consumes per day.   
**Value type**:  integer  
**Variable unit**:  cups/day 
**Category coding**:  N/A  

**Harmonization status**:  impossible    
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
 

```  
### **Variable label**:  Quantity daily coffee  
**Variable name**:  lsb_coffee_qty_4  
**Variable description**:  Current quantity of coffee the participant consumes per day.   
**Value type**:  integer  
**Variable unit**:  cups/day  
**Category coding**:  N/A  

**Harmonization status**:  impossible    
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
 

```  

# Sleep quality subdomain

### **Variable label**:  Average sleep hours  
**Variable name**:  lsb_sleep_hours_0  
**Variable description**:  Average number of hours the participant sleeps per night.  
**Value type**:  integer  
**Variable unit**:  hours/night  
**Category coding**:  N/A  

**Harmonization status**:  complete      
**Harmonization comment**: The study-specific variable "How many hours do you sleep or get rest per night?" is used in harmonization.  
**R script**:  
```{r, echo=TRUE}

table(ROTTERDAM_0$ep_pisleepn)
lsb_ROTTERDAM_0$lsb_sleep_hours_0 <-ifelse(ROTTERDAM_0$ep_pisleepn>77,NA, as.integer(round(ROTTERDAM_0$ep_pisleepn)))
table(lsb_ROTTERDAM_0$lsb_sleep_hours_0)

```  
### **Variable label**:  Average sleep hours  
**Variable name**:  lsb_sleep_hours_1  
**Variable description**:  Average number of hours the participant sleeps per night.  
**Value type**:  integer  
**Variable unit**:  hours/night   
**Category coding**:  N/A  

**Harmonization status**:  impossible    
**Harmonization comment**:   The study specific variable is "During the last month, how many hours of actual sleep did you get at night?"

**R script**:  
```{r, echo=TRUE}
 
table(ROTTERDAM_1$e4_dipsq4, useNA="always")
lsb_ROTTERDAM_1$lsb_sleep_hours_1 <-ifelse(ROTTERDAM_1$e4_dipsq4>=77,NA, as.integer(round(ROTTERDAM_1$e4_dipsq4)))
table(lsb_ROTTERDAM_1$lsb_sleep_hours_1)

```  
### **Variable label**:  Average sleep hours  
**Variable name**:  lsb_sleep_hours_2  
**Variable description**:  Average number of hours the participant sleeps per night.  
**Value type**:  integer  
**Variable unit**:  hours/night 
**Category coding**:  N/A  

**Harmonization status**:  complete      
**Harmonization comment**:   The study specific variable is "During the last month, how many hours of actual sleep did you get at night?"
**R script**:  
```{r, echo=TRUE}
 
lsb_ROTTERDAM_2$lsb_sleep_hours_2 <-ifelse(ROTTERDAM_2$e5_YIPSQ4>=77,NA, as.integer(round(ROTTERDAM_2$e5_YIPSQ4)))
table(lsb_ROTTERDAM_2$lsb_sleep_hours_2)

```  
### **Variable label**:  Average sleep hours  
**Variable name**:  lsb_sleep_hours_3  
**Variable description**:  Average number of hours the participant sleeps per night.  
**Value type**:  integer  
**Variable unit**:  hours/night
**Category coding**:  N/A  

**Harmonization status**:  complete      
**Harmonization comment**:  The study specific variable is "During the last month, how many hours of actual sleep did you get at night?"
**R script**:  
```{r, echo=TRUE}

lsb_ROTTERDAM_3$lsb_sleep_hours_3 <-ifelse(ROTTERDAM_3$e6_YIPSQ4>=77,NA, as.integer(round(ROTTERDAM_3$e6_YIPSQ4)))
table(lsb_ROTTERDAM_3$lsb_sleep_hours_3, useNA="always")

```  
### **Variable label**:  Average sleep hours  
**Variable name**:  lsb_sleep_hours_4    
**Variable description**:  Average number of hours the participant sleeps per night.  
**Value type**:  integer  
**Variable unit**:  hours/night   
**Category coding**:  N/A  

**Harmonization status**:  impossible    
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
 

```  
### **Variable label**:  Average sleep hours  
**Variable name**:  lsb_sleep_hours_5  
**Variable description**:  Average number of hours the participant sleeps per night.  
**Value type**:  integer  
**Variable unit**:  hours/night    
**Category coding**:  N/A  

**Harmonization status**:  impossible    
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
 

```  

### **Variable label**:  Difficulty falling asleep  
**Variable name**:  lsb_sleep_diff_0  
**Variable description**:  Indicator of whether the participant ever has any difficulty falling asleep.  
**Value type**:  integer  
**Variable unit**:  N/A  
**Category coding**:    

**Code** | **Category Label**  
------------- | -------------  
0 |  Never has difficulty falling asleep
1 |  Sometimes has difficulty falling asleep

**Harmonization status**:  impossible    
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
 
   
```  
### **Variable label**:  Difficulty falling asleep  
**Variable name**:  lsb_sleep_diff_1  
**Variable description**:  Indicator of whether the participant ever has any difficulty falling asleep.  
**Value type**:  integer  
**Variable unit**:  N/A  
**Category coding**:    

**Code** | **Category Label**  
------------- | -------------  
0 |  Never has difficulty falling asleep
1 |  Sometimes has difficulty falling asleep

**Harmonization status**:  complete      
**Harmonization comment**:  The study-specific variable is: "During the past month, how often have you had trouble sleeping because you cannot get to sleep within 30 minutes?"
**R script**:  
```{r, echo=TRUE}
 
table(ROTTERDAM_1$e4_dipsq5a, useNA="always")

lsb_ROTTERDAM_1$lsb_sleep_diff_1 <- ifelse(ROTTERDAM_1$e4_dipsq5a==0, 0L, ifelse(ROTTERDAM_1$e4_dipsq5a %in%c(1,2,3), 1L, NA))
table(lsb_ROTTERDAM_1$lsb_sleep_diff_1, useNA="always")

```  
### **Variable label**:  Difficulty falling asleep  
**Variable name**:  lsb_sleep_diff_2    
**Variable description**:  Indicator of whether the participant ever has any difficulty falling asleep.  
**Value type**:  integer  
**Variable unit**:  N/A  
**Category coding**:    

**Code** | **Category Label**  
------------- | -------------  
0 |  Never has difficulty falling asleep
1 |  Sometimes has difficulty falling asleep

**Harmonization status**:  complete      
**Harmonization comment**:  The study-specific variable is: "During the past month, how often have you had trouble sleeping because you cannot get to sleep within 30 minutes?"
**R script**:  
```{r, echo=TRUE}

table(ROTTERDAM_2$e5_YIPSQ5A, useNA="always")

lsb_ROTTERDAM_2$lsb_sleep_diff_2 <- ifelse(ROTTERDAM_2$e5_YIPSQ5A==0, 0L, ifelse(ROTTERDAM_2$e5_YIPSQ5A %in%c(1,2,3), 1L, NA))
table(lsb_ROTTERDAM_2$lsb_sleep_diff_2, useNA="always")

```  
### **Variable label**:  Difficulty falling asleep  
**Variable name**:  lsb_sleep_diff_3  
**Variable description**:  Indicator of whether the participant ever has any difficulty falling asleep.  
**Value type**:  integer  
**Variable unit**:  N/A  
**Category coding**:    

**Code** | **Category Label**  
------------- | -------------  
0 |  Never has difficulty falling asleep
1 |  Sometimes has difficulty falling asleep

**Harmonization status**:  complete      
**Harmonization comment**:  The study-specific variable is: "During the past month, how often have you had trouble sleeping because you cannot get to sleep within 30 minutes?"
**R script**:  
```{r, echo=TRUE}
 
table(ROTTERDAM_3$e6_YIPSQ5A, useNA="always")

lsb_ROTTERDAM_3$lsb_sleep_diff_3 <- ifelse(ROTTERDAM_3$e6_YIPSQ5A==0, 0L, ifelse(ROTTERDAM_3$e6_YIPSQ5A %in%c(1,2,3), 1L, NA))
table(lsb_ROTTERDAM_3$lsb_sleep_diff_3, useNA="always")
   
```  
### **Variable label**:  Difficulty falling asleep  
**Variable name**:  lsb_sleep_diff_4  
**Variable description**:  Indicator of whether the participant ever has any difficulty falling asleep.  
**Value type**:  integer  
**Variable unit**:  N/A  
**Category coding**:    

**Code** | **Category Label**  
------------- | -------------  
0 |  Never has difficulty falling asleep
1 |  Sometimes has difficulty falling asleep

**Harmonization status**:  impossible    
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
 
   
```  
### **Variable label**:  Difficulty falling asleep  
**Variable name**:  lsb_sleep_diff_5  
**Variable description**:  Indicator of whether the participant ever has any difficulty falling asleep.  
**Value type**:  integer  
**Variable unit**:  N/A  
**Category coding**:    

**Code** | **Category Label**  
------------- | -------------  
0 |  Never has difficulty falling asleep
1 |  Sometimes has difficulty falling asleep

**Harmonization status**:  impossible    
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
 
   
```  
