---
title: "Lifestyle and behaviours DataSchema"
output: html_document
---
# Table of Contents
1. [Alcohol consumption subdomain](#alcohol-consumption-subdomain)
2. [Tobacco consumption subdomain](#tobacco-consumption-subdomain)
3. [Physical activity subdomain](#physical-activity-subdomain)
4. [Diet and nutrition subdomain](#diet-and-nutrition-subdomain)
5. [Sleep quality subdomain](#sleep-quality-subdomain)

# Alcohol consumption subdomain

### **Variable label**:  Current consumption of alcohol  
**Variable name**: LSB_ALC_CUR  
**Variable description**:  Indicator of whether the participant currently consumes alcohol.  
**Value type**: integer  
**Variable unit**: N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 |  Does not currently consumes alcohol   
1 |  Currently consumes alcohol  

**Harmonization status**:  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
#This is where the R-script will be written

```

### **Variable label**:   Ever consumption of alcohol  
**Variable name**: LSB_ALC_EVER  
**Variable description**:  Indicator of whether the participant has ever consumed alcohol.  
**Value type**: integer  
**Variable unit**: N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 |   Never consumed alcohol  
1 |   Ever consumed alcohol  

**Harmonization status**:  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
#This is where the R-script will be written

```

### **Variable label**:   Frequency of binge drinking  
**Variable name**: LSB_ALC_BINGE  
**Variable description**:  Frequency of binge drinking.  
**Value type**: integer  
**Variable unit**: N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
1 |  Less than monthly  
2 |  Monthly   
3 |  Weekly  
4 |  (Almost) daily  

**Harmonization status**:  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
#This is where the R-script will be written

```

### **Variable label**:   Current quantity of alcohol consumed per week (total)  
**Variable name**: LSB_ALC_TOTAL  
**Variable description**:  Current quantity of alcoholic beverages consumed per week. The definition of quantity per drink may differ across studies.  
**Value type**: integer  
**Variable unit**: drinks per week  
**Category coding**:  N/A  

**Harmonization status**:  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
#This is where the R-script will be written

```

### **Variable label**:   Current quantity of wine consumed per week  
**Variable name**: LSB_ALC_WINE  
**Variable description**:  Current quantity of  wine consumed per week. The definition of quantity per drink may differ across studies.  
**Value type**: integer  
**Variable unit**: drinks per week  
**Category coding**:  N/A  

**Harmonization status**:  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
#This is where the R-script will be written

```

### **Variable label**:   Current quantity of beer consumed per week  
**Variable name**: LSB_ALC_BEER  
**Variable description**:  Current quantity of beer consumed per week. The definition of quantity per drink may differ across studies.  
**Value type**: integer  
**Variable unit**: drinks per week  
**Category coding**:  N/A  
 

**Harmonization status**:  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
#This is where the R-script will be written

```

### **Variable label**:   Current quantity of liquor consumed per week  
**Variable name**: LSB_ALC_LIQ  
**Variable description**:  Current quantity of liquor consumed per week. The definition of quantity per drink may differ across studies.  
**Value type**: integer  
**Variable unit**: drinks per week  
**Category coding**:  N/A  
 

**Harmonization status**:  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
#This is where the R-script will be written

```

# Tobacco consumption subdomain

### **Variable label**:  Current tobakko smoking  
**Variable name**:  LSB_SMOK_CUR  
**Variable description**:  Indicator of whether the participant currently smokes any tobacco product.  
**Value type**:  integer  
**Variable unit**:  N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 |   Does not smoked any tobacco product  
1 |   Currently smokes any tobacco product  

**Harmonization status**:  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
#This is where the R-script will be written

```

### **Variable label**:  Smoking status  
**Variable name**:  LSB_SMOK_CAT  
**Variable description**:  Smoking status.  
**Value type**:  integer  
**Variable unit**:  N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 |   Never smoker  
1 |   Former smoker  
3 |   Current smoker  

**Harmonization status**:  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
#This is where the R-script will be written

```

### **Variable label**:  Ever tobacco smoking  
**Variable name**:  LSB_SMOK_EVER  
**Variable description**:  Indicator of whether the participant has ever smoked any tobacco product.  
**Value type**:  integer  
**Variable unit**:  N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 |   Never smoked tobacco  
1 |   Ever smoked tobacco  

**Harmonization status**:  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
#This is where the R-script will be written

```

### **Variable label**:  Cigarettes smoked    
**Variable name**:  LSB_SMOK_CIG  
**Variable description**:  Current average number of cigarettes smoked per day.  
**Value type**:  integer  
**Variable unit**:  number of cigarettes per day  
**Category coding**:  

**Harmonization status**:  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
#This is where the R-script will be written

```

### **Variable label**:  Smoking initiation age    
**Variable name**:  LSB_SMOK_START  
**Variable description**:  Age at which the participant started smoking any tobacco product.  
**Value type**:  integer  
**Variable unit**:  age in years  
**Category coding**:  

**Harmonization status**:  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
#This is where the R-script will be written

```

### **Variable label**:  Smoking cessation age  
**Variable name**:  LSB_SMOK_STOP  
**Variable description**:  Age at which the participant last smoked any tobacco product.  
**Value type**:  integer  
**Variable unit**:  age in years  
**Category coding**:  

**Harmonization status**:  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
#This is where the R-script will be written

```

### **Variable label**:  Pack years  
**Variable name**:  LSB_SMOK_PY  
**Variable description**:  Pack years - equivalent of years smoking twenty cigarettes per day - NOTE: no differentiation in number of cigarettes across the smoking period.  
**Value type**:  integer  
**Variable unit**:  pack years (years smoking twenty cigarettes per day)  
**Category coding**:  

**Harmonization status**:  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
#This is where the R-script will be written

```

# Physical activity subdomain

### **Variable label**: Walking per week  
**Variable name**:    LSB_PA_WALK_DAYS  
**Variable description**:  Average days a week in which a participates walks.  
**Value type**:  integer  
**Variable unit**:  N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 |  never  
1 |  seldom (1-2 dyas)  
3 |  sometimes (3-4 days)  
4 |  often (5-7 days  

**Harmonization status**:  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
#This is where the R-script will be written

```

### **Variable label**:  Walking per day   
**Variable name**:   LSB_PA_WALK_TIME  
**Variable description**:  Average time a day spent walking.  
**Value type**:  integer  
**Variable unit**:  N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 |  less than 30 minutes  
1 |  30 minutes but less than 1 hour  
3 |  1 hour but less than 2 hours
4 |  2 hours but less than 4 hours  
5 |  4 hours or more  

**Harmonization status**:  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
#This is where the R-script will be written

```

### **Variable label**:  Walking for transport  
**Variable name**:  LSB_PA_WALK_TRANS  
**Variable description**:  Minutes per week spent on walking for transport (utilitarian wlaking).  
**Value type**:  integer  
**Variable unit**:  minutes per week  
**Category coding**:  N/A  

**Harmonization status**:  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
#This is where the R-script will be written

```

### **Variable label**:  Walking for leisure  
**Variable name**:  LSB_PA_WALK_LEIS  
**Variable description**:  Minutes per week spent on walking for leisure.  
**Value type**:  integer  
**Variable unit**:  minutes per week  
**Category coding**:  N/A  

**Harmonization status**:  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
#This is where the R-script will be written

```

### **Variable label**:  Cycling per week  
**Variable name**:  LSB_PA_CYCLE  
**Variable description**:  Minutes per week spent on cycling.  
**Value type**:  integer  
**Variable unit**:  minutes per week  
**Category coding**:  N/A  

**Harmonization status**:  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
#This is where the R-script will be written

```

### **Variable label**:  Does any gardening  
**Variable name**:  LSB_PA_GARD_ANY
**Variable description**:  Does any gardening activities that require some sort of physical activity.
**Value type**:  integer  
**Variable unit**:  N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 |   no, does not do any gardening activities  
1 |   yes, does any gardeing activities  

**Harmonization status**:  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
#This is where the R-script will be written

```

### **Variable label**:  Times spent gardening  
**Variable name**:  LSB_PA_GARD_TIME  
**Variable description**:  Minutes per week spend on gardening activities that require some sort of physical activity.  
**Value type**:  integer  
**Variable unit**:  minutes per week  
**Category coding**:  N/A  

**Harmonization status**:  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
#This is where the R-script will be written

```

### **Variable label**:  Does any household activities  
**Variable name**:  LSB_PA_HOUSE_ANY  
**Variable description**:  Does any household activities that require some sort of physical activity.   
**Value type**:  integer  
**Variable unit**:  N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 |   no, does not do any household activities  
1 |   yes, does any household activities  

**Harmonization status**:  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
#This is where the R-script will be written

```

### **Variable label**:  Times spent doing household activities      
**Variable name**:  LSB_PA_HOUSE_TIME  
**Variable description**:  Minutes per week spent on household activities that require some sort of physical activity.  
**Value type**:  integer  
**Variable unit**:  minutes per week  
**Category coding**:  N/A  

**Harmonization status**:  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
#This is where the R-script will be written

```

### **Variable label**:  Sports or exercise participation       
**Variable name**:  LSB_SPORT  
**Variable description**:  Time spent a week exercising or doing sport activities.  
**Value type**:  
**Variable unit**:  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 |  never   
1 |  less than 1 hour a week   
3 |  between 1 and 2 hours a week   
4 |  more than 2 hours a week  

**Harmonization status**:  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
#This is where the R-script will be written

```

# Diet and nutrition subdomain

### **Variable label**:  Daily vegetable consumption  
**Variable name**:  LSB_VEGETABLE  
**Variable description**:  Indicator of whether the participant currently consumes vegetables on a daily basis.   
**Value type**:  integer  
**Variable unit**:  N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 |   Does not consume vegetables on a daily basis
1 |   Consumes vegetables on a daily basis

**Harmonization status**:  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
#This is where the R-script will be written

```

### **Variable label**:  Daily fruit consumption  
**Variable name**:  LSB_FRUIT  
**Variable description**:  Indicator of whether the participant currently consumes fruit on a daily basis.   
**Value type**:  integer  
**Variable unit**:  N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 |   Does not consume fruit on a daily basis
1 |   Consumes fruit on a daily basis

**Harmonization status**:  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
#This is where the R-script will be written

```

### **Variable label**:  Daily water consumption  
**Variable name**:  LSB_WATER  
**Variable description**:  Indicator of whether the participant currently drinks water on a daily basis.   
**Value type**:  integer  
**Variable unit**:  N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 |   Does not drinks water on a daily basis
1 |   Drinks water on a daily basis

**Harmonization status**:  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
#This is where the R-script will be written

```

### **Variable label**:  Daily coffeee consumption  
**Variable name**:  LSB_WATER  
**Variable description**:  Current quantity of coffee consumed per day.   
**Value type**:  integer  
**Variable unit**:  cups per day  
**Category coding**:  N/A  

**Harmonization status**:  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
#This is where the R-script will be written

```

# Sleep quality subdomain

### **Variable label**:  Average hours of sleep per night  
**Variable name**:  LSB_SLEEP_HOURS  
**Variable description**:  Average hours of sleep per night.  
**Value type**:  integer  
**Variable unit**:  hours  
**Category coding**:  N/A  

**Harmonization status**:  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
#This is where the R-script will be written

```

### **Variable label**:  Difficulty falling a sleep  
**Variable name**:  LSB_SLEEP_FALLING  
**Variable description**:  Indicator of whether the participant ever has any diffulty falling a sleep.  
**Value type**:  integer  
**Variable unit**:  N/A  
**Category coding**:    

**Code** | **Category Label**  
------------- | -------------  
0 |  Never has difficulty falling a sleep
1 |  Sometimes has difficulty falling a sleep

**Harmonization status**:  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
#This is where the R-script will be written

```

### **Variable label**:  Having trouble sleeping  
**Variable name**:  LSB_SLEEP_TROUBLE  
**Variable description**:  Indicator of whether the participant has any trouble with sleeping.    
**Value type**:  integer  
**Variable unit**:  N/A  
**Category coding**:    

**Code** | **Category Label**  
------------- | -------------  
0 |  Has no trouble sleeping 
1 |  Has trouble sleeping 

**Harmonization status**:  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
#This is where the R-script will be written

```



