---
title: "Lifestyle and behaviours DataSchema"
output: html_document
---
# Connecting with Opal data server
## Login to server and assign study data
```{r, echo=FALSE}
#Load R libraries
library(opal)
library(tidyverse)
library(epiDisplay)
# Create an opal object with the login information
erasmus_opal <- opal.login()
#Login to Opal server and assign the content of the LUCAS table(s) to your RStudio environment
opal.assign.table.tibble(erasmus_opal, 'LASA1B', 'LASA.LASA1B',variables = list('bmvar24','bmvar27','bmvar26','bmvar28','bmvar29','bmvar31','bmvar35','bmvar34','bmvar33','blphya06','blphya09','blphya13','blphya11','blphya17','blphya15','blphya19','blphya21','blphya25','blphya24','blphya28','bcesd11','bqsleep2','bmvar44','bmvar41','bmvar38','bmvar32','blphya08','blphya14','blphya31','blphya35','blphya17','blphya15','blphya32','blphya36','blphya10','bmvar37','bage','blphya12','bqsleep1','bmvar37p','bmvar25'))
LASA1B <- opal.execute(erasmus_opal,'LASA1B')

opal.assign.table.tibble(erasmus_opal, 'LASA1C', 'LASA.LASA1C',variables = list('cmvar24','cmvar25a','cmvar351','cmvar353','cmvar352','cmvar34','cmvar33','cmvar32','cmvar351','cmvar31','clphya07','clphya09','clphya11','clphya10','clphya13','clphya12','clphya22','clphya24','clphya26','clphya21','clphya25','clphya28','ccesd11','cqsleep2','clphya08','clphya14','clphya32','clphya36','clphya17','clphya15','clphya14','cmvar24','cmvar28','cmvar29','cmvar36','cmvar351','clphya19','cqsleep1'))
LASA1C <- opal.execute(erasmus_opal,'LASA1C')

opal.assign.table.tibble(erasmus_opal, 'LASA1D', 'LASA.LASA1D',variables = list('dmalcohu','dmalcoh6','dmvar31','dmvar35','dmvar32','dmvar33','dmvar34','dmvar40','dmvar37','dlphya08','dlphya09','dlphya07','dlphya06','dlphya10','dlphya13','dlphya11','dlphya12','dlphya15','dlphya18','dlphya19','dlphya17','dlphya35','dlphya38','dlphya31','dmvar30','dlphya32','dlphya34','dlphya33','dlphya36','dlphya37','dcesd11','dqsleep2','dlphya14','dlphya32','dlphya36','dlphya17','dlphya15','dlphya14','dmalcohu','dqsleep1','dmvar38','dmalcohn','dmalcohd'))
LASA1D <- opal.execute(erasmus_opal,'LASA1D')

opal.assign.table.tibble(erasmus_opal, 'LASA1E', 'LASA.LASA1E',variables = list('emalcohu','emalcoh6','emvar32','emvar31','emvar33','emvar35','emvar34','elphya08','elphya07','elphya09','elphya06','elphya10','elphya13','elphya11','elphya12','elphya15','elphya18','elphya17','elphya19','elphya37','elphya36','elphya35','elphya34','elphya38','elphya32','elphya33','elphya31','ecesd11','eqsleep2','elphya14','elphya32','elphya36','elphya17','elphya15','elphya14','emalcohu','eqsleep1','emvar37','emalcohd','emalcohn'))
LASA1E <- opal.execute(erasmus_opal,'LASA1E')

opal.assign.table.tibble(erasmus_opal, 'LASA1F', 'LASA.LASA1F',variables = list('fmalcoh6','fmalcohd','fmalcohu','fmvar34','fmvar33','fmvar32','fmvar31','flphya08','flphya07','flphya09','flphya06','flphya10','flphya11','flphya13','flphya12','flphya18','flphya15','flphya17','flphya19','flphya37','flphya32','flphya33','flphya36','flphya34','flphya38','flphya31','flphya35','fcesd11','fqsleep2','flphya14','flphya32','flphya36','flphya17','flphya15','flphya14','fmalcohu','fqsleep1','fmvar35','fmvar37','fmalcohd','fmalcohn'))
LASA1F <- opal.execute(erasmus_opal,'LASA1F')

opal.assign.table.tibble(erasmus_opal, 'LASA1G', 'LASA.LASA1G',variables = list('gmalcoh6','gmalcohn','gmalcohu','gmvar34','gmvar33','gmvar31','gmvar32','glphya08','glphya07','glphya09','glphya06','glphya10','glphya13','glphya11','glphya12','glphya14','glphya17','glphya15','glphya18','glphya19','glphya36','glphya37','glphya34','glphya32','glphya33','glphya38','glphya31','glphya35','gcesd11','gqsleep2','gqsleep5','glphya14','glphya32','glphya36','glphya17','glphya15','glphya14','gmalcohu','gqsleep1','gmvar35','gmvar37','gmalcohd','gmalcohn'))
LASA1G <- opal.execute(erasmus_opal,'LASA1G')

opal.assign.table.tibble(erasmus_opal, 'LASA1H', 'LASA.LASA1H',variables = list('HMALCOHN','HMALCOH6','HMALCOHU','HMVAR34','HMVAR33','HMVAR31','HMVAR32','HLPHYA08','HLPHYA09','HLPHYA07','HLPHYA06','HLPHYA10','HLPHYA13','HLPHYA11','HLPHYA12','HLPHYA15','HLPHYA17','HLPHYA14','HLPHYA18','HLPHYA19','HLPHYA32','HLPHYA36','HLPHYA33','HLPHYA37','HLPHYA34','HLPHYA38','HLPHYA35','HLPHYA31','hcesd11','hqsleepm','hqsleep2','hqsleep5','hqsleeph','HLPHYA14','HLPHYA32','HLPHYA36','HLPHYA17','HLPHYA15','HLPHYA14','HMALCOHU','hqsleep1','HMVAR31','HMVAR37','HMVAR35','HMALCOHD','HMALCOHN'))
LASA1H <- opal.execute(erasmus_opal,'LASA1H')
```
## Assign participant id as first column of your harmonized dataframes
```{r, echo=FALSE}
lsb_LASA1_0<- data.frame(id = LASA1B$id)
lsb_LASA1_1<- data.frame(id= LASA1C$id)
lsb_LASA1_2<- data.frame(id= LASA1D$id)
lsb_LASA1_3<- data.frame(id= LASA1E$id)
lsb_LASA1_4<- data.frame(id= LASA1F$id)
lsb_LASA1_5<- data.frame(id= LASA1G$id)
lsb_LASA1_6<- data.frame(id= LASA1H$id)
```
## When you are done with your work, logout of Opal server
```{r, echo=FALSE}
opal.logout(erasmus_opal) 
```
# Table of Contents
1. [Alcohol consumption subdomain](#alcohol-consumption-subdomain)
2. [Tobacco consumption subdomain](#tobacco-consumption-subdomain)
3. [Physical activity subdomain](#physical-activity-subdomain)
4. [Diet and nutrition subdomain](#diet-and-nutrition-subdomain)
5. [Sleep quality subdomain](#sleep-quality-subdomain)

# Alcohol consumption subdomain

### **Variable label**:  Current consumption of alcohol  
**Variable name**: lsb_alc_cur_0  
**Variable description**:  Indicator of whether the participant currently consumes alcohol or has consumed alcohol in the past 12 months.  
**Value type**: integer  
**Variable unit**: N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 |  Does not currently consumes alcohol   
1 |  Currently consumes alcohol  

**Harmonization status**:  complete  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
lsb_LASA1_0$lsb_alc_cur_0 <- recode(as.integer(LASA1B$bmvar24), '1'=0L, '2'=1L, .default=NA_integer_)
#LASA1B$lsb_alc_cur_0 <- recode(as.integer(LASA1B$bmvar24), '1'=0L, '2'=1L, .default=NA_integer_)
```  
### **Variable label**:  Current consumption of alcohol  
**Variable name**: lsb_alc_cur_1  
**Variable description**:  Indicator of whether the participant currently consumes alcohol or has consumed alcohol in the past 12 months.  
**Value type**: integer  
**Variable unit**: N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 |  Does not currently consumes alcohol   
1 |  Currently consumes alcohol   

**Harmonization status**:  complete  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
lsb_LASA1_1$lsb_alc_cur_1 <- recode(as.integer(LASA1C$cmvar24),'1'=0L,'2'=1L, .default=NA_integer_)
```  
### **Variable label**:  Current consumption of alcohol  
**Variable name**: lsb_alc_cur_2  
**Variable description**:  Indicator of whether the participant currently consumes alcohol or has consumed alcohol in the past 12 months.  
**Value type**: integer  
**Variable unit**: N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 |  Does not currently consumes alcohol   
1 |  Currently consumes alcohol  

**Harmonization status**:  complete  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
lsb_LASA1_2$lsb_alc_cur_2 <- recode(as.integer(LASA1D$dmalcohu),'1'=0L, '2'=1L, .default=NA_integer_)
```  
### **Variable label**:  Current consumption of alcohol  
**Variable name**: lsb_alc_cur_3  
**Variable description**:  Indicator of whether the participant currently consumes alcohol or has consumed alcohol in the past 12 months.  
**Value type**: integer  
**Variable unit**: N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 |  Does not currently consumes alcohol   
1 |  Currently consumes alcohol  

**Harmonization status**:  complete  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
lsb_LASA1_3$lsb_alc_cur_3 <- recode(as.integer(LASA1E$emalcohu), '1'=0L, '2'=1L, .default= NA_integer_)
```  
### **Variable label**:  Current consumption of alcohol  
**Variable name**: lsb_alc_cur_4  
**Variable description**:  Indicator of whether the participant currently consumes alcohol or has consumed alcohol in the past 12 months.  
**Value type**: integer  
**Variable unit**: N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 |  Does not currently consumes alcohol   
1 |  Currently consumes alcohol  

**Harmonization status**:  complete  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
lsb_LASA1_4$lsb_alc_cur_4 <- recode(as.integer(LASA1F$fmalcohu),'1'=0L, '2'=1L, .default= NA_integer_)
```  
### **Variable label**:  Current consumption of alcohol  
**Variable name**: lsb_alc_cur_5  
**Variable description**:  Indicator of whether the participant currently consumes alcohol or has consumed alcohol in the past 12 months.  
**Value type**: integer  
**Variable unit**: N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 |  Does not currently consumes alcohol   
1 |  Currently consumes alcohol  

**Harmonization status**:  complete    
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
lsb_LASA1_5$lsb_alc_cur_5 <- recode(as.integer(LASA1G$gmalcohu), '1'=0L, '2'=1L, .default= NA_integer_)
```  
### **Variable label**:  Current consumption of alcohol  
**Variable name**: lsb_alc_cur_6  
**Variable description**:  Indicator of whether the participant currently consumes alcohol or has consumed alcohol in the past 12 months.  
**Value type**: integer  
**Variable unit**: N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 |  Does not currently consumes alcohol   
1 |  Currently consumes alcohol  

**Harmonization status**:  complete    
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
lsb_LASA1_6$lsb_alc_cur_6 <- recode(as.integer(LASA1H$HMALCOHU), '1'=0L,'2'=1L, .default= NA_integer_)
```  

### **Variable label**:   Ever consumption of alcohol  
**Variable name**: lsb_alc_ever_0    
**Variable description**:  Indicator of whether the participant has ever consumed alcohol.  
**Value type**: integer  
**Variable unit**: N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 |   Never consumed alcohol  
1 |   Ever consumed alcohol  

**Harmonization status**:  complete  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
#Merging the raw tables LASA1B-LASA1H
MyMerge <- function(x,y){
  df <- merge(x,y, by="id",all=TRUE)
  return(df)
}
#Reducing the table to the variables needed
alc_table <- Reduce(MyMerge, list(LASA1B,LASA1C,LASA1D,LASA1E,LASA1F,LASA1G,LASA1H))
alc_table<- alc_table[,c("id","bmvar26","cmvar24","dmalcohu","emalcohu","fmalcohu","gmalcohu","HMALCOHU")]


#Harmonization scripts to create "ever drank alcohol" for all participants in all waves
alc_table$lsb_alc_ever_0 <- ifelse(as.integer(alc_table$bmvar26)==2 | as.integer(alc_table$bmvar26)==-2,1L, ifelse(as.integer(alc_table$bmvar26)==1,0L,NA))
#Direct mapping to harmonized tables keeping correct participants for each wave
lsb_LASA1_0 <- merge(lsb_LASA1_0, alc_table[,c("id","lsb_alc_ever_0")],by="id",all.x=TRUE)
```  
### **Variable label**:   Ever consumption of alcohol  
**Variable name**: lsb_alc_ever_1    
**Variable description**:  Indicator of whether the participant has ever consumed alcohol.  
**Value type**: integer  
**Variable unit**: N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 |   Never consumed alcohol  
1 |   Ever consumed alcohol  

**Harmonization status**:  complete      
**Harmonization comment**:  Drank before was only asked at baseline (bmvar26). Ever drank alcohol is created using "currently drinks" and previous followups.    
**R script**:  
```{r, echo=TRUE}
#Harmonization scripts to create "ever drank alcohol" for all participants in all waves
alc_table$lsb_alc_ever_1 <- ifelse(alc_table$lsb_alc_ever_0 ==0 & as.integer(alc_table$cmvar24)==1,0L, ifelse(alc_table$lsb_alc_ever_0==1 | as.integer(alc_table$cmvar24)==2,1L,NA))
#Direct mapping to harmonized tables keeping correct participants for each wave
lsb_LASA1_1 <- merge(lsb_LASA1_1, alc_table[,c("id","lsb_alc_ever_1")],by="id",all.x=TRUE)
```  
### **Variable label**:   Ever consumption of alcohol  
**Variable name**: lsb_alc_ever_2    
**Variable description**:  Indicator of whether the participant has ever consumed alcohol.  
**Value type**: integer  
**Variable unit**: N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 |   Never consumed alcohol  
1 |   Ever consumed alcohol  

**Harmonization status**:  complete  
**Harmonization comment**:   Drank before was only asked at baseline (bmvar26). Ever drank alcohol was created using "currently drinks alcohol" of previous and current waves. To create this variable, all LASA1 data tables were merged by ID in order to facilitate the harmonization work and intermediate variables were created.   
**R script**:  
```{r, echo=TRUE}
#Harmonization scripts to create "ever drank alcohol" for all participants in all waves
alc_table$lsb_alc_ever_2  <- ifelse(alc_table$lsb_alc_ever_1 ==0 & as.integer(alc_table$dmalcohu)==1,0L, ifelse(alc_table$lsb_alc_ever_1==1 | as.integer(alc_table$dmalcohu)==2,1L,NA))
#Direct mapping to harmonized tables keeping correct participants for each wave
lsb_LASA1_2 <- merge(lsb_LASA1_2, alc_table[,c("id","lsb_alc_ever_2")],by="id",all.x=TRUE)
```  
### **Variable label**:   Ever consumption of alcohol  
**Variable name**: lsb_alc_ever_3    
**Variable description**:  Indicator of whether the participant has ever consumed alcohol.  
**Value type**: integer  
**Variable unit**: N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 |   Never consumed alcohol  
1 |   Ever consumed alcohol  

**Harmonization status**:  complete  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
#Harmonization scripts to create "ever drank alcohol" for all participants in all waves
alc_table$lsb_alc_ever_3  <- ifelse(alc_table$lsb_alc_ever_2 ==0 & as.integer(alc_table$emalcohu)==1,0L, ifelse(alc_table$lsb_alc_ever_2==1 | as.integer(alc_table$emalcohu)==2,1L,NA))
#Direct mapping to harmonized tables keeping correct participants for each wave
lsb_LASA1_3 <- merge(lsb_LASA1_3, alc_table[,c("id","lsb_alc_ever_3")],by="id",all.x=TRUE)
```  
### **Variable label**:   Ever consumption of alcohol  
**Variable name**: lsb_alc_ever_4    
**Variable description**:  Indicator of whether the participant has ever consumed alcohol.  
**Value type**: integer  
**Variable unit**: N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 |   Never consumed alcohol  
1 |   Ever consumed alcohol  

**Harmonization status**:  complete  
**Harmonization comment**:   
**R script**:   
```{r, echo=TRUE}
#Harmonization scripts to create "ever drank alcohol" for all participants in all waves
alc_table$lsb_alc_ever_4  <- ifelse(alc_table$lsb_alc_ever_3 ==0 & as.integer(alc_table$fmalcohu)==1,0L, ifelse(alc_table$lsb_alc_ever_3==1 | as.integer(alc_table$fmalcohu)==2,1L,NA))
#Direct mapping to harmonized tables keeping correct participants for each wave
lsb_LASA1_4 <- merge(lsb_LASA1_4, alc_table[,c("id","lsb_alc_ever_4")],by="id",all.x=TRUE)
```  
### **Variable label**:   Ever consumption of alcohol  
**Variable name**: lsb_alc_ever_5    
**Variable description**:  Indicator of whether the participant has ever consumed alcohol.  
**Value type**: integer  
**Variable unit**: N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 |   Never consumed alcohol  
1 |   Ever consumed alcohol  

**Harmonization status**:  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
#Harmonization scripts to create "ever drank alcohol" for all participants in all waves
alc_table$lsb_alc_ever_5  <- ifelse(alc_table$lsb_alc_ever_4 ==0 & as.integer(alc_table$gmalcohu)==1,0L, ifelse(alc_table$lsb_alc_ever_4==1 | as.integer(alc_table$gmalcohu)==2,1L,NA))
#Direct mapping to harmonized tables keeping correct participants for each wave
lsb_LASA1_5 <- merge(lsb_LASA1_5, alc_table[,c("id","lsb_alc_ever_5")],by="id",all.x=TRUE)
```  
### **Variable label**:   Ever consumption of alcohol  
**Variable name**: lsb_alc_ever_6    
**Variable description**:  Indicator of whether the participant has ever consumed alcohol.  
**Value type**: integer  
**Variable unit**: N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 |   Never consumed alcohol  
1 |   Ever consumed alcohol  

**Harmonization status**:  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
#Harmonization scripts to create "ever drank alcohol" for all participants in all waves
alc_table$lsb_alc_ever_6  <- ifelse(alc_table$lsb_alc_ever_5 ==0 & as.integer(alc_table$HMALCOHU)==1,0L, ifelse(alc_table$lsb_alc_ever_5==1 | as.integer(alc_table$HMALCOHU)==2,1L,NA))
#Direct mapping to harmonized tables keeping correct participants for each wave
lsb_LASA1_6 <- merge(lsb_LASA1_6, alc_table[,c("id","lsb_alc_ever_6")],by="id",all.x=TRUE)
```  

### **Variable label**:   Frequency of binge drinking  
**Variable name**: lsb_alc_binge_0  
**Variable description**:  Frequency of drinking 4 or more drinks in one day.  
**Value type**: integer  
**Variable unit**: N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
1 |  0 to 3 times a month  
2 |  1 to 3 times a week   
3 |  3 times a week or more  

**Harmonization status**:    
**Harmonization comment**:   bmvar28 ('Alcohol: Number of glasses at one time') seems to also be answered by participants who said that they don't drink in bmvar24 ('Alcohol: Do you drink alcohol'). These participants are coded to '0-3 times a month' in the DataSchema variable.
**R script**:  
```{r, echo=TRUE}
lsb_LASA1_0$lsb_alc_binge_0 <- ifelse(as.integer(LASA1B$bmvar24)==1,1L, 
                               ifelse(as.integer(LASA1B$bmvar28) %in% c(5,6) & as.integer(LASA1B$bmvar29) %in% c(1:3),3L,       
                               ifelse(as.integer(LASA1B$bmvar28) %in% c(5,6) & as.integer(LASA1B$bmvar29) %in% c(4),2L,  
                               ifelse(as.integer(LASA1B$bmvar28) %in% c(5,6) & as.integer(LASA1B$bmvar29) %in% c(-2,5,6),1L, 
                               ifelse(as.integer(LASA1B$bmvar28) %in% c(1:4) & as.integer(LASA1B$bmvar25) %in% c(1:3),3L, 
                               ifelse(as.integer(LASA1B$bmvar28) %in% c(1:4) & as.integer(LASA1B$bmvar25) %in% c(4),2L, 
                               ifelse(as.integer(LASA1B$bmvar28) %in% c(1:4) & as.integer(LASA1B$bmvar25) %in% c(-2,5,6),1L,
                               NA)))))))
```  
### **Variable label**:   Frequency of binge drinking  
**Variable name**: lsb_alc_binge_1  
**Variable description**:  Frequency of drinking 4 or more drinks in one day.  
**Value type**: integer  
**Variable unit**: N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
1 |  0 to 3 times a month  
2 |  1 to 3 times a week   
3 |  3 times a week or more  

**Harmonization status**:  complete  
**Harmonization comment**:  Participants who responded usually drinking less than 6 drinks at one time were later asked the frequency of drinking 6 glasses or more and this variable was used to derive binge drinking for these participants. For participants who responded usually drinking 6 glasses or more, frequency of drinking alcohol was used to derive frequency of binge drinking.    
**R script**:  
```{r, echo=TRUE}
lsb_LASA1_1$lsb_alc_binge_1 <- ifelse(as.integer(LASA1C$cmvar24)==1,1L, 
                               ifelse(as.integer(LASA1C$cmvar28) %in% c(5,6) & as.integer(LASA1C$cmvar29) %in% c(1:3),3L,       
                               ifelse(as.integer(LASA1C$cmvar28) %in% c(5,6) & as.integer(LASA1C$cmvar29) %in% c(4),2L,  
                               ifelse(as.integer(LASA1C$cmvar28) %in% c(5,6) & as.integer(LASA1C$cmvar29) %in% c(5,6),1L, 
                               ifelse(as.integer(LASA1C$cmvar28) %in% c(1:4) & as.integer(LASA1C$cmvar25a) %in% c(1:3),3L, 
                               ifelse(as.integer(LASA1C$cmvar28) %in% c(1:4) & as.integer(LASA1C$cmvar25a) %in% c(4),2L, 
                               ifelse(as.integer(LASA1C$cmvar28) %in% c(1:4) & as.integer(LASA1C$cmvar25a) %in% c(5,6),1L,
                               NA)))))))
#lsb_LASA1_1$lsb_alc_binge_1 <- ifelse(as.integer(LASA1C$cmvar24)==1,1L, ifelse((as.integer(LASA1C$cmvar28)>=1 & as.integer(LASA1C$cmvar28)<=4) & (as.integer(LASA1C$cmvar25a)>=-2 & as.integer(LASA1C$cmvar25a)<=3),3L, ifelse((as.integer(LASA1C$cmvar28)>=1 & as.integer(LASA1C$cmvar28)<=4) & as.integer(LASA1C$cmvar25a)>=4,2L, ifelse((as.integer(LASA1C$cmvar28)>=1 & as.integer(LASA1C$cmvar28)<=4) & as.integer(LASA1C$cmvar25a)>=5,1L, ifelse(as.integer(LASA1C$cmvar28)>=5 & (as.integer(LASA1C$cmvar29)>=-2 & as.integer(LASA1C$cmvar29)<=3),3L, ifelse(as.integer(LASA1C$cmvar28)>=5 & as.integer(LASA1C$cmvar29)==4,2L,ifelse(as.integer(LASA1C$cmvar28)>=5 & as.integer(LASA1C$cmvar29)>=5,1L,NA)))))))
```  
### **Variable label**:   Frequency of binge drinking  
**Variable name**: lsb_alc_binge_2  
**Variable description**:  Frequency of drinking 4 or more drinks in one day.  
**Value type**: integer  
**Variable unit**: N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
1 |  0 to 3 times a month  
2 |  1 to 3 times a week   
3 |  3 times a week or more  

**Harmonization status**:  complete  
**Harmonization comment**:  Participants who responded usually drinking less than 6 drinks at one time were later asked the frequency of drinking 6 glasses or more and this variable was used to derive binge drinking for these participants. For participants who responded usually drinking 6 glasses or more, frequency of drinking alcohol was used to derive frequency of binge drinking.    
**R script**:  
```{r, echo=TRUE}
lsb_LASA1_2$lsb_alc_binge_2 <- ifelse(as.integer(LASA1D$dmalcohu)==1,1L, 
                               ifelse(as.integer(LASA1D$dmalcohn) %in% c(5,6) & as.integer(LASA1D$dmalcoh6) %in% c(1:3),3L,       
                               ifelse(as.integer(LASA1D$dmalcohn) %in% c(5,6) & as.integer(LASA1D$dmalcoh6) %in% c(4),2L,  
                               ifelse(as.integer(LASA1D$dmalcohn) %in% c(5,6) & as.integer(LASA1D$dmalcoh6) %in% c(5,6),1L,
                               ifelse(as.integer(LASA1D$dmalcohn) %in% c(1:4) & as.integer(LASA1D$dmalcohd) %in% c(1:3),3L, 
                               ifelse(as.integer(LASA1D$dmalcohn) %in% c(1:4) & as.integer(LASA1D$dmalcohd) %in% c(4),2L, 
                               ifelse(as.integer(LASA1D$dmalcohn) %in% c(1:4) & as.integer(LASA1D$dmalcohd) %in%  
                               c(5,6),1L,NA)))))))

addmargins(table(interaction(LASA1D$dmalcohu,LASA1D$dmalcohd,LASA1D$dmalcohn,LASA1D$dmalcoh6,drop=TRUE),useNA='always'))

addmargins(table(interaction(
  LASA1D$dmalcohu[as.integer(LASA1D$dmalcohn) %in% c(5,6) & as.integer(LASA1D$dmalcoh6) %in% c(1:3)],  
  LASA1D$dmalcohd[as.integer(LASA1D$dmalcohn) %in% c(5,6) & as.integer(LASA1D$dmalcoh6) %in% c(1:3)],  
  LASA1D$dmalcohn[as.integer(LASA1D$dmalcohn) %in% c(5,6) & as.integer(LASA1D$dmalcoh6) %in% c(1:3)],  
  LASA1D$dmalcoh6[as.integer(LASA1D$dmalcohn) %in% c(5,6) & as.integer(LASA1D$dmalcoh6) %in% c(1:3)],
drop=TRUE),useNA='always'))

addmargins(table(interaction(
  LASA1D$dmalcohu[as.integer(LASA1D$dmalcohn) %in% c(1:4) & as.integer(LASA1D$dmalcohd) %in% c(1:3)],  
  LASA1D$dmalcohd[as.integer(LASA1D$dmalcohn) %in% c(1:4) & as.integer(LASA1D$dmalcohd) %in% c(1:3)],  
  LASA1D$dmalcohn[as.integer(LASA1D$dmalcohn) %in% c(1:4) & as.integer(LASA1D$dmalcohd) %in% c(1:3)],  
  LASA1D$dmalcoh6[as.integer(LASA1D$dmalcohn) %in% c(1:4) & as.integer(LASA1D$dmalcohd) %in% c(1:3)],
drop=TRUE),useNA='always'))

```  
### **Variable label**:   Frequency of binge drinking  
**Variable name**: lsb_alc_binge_3  
**Variable description**:  Frequency of drinking 4 or more drinks in one day.  
**Value type**: integer  
**Variable unit**: N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
1 |  0 to 3 times a month  
2 |  1 to 3 times a week   
3 |  3 times a week or more  

**Harmonization status**:  complete  
**Harmonization comment**:   question  
**R script**:  
```{r, echo=TRUE}
lsb_LASA1_3$lsb_alc_binge_3 <- ifelse(as.integer(LASA1E$emalcohu)==1,1L, 
                               ifelse(as.integer(LASA1E$emalcohn) %in% c(5,6) & as.integer(LASA1E$emalcoh6) %in% c(1:3),3L,       
                               ifelse(as.integer(LASA1E$emalcohn) %in% c(5,6) & as.integer(LASA1E$emalcoh6) %in% c(4),2L,  
                               ifelse(as.integer(LASA1E$emalcohn) %in% c(5,6) & as.integer(LASA1E$emalcoh6) %in% c(5,6),1L,
                               ifelse(as.integer(LASA1E$emalcohn) %in% c(1:4) & as.integer(LASA1E$emalcohd) %in% c(1:3),3L, 
                               ifelse(as.integer(LASA1E$emalcohn) %in% c(1:4) & as.integer(LASA1E$emalcohd) %in% c(4),2L, 
                               ifelse(as.integer(LASA1E$emalcohn) %in% c(1:4) & as.integer(LASA1E$emalcohd) %in%  
                               c(5,6),1L,NA)))))))

#lsb_LASA1_3$lsb_alc_binge_3 <-  ifelse(((as.integer(LASA1E$emalcohn)>=1 & as.integer(LASA1E$emalcohn)<=4) & (as.integer(LASA1E$emalcohd)>=-2 & as.integer(LASA1E$emalcohd)<=3)),3L, ifelse(((as.integer(LASA1E$emalcohn)>=1 & as.integer(LASA1E$emalcohn)<=4) & as.integer(LASA1E$emalcohd)>=4),2L, ifelse((((as.integer(LASA1E$emalcohn)>=1 & as.integer(LASA1E$emalcohn)<=4) & as.integer(LASA1E$emalcohd)>=5) | as.integer(LASA1E$emalcohn)==-2),1L, ifelse((as.integer(LASA1E$emalcohn)>=5 & (as.integer(LASA1E$emalcoh6)>=-2 & as.integer(LASA1E$emalcoh6)<=3)),3L, ifelse((as.integer(LASA1E$emalcohn)>=5 & as.integer(LASA1E$emalcoh6)==4),2L,ifelse((as.integer(LASA1E$emalcohn)>=5 & as.integer(LASA1E$emalcoh6)>=5),1L,NA))))))
```  
### **Variable label**:   Frequency of binge drinking  
**Variable name**: lsb_alc_binge_4  
**Variable description**:  Frequency of drinking 4 or more drinks in one day.  
**Value type**: integer  
**Variable unit**: N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
1 |  0 to 3 times a month  
2 |  1 to 3 times a week   
3 |  3 times a week or more  

**Harmonization status**:  complete  
**Harmonization comment**:   question    
**R script**:  
```{r, echo=TRUE}
lsb_LASA1_4$lsb_alc_binge_4 <- ifelse(as.integer(LASA1F$fmalcohu)==1,1L, 
                               ifelse(as.integer(LASA1F$fmalcohn) %in% c(5,6) & as.integer(LASA1F$fmalcoh6) %in% c(1:3),3L,       
                               ifelse(as.integer(LASA1F$fmalcohn) %in% c(5,6) & as.integer(LASA1F$fmalcoh6) %in% c(4),2L,  
                               ifelse(as.integer(LASA1F$fmalcohn) %in% c(5,6) & as.integer(LASA1F$fmalcoh6) %in% c(5,6),1L,
                               ifelse(as.integer(LASA1F$fmalcohn) %in% c(1:4) & as.integer(LASA1F$fmalcohd) %in% c(1:3),3L, 
                               ifelse(as.integer(LASA1F$fmalcohn) %in% c(1:4) & as.integer(LASA1F$fmalcohd) %in% c(4),2L, 
                               ifelse(as.integer(LASA1F$fmalcohn) %in% c(1:4) & as.integer(LASA1F$fmalcohd) %in%  
                               c(5,6),1L,NA)))))))

#lsb_LASA1_4$lsb_alc_binge_4<- ifelse(as.integer(LASA1F$fmalcohn)<=4 & as.integer(LASA1F$fmalcohn)>=1, ifelse(as.integer(LASA1F$fmalcohd)==1 | as.integer(LASA1F$fmalcohd)==2 | as.integer(LASA1F$fmalcohd)==3 | as.integer(LASA1F$fmalcohd)==-2,3L, ifelse(as.integer(LASA1F$fmalcohd)==4,2L, ifelse(as.integer(LASA1F$fmalcohd)== 5 | as.integer(LASA1F$fmalcohd)==6,1L, ifelse(as.integer(LASA1F$fmalcohn)>=5, ifelse(as.integer(LASA1F$fmalcoh6)==1 |as.integer(LASA1F$fmalcoh6)==2 |as.integer(LASA1F$fmalcoh6)==3 |as.integer(LASA1F$fmalcoh6)==-2,3L, ifelse(as.integer(LASA1F$fmalcoh6)==4,2L,ifelse(LASA1F$fmalcoh6)>=5,1L,NA)))))))
```  
### **Variable label**:   Frequency of binge drinking  
**Variable name**: lsb_alc_binge_5  
**Variable description**:  Frequency of drinking 4 or more drinks in one day.  
**Value type**: integer  
**Variable unit**: N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
1 |  0 to 3 times a month  
2 |  1 to 3 times a week   
3 |  3 times a week or more  

**Harmonization status**:  complete  
**Harmonization comment**:   question  
**R script**:  
```{r, echo=TRUE}
lsb_LASA1_5$lsb_alc_binge_5 <- ifelse(as.integer(LASA1G$gmalcohu)==1,1L, 
                               ifelse(as.integer(LASA1G$gmalcohn) %in% c(5,6) & as.integer(LASA1G$gmalcoh6) %in% c(1:3),3L,       
                               ifelse(as.integer(LASA1G$gmalcohn) %in% c(5,6) & as.integer(LASA1G$gmalcoh6) %in% c(4),2L,  
                               ifelse(as.integer(LASA1G$gmalcohn) %in% c(5,6) & as.integer(LASA1G$gmalcoh6) %in% c(5,6),1L,
                               ifelse(as.integer(LASA1G$gmalcohn) %in% c(1:4) & as.integer(LASA1G$gmalcohd) %in% c(1:3),3L, 
                               ifelse(as.integer(LASA1G$gmalcohn) %in% c(1:4) & as.integer(LASA1G$gmalcohd) %in% c(4),2L, 
                               ifelse(as.integer(LASA1G$gmalcohn) %in% c(1:4) & as.integer(LASA1G$gmalcohd) %in%  
                               c(5,6),1L,NA)))))))
```  
### **Variable label**:   Frequency of binge drinking  
**Variable name**: lsb_alc_binge_6  
**Variable description**:  Frequency of drinking 4 or more drinks in one day.  
**Value type**: integer  
**Variable unit**: N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
1 |  0 to 3 times a month  
2 |  1 to 3 times a week   
3 |  3 times a week or more  

**Harmonization status**:  complete  
**Harmonization comment**:   question    
**R script**:  
```{r, echo=TRUE}
lsb_LASA1_6$lsb_alc_binge_6 <- ifelse(as.integer(LASA1H$HMALCOHU)==1,1L, 
                               ifelse(as.integer(LASA1H$HMALCOHN) %in% c(5,6) & as.integer(LASA1H$HMALCOH6) %in% c(1:3),3L,       
                               ifelse(as.integer(LASA1H$HMALCOHN) %in% c(5,6) & as.integer(LASA1H$HMALCOH6) %in% c(4),2L,  
                               ifelse(as.integer(LASA1H$HMALCOHN) %in% c(5,6) & as.integer(LASA1H$HMALCOH6) %in% c(5,6),1L,
                               ifelse(as.integer(LASA1H$HMALCOHN) %in% c(1:4) & as.integer(LASA1H$HMALCOHD) %in% c(1:3),3L, 
                               ifelse(as.integer(LASA1H$HMALCOHN) %in% c(1:4) & as.integer(LASA1H$HMALCOHD) %in% c(4),2L, 
                               ifelse(as.integer(LASA1H$HMALCOHN) %in% c(1:4) & as.integer(LASA1H$HMALCOHD) %in%  
                               c(5,6),1L,NA)))))))
```  

### **Variable label**:   Current quantity of alcohol consumed per week (total)      
**Variable name**: lsb_alc_total_0  
**Variable description**:  Current quantity of wine, beer and liquor consumed per week.    
**Value type**: decimal    
**Variable unit**: drinks/week  
**Category coding**:  N/A  

**Harmonization status**:  impossible  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}

```  
### **Variable label**:   Current quantity of alcohol consumed per week (total)  
**Variable name**: lsb_alc_total_1  
**Variable description**:  Current quantity of wine, beer and liquor consumed per week.    
**Value type**: decimal    
**Variable unit**: drinks/week  
**Category coding**:  N/A  

**Harmonization status**:  impossible  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}

```  
### **Variable label**:   Current quantity of alcohol consumed per week (total)  
**Variable name**: lsb_alc_total_2  
**Variable description**:  Current quantity of wine, beer and liquor consumed per week.    
**Value type**: decimal    
**Variable unit**: drinks/week  
**Category coding**:  N/A  

**Harmonization status**:  impossible  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}

```  
### **Variable label**:   Current quantity of alcohol consumed per week (total)  
**Variable name**: lsb_alc_total_3  
**Variable description**:  Current quantity of wine, beer and liquor consumed per week.    
**Value type**: decimal    
**Variable unit**: drinks/week  
**Category coding**:  N/A  

**Harmonization status**:  impossible  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}

```  

### **Variable label**:   Current quantity of wine consumed per week  
**Variable name**: lsb_alc_wine_0  
**Variable description**:  Current quantity of wine consumed per week.    
**Value type**: decimal    
**Variable unit**: drinks/week  
**Category coding**:  N/A  

**Harmonization status**:  impossible  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}

```  
### **Variable label**:   Current quantity of wine consumed per week  
**Variable name**: lsb_alc_wine_1  
**Variable description**:  Current quantity of wine consumed per week.    
**Value type**: decimal    
**Variable unit**: drinks/week  
**Category coding**:  N/A  

**Harmonization status**:  impossible  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}

```  
### **Variable label**:   Current quantity of wine consumed per week  
**Variable name**: lsb_alc_wine_2  
**Variable description**:  Current quantity of wine consumed per week.    
**Value type**: decimal    
**Variable unit**: drinks/week  
**Category coding**:  N/A  

**Harmonization status**:  impossible  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}

```  
### **Variable label**:   Current quantity of wine consumed per week  
**Variable name**: lsb_alc_wine_3  
**Variable description**:  Current quantity of wine consumed per week.    
**Value type**: decimal    
**Variable unit**: drinks/week  
**Category coding**:  N/A  

**Harmonization status**:  impossible  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}

```  

### **Variable label**:   Current quantity of beer consumed per week  
**Variable name**: lsb_alc_beer_0  
**Variable description**:  Current quantity of beer consumed per week.   
**Value type**: decimal    
**Variable unit**: drinks/week  
**Category coding**:  N/A  
 

**Harmonization status**:  impossible  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}

```  
### **Variable label**:   Current quantity of beer consumed per week  
**Variable name**: lsb_alc_beer_1  
**Variable description**:  Current quantity of beer consumed per week.    
**Value type**: decimal    
**Variable unit**: drinks/week  
**Category coding**:  N/A  
 

**Harmonization status**:  impossible  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}

```  
### **Variable label**:   Current quantity of beer consumed per week  
**Variable name**: lsb_alc_beer_2  
**Variable description**:  Current quantity of beer consumed per week.    
**Value type**: decimal    
**Variable unit**: drinks/week  
**Category coding**:  N/A  
 

**Harmonization status**:  impossible  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}

```  
### **Variable label**:   Current quantity of beer consumed per week  
**Variable name**: lsb_alc_beer_3  
**Variable description**:  Current quantity of beer consumed per week.    
**Value type**: decimal    
**Variable unit**: drinks/week  
**Category coding**:  N/A  
 

**Harmonization status**:  impossible  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}

```  

### **Variable label**:   Current quantity of liquor consumed per week  
**Variable name**: lsb_alc_liq_0  
**Variable description**:  Current quantity of liquor consumed per week.    
**Value type**: decimal    
**Variable unit**: drinks/week  
**Category coding**:  N/A  
 

**Harmonization status**:  impossible  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}

```  
### **Variable label**:   Current quantity of liquor consumed per week  
**Variable name**: lsb_alc_liq_1  
**Variable description**:  Current quantity of liquor consumed per week.   
**Value type**: decimal    
**Variable unit**: drinks/week  
**Category coding**:  N/A  
 

**Harmonization status**:  impossible  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}

```  
### **Variable label**:   Current quantity of liquor consumed per week  
**Variable name**: lsb_alc_liq_2  
**Variable description**:  Current quantity of liquor consumed per week.    
**Value type**: decimal    
**Variable unit**: drinks/week  
**Category coding**:  N/A  
 

**Harmonization status**:  impossible  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}

```  
### **Variable label**:   Current quantity of liquor consumed per week  
**Variable name**: lsb_alc_liq_3  
**Variable description**:  Current quantity of liquor consumed per week.   
**Value type**: decimal    
**Variable unit**: drinks/week  
**Category coding**:  N/A  
 

**Harmonization status**:  impossible  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}

```  

# Tobacco consumption subdomain

### **Variable label**:  Current tobacco smoking  
**Variable name**:  lsb_smk_cur_0  
**Variable description**:  Indicator of whether the participant currently smokes any tobacco product.  
**Value type**:  integer  
**Variable unit**:  N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 |   Currently does not smoke any tobacco product  
1 |   Currently smokes any tobacco product  

**Harmonization status**:  complete  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
lsb_LASA1_0$lsb_smk_cur_0 <- recode(as.integer(LASA1B$bmvar31),'1'=0L, '2'=1L, .default=NA_integer_)
```  
### **Variable label**:  Current tobacco smoking  
**Variable name**:  lsb_smk_cur_1  
**Variable description**:  Indicator of whether the participant currently smokes any tobacco product.  
**Value type**:  integer  
**Variable unit**:  N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 |   Currently does not smoke any tobacco product  
1 |   Currently smokes any tobacco product  

**Harmonization status**:  complete  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
lsb_LASA1_1$lsb_smk_cur_1 <- recode(as.integer(LASA1C$cmvar31), '1'=0L, '2'=1L, .default=NA_integer_)
```  
### **Variable label**:  Current tobacco smoking  
**Variable name**:  lsb_smk_cur_2  
**Variable description**:  Indicator of whether the participant currently smokes any tobacco product.  
**Value type**:  integer  
**Variable unit**:  N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 |   Currently does not smoke any tobacco product  
1 |   Currently smokes any tobacco product  

**Harmonization status**:  complete  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
lsb_LASA1_2$lsb_smk_cur_2 <- recode(as.integer(LASA1D$dmvar31), '1'=0L, '2'=1L, .default=NA_integer_)
```  
### **Variable label**:  Current tobacco smoking  
**Variable name**:  lsb_smk_cur_3  
**Variable description**:  Indicator of whether the participant currently smokes any tobacco product.  
**Value type**:  integer  
**Variable unit**:  N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 |   Currently does not smoke any tobacco product  
1 |   Currently smokes any tobacco product  

**Harmonization status**:  complete  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
lsb_LASA1_3$lsb_smk_cur_3 <- recode(as.integer(LASA1E$emvar31), '1'=0L, '2'=1L, .default= NA_integer_)
```  
### **Variable label**:  Current tobacco smoking  
**Variable name**:  lsb_smk_cur_4  
**Variable description**:  Indicator of whether the participant currently smokes any tobacco product.  
**Value type**:  integer  
**Variable unit**:  N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 |   Currently does not smoke any tobacco product  
1 |   Currently smokes any tobacco product  

**Harmonization status**:  complete  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
lsb_LASA1_4$lsb_smk_cur_4 <- recode(as.integer(LASA1F$fmvar31), '1'=0L, '2'=1L, .default= NA_integer_)
```  
### **Variable label**:  Current tobacco smoking  
**Variable name**:  lsb_smk_cur_5  
**Variable description**:  Indicator of whether the participant currently smokes any tobacco product.  
**Value type**:  integer  
**Variable unit**:  N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 |   Currently does not smoke any tobacco product  
1 |   Currently smokes any tobacco product  

**Harmonization status**:  complete  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
lsb_LASA1_5$lsb_smk_cur_5 <- recode(as.integer(LASA1G$gmvar31), '1'=0L, '2'=1L, .default= NA_integer_)
```  
### **Variable label**:  Current tobacco smoking  
**Variable name**:  lsb_smk_cur_6  
**Variable description**:  Indicator of whether the participant currently smokes any tobacco product.  
**Value type**:  integer  
**Variable unit**:  N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 |   Currently does not smoke any tobacco product  
1 |   Currently smokes any tobacco product  

**Harmonization status**:  complete  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
lsb_LASA1_6$lsb_smk_cur_6 <- recode(as.integer(LASA1H$HMVAR31), '1'=0L, '2'=1L, .default=NA_integer_)
```  

### **Variable label**:  Smoking status  
**Variable name**:  lsb_smk_status_0  
**Variable description**:  Smoking status of the participant.  
**Value type**:  integer  
**Variable unit**:  N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 |   Never smoker  
1 |   Former smoker  
2 |   Current smoker  

**Harmonization status**:  complete  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
lsb_LASA1_0$lsb_smk_status_0 <- ifelse(as.integer(LASA1B$bmvar32)== 1, 0L, ifelse(as.integer(LASA1B$bmvar32)== 2, 1L, ifelse((as.integer(LASA1B$bmvar32)== '-2' & as.integer(LASA1B$bmvar31)== 2), 2L, NA)))
```  
### **Variable label**:  Smoking status  
**Variable name**:  lsb_smk_status_1  
**Variable description**:  Smoking status of the participant.  
**Value type**:  integer  
**Variable unit**:  N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 |   Never smoker  
1 |   Former smoker  
2 |   Current smoker  

**Harmonization status**:  complete  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
lsb_LASA1_1$lsb_smk_status_1 <- ifelse(as.integer(LASA1C$cmvar32)== 1, 0L, ifelse(as.integer(LASA1C$cmvar32)== 2,1L, ifelse((as.integer(LASA1C$cmvar32)== '-2' & as.integer(LASA1C$cmvar31)==2), 2L, NA)))
```  
### **Variable label**:  Smoking status  
**Variable name**:  lsb_smk_status_2  
**Variable description**:  Smoking status of the participant.  
**Value type**:  integer  
**Variable unit**:  N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 |   Never smoker  
1 |   Former smoker  
2 |   Current smoker  

**Harmonization status**:  complete  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
lsb_LASA1_2$lsb_smk_status_2 <- ifelse(as.integer(LASA1D$dmvar32)== 1, 0L, ifelse(as.integer(LASA1D$dmvar32)== 2,1L, ifelse((as.integer(LASA1D$dmvar32)== '-2' & as.integer(LASA1D$dmvar31)==2), 2L, NA)))
```  
### **Variable label**:  Smoking status  
**Variable name**:  lsb_smk_status_3  
**Variable description**:  Smoking status of the participant.  
**Value type**:  integer  
**Variable unit**:  N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 |   Never smoker  
1 |   Former smoker  
2 |   Current smoker  

**Harmonization status**:  complete    
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
lsb_LASA1_3$lsb_smk_status_3 <- ifelse(as.integer(LASA1E$emvar32)== 1, 0L, ifelse(as.integer(LASA1E$emvar32)== 2,1L, ifelse((as.integer(LASA1E$emvar32)== '-2' & as.integer(LASA1E$emvar31)==2), 2L, NA)))
```  
### **Variable label**:  Smoking status  
**Variable name**:  lsb_smk_status_4  
**Variable description**:  Smoking status of the participant.  
**Value type**:  integer  
**Variable unit**:  N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 |   Never smoker  
1 |   Former smoker  
2 |   Current smoker  

**Harmonization status**:  complete  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
lsb_LASA1_4$lsb_smk_status_4 <- ifelse(as.integer(LASA1F$fmvar32)== 1, 0L, ifelse(as.integer(LASA1F$fmvar32)== 2,1L, ifelse((as.integer(LASA1F$fmvar32)== '-2' & as.integer(LASA1F$fmvar31)==2), 2L, NA)))
```  
### **Variable label**:  Smoking status  
**Variable name**:  lsb_smk_status_5  
**Variable description**:  Smoking status of the participant.  
**Value type**:  integer  
**Variable unit**:  N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 |   Never smoker  
1 |   Former smoker  
2 |   Current smoker  

**Harmonization status**:  complete  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
lsb_LASA1_5$lsb_smk_status_5 <- ifelse(as.integer(LASA1G$gmvar32)== 1, 0L, ifelse(as.integer(LASA1G$gmvar32)== 2,1L, ifelse((as.integer(LASA1G$gmvar32)== '-2' & as.integer(LASA1G$gmvar31)==2), 2L, NA)))
```  
### **Variable label**:  Smoking status  
**Variable name**:  lsb_smk_status_6  
**Variable description**:  Smoking status of the participant.  
**Value type**:  integer  
**Variable unit**:  N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 |   Never smoker  
1 |   Former smoker  
2 |   Current smoker  

**Harmonization status**:  complete  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
lsb_LASA1_6$lsb_smk_status_6 <- ifelse(as.integer(LASA1H$HMVAR32)== 1, 0L, ifelse(as.integer(LASA1H$HMVAR32)== 2,1L, ifelse((as.integer(LASA1H$HMVAR32)== '-2' & as.integer(LASA1H$HMVAR31)==2), 2L, NA)))
```  

### **Variable label**:  Ever tobacco smoking  
**Variable name**:  lsb_smk_ever_0    
**Variable description**:  Indicator of whether the participant has ever smoked any tobacco product.  
**Value type**:  integer  
**Variable unit**:  N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 |   Never smoked tobacco  
1 |   Ever smoked tobacco  

**Harmonization status**:  complete  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
lsb_LASA1_0$lsb_smk_ever_0 <- ifelse(as.integer(LASA1B$bmvar32)== 1, 0L, ifelse(as.integer(LASA1B$bmvar32)== 2,1L, ifelse((as.integer(LASA1B$bmvar32)== '-2' & as.integer(LASA1B$bmvar31)==2), 1L, NA)))
```  
### **Variable label**:  Ever tobacco smoking  
**Variable name**:  lsb_smk_ever_1    
**Variable description**:  Indicator of whether the participant has ever smoked any tobacco product.  
**Value type**:  integer  
**Variable unit**:  N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 |   Never smoked tobacco  
1 |   Ever smoked tobacco  

**Harmonization status**:  complete  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
lsb_LASA1_1$lsb_smk_ever_1 <- ifelse(as.integer(LASA1C$cmvar32)== 1, 0L, ifelse(as.integer(LASA1C$cmvar32)== 2,1L, ifelse((as.integer(LASA1C$cmvar32)== '-2' & as.integer(LASA1C$cmvar31)==2), 1L, NA)))
```  
### **Variable label**:  Ever tobacco smoking  
**Variable name**:  lsb_smk_ever_2    
**Variable description**:  Indicator of whether the participant has ever smoked any tobacco product.  
**Value type**:  integer  
**Variable unit**:  N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 |   Never smoked tobacco  
1 |   Ever smoked tobacco  

**Harmonization status**:  complete  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
lsb_LASA1_2$lsb_smk_ever_2 <- ifelse(as.integer(LASA1D$dmvar32)== 1, 0L, ifelse(as.integer(LASA1D$dmvar32)== 2,1L, ifelse((as.integer(LASA1D$dmvar32)== '-2' & as.integer(LASA1D$dmvar31)==2), 1L, NA)))
```  
### **Variable label**:  Ever tobacco smoking  
**Variable name**:  lsb_smk_ever_3    
**Variable description**:  Indicator of whether the participant has ever smoked any tobacco product.  
**Value type**:  integer  
**Variable unit**:  N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 |   Never smoked tobacco  
1 |   Ever smoked tobacco  

**Harmonization status**:  complete  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
lsb_LASA1_3$lsb_smk_ever_3 <- ifelse(as.integer(LASA1E$emvar32)== 1, 0L, ifelse(as.integer(LASA1E$emvar32)== 2,1L, ifelse((as.integer(LASA1E$emvar32)== '-2' & as.integer(LASA1E$emvar31)==2), 1L, NA)))
```  
### **Variable label**:  Ever tobacco smoking  
**Variable name**:  lsb_smk_ever_4    
**Variable description**:  Indicator of whether the participant has ever smoked any tobacco product.  
**Value type**:  integer  
**Variable unit**:  N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 |   Never smoked tobacco  
1 |   Ever smoked tobacco  

**Harmonization status**:  complete  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
lsb_LASA1_4$lsb_smk_ever_4 <- ifelse(as.integer(LASA1F$fmvar32)== 1, 0L, ifelse(as.integer(LASA1F$fmvar32)== 2,1L, ifelse((as.integer(LASA1F$fmvar32)== '-2' & as.integer(LASA1F$fmvar31)==2), 1L, NA)))
```  
### **Variable label**:  Ever tobacco smoking  
**Variable name**:  lsb_smk_ever_5    
**Variable description**:  Indicator of whether the participant has ever smoked any tobacco product.  
**Value type**:  integer  
**Variable unit**:  N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 |   Never smoked tobacco  
1 |   Ever smoked tobacco  

**Harmonization status**:  complete  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
lsb_LASA1_5$lsb_smk_ever_5 <- ifelse(as.integer(LASA1G$gmvar32)== 1, 0L, ifelse(as.integer(LASA1G$gmvar32)== 2,1L, ifelse((as.integer(LASA1G$gmvar32)== '-2' & as.integer(LASA1G$gmvar31)==2), 1L, NA)))
```  
### **Variable label**:  Ever tobacco smoking  
**Variable name**:  lsb_smk_ever_6    
**Variable description**:  Indicator of whether the participant has ever smoked any tobacco product.  
**Value type**:  integer  
**Variable unit**:  N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 |   Never smoked tobacco  
1 |   Ever smoked tobacco  

**Harmonization status**:  complete  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
lsb_LASA1_6$lsb_smk_ever_6 <- ifelse(as.integer(LASA1H$HMVAR32)== 1, 0L, ifelse(as.integer(LASA1H$HMVAR32)== 2,1L, ifelse((as.integer(LASA1H$HMVAR32)== '-2' & as.integer(LASA1H$HMVAR31)==2), 1L, NA)))
```  

### **Variable label**:  Quantity cigarettes smoked    
**Variable name**:  lsb_cig_qty_0   
**Variable description**:  Current average number of cigarettes smoked per day.  
**Value type**:  integer  
**Variable unit**:  cigarettes/day  
**Category coding**:  

**Harmonization status**:  complete    
**Harmonization comment**:   This wave collects number of cigarettes a week compared to other waves in LASA which collect number of cigarettes and self-rolled cigarettes.     
**R script**:  
```{r, echo=TRUE}
lsb_LASA1_0$lsb_cig_qty_0 <- ifelse(as.integer(LASA1B$bmvar37)==-2 | as.integer(LASA1B$bmvar37)==-3,0L, ifelse(as.integer(LASA1B$bmvar37)<0,NA,as.integer(LASA1B$bmvar37)/7))
```  
### **Variable label**:  Quantity cigarettes smoked    
**Variable name**:  lsb_cig_qty_1   
**Variable description**:  Current average number of cigarettes smoked per day.  
**Value type**:  integer  
**Variable unit**:  cigarettes/day  
**Category coding**:  

**Harmonization status**:  complete    
**Harmonization comment**:   Study-specific variables is quantity a week of cigarettes and self-rolled cigarettes combined.    
**R script**:  
```{r, echo=TRUE}
lsb_LASA1_1$lsb_cig_qty_1 <- ifelse(as.integer(LASA1C$cmvar31)==1 | as.integer(LASA1C$cmvar351)==0,0L, ifelse(as.integer(LASA1C$cmvar351)==1 & as.integer(LASA1C$cmvar36)>0, as.integer(as.integer(LASA1C$cmvar36)/7),NA))
```  
### **Variable label**:  Quantity cigarettes smoked    
**Variable name**:  lsb_cig_qty_2   
**Variable description**:  Current average number of cigarettes smoked per day.  
**Value type**:  integer  
**Variable unit**:  cigarettes/day  
**Category coding**:  

**Harmonization status**:  complete    
**Harmonization comment**:   Study-specific variables self-rolled cigarettes a week (dmvar40) and cigarette a week (dmvar37) were combined to be consistent with the other waves.  If participant smokes both cigarettes and self-rolled cigarettes but value of quantity smoked a week for one is missing, coded to NA.  
**R script**:  
```{r, echo=TRUE}
lsb_LASA1_2$lsb_cig_qty_2 <- ifelse(as.integer(LASA1D$dmvar31)==1 | (as.integer(LASA1D$dmvar35)==2 & as.integer(LASA1D$dmvar38)==2),0L, ifelse(as.integer(LASA1D$dmvar35)==1 & as.integer(LASA1D$dmvar38)==1, as.integer(sum(as.integer(LASA1D$dmvar37),as.integer(LASA1D$dmvar40),na.rm=F)/7), ifelse(as.integer(LASA1D$dmvar35)==1 & as.integer(LASA1D$dmvar38)==2,as.integer(as.integer(LASA1D$dmvar37)/7), ifelse(as.integer(LASA1D$dmvar38)==1 & as.integer(LASA1D$dmvar35)==2,as.integer(as.integer(LASA1D$dmvar40)/7),NA))))
```  
### **Variable label**:  Quantity cigarettes smoked    
**Variable name**:  lsb_cig_qty_3   
**Variable description**:  Current average number of cigarettes smoked per day.  
**Value type**:  integer  
**Variable unit**:  cigarettes/day  
**Category coding**:  

**Harmonization status**:  complete    
**Harmonization comment**:   Study-specific variables is quantity a week of cigarettes and self-rolled cigarettes combined.    
**R script**:  
```{r, echo=TRUE}
lsb_LASA1_3$lsb_cig_qty_3 <- ifelse(as.integer(LASA1E$emvar31)==1 | as.integer(LASA1E$emvar35)==2,0L, ifelse(as.integer(LASA1E$emvar35)==1 & as.integer(LASA1E$emvar37)>0, as.integer(as.integer(LASA1E$emvar37)/7),NA))
```  
### **Variable label**:  Quantity cigarettes smoked    
**Variable name**:  lsb_cig_qty_4   
**Variable description**:  Current average number of cigarettes smoked per day.  
**Value type**:  integer  
**Variable unit**:  cigarettes/day  
**Category coding**:  

**Harmonization status**:  complete    
**Harmonization comment**:  Study-specific variables is quantity a week of cigarettes and self-rolled cigarettes combined.    
**R script**:  
```{r, echo=TRUE}
lsb_LASA1_4$lsb_cig_qty_4 <- ifelse(as.integer(LASA1F$fmvar31)==1 | as.integer(LASA1F$fmvar35)==2,0L, ifelse(as.integer(LASA1F$fmvar35)==1 & as.integer(LASA1F$fmvar37)>0, as.integer(as.integer(LASA1F$fmvar37)/7),NA))
```  
### **Variable label**:  Quantity cigarettes smoked    
**Variable name**:  lsb_cig_qty_5   
**Variable description**:  Current average number of cigarettes smoked per day.  
**Value type**:  integer  
**Variable unit**:  cigarettes/day  
**Category coding**:  

**Harmonization status**:  complete    
**Harmonization comment**:  Study-specific variables is quantity a week of cigarettes and self-rolled cigarettes combined.    
**R script**:  
```{r, echo=TRUE}
lsb_LASA1_5$lsb_cig_qty_5 <- ifelse(as.integer(LASA1G$gmvar31)==1 | as.integer(LASA1G$gmvar35)==2,0L, ifelse(as.integer(LASA1G$gmvar35)==1 & as.integer(LASA1G$gmvar37)>0, as.integer(as.integer(LASA1G$gmvar37)/7),NA))
```  
### **Variable label**:  Quantity cigarettes smoked    
**Variable name**:  lsb_cig_qty_6   
**Variable description**:  Current average number of cigarettes smoked per day.  
**Value type**:  integer  
**Variable unit**:  cigarettes/day  
**Category coding**:  

**Harmonization status**:  complete    
**Harmonization comment**:  Study-specific variables is quantity a week of cigarettes and self-rolled cigarettes combined.    
**R script**:  
```{r, echo=TRUE}
lsb_LASA1_6$lsb_cig_qty_6 <- ifelse(as.integer(LASA1H$HMVAR31)==1 | as.integer(LASA1H$HMVAR35)==2,0L, ifelse(as.integer(LASA1H$HMVAR35)==1 & as.integer(LASA1H$HMVAR37)>0, as.integer(as.integer(LASA1H$HMVAR37)/7),NA))
```  

### **Variable label**:  Smoking initiation age    
**Variable name**:  lsb_smk_start_0    
**Variable description**:  Age at which the participant started smoking any tobacco product.  
**Value type**:  integer  
**Variable unit**:  years  
**Category coding**:  

**Harmonization status**:  complete  
**Harmonization comment**:     
**R script**:  
```{r, echo=TRUE}
lsb_LASA1_0$lsb_smk_start_0 <- ifelse(as.integer(LASA1B$bmvar33)< 0, NA, LASA1B$bmvar33)
```  
### **Variable label**:  Smoking initiation age    
**Variable name**:  lsb_smk_start_1    
**Variable description**:  Age at which the participant started smoking any tobacco product.  
**Value type**:  integer  
**Variable unit**:  years  
**Category coding**:  

**Harmonization status**:  complete  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
lsb_LASA1_1$lsb_smk_start_1 <- ifelse(as.integer(LASA1C$cmvar33)< 0, NA, LASA1C$cmvar33)
```  
### **Variable label**:  Smoking initiation age    
**Variable name**:  lsb_smk_start_2    
**Variable description**:  Age at which the participant started smoking any tobacco product.  
**Value type**:  integer  
**Variable unit**:  years  
**Category coding**:  

**Harmonization status**:  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
lsb_LASA1_2$lsb_smk_start_2 <- ifelse(as.integer(LASA1D$dmvar33)< 0, NA, LASA1D$dmvar33)
```  
### **Variable label**:  Smoking initiation age    
**Variable name**:  lsb_smk_start_3    
**Variable description**:  Age at which the participant started smoking any tobacco product.  
**Value type**:  integer  
**Variable unit**:  years  
**Category coding**:  

**Harmonization status**:  complete  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
lsb_LASA1_3$lsb_smk_start_3 <- ifelse(as.integer(LASA1E$emvar33)< 0, NA, LASA1E$emvar33)
```  
### **Variable label**:  Smoking initiation age    
**Variable name**:  lsb_smk_start_4    
**Variable description**:  Age at which the participant started smoking any tobacco product.  
**Value type**:  integer  
**Variable unit**:  years  
**Category coding**:  

**Harmonization status**:  complete  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
lsb_LASA1_4$lsb_smk_start_4 <- ifelse(as.integer(LASA1F$fmvar33)< 0, NA, as.integer(LASA1F$fmvar33))
```  
### **Variable label**:  Smoking initiation age    
**Variable name**:  lsb_smk_start_5    
**Variable description**:  Age at which the participant started smoking any tobacco product.  
**Value type**:  integer  
**Variable unit**:  years  
**Category coding**:  

**Harmonization status**:  complete  
**Harmonization comment**:     
**R script**:  
```{r, echo=TRUE}
lsb_LASA1_5$lsb_smk_start_5 <- ifelse(as.integer(LASA1G$gmvar33)< 0, NA, as.integer(LASA1G$gmvar33))
```  
### **Variable label**:  Smoking initiation age    
**Variable name**:  lsb_smk_start_6    
**Variable description**:  Age at which the participant started smoking any tobacco product.  
**Value type**:  integer  
**Variable unit**:  years  
**Category coding**:  

**Harmonization status**:  complete  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
lsb_LASA1_6$lsb_smk_start_6 <- ifelse(as.integer(LASA1H$HMVAR33)< 0, NA, as.integer(LASA1H$HMVAR33))
```  

### **Variable label**:  Smoking cessation age  
**Variable name**:  lsb_smk_stop_0   
**Variable description**:  Age at which the participant last smoked any tobacco product.  
**Value type**:  integer  
**Variable unit**:  years  
**Category coding**:  

**Harmonization status**:  complete  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
lsb_LASA1_0$lsb_smk_start_0 <- ifelse(as.integer(LASA1B$bmvar34)< 0, NA, as.integer(LASA1B$bmvar34))
```  
### **Variable label**:  Smoking cessation age  
**Variable name**:  lsb_smk_stop_1   
**Variable description**:  Age at which the participant last smoked any tobacco product.  
**Value type**:  integer  
**Variable unit**:  years  
**Category coding**:  

**Harmonization status**:  complete  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
lsb_LASA1_1$lsb_smk_start_1 <- ifelse(as.integer(LASA1C$cmvar34)< 0, NA, as.integer(LASA1C$cmvar34))
```  
### **Variable label**:  Smoking cessation age  
**Variable name**:  lsb_smk_stop_2   
**Variable description**:  Age at which the participant last smoked any tobacco product.  
**Value type**:  integer  
**Variable unit**:  years  
**Category coding**:  

**Harmonization status**:  complete  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
lsb_LASA1_2$lsb_smk_start_2 <- ifelse(as.integer(LASA1D$dmvar34)< 0, NA, as.integer(LASA1D$dmvar34))
```  
### **Variable label**:  Smoking cessation age  
**Variable name**:  lsb_smk_stop_3   
**Variable description**:  Age at which the participant last smoked any tobacco product.  
**Value type**:  integer  
**Variable unit**:  years  
**Category coding**:  

**Harmonization status**:  complete  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
lsb_LASA1_3$lsb_smk_start_3 <- ifelse(as.integer(LASA1E$emvar34)< 0, NA, as.integer(LASA1E$emvar34))
```  
### **Variable label**:  Smoking cessation age  
**Variable name**:  lsb_smk_stop_4   
**Variable description**:  Age at which the participant last smoked any tobacco product.  
**Value type**:  integer  
**Variable unit**:  years  
**Category coding**:  

**Harmonization status**:  complete  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
lsb_LASA1_4$lsb_smk_start_4 <- ifelse(as.integer(LASA1F$fmvar34)< 0, NA, as.integer(LASA1F$fmvar34))
```  
### **Variable label**:  Smoking cessation age  
**Variable name**:  lsb_smk_stop_5   
**Variable description**:  Age at which the participant last smoked any tobacco product.  
**Value type**:  integer  
**Variable unit**:  years  
**Category coding**:  

**Harmonization status**:  complete  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
lsb_LASA1_5$lsb_smk_start_5 <- ifelse(as.integer(LASA1G$gmvar34)< 0, NA, as.integer(LASA1G$gmvar34))
```  
### **Variable label**:  Smoking cessation age  
**Variable name**:  lsb_smk_stop_6   
**Variable description**:  Age at which the participant last smoked any tobacco product.  
**Value type**:  integer  
**Variable unit**:  years  
**Category coding**:  

**Harmonization status**:  complete  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
lsb_LASA1_6$lsb_smk_start_6 <- ifelse(as.integer(LASA1H$HMVAR34)< 0, NA, as.integer(LASA1H$HMVAR34))
```  

### **Variable label**:  Pack years  
**Variable name**:  lsb_smk_py_0    
**Variable description**:  Number of estimated pack years of the participant.   
**Value type**:  integer  
**Variable unit**:  pack-years    
**Category coding**:  

**Harmonization status**:  impossible      
**Harmonization comment**:    
**R script**:  
```{r, echo=TRUE}

```  
### **Variable label**:  Pack years  
**Variable name**:  lsb_smk_py_1    
**Variable description**:  Number of estimated pack years of the participant.     
**Value type**:  integer  
**Variable unit**:  pack-years    
**Category coding**:  

**Harmonization status**:  impossible      
**Harmonization comment**:     
**R script**:  
```{r, echo=TRUE}

```  
### **Variable label**:  Pack years  
**Variable name**:  lsb_smk_py_2    
**Variable description**:  Number of estimated pack years of the participant.     
**Value type**:  integer  
**Variable unit**:  pack-years    
**Category coding**:  

**Harmonization status**:  impossible      
**Harmonization comment**:    
**R script**:  
```{r, echo=TRUE}

```  

# Physical activity subdomain

### **Variable label**: Frequency of walking    
**Variable name**:    lsb_pa_walk_freq_0    
**Variable description**:  Number of times the participant went for a walk in last week.    
**Value type**:  integer  
**Variable unit**:  N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 |  Never  
1 |  Seldom (1-2 dyas)  
2 |  Sometimes (3-4 days)  
3 |  Often (5-7 days)  

**Harmonization status**:  impossible    
**Harmonization comment**:   study-specific asks for number of times walked outside in the past two weeks, not number of days the partcicipant went for a walk.     
**R script**:  
```{r, echo=TRUE}

```  
### **Variable label**: Frequency of walking    
**Variable name**:    lsb_pa_walk_freq_1    
**Variable description**:  Number of times the participant went for a walk in last week.    
**Value type**:  integer  
**Variable unit**:  N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 |  Never  
1 |  Seldom (1-2 dyas)  
2 |  Sometimes (3-4 days)  
3 |  Often (5-7 days)  

**Harmonization status**:  impossible    
**Harmonization comment**:   study-specific asks for number of times walked outside in the past two weeks, not number of days the partcicipant went for a walk.  
**R script**:  
```{r, echo=TRUE}

```  
### **Variable label**: Frequency of walking    
**Variable name**:    lsb_pa_walk_freq_2    
**Variable description**:  Number of times the participant went for a walk in last week.    
**Value type**:  integer  
**Variable unit**:  N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 |  Never  
1 |  Seldom (1-2 dyas)  
2 |  Sometimes (3-4 days)  
3 |  Often (5-7 days)    

**Harmonization status**:  impossible    
**Harmonization comment**:   study-specific asks for number of times walked outside in the past two weeks, not number of days the partcicipant went for a walk.  
**R script**:  
```{r, echo=TRUE}

```  
### **Variable label**: Frequency of walking    
**Variable name**:    lsb_pa_walk_freq_3    
**Variable description**:  Number of times the participant went for a walk in last week.    
**Value type**:  integer  
**Variable unit**:  N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 |  Never  
1 |  Seldom (1-2 dyas)  
2 |  Sometimes (3-4 days)  
3 |  Often (5-7 days)    

**Harmonization status**:  impossible    
**Harmonization comment**:   study-specific asks for number of times walked outside in the past two weeks, not number of days the partcicipant went for a walk.  
**R script**:  
```{r, echo=TRUE}

```  
### **Variable label**: Frequency of walking    
**Variable name**:    lsb_pa_walk_freq_4    
**Variable description**:  Number of times the participant went for a walk in last week.    
**Value type**:  integer  
**Variable unit**:  N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 |  Never  
1 |  Seldom (1-2 dyas)  
2 |  Sometimes (3-4 days)  
3 |  Often (5-7 days)    

**Harmonization status**:  impossible    
**Harmonization comment**:   study-specific asks for number of times walked outside in the past two weeks, not number of days the partcicipant went for a walk.  
**R script**:  
```{r, echo=TRUE}

```  
### **Variable label**: Frequency of walking    
**Variable name**:    lsb_pa_walk_freq_5    
**Variable description**:  Number of times the participant went for a walk in last week.    
**Value type**:  integer  
**Variable unit**:  N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 |  Never  
1 |  Seldom (1-2 dyas)  
2 |  Sometimes (3-4 days)  
3 |  Often (5-7 days)    

**Harmonization status**:  impossible    
**Harmonization comment**:   study-specific asks for number of times walked outside in the past two weeks, not number of days the partcicipant went for a walk.  
**R script**:  
```{r, echo=TRUE}

```  
### **Variable label**: Frequency of walking    
**Variable name**:    lsb_pa_walk_freq_6    
**Variable description**:  Number of times the participant went for a walk in last week.    
**Value type**:  integer  
**Variable unit**:  N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 |  Never  
1 |  Seldom (1-2 dyas)  
2 |  Sometimes (3-4 days)  
3 |  Often (5-7 days)    

**Harmonization status**:  impossible    
**Harmonization comment**:   study-specific asks for number of times walked outside in the past two weeks, not number of days the partcicipant went for a walk.  
**R script**:  
```{r, echo=TRUE}

```  

### **Variable label**:  Average walking time     
**Variable name**:   lsb_pa_walk_time_0  
**Variable description**:  Average time the participant spends walking per day.    
**Value type**:  integer  
**Variable unit**:  N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 |  Less than 30 minutes  
1 |  30 minutes but less than 1 hour  
2 |  1 hour but less than 2 hours
3 |  2 hours but less than 4 hours  
4 |  4 hours or more  

**Harmonization status**:  complete  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}

```  
### **Variable label**:  Average walking time   
**Variable name**:   lsb_pa_walk_time_1  
**Variable description**:  Average time the participant spends walking per day.    
**Value type**:  integer  
**Variable unit**:  N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 |  Less than 30 minutes  
1 |  30 minutes but less than 1 hour  
2 |  1 hour but less than 2 hours
3 |  2 hours but less than 4 hours  
4 |  4 hours or more   

**Harmonization status**:  complete  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}

```  
### **Variable label**:  Average walking time    
**Variable name**:   lsb_pa_walk_time_2  
**Variable description**:  Average time the participant spends walking per day.    
**Value type**:  integer  
**Variable unit**:  N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 |  Less than 30 minutes  
1 |  30 minutes but less than 1 hour  
2 |  1 hour but less than 2 hours
3 |  2 hours but less than 4 hours  
4 |  4 hours or more   

**Harmonization status**:  complete  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}

```  
### **Variable label**:  Average walking time     
**Variable name**:   lsb_pa_walk_time_3  
**Variable description**:  Average time the participant spends walking per day.    
**Value type**:  integer  
**Variable unit**:  N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 |  Less than 30 minutes  
1 |  30 minutes but less than 1 hour  
2 |  1 hour but less than 2 hours
3 |  2 hours but less than 4 hours  
4 |  4 hours or more   

**Harmonization status**:  complete  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}

```  
### **Variable label**:  Average walking time    
**Variable name**:   lsb_pa_walk_time_4  
**Variable description**:  Average time the participant spends walking per day.    
**Value type**:  integer  
**Variable unit**:  N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 |  Less than 30 minutes  
1 |  30 minutes but less than 1 hour  
2 |  1 hour but less than 2 hours
3 |  2 hours but less than 4 hours  
4 |  4 hours or more     

**Harmonization status**:  complete  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}

```  
### **Variable label**:  Average walking time     
**Variable name**:   lsb_pa_walk_time_5  
**Variable description**:  Average time the participant spends walking per day.    
**Value type**:  integer  
**Variable unit**:  N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 |  Less than 30 minutes  
1 |  30 minutes but less than 1 hour  
2 |  1 hour but less than 2 hours
3 |  2 hours but less than 4 hours  
4 |  4 hours or more     

**Harmonization status**:  complete  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}

```  
### **Variable label**:  Average walking time     
**Variable name**:   lsb_pa_walk_time_6  
**Variable description**:  Average time the participant spends walking per day.    
**Value type**:  integer  
**Variable unit**:  N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 |  Less than 30 minutes  
1 |  30 minutes but less than 1 hour  
2 |  1 hour but less than 2 hours
3 |  2 hours but less than 4 hours  
4 |  4 hours or more    

**Harmonization status**:  complete  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}

```  

### **Variable label**:  Average walking time for transportation  
**Variable name**:  lsb_pa_walk_trans_0    
**Variable description**:  Minutes per week the participant spent on walking for transportation (utilitarian walking) in the last week.  
**Value type**:  decimal    
**Variable unit**:  minutes/week  
**Category coding**:  N/A  

**Harmonization status**:  impossible  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}

```  
### **Variable label**:  Average walking time for transportation    
**Variable name**:  lsb_pa_walk_trans_1    
**Variable description**: Minutes per week the participant spent on walking for transportation (utilitarian walking) in the last week.    
**Value type**:  decimal    
**Variable unit**:  minutes/week  
**Category coding**:  N/A  

**Harmonization status**:  impossile  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}

```  
### **Variable label**:  Average walking time for transportation    
**Variable name**:  lsb_pa_walk_trans_2    
**Variable description**:  Minutes per week the participant spent on walking for transportation (utilitarian walking) in the last week.  
**Value type**:  decimal    
**Variable unit**:  minutes/week  
**Category coding**:  N/A  

**Harmonization status**:  impossible  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}

```  
### **Variable label**:  Average walking for transportation    
**Variable name**:  lsb_pa_walk_trans_4    
**Variable description**:  Minutes per week the participant spent on walking for transportation (utilitarian walking) in the last week.    
**Value type**:  decimal    
**Variable unit**:  minutes/week  
**Category coding**:  N/A  

**Harmonization status**:  impossible  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}

```  

### **Variable label**:  Average walking time for leisure  
**Variable name**:  lsb_pa_walk_leis_0    
**Variable description**:  Minutes per week the participant spent on walking for leisure in the last week.  
**Value type**:  decimal    
**Variable unit**:  minutes/week  
**Category coding**:  N/A  

**Harmonization status**:  impossible  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}

```  
### **Variable label**:  Average walking time for leisure  
**Variable name**:  lsb_pa_walk_leis_2    
**Variable description**:  Minutes per week the participant spent on walking for leisure in the last week.  
**Value type**:  decimal    
**Variable unit**:  minutes/week  
**Category coding**:  N/A  

**Harmonization status**:  impossible  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}

```  
### **Variable label**:  Average walking time for leisure  
**Variable name**:  lsb_pa_walk_leis_3    
**Variable description**:  Minutes per week the participant spent on walking for leisure in the last week.  
**Value type**:  decimal    
**Variable unit**:  minutes/week  
**Category coding**:  N/A  

**Harmonization status**:  impossible  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}

```  
### **Variable label**:  Average walking for leisure  
**Variable name**:  lsb_pa_walk_leis_4    
**Variable description**:  Minutes per week the participant spent on walking for leisure in the last week.  
**Value type**:  decimal    
**Variable unit**:  minutes/week  
**Category coding**:  N/A  

**Harmonization status**:  impossible  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}

```  

### **Variable label**:  Average cycling time    
**Variable name**:  lsb_pa_cycle_0  
**Variable description**:  Average minutes per week the participant spent on cycling in the last week.  
**Value type**:  decimal    
**Variable unit**:  minutes per week  
**Category coding**:  N/A  

**Harmonization status**:  complete  
**Harmonization comment**:   blphya13=minutes, blphya11=2weeks, blphya10=biking |as.integer(LASA1B$blphya11)==-2) (redo)
**R script**:  
```{r, echo=TRUE}
#lsb_LASA1_0$lsb_pa_cycle_0 <- ifelse(as.integer(LASA1B$blphya13)==-1 | as.integer(LASA1B$blphya13)==-3 | as.integer(LASA1B$blphya11)==-1 | as.integer(LASA1B$blphya10)==-1,NA_integer_, ifelse(as.integer(LASA1B$blphya13)==-2 & as.integer(LASA1B$blphya11)==1, 0L, ifelse(as.integer(LASA1B$blphya13)==-2 & as.integer(LASA1B$blphya11)==-2 & as.integer(LASA1B$blphya10)==1,0L, (as.numeric(LASA1B$blphya13)/2))))

#lsb_LASA1_0$lsb_pa_cycle_0 <- ifelse(as.integer(LASA1B$blphya13)==-2 & as.integer(LASA1B$blphya11)==1, 0L, ifelse(as.integer(LASA1B$blphya13)==-2 & as.integer(LASA1B$blphya11)==-2 & as.integer(LASA1B$blphya10)==1,0L, ifelse(as.integer(LASA1B$blphya13) <0 | as.integer(LASA1B$blphya11) <0 | as.integer(LASA1B$blphya10)<0 ,NA_integer_, ((as.numeric(LASA1B$blphya12)*as.numeric(LASA1B$blphya13))/2))))

lsb_LASA1_0$lsb_pa_cycle_0 <- ifelse(as.integer(LASA1B$blphya10)==1 | as.integer(LASA1B$blphya11)==1,0L, ifelse(as.integer(LASA1B$blphya11)==2 & as.integer(LASA1B$blphya12)>0 & as.integer(LASA1B$blphya13)>0,((as.numeric(LASA1B$blphya12)*as.numeric(LASA1B$blphya13))/2),NA))
```  
### **Variable label**:  Average cycling time    
**Variable name**:  lsb_pa_cycle_1  
**Variable description**:  Average minutes per week the participant spent on cycling in the last week.    
**Value type**:  decimal    
**Variable unit**:  minutes per week  
**Category coding**:  N/A  

**Harmonization status**:  complete  
**Harmonization comment**:   (redo)  
**R script**:  
```{r, echo=TRUE}
#lsb_LASA1_1$lsb_pa_cycle_1 <- ifelse(as.integer(LASA1C$clphya13)<0, NA_integer_, (as.integer(LASA1C$clphya13)/2))
```  
### **Variable label**:  Average cycling time    
**Variable name**:  lsb_pa_cycle_2  
**Variable description**:  Average minutes per week the participant spent on cycling in the last week.    
**Value type**:  decimal    
**Variable unit**:  minutes per week  
**Category coding**:  N/A  

**Harmonization status**:  complete  
**Harmonization comment**:   (redo)  
**R script**:  
```{r, echo=TRUE}
#lsb_LASA1_2$lsb_pa_cycle_2 <- (as.integer(LASA1D$dlphya13)/2)
```  
### **Variable label**:  Average cycling time    
**Variable name**:  lsb_pa_cycle_3  
**Variable description**:  Average minutes per week the participant spent on cycling in the last week.    
**Value type**:  decimal    
**Variable unit**:  minutes per week  
**Category coding**:  N/A  

**Harmonization status**:  complete  
**Harmonization comment**:   (redo)  
**R script**:  
```{r, echo=TRUE}
#lsb_LASA1_3$lsb_pa_cycle_3 <- (as.integer(LASA1E$elphya13)/2)
```  
### **Variable label**:  Average cycling time    
**Variable name**:  lsb_pa_cycle_4  
**Variable description**:  Average minutes per week the participant spent on cycling in the last week.    
**Value type**:  decimal    
**Variable unit**:  minutes per week  
**Category coding**:  N/A  

**Harmonization status**:  complete  
**Harmonization comment**:   (redo)  
**R script**:  
```{r, echo=TRUE}
#lsb_LASA1_4$lsb_pa_cycle_4 <- (as.integer(LASA1F$flphya13)/2)
```  
### **Variable label**:  Average cycling time    
**Variable name**:  lsb_pa_cycle_5  
**Variable description**:  Average minutes per week the participant spent on cycling in the last week.    
**Value type**:  decimal    
**Variable unit**:  minutes per week  
**Category coding**:  N/A  

**Harmonization status**:  complete  
**Harmonization comment**:   (redo)  
**R script**:  
```{r, echo=TRUE}
#lsb_LASA1_5$lsb_pa_cycle_5 <- (as.integer(LASA1G$glphya13)/2)
```  
### **Variable label**:  Average cycling time    
**Variable name**:  lsb_pa_cycle_6  
**Variable description**:  Average minutes per week the participant spent on cycling in the last week.    
**Value type**:  decimal    
**Variable unit**:  minutes per week  
**Category coding**:  N/A  

**Harmonization status**:  complete  
**Harmonization comment**:   (redo)  
**R script**:  
```{r, echo=TRUE}
#lsb_LASA1_6$lsb_pa_cycle_6 <- (as.integer(LASA1H$HLPHYA13)/2)
```  

### **Variable label**:  Gardening   
**Variable name**:  lsb_pa_garden_0  
**Variable description**:  Indicator of whether the participant does any gardening activities.  
**Value type**:  integer  
**Variable unit**:  N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 |   Does not do any gardening activities  
1 |   Does any gardeing activities  

**Harmonization status**:  complete  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
lsb_LASA1_0$lsb_pa_garden_0 <- ifelse(as.integer(LASA1B$blphya17)==2,1L, ifelse(as.integer(LASA1B$blphya17)==1, 0L, ifelse(as.integer(LASA1B$blphya17)==-2 & as.integer(LASA1B$blphya15)==-2 & as.integer(LASA1B$blphya14)==1,0L,NA)))
```  
### **Variable label**:  Gardening    
**Variable name**:  lsb_pa_garden_1  
**Variable description**:  Indicator of whether the participant does any gardening activities.  
**Value type**:  integer  
**Variable unit**:  N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 |   Does not do any gardening activities  
1 |   Does any gardeing activities  

**Harmonization status**:  complete  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
lsb_LASA1_1$lsb_pa_garden_1 <- ifelse(as.integer(LASA1C$clphya17)==2, 1L, ifelse(as.integer(LASA1C$clphya17)==1, 0L, ifelse(as.integer(LASA1C$clphya17)==-2 & as.integer(LASA1C$clphya15)==-2 & as.integer(LASA1C$clphya14)==1,0L,NA)))
```  
### **Variable label**:  Gardening    
**Variable name**:  lsb_pa_garden_2  
**Variable description**:  Indicator of whether the participant does any gardening activities.  
**Value type**:  integer  
**Variable unit**:  N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 |   Does not do any gardening activities  
1 |   Does any gardeing activities  

**Harmonization status**:  complete  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
lsb_LASA1_2$lsb_pa_garden_2 <- ifelse(as.integer(LASA1D$dlphya17)==2, 1L, ifelse(as.integer(LASA1D$dlphya17)==1,0L, ifelse(as.integer(LASA1D$dlphya17)==-2 & as.integer(LASA1D$dlphya15)==-2 & as.integer(LASA1D$dlphya14)==1,0L,NA)))
```  
### **Variable label**:  Gardening    
**Variable name**:  lsb_pa_garden_3  
**Variable description**:  Indicator of whether the participant does any gardening activities.  
**Value type**:  integer  
**Variable unit**:  N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 |   Does not do any gardening activities  
1 |   Does any gardeing activities  

**Harmonization status**:  complete  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
lsb_LASA1_3$lsb_pa_garden_3 <- ifelse(as.integer(LASA1E$elphya17)==2, 1L, ifelse(as.integer(LASA1E$elphya17)==1, 0L, ifelse(as.integer(LASA1E$elphya17)==-2 & as.integer(LASA1E$elphya15)==-2 & as.integer(LASA1E$elphya14)==1,0L,NA)))
```  
### **Variable label**:  Gardening    
**Variable name**:  lsb_pa_garden_4  
**Variable description**:  Indicator of whether the participant does any gardening activities.  
**Value type**:  integer  
**Variable unit**:  N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 |   Does not do any gardening activities  
1 |   Does any gardeing activities  

**Harmonization status**:  complete  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
lsb_LASA1_4$lsb_pa_garden_4 <- ifelse(as.integer(LASA1F$flphya17)==2,1L, ifelse(as.integer(LASA1F$flphya17)==1,0L, ifelse(as.integer(LASA1F$flphya17)==-2 & as.integer(LASA1F$flphya15)==-2 & as.integer(LASA1F$flphya14)==1,0L,NA)))
```  
### **Variable label**:  Gardening    
**Variable name**:  lsb_pa_garden_5  
**Variable description**:  Indicator of whether the participant does any gardening activities.  
**Value type**:  integer  
**Variable unit**:  N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 |   Does not do any gardening activities  
1 |   Does any gardeing activities  

**Harmonization status**:  complete  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
lsb_LASA1_5$lsb_pa_garden_5 <- ifelse(as.integer(LASA1G$glphya17)==2,1L, ifelse(as.integer(LASA1G$glphya17)==1,0L, ifelse(as.integer(LASA1G$glphya17)==-2 & as.integer(LASA1G$glphya15)==-2 & as.integer(LASA1G$glphya14)==1,0L,NA)))
```  
### **Variable label**:  Gardening    
**Variable name**:  lsb_pa_garden_6  
**Variable description**:  Indicator of whether the participant does any gardening activities.  
**Value type**:  integer  
**Variable unit**:  N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 |   Does not do any gardening activities  
1 |   Does any gardeing activities  

**Harmonization status**:  complete  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
lsb_LASA1_6$lsb_pa_garden_6 <- ifelse(as.integer(LASA1H$HLPHYA17)==2, 1L, ifelse(as.integer(LASA1H$HLPHYA17)==1,0L, ifelse(as.integer(LASA1H$HLPHYA17)==-2 & as.integer(LASA1H$HLPHYA15)==-2 & as.integer(LASA1H$HLPHYA14)==1,0L,NA)))
```  
### **Variable label**:  Average gardening time    
**Variable name**:  lsb_pa_garden_time_0    
**Variable description**:  Average minutes per week the participant spent on gardening activities in the last week.    
**Value type**:  decimal    
**Variable unit**:  minutes/week  
**Category coding**:  N/A  

**Harmonization status**:  complete  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
lsb_LASA1_0$lsb_pa_garden_time_0 <- ifelse(as.integer(LASA1B$blphya19)==-2 & as.integer(LASA1B$blphya17)==-2 & as.integer(LASA1B$blphya14)==1,0L, ifelse(as.integer(LASA1B$blphya19)<0, NA,as.integer(LASA1B$blphya19)/2))
```  
### **Variable label**:  Average gardening time    
**Variable name**:  lsb_pa_garden_time_1    
**Variable description**:  Average minutes per week the participant spent on gardening activities in the last week.       
**Value type**:  decimal    
**Variable unit**:  minutes/week    
**Category coding**:  N/A  

**Harmonization status**:  complete  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
lsb_LASA1_1$lsb_pa_garden_time_1 <- ifelse(as.integer(LASA1C$clphya19)==-2 & as.integer(LASA1C$clphya17)==-2 & as.integer(LASA1C$clphya14)==1,0L, ifelse(as.integer(LASA1C$clphya19)<0, NA,as.integer(LASA1C$clphya19)/2))
```  
### **Variable label**:  Average gardening time    
**Variable name**:  lsb_pa_garden_time_2    
**Variable description**:  Average minutes per week the participant spent on gardening activities in the last week.       
**Value type**:  decimal    
**Variable unit**:  minutes/week    
**Category coding**:  N/A  

**Harmonization status**:  complete  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
lsb_LASA1_2$lsb_pa_garden_time_2 <- ifelse(as.integer(LASA1D$dlphya19)==-2 & as.integer(LASA1D$dlphya17)==-2 & as.integer(LASA1D$dlphya14)==1,0L, ifelse(as.integer(LASA1D$dlphya19)<0, NA,as.integer(LASA1D$dlphya19)/2))
```  
### **Variable label**:  Average gardening time    
**Variable name**:  lsb_pa_garden_time_3    
**Variable description**:  Average minutes per week the participant spent on gardening activities in the last week.       
**Value type**:  decimal    
**Variable unit**:  minutes/week    
**Category coding**:  N/A  

**Harmonization status**:  complete  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
lsb_LASA1_3$lsb_pa_garden_time_3 <- ifelse(as.integer(LASA1E$elphya19)==-2 & as.integer(LASA1E$elphya17)==-2 & as.integer(LASA1E$elphya14)==1,0L, ifelse(as.integer(LASA1E$elphya19)<0, NA,as.integer(LASA1E$elphya19)/2))
```  
### **Variable label**:  Average gardening time    
**Variable name**:  lsb_pa_garden_time_4    
**Variable description**:  Average minutes per week the participant spent on gardening activities in the last week.       
**Value type**:  decimal    
**Variable unit**:  minutes/week    
**Category coding**:  N/A  

**Harmonization status**:  complete  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
lsb_LASA1_4$lsb_pa_garden_time_4 <- ifelse(as.integer(LASA1F$flphya19)==-2 & as.integer(LASA1F$flphya17)==-2 & as.integer(LASA1F$flphya14)==1,0L, ifelse(as.integer(LASA1F$flphya19)<0, NA,as.integer(LASA1F$flphya19)/2))
```  
### **Variable label**:  Average gardening time    
**Variable name**:  lsb_pa_garden_time_5    
**Variable description**:  Average minutes per week the participant spent on gardening activities in the last week.       
**Value type**:  decimal    
**Variable unit**:  minutes/week    
**Category coding**:  N/A  

**Harmonization status**:  complete  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
lsb_LASA1_5$lsb_pa_garden_time_5 <- ifelse(as.integer(LASA1G$glphya19)==-2 & as.integer(LASA1G$glphya17)==-2 & as.integer(LASA1G$glphya14)==1,0L, ifelse(as.integer(LASA1G$glphya19)<0, NA,as.integer(LASA1G$glphya19)/2))
```  
### **Variable label**:  Average gardening time    
**Variable name**:  lsb_pa_garden_time_6    
**Variable description**:  Average minutes per week the participant spent on gardening activities in the last week.       
**Value type**:  decimal    
**Variable unit**:  minutes/week    
**Category coding**:  N/A  

**Harmonization status**:  complete  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
lsb_LASA1_6$lsb_pa_garden_time_6 <- ifelse(as.integer(LASA1H$HLPHYA19)==-2 & as.integer(LASA1H$HLPHYA17)==-2 & as.integer(LASA1H$HLPHYA14)==1,0L, ifelse(as.integer(LASA1H$HLPHYA19)<0, NA,as.integer(LASA1H$HLPHYA19)/2))
```  

### **Variable label**:  Household activities  
**Variable name**:  lsb_pa_house_0  
**Variable description**:  Indicator of whether the participant does any household activities (light, moderate or vigorous).     
**Value type**:  integer  
**Variable unit**:  N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 |   Does not do any household activities  
1 |   Does any household activities  

**Harmonization status**:  complete  
**Harmonization comment**: blphya32= light 2weeks, blphya31= light, blphya36= heavy 2weeks, blphya35= heavy (redo)
**R script**:  
```{r, echo=TRUE}
lsb_LASA1_0$lsb_pa_house_0<- ifelse((as.integer(LASA1B$blphya32)== 1 & as.integer(LASA1B$blphya36)== 1) | 
                                      ((as.integer(LASA1B$blphya32)== -2 & as.integer(LASA1B$blphya31)== 1) &
                                         (as.integer(LASA1B$blphya36)== -2) & as.integer(LASA1B$blphya35)==1) |
                                      ((as.integer(LASA1B$blphya32)== -2 & as.integer(LASA1B$blphya31)== 1)& 
                                         as.integer(LASA1B$blphya36)== 1) |
                                      (as.integer(LASA1B$blphya32)== 1 & 
                                          (as.integer(LASA1B$blphya36)== -2 & as.integer(LASA1B$blphya35)==1)), 0L,
                              ifelse((as.integer(LASA1B$blphya32)== 2 & as.integer(LASA1B$blphya36)== 1) |
                                        (as.integer(LASA1B$blphya32)== 1 & as.integer(LASA1B$blphya36)== 2) |
                                        (as.integer(LASA1B$blphya32)== 2 & as.integer(LASA1B$blphya36)== 1) |
                                        (as.integer(LASA1B$blphya32)== 2 & as.integer(LASA1B$blphya36)== 2) |
                                        (as.integer(LASA1B$blphya32)== 2 & as.integer(LASA1B$blphya36)== 3) |
                                        (as.integer(LASA1B$blphya32)== 2 & as.integer(LASA1B$blphya36)== 4) |
                                        (as.integer(LASA1B$blphya32)== 3 & as.integer(LASA1B$blphya36)== 2) |
                                        (as.integer(LASA1B$blphya32)== 2 & 
                                           (as.integer(LASA1B$blphya36)== -2 & as.integer(LASA1B$blphya35)==1)) |
                                        ((as.integer(LASA1B$blphya32)== -2& as.integer(LASA1B$blphya31)==1) 
                                           & as.integer(LASA1B$blphya36)== 2), 1L, NA))
```  
### **Variable label**:  Household activities  
**Variable name**:  lsb_pa_house_1  
**Variable description**:  Indicator of whether the participant does any household activities (light, moderate or vigorous).     
**Value type**:  integer  
**Variable unit**:  N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 |   Does not do any household activities  
1 |   Does any household activities  

**Harmonization status**:  complete  
**Harmonization comment**:   (redo)
**R script**:  
```{r, echo=TRUE}
lsb_LASA1_1$lsb_pa_house_1<- ifelse((as.integer(LASA1C$clphya32)== 1 & as.integer(LASA1C$clphya36)== 1) | 
                                      (as.integer(LASA1C$clphya32)== -2 & as.integer(LASA1C$clphya36)== -2) |
                                      (as.integer(LASA1C$clphya32)== -2 & as.integer(LASA1C$clphya36)== 1) |
                                      (as.integer(LASA1C$clphya32)== 1 & as.integer(LASA1C$clphya36)== -2), 0L,
                              ifelse((as.integer(LASA1C$clphya32)== 2 & as.integer(LASA1C$clphya36)== 1) |
                                        (as.integer(LASA1C$clphya32)== 1 & as.integer(LASA1C$clphya36)== 2) |
                                        (as.integer(LASA1C$clphya32)== 2 & as.integer(LASA1C$clphya36)== 1) |
                                        (as.integer(LASA1C$clphya32)== 2 & as.integer(LASA1C$clphya36)== 2) |
                                        (as.integer(LASA1C$clphya32)== 2 & as.integer(LASA1C$clphya36)== 3) |
                                        (as.integer(LASA1C$clphya32)== 2 & as.integer(LASA1C$clphya36)== 4) |
                                        (as.integer(LASA1C$clphya32)== 3 & as.integer(LASA1C$clphya36)== 2) |
                                        (as.integer(LASA1C$clphya32)== 2 & as.integer(LASA1C$clphya36)== -2) |
                                        (as.integer(LASA1C$clphya32)== -2 & as.integer(LASA1C$clphya36)== 2), 1L, NA))
```  
### **Variable label**:  Household activities  
**Variable name**:  lsb_pa_house_2  
**Variable description**:  Indicator of whether the participant does any household activities (light, moderate or vigorous).     
**Value type**:  integer  
**Variable unit**:  N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 |   Does not do any household activities  
1 |   Does any household activities  

**Harmonization status**:  complete  
**Harmonization comment**:   (redo)
**R script**:  
```{r, echo=TRUE}
lsb_LASA1_2$lsb_pa_house_2<- ifelse((as.integer(LASA1D$dlphya32)== 1 & as.integer(LASA1D$dlphya36)== 1) | 
                                      (as.integer(LASA1D$dlphya32)== -2 & as.integer(LASA1D$dlphya36)== -2) |
                                      (as.integer(LASA1D$dlphya32)== -2 & as.integer(LASA1D$dlphya36)== 1) |
                                      (as.integer(LASA1D$dlphya32)== 1 & as.integer(LASA1D$dlphya36)== -2), 0L,
                              ifelse((as.integer(LASA1D$dlphya32)== 2 & as.integer(LASA1D$dlphya36)== 1) |
                                        (as.integer(LASA1D$dlphya32)== 1 & as.integer(LASA1D$dlphya36)== 2) |
                                        (as.integer(LASA1D$dlphya32)== 2 & as.integer(LASA1D$dlphya36)== 1) |
                                        (as.integer(LASA1D$dlphya32)== 2 & as.integer(LASA1D$dlphya36)== 2) |
                                        (as.integer(LASA1D$dlphya32)== 2 & as.integer(LASA1D$dlphya36)== 3) |
                                        (as.integer(LASA1D$dlphya32)== 2 & as.integer(LASA1D$dlphya36)== 4) |
                                        (as.integer(LASA1D$dlphya32)== 3 & as.integer(LASA1D$dlphya36)== 2) |
                                        (as.integer(LASA1D$dlphya32)== 2 & as.integer(LASA1D$dlphya36)== -2) |
                                        (as.integer(LASA1D$dlphya32)== -2 & as.integer(LASA1D$dlphya36)== 2), 1L, NA))
```  
### **Variable label**:  Household activities  
**Variable name**:  lsb_pa_house_3  
**Variable description**:  Indicator of whether the participant does any household activities (light, moderate or vigorous).     
**Value type**:  integer  
**Variable unit**:  N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 |   Does not do any household activities  
1 |   Does any household activities  

**Harmonization status**:  complete  
**Harmonization comment**:   (redo)
**R script**:  
```{r, echo=TRUE}
lsb_LASA1_3$lsb_pa_house_3<- ifelse((as.integer(LASA1E$elphya32)== 1 & as.integer(LASA1E$elphya36)== 1) | 
                                      (as.integer(LASA1E$elphya32)== -2 & as.integer(LASA1E$elphya36)== -2) |
                                      (as.integer(LASA1E$elphya32)== -2 & as.integer(LASA1E$elphya36)== 1) |
                                      (as.integer(LASA1E$elphya32)== 1 & as.integer(LASA1E$elphya36)== -2), 0L,
                              ifelse((as.integer(LASA1E$elphya32)== 2 & as.integer(LASA1E$elphya36)== 1) |
                                        (as.integer(LASA1E$elphya32)== 1 & as.integer(LASA1E$elphya36)== 2) |
                                        (as.integer(LASA1E$elphya32)== 2 & as.integer(LASA1E$elphya36)== 1) |
                                        (as.integer(LASA1E$elphya32)== 2 & as.integer(LASA1E$elphya36)== 2) |
                                        (as.integer(LASA1E$elphya32)== 2 & as.integer(LASA1E$elphya36)== 3) |
                                        (as.integer(LASA1E$elphya32)== 2 & as.integer(LASA1E$elphya36)== 4) |
                                        (as.integer(LASA1E$elphya32)== 3 & as.integer(LASA1E$elphya36)== 2) |
                                        (as.integer(LASA1E$elphya32)== 2 & as.integer(LASA1E$elphya36)== -2) |
                                        (as.integer(LASA1E$elphya32)== -2 & as.integer(LASA1E$elphya36)== 2), 1L, NA))
```  
### **Variable label**:  Household activities  
**Variable name**:  lsb_pa_house_4  
**Variable description**:  Indicator of whether the participant does any household activities (light, moderate or vigorous).     
**Value type**:  integer  
**Variable unit**:  N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 |   Does not do any household activities  
1 |   Does any household activities  

**Harmonization status**:  complete  
**Harmonization comment**:   (redo)
**R script**:  
```{r, echo=TRUE}
lsb_LASA1_4$lsb_pa_house_4<- ifelse((as.integer(LASA1F$flphya32)== 1 & as.integer(LASA1F$flphya36)== 1) | 
                                      (as.integer(LASA1F$flphya32)== -2 & as.integer(LASA1F$flphya36)== -2) |
                                      (as.integer(LASA1F$flphya32)== -2 & as.integer(LASA1F$flphya36)== 1) |
                                      (as.integer(LASA1F$flphya32)== 1 & as.integer(LASA1F$flphya36)== -2), 0L,
                              ifelse((as.integer(LASA1F$flphya32)== 2 & as.integer(LASA1F$flphya36)== 1) |
                                        (as.integer(LASA1F$flphya32)== 1 & as.integer(LASA1F$flphya36)== 2) |
                                        (as.integer(LASA1F$flphya32)== 2 & as.integer(LASA1F$flphya36)== 1) |
                                        (as.integer(LASA1F$flphya32)== 2 & as.integer(LASA1F$flphya36)== 2) |
                                        (as.integer(LASA1F$flphya32)== 2 & as.integer(LASA1F$flphya36)== 3) |
                                        (as.integer(LASA1F$flphya32)== 2 & as.integer(LASA1F$flphya36)== 4) |
                                        (as.integer(LASA1F$flphya32)== 3 & as.integer(LASA1F$flphya36)== 2) |
                                        (as.integer(LASA1F$flphya32)== 2 & as.integer(LASA1F$flphya36)== -2) |
                                        (as.integer(LASA1F$flphya32)== -2 & as.integer(LASA1F$flphya36)== 2), 1L, NA))
```  
### **Variable label**:  Household activities  
**Variable name**:  lsb_pa_house_5  
**Variable description**:  Indicator of whether the participant does any household activities (light, moderate or vigorous).     
**Value type**:  integer  
**Variable unit**:  N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 |   Does not do any household activities  
1 |   Does any household activities  

**Harmonization status**:  complete  
**Harmonization comment**:   (redo)
**R script**:  
```{r, echo=TRUE}
lsb_LASA1_5$lsb_pa_house_5<- ifelse((as.integer(LASA1G$glphya32)== 1 & as.integer(LASA1G$glphya36)== 1) | 
                                      (as.integer(LASA1G$glphya32)== -2 & as.integer(LASA1G$glphya36)== -2) |
                                      (as.integer(LASA1G$glphya32)== -2 & as.integer(LASA1G$glphya36)== 1) |
                                      (as.integer(LASA1G$glphya32)== 1 & as.integer(LASA1G$glphya36)== -2), 0L,
                              ifelse((as.integer(LASA1G$glphya32)== 2 & as.integer(LASA1G$glphya36)== 1) |
                                        (as.integer(LASA1G$glphya32)== 1 & as.integer(LASA1G$glphya36)== 2) |
                                        (as.integer(LASA1G$glphya32)== 2 & as.integer(LASA1G$glphya36)== 1) |
                                        (as.integer(LASA1G$glphya32)== 2 & as.integer(LASA1G$glphya36)== 2) |
                                        (as.integer(LASA1G$glphya32)== 2 & as.integer(LASA1G$glphya36)== 3) |
                                        (as.integer(LASA1G$glphya32)== 2 & as.integer(LASA1G$glphya36)== 4) |
                                        (as.integer(LASA1G$glphya32)== 3 & as.integer(LASA1G$glphya36)== 2) |
                                        (as.integer(LASA1G$glphya32)== 2 & as.integer(LASA1G$glphya36)== -2) |
                                        (as.integer(LASA1G$glphya32)== -2 & as.integer(LASA1G$glphya36)== 2), 1L, NA))
```  
### **Variable label**:  Household activities  
**Variable name**:  lsb_pa_house_6  
**Variable description**:  Indicator of whether the participant does any household activities (light, moderate or vigorous).     
**Value type**:  integer  
**Variable unit**:  N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 |   Does not do any household activities  
1 |   Does any household activities  

**Harmonization status**:  complete  
**Harmonization comment**:   (redo)
**R script**:  
```{r, echo=TRUE}
lsb_LASA1_6$lsb_pa_house_6<- ifelse((as.integer(LASA1H$HLPHYA32)== 1 & as.integer(LASA1H$HLPHYA36)== 1) | 
                                      (as.integer(LASA1H$HLPHYA32)== -2 & as.integer(LASA1H$HLPHYA36)== -2) |
                                      (as.integer(LASA1H$HLPHYA32)== -2 & as.integer(LASA1H$HLPHYA36)== 1) |
                                      (as.integer(LASA1H$HLPHYA32)== 1 & as.integer(LASA1H$HLPHYA36)== -2), 0L,
                              ifelse((as.integer(LASA1H$HLPHYA32)== 2 & as.integer(LASA1H$HLPHYA36)== 1) |
                                        (as.integer(LASA1H$HLPHYA32)== 1 & as.integer(LASA1H$HLPHYA36)== 2) |
                                        (as.integer(LASA1H$HLPHYA32)== 2 & as.integer(LASA1H$HLPHYA36)== 1) |
                                        (as.integer(LASA1H$HLPHYA32)== 2 & as.integer(LASA1H$HLPHYA36)== 2) |
                                        (as.integer(LASA1H$HLPHYA32)== 2 & as.integer(LASA1H$HLPHYA36)== 3) |
                                        (as.integer(LASA1H$HLPHYA32)== 2 & as.integer(LASA1H$HLPHYA36)== 4) |
                                        (as.integer(LASA1H$HLPHYA32)== 3 & as.integer(LASA1H$HLPHYA36)== 2) |
                                        (as.integer(LASA1H$HLPHYA32)== 2 & as.integer(LASA1H$HLPHYA36)== -2) |
                                        (as.integer(LASA1H$HLPHYA32)== -2 & as.integer(LASA1H$HLPHYA36)== 2), 1L, NA))
```  

### **Variable label**:  Average household activities time      
**Variable name**:  lsb_pa_house_time_0  
**Variable description**:  Average minutes per week the participant spent doing household activities in last week.  
**Value type**:  decimal    
**Variable unit**:  minutes per week  
**Category coding**:  N/A  

**Harmonization status**:  complete  
**Harmonization comment**:   question  
**R script**:  
```{r, echo=TRUE}
#lsb_LASA1_0$lsb_pa_house_time_0 <- 
```  
### **Variable label**:  Average household activities time      
**Variable name**:  lsb_pa_house_time_1  
**Variable description**:  Average minutes per week the participant spent doing household activities in last week.  
**Value type**:  decimal    
**Variable unit**:  minutes per week  
**Category coding**:  N/A  

**Harmonization status**:  
**Harmonization comment**:   question  
**R script**:  
```{r, echo=TRUE}
#This is where the R-script will be written

```  
### **Variable label**:  Average household activities time      
**Variable name**:  lsb_pa_house_time_2  
**Variable description**:  Average minutes per week the participant spent doing household activities in last week.  
**Value type**:  decimal    
**Variable unit**:  minutes per week  
**Category coding**:  N/A  

**Harmonization status**:  
**Harmonization comment**:   question  
**R script**:  
```{r, echo=TRUE}
#This is where the R-script will be written

```  
### **Variable label**:  Average household activities time      
**Variable name**:  lsb_pa_house_time_3  
**Variable description**:  Average minutes per week the participant spent doing household activities in last week.  
**Value type**:  decimal    
**Variable unit**:  minutes per week  
**Category coding**:  N/A  

**Harmonization status**:  
**Harmonization comment**:  question  
**R script**:  
```{r, echo=TRUE}
#This is where the R-script will be written

```  
### **Variable label**:  Average household activities time      
**Variable name**:  lsb_pa_house_time_4  
**Variable description**:  Average minutes per week the participant spent doing household activities in last week.  
**Value type**:  decimal    
**Variable unit**:  minutes per week  
**Category coding**:  N/A  

**Harmonization status**:  
**Harmonization comment**:   question  
**R script**:  
```{r, echo=TRUE}
#This is where the R-script will be written

```  
### **Variable label**:  Average household activities time      
**Variable name**:  lsb_pa_house_time_5  
**Variable description**:  Average minutes per week the participant spent doing household activities in last week.  
**Value type**:  decimal    
**Variable unit**:  minutes per week  
**Category coding**:  N/A  

**Harmonization status**:  
**Harmonization comment**:   question  
**R script**:  
```{r, echo=TRUE}
#This is where the R-script will be written

```  
### **Variable label**:  Average household activities time      
**Variable name**:  lsb_pa_house_time_6  
**Variable description**:  Average minutes per week the participant spent doing household activities in last week.  
**Value type**:  decimal    
**Variable unit**:  minutes per week  
**Category coding**:  N/A  

**Harmonization status**:  
**Harmonization comment**:   question  
**R script**:  
```{r, echo=TRUE}
#This is where the R-script will be written

```  
### **Variable label**: Sports or exercise      
**Variable name**:  lsb_pa_sport_0  
**Variable description**:  Indicator of whether the participant does any sports or exercise.  
**Value type**:  integer  
**Variable unit**:  N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 |  Does not do any sports or exercise   
1 |  Does any sports or exercise

**Harmonization status**:  impossible  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}

```   
### **Variable label**: Sports or exercise      
**Variable name**:  lsb_pa_sport_1  
**Variable description**:  Indicator of whether the participant does any sports or exercise.  
**Value type**:  integer  
**Variable unit**:  N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 |  Does not do any sports or exercise   
1 |  Does any sports or exercise

**Harmonization status**:  impossible  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}

```   
### **Variable label**: Sports or exercise      
**Variable name**:  lsb_pa_sport_2  
**Variable description**:  Indicator of whether the participant does any sports or exercise.  
**Value type**:  integer  
**Variable unit**:  N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 |  Does not do any sports or exercise   
1 |  Does any sports or exercise

**Harmonization status**:  impossible  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}

```   
### **Variable label**: Sports or exercise      
**Variable name**:  lsb_pa_sport_3  
**Variable description**:  Indicator of whether the participant does any sports or exercise.  
**Value type**:  integer  
**Variable unit**:  N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 |  Does not do any sports or exercise   
1 |  Does any sports or exercise

**Harmonization status**:  impossible  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}

```   
### **Variable label**: Sports or exercise      
**Variable name**:  lsb_pa_sport_4  
**Variable description**:  Indicator of whether the participant does any sports or exercise.  
**Value type**:  integer  
**Variable unit**:  N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 |  Does not do any sports or exercise   
1 |  Does any sports or exercise

**Harmonization status**:  impossible  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}

```   
### **Variable label**: Sports or exercise      
**Variable name**:  lsb_pa_sport_5  
**Variable description**:  Indicator of whether the participant does any sports or exercise.  
**Value type**:  integer  
**Variable unit**:  N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 |  Does not do any sports or exercise   
1 |  Does any sports or exercise

**Harmonization status**:  impossible  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}

```   
### **Variable label**: Sports or exercise      
**Variable name**:  lsb_pa_sport_6  
**Variable description**:  Indicator of whether the participant does any sports or exercise.  
**Value type**:  integer  
**Variable unit**:  N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 |  Does not do any sports or exercise   
1 |  Does any sports or exercise

**Harmonization status**:  impossible  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}

```   

### **Variable label**:  Average sports or exercise time       
**Variable name**:  lsb_pa_sport_time_0  
**Variable description**:  Average time a week the participant spent on sports or exercise.    
**Value type**: integer  
**Variable unit**:  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 |  never   
1 |  less than 1 hour a week   
2 |  between 1 and 2 hours a week   
3 |  more than 2 hours a week  

**Harmonization status**:  impossible  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}

```  
### **Variable label**:  Average sports or exercise time       
**Variable name**:  lsb_pa_sport_time_1  
**Variable description**:  Average time a week the participant spent on sports or exercise.    
**Value type**: integer    
**Variable unit**:  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 |  never   
1 |  less than 1 hour a week   
2 |  between 1 and 2 hours a week   
3 |  more than 2 hours a week   

**Harmonization status**:  impossible  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}

```  
### **Variable label**:  Average sports or exercise time       
**Variable name**:  lsb_pa_sport_time_2  
**Variable description**:  Average time a week the participant spent on sports or exercise.    
**Value type**: integer   
**Variable unit**:  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 |  never   
1 |  less than 1 hour a week   
2 |  between 1 and 2 hours a week   
3 |  more than 2 hours a week    

**Harmonization status**:  impossible  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}

```  
### **Variable label**:  Average sports or exercise time       
**Variable name**:  lsb_pa_sport_time_3  
**Variable description**:  Average time a week the participant spent on sports or exercise.    
**Value type**: integer    
**Variable unit**:  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 |  never   
1 |  less than 1 hour a week   
2 |  between 1 and 2 hours a week   
3 |  more than 2 hours a week    

**Harmonization status**:  impossible  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}

```  
### **Variable label**:  Average sports or exercise time       
**Variable name**:  lsb_pa_sport_time_4  
**Variable description**:  Average time a week the participant spent on sports or exercise.    
**Value type**: integer   
**Variable unit**:  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 |  never   
1 |  less than 1 hour a week   
2 |  between 1 and 2 hours a week   
3 |  more than 2 hours a week    

**Harmonization status**:  impossible  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}

```  
### **Variable label**:  Average sports or exercise time       
**Variable name**:  lsb_pa_sport_time_5  
**Variable description**:  Average time a week the participant spent on sports or exercise.    
**Value type**: integer   
**Variable unit**:  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 |  never   
1 |  less than 1 hour a week   
2 |  between 1 and 2 hours a week   
3 |  more than 2 hours a week    

**Harmonization status**:  impossible  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}

```  
### **Variable label**:  Average sports or exercise time       
**Variable name**:  lsb_pa_sport_time_6  
**Variable description**:  Average time a week the participant spent on sports or exercise.    
**Value type**: integer   
**Variable unit**:  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 |  never   
1 |  less than 1 hour a week   
2 |  between 1 and 2 hours a week   
3 |  more than 2 hours a week    

**Harmonization status**:  impossible  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}

```  

# Diet and nutrition subdomain

### **Variable label**:  Daily vegetable consumption  
**Variable name**:  lsb_veg_0    
**Variable description**:  Indicator of whether the participant currently consumes vegetables on a daily basis.   
**Value type**:  integer  
**Variable unit**:  N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 |   Does not consume vegetables on a daily basis  
1 |   Consumes vegetables on a daily basis  

**Harmonization status**:  impossible  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}

```  
### **Variable label**:  Daily vegetable consumption  
**Variable name**:  lsb_veg_1    
**Variable description**:  Indicator of whether the participant currently consumes vegetables on a daily basis.   
**Value type**:  integer  
**Variable unit**:  N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 |   Does not consume vegetables on a daily basis  
1 |   Consumes vegetables on a daily basis  

**Harmonization status**:  impossible  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}

```  
### **Variable label**:  Daily vegetable consumption  
**Variable name**:  lsb_veg_2    
**Variable description**:  Indicator of whether the participant currently consumes vegetables on a daily basis.   
**Value type**:  integer  
**Variable unit**:  N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 |   Does not consume vegetables on a daily basis  
1 |   Consumes vegetables on a daily basis  

**Harmonization status**:  impossible  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}

```  

### **Variable label**:  Daily fruit consumption  
**Variable name**:  lsb_fruit_0  
**Variable description**:  Indicator of whether the participant currently consumes fruit on a daily basis.   
**Value type**:  integer  
**Variable unit**:  N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 |   Does not consume fruit on a daily basis
1 |   Consumes fruit on a daily basis  

**Harmonization status**:  impossible  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}

```  
### **Variable label**:  Daily fruit consumption  
**Variable name**:  lsb_fruit_1  
**Variable description**:  Indicator of whether the participant currently consumes fruit on a daily basis.   
**Value type**:  integer  
**Variable unit**:  N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 |   Does not consume fruit on a daily basis
1 |   Consumes fruit on a daily basis  

**Harmonization status**:  impossible  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}

```  
### **Variable label**:  Daily fruit consumption  
**Variable name**:  lsb_fruit_2  
**Variable description**:  Indicator of whether the participant currently consumes fruit on a daily basis.   
**Value type**:  integer  
**Variable unit**:  N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 |   Does not consume fruit on a daily basis
1 |   Consumes fruit on a daily basis  

**Harmonization status**:  impossible  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}

```  

### **Variable label**:  Daily water consumption  
**Variable name**:  lsb_water_0    
**Variable description**:  Indicator of whether the participant drinks water on a daily basis.   
**Value type**:  integer  
**Variable unit**:  N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 |   Does not drinks water on a daily basis
1 |   Drinks water on a daily basis

**Harmonization status**:  impossible  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}

```  
### **Variable label**:  Daily water consumption  
**Variable name**:  lsb_water_1    
**Variable description**:  Indicator of whether the participant drinks water on a daily basis.   
**Value type**:  integer  
**Variable unit**:  N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 |   Does not drinks water on a daily basis
1 |   Drinks water on a daily basis

**Harmonization status**:  impossible  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}

```  
### **Variable label**:  Daily water consumption  
**Variable name**:  lsb_water_2    
**Variable description**:  Indicator of whether the participant drinks water on a daily basis.   
**Value type**:  integer  
**Variable unit**:  N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 |   Does not drinks water on a daily basis
1 |   Drinks water on a daily basis

**Harmonization status**:  impossible  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}

```  
### **Variable label**:  Daily water consumption  
**Variable name**:  lsb_water_4    
**Variable description**:  Indicator of whether the participant drinks water on a daily basis.   
**Value type**:  integer  
**Variable unit**:  N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 |   Does not drinks water on a daily basis
1 |   Drinks water on a daily basis

**Harmonization status**:  impossible  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}

```  

### **Variable label**:  Quantity daily coffee  
**Variable name**:  lsb_coffee_qty_0  
**Variable description**:  Current quantity of coffee the participant consumes per day.   
**Value type**:  integer  
**Variable unit**:  cups/day  
**Category coding**:  N/A  

**Harmonization status**:  impossible  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}

```  
### **Variable label**:  Quantity daily coffee  
**Variable name**:  lsb_coffee_qty_1  
**Variable description**:  Current quantity of coffee the participant consumes per day.   
**Value type**:  integer  
**Variable unit**:  cups/day 
**Category coding**:  N/A  

**Harmonization status**:  impossible  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}

```  
### **Variable label**:  Quantity daily coffee  
**Variable name**:  lsb_coffee_qty_2  
**Variable description**:  Current quantity of coffee the participant consumes per day.   
**Value type**:  integer  
**Variable unit**:  cups/day  
**Category coding**:  N/A  

**Harmonization status**:  impossible  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}

```  
### **Variable label**:  Quantity daily coffee  
**Variable name**:  lsb_coffee_qty_3  
**Variable description**:  Current quantity of coffee the participant consumes per day.   
**Value type**:  integer  
**Variable unit**:  cups/day 
**Category coding**:  N/A  

**Harmonization status**:  impossible  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}

```  
### **Variable label**:  Quantity daily coffee  
**Variable name**:  lsb_coffee_qty_4  
**Variable description**:  Current quantity of coffee the participant consumes per day.   
**Value type**:  integer  
**Variable unit**:  cups/day  
**Category coding**:  N/A  

**Harmonization status**:  impossible  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}

```  

# Sleep quality subdomain

### **Variable label**:  Average sleep hours  
**Variable name**:  lsb_sleep_hours_0  
**Variable description**:  Average number of hours the participant sleeps per night.  
**Value type**:  integer  
**Variable unit**:  hours/night  
**Category coding**:  N/A  

**Harmonization status**:  complete    
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
lsb_LASA1_0$lsb_sleep_hours_0 <- ifelse(as.integer(LASA1B$bqsleep1)<0,NA, as.integer(LASA1B$bqsleep1))
```  
### **Variable label**:  Average sleep hours  
**Variable name**:  lsb_sleep_hours_1  
**Variable description**:  Average number of hours the participant sleeps per night.  
**Value type**:  integer  
**Variable unit**:  hours/night   
**Category coding**:  N/A  

**Harmonization status**:  complete    
**Harmonization comment**:    
**R script**:  
```{r, echo=TRUE}
lsb_LASA1_1$lsb_sleep_hours_1 <- ifelse(as.integer(LASA1C$cqsleep1)<0,NA, as.integer(LASA1C$cqsleep1))
``` 
### **Variable label**:  Average sleep hours  
**Variable name**:  lsb_sleep_hours_2  
**Variable description**:  Average number of hours the participant sleeps per night.  
**Value type**:  integer  
**Variable unit**:  hours/night 
**Category coding**:  N/A  

**Harmonization status**:  complete    
**Harmonization comment**:    
**R script**:  
```{r, echo=TRUE}
lsb_LASA1_2$lsb_sleep_hours_2 <- ifelse(as.integer(LASA1D$dqsleep1)<0,NA, as.integer(LASA1D$dqsleep1))
``` 
### **Variable label**:  Average sleep hours  
**Variable name**:  lsb_sleep_hours_3  
**Variable description**:  Average number of hours the participant sleeps per night.  
**Value type**:  integer  
**Variable unit**:  hours/night
**Category coding**:  N/A  

**Harmonization status**:  complete    
**Harmonization comment**:     
**R script**:  
```{r, echo=TRUE}
lsb_LASA1_3$lsb_sleep_hours_3 <- ifelse(as.integer(LASA1E$eqsleep1)<0,NA, as.integer(LASA1E$eqsleep1))
``` 
### **Variable label**:  Average sleep hours  
**Variable name**:  lsb_sleep_hours_4    
**Variable description**:  Average number of hours the participant sleeps per night.  
**Value type**:  integer  
**Variable unit**:  hours/night   
**Category coding**:  N/A  

**Harmonization status**:  complete    
**Harmonization comment**:     
**R script**:  
```{r, echo=TRUE}
lsb_LASA1_4$lsb_sleep_hours_4 <- ifelse(as.integer(LASA1F$fqsleep1)<0,NA, as.integer(LASA1F$fqsleep1))
``` 
### **Variable label**:  Average sleep hours  
**Variable name**:  lsb_sleep_hours_5  
**Variable description**:  Average number of hours the participant sleeps per night.  
**Value type**:  integer  
**Variable unit**:  hours/night    
**Category coding**:  N/A  

**Harmonization status**:  complete    
**Harmonization comment**:     
**R script**:  
```{r, echo=TRUE}
lsb_LASA1_5$lsb_sleep_hours_5 <- ifelse(as.integer(LASA1G$gqsleep1)<0,NA, as.integer(LASA1G$gqsleep1))
``` 

### **Variable label**:  Difficulty falling a sleep  
**Variable name**:  lsb_sleep_diff_0  
**Variable description**:  Indicator of whether the participant ever has any diffulty falling a sleep.  
**Value type**:  integer  
**Variable unit**:  N/A  
**Category coding**:    

**Code** | **Category Label**  
------------- | -------------  
0 |  Never has difficulty falling asleep
1 |  Sometimes has difficulty falling asleep

**Harmonization status**:  complete    
**Harmonization comment**:     
**R script**:  
```{r, echo=TRUE}
lsb_LASA1_0$lsb_sleep_diff_0 <- recode(as.integer(LASA1B$bqsleep2),'1'=0L,'2'=1L,'3'=1L,'4'=1L,.default=NA_integer_)
```  
### **Variable label**:  Difficulty falling a sleep  
**Variable name**:  lsb_sleep_diff_1  
**Variable description**:  Indicator of whether the participant ever has any diffulty falling a sleep.  
**Value type**:  integer  
**Variable unit**:  N/A  
**Category coding**:    

**Code** | **Category Label**  
------------- | -------------  
0 |  Never has difficulty falling asleep
1 |  Sometimes has difficulty falling asleep

**Harmonization status**:  complete  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
lsb_LASA1_1$lsb_sleep_diff_1 <- recode(as.integer(LASA1C$cqsleep2),'1'=0L,'2'=1L,'3'=1L,'4'=1L,.default=NA_integer_)
```  
### **Variable label**:  Difficulty falling a sleep  
**Variable name**:  lsb_sleep_diff_2    
**Variable description**:  Indicator of whether the participant ever has any diffulty falling a sleep.  
**Value type**:  integer  
**Variable unit**:  N/A  
**Category coding**:    

**Code** | **Category Label**  
------------- | -------------  
0 |  Never has difficulty falling asleep
1 |  Sometimes has difficulty falling asleep

**Harmonization status**:  complete    
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
lsb_LASA1_2$lsb_sleep_diff_2 <- recode(as.integer(LASA1D$dqsleep2),'1'=0L,'2'=1L,'3'=1L,'4'=1L,.default=NA_integer_)
``` 
### **Variable label**:  Difficulty falling a sleep  
**Variable name**:  lsb_sleep_diff_3  
**Variable description**:  Indicator of whether the participant ever has any diffulty falling a sleep.  
**Value type**:  integer  
**Variable unit**:  N/A  
**Category coding**:    

**Code** | **Category Label**  
------------- | -------------  
0 |  Never has difficulty falling asleep
1 |  Sometimes has difficulty falling asleep

**Harmonization status**:  complete    
**Harmonization comment**:    
**R script**:  
```{r, echo=TRUE}
lsb_LASA1_3$lsb_sleep_diff_3 <- recode(as.integer(LASA1E$eqsleep2),'1'=0L,'2'=1L,'3'=1L,'4'=1L,.default=NA_integer_)
``` 
### **Variable label**:  Difficulty falling a sleep  
**Variable name**:  lsb_sleep_diff_4  
**Variable description**:  Indicator of whether the participant ever has any diffulty falling a sleep.  
**Value type**:  integer  
**Variable unit**:  N/A  
**Category coding**:    

**Code** | **Category Label**  
------------- | -------------  
0 |  Never has difficulty falling asleep
1 |  Sometimes has difficulty falling asleep

**Harmonization status**:  complete    
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
lsb_LASA1_4$lsb_sleep_diff_4 <- recode(as.integer(LASA1F$fqsleep2),'1'=0L,'2'=1L,'3'=1L,'4'=1L,.default=NA_integer_)
``` 
### **Variable label**:  Difficulty falling a sleep  
**Variable name**:  lsb_sleep_diff_5  
**Variable description**:  Indicator of whether the participant ever has any diffulty falling a sleep.  
**Value type**:  integer  
**Variable unit**:  N/A  
**Category coding**:    

**Code** | **Category Label**  
------------- | -------------  
0 |  Never has difficulty falling asleep
1 |  Sometimes has difficulty falling asleep

**Harmonization status**:  complete    
**Harmonization comment**:     
**R script**:  
```{r, echo=TRUE}
lsb_LASA1_5$lsb_sleep_diff_5 <- recode(as.integer(LASA1G$gqsleep2),'1'=0L,'2'=1L,'3'=1L,'4'=1L,.default=NA_integer_)
```  

### **Variable label**:  Quality of sleep  
**Variable name**:  lsb_sleep_qlty_0  
**Variable description**:  Indicator of the quality of sleep of the participant.    
**Value type**:  integer  
**Variable unit**:  N/A  
**Category coding**:    

**Code** | **Category Label**  
------------- | -------------  
0 |  Very bad 
1 |  Fairly bad
2 |  Fairly good
3 |  Very good  

**Harmonization status**:  impossible  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}

```  

### **Variable label**:  Quality of sleep  
**Variable name**:  lsb_sleep_qlty_1  
**Variable description**:  Indicator of the quality of sleep of the participant.    
**Value type**:  integer  
**Variable unit**:  N/A  
**Category coding**:    

**Code** | **Category Label**  
------------- | -------------  
0 |  Very bad 
1 |  Fairly bad
2 |  Fairly good
3 |  Very good  

**Harmonization status**:  impossible  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}

``` 

### **Variable label**:  Quality of sleep  
**Variable name**:  lsb_sleep_qlty_2  
**Variable description**:  Indicator of the quality of sleep of the participant.    
**Value type**:  integer  
**Variable unit**:  N/A  
**Category coding**:    

**Code** | **Category Label**  
------------- | -------------  
0 |  Very bad 
1 |  Fairly bad
2 |  Fairly good
3 |  Very good  

**Harmonization status**:  impossible  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}

``` 
### **Variable label**:  Quality of sleep  
**Variable name**:  lsb_sleep_qlty_3  
**Variable description**:  Indicator of the quality of sleep of the participant.    
**Value type**:  integer  
**Variable unit**:  N/A  
**Category coding**:    

**Code** | **Category Label**  
------------- | -------------  
0 |  Very bad 
1 |  Fairly bad
2 |  Fairly good
3 |  Very good  

**Harmonization status**:  impossible  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}

```  
### **Variable label**:  Quality of sleep  
**Variable name**:  lsb_sleep_qlty_4  
**Variable description**:  Indicator of the quality of sleep of the participant.    
**Value type**:  integer  
**Variable unit**:  N/A  
**Category coding**:    

**Code** | **Category Label**  
------------- | -------------  
0 |  Very bad 
1 |  Fairly bad
2 |  Fairly good
3 |  Very good  

**Harmonization status**:  impossible  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}

```  
### **Variable label**:  Quality of sleep  
**Variable name**:  lsb_sleep_qlty_5  
**Variable description**:  Indicator of the quality of sleep of the participant.    
**Value type**:  integer  
**Variable unit**:  N/A  
**Category coding**:    

**Code** | **Category Label**  
------------- | -------------  
0 |  Very bad 
1 |  Fairly bad
2 |  Fairly good
3 |  Very good  

**Harmonization status**:  impossible  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}

```  



