---
title: "Lifestyle and behaviours DataSchema"
output: html_document
---
# Table of Contents
1. [Alcohol consumption subdomain](#alcohol-consumption-subdomain)
2. [Tobacco consumption subdomain](#tobacco-consumption-subdomain)
3. [Physical activity subdomain](#physical-activity-subdomain)
4. [Diet and nutrition subdomain](#diet-and-nutrition-subdomain)
5. [Sleep quality subdomain](#sleep-quality-subdomain)

# Alcohol consumption subdomain

### **Variable label**:   
**Variable name**: LSB_ALC_CUR  
**Variable description**:  Current consumption of alcohol  
**Value type**: integer  
**Variable unit**: N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 |  no, does not currently drink alcohol   
1 |  yes, currently drinks alcohol  

**Harmonization status**:  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
#This is where the R-script will be written

```

### **Variable label**:   
**Variable name**: LSB_ALC_EVER  
**Variable description**:  Ever consumption of alcohol  
**Value type**: integer  
**Variable unit**: N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 |   Never consumed alcohol  
1 |   Ever consumed alcohol  

**Harmonization status**:  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
#This is where the R-script will be written

```

### **Variable label**:   
**Variable name**: LSB_ALC_BINGE  
**Variable description**:  Frequency of binge drinking  
**Value type**: integer  
**Variable unit**: N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
1 |  less than monthly  
2 |  monthly   
3 |  weekly  
4 |  daily  

**Harmonization status**:  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
#This is where the R-script will be written

```

### **Variable label**:   
**Variable name**: LSB_ALC_TOTAL  
**Variable description**:  Average number of alcoholic drinks (total) per week  
**Value type**: integer  
**Variable unit**: drinks per week  
**Category coding**:  N/A  

**Harmonization status**:  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
#This is where the R-script will be written

```

### **Variable label**:   
**Variable name**: LSB_ALC_WINE  
**Variable description**:  Average number of alcoholic drinks (wine) per week  
**Value type**: integer  
**Variable unit**: drinks per week  
**Category coding**:  N/A  

**Harmonization status**:  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
#This is where the R-script will be written

```

### **Variable label**:   
**Variable name**: LSB_ALC_BEER  
**Variable description**:  Average number of alcoholic drinks (beer) per week  
**Value type**: integer  
**Variable unit**: drinks per week  
**Category coding**:  N/A  
 

**Harmonization status**:  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
#This is where the R-script will be written

```

### **Variable label**:   
**Variable name**: LSB_ALC_LIQ  
**Variable description**:  Average number of alcoholic drinks (liquor) per week  
**Value type**: integer  
**Variable unit**: drinks per week  
**Category coding**:  N/A  
 

**Harmonization status**:  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
#This is where the R-script will be written

```

# Tobacco consumption subdomain

### **Variable label**:  
**Variable name**:  LSB_SMOK_CUR  
**Variable description**:  Current tobakko smoking  
**Value type**:  integer  
**Variable unit**:  N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 |   no, does not currently smokes tobacco  
1 |   yes, smokes currently tobacco  

**Harmonization status**:  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
#This is where the R-script will be written

```

### **Variable label**:  
**Variable name**:  LSB_SMOK_CAT  
**Variable description**:  Smoking status  
**Value type**:  integer  
**Variable unit**:  N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 |   Never smoker  
1 |   Former smoker  
3 |   Current smoker  

**Harmonization status**:  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
#This is where the R-script will be written

```

### **Variable label**:  
**Variable name**:  LSB_SMOK_EVER  
**Variable description**:  Ever tobacco smoking  
**Value type**:  integer  
**Variable unit**:  N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 |   Never smoked tobacco  
1 |   Ever smoked tobacco  

**Harmonization status**:  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
#This is where the R-script will be written

```

### **Variable label**:  
**Variable name**:  LSB_SMOK_CIG  
**Variable description**:  Average number of cigarettes smoked per day  
**Value type**:  integer  
**Variable unit**:  number of cigarettes per day  
**Category coding**:  

**Harmonization status**:  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
#This is where the R-script will be written

```

### **Variable label**:  
**Variable name**:  LSB_SMOK_START  
**Variable description**:  Age at which started smoking  
**Value type**:  integer  
**Variable unit**:  age in years  
**Category coding**:  

**Harmonization status**:  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
#This is where the R-script will be written

```

### **Variable label**:  
**Variable name**:  LSB_SMOK_STOP  
**Variable description**:  Age at which stopped smoking
**Value type**:  integer  
**Variable unit**:  age in years  
**Category coding**:  

**Harmonization status**:  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
#This is where the R-script will be written

```

### **Variable label**:  
**Variable name**:  LSB_SMOK_PY  
**Variable description**:  Pack years - equivalent of years smoking twenty cigarettes per day  
**Value type**:  integer  
**Variable unit**:  pack years (years smoking twenty cigarettes per day)  
**Category coding**:  

**Harmonization status**:  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
#This is where the R-script will be written

```

# Physical activity subdomain

### **Variable label**:  
**Variable name**:  
**Variable description**:  
**Value type**:  
**Variable unit**:  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 |   
1 |   

**Harmonization status**:  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
#This is where the R-script will be written

```

# Diet and nutrition subdomain

### **Variable label**:  
**Variable name**:  
**Variable description**:  
**Value type**:  
**Variable unit**:  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 |   
1 |   

**Harmonization status**:  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
#This is where the R-script will be written

```

# Sleep quality subdomain

### **Variable label**:  
**Variable name**:  
**Variable description**:  
**Value type**:  
**Variable unit**:  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 |   
1 |   

**Harmonization status**:  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
#This is where the R-script will be written
#small change
#3rd change using fork
```




