---
title: "Lifestyle and behaviours DataSchema"
output: html_document
---
# Connecting with Opal data server
## Login to server and assign study data
```{r, echo=FALSE}
#Load R libraries
library(opal)
library(tidyverse)
library(epiDisplay)
# Create an opal object with the login information
erasmus_opal <- opal.login()
#Login to Opal server and assign the content of the LUCAS table(s) to your RStudio environment
opal.assign.table.tibble(erasmus_opal, 'LASA2B', 'LASA.LASA2B',variables = list('bmalcoh6','bmalcohn','bmalcohu','bmalcuse','bmalcohu','bmalcohd','bmvar33','bmvar34','bmvar35','bmvar35p','bmvar41','bmvar31','bmvar32','blphya08','badl5a','badl5c','blphya09','badl5b','blphya07','badl5d','blphya06','blphya10','blphya11','blphya12','blphya13','blphya14','blphya15','blphya16','blphya17','blphya18','blphya19','blphya20','blphya31','blphya32','blphya33','blphya34','blphya35','blphya36','blphya37','blphya38','blphya29','blphya30','bcesd11','bqsleep2','bqsleep1','bqsleep4','bqsleep3'))
LASA2B <- opal.execute(erasmus_opal,'LASA2B')

opal.assign.table.tibble(erasmus_opal, 'LASA2F', 'LASA.LASA2F',variables = list('fmalcoh6','fmalcohn','bmalcohu','fmalcuse','fmalcohu','fmalcohd','fmvar31','fmvar32','fmvar33','fmvar34','fmvar35','fmvar35p','fmvar41','flphya08','fadl5a','fadl5c','flphya09','fadl5b','flphya07','fadl5d','flphya06','flphya10','flphya11','flphya12','flphya13','flphya14','flphya15','flphya16','flphya17','flphya18','flphya19','flphya20','flphya31','flphya32','flphya33','flphya34','flphya35','flphya36','flphya37','flphya38','flphya29','flphya30','fcesd11','fqsleep2','fqsleep1','fqsleep4','fqsleep3'))
LASA2F <- opal.execute(erasmus_opal,'LASA2F')

opal.assign.table.tibble(erasmus_opal, 'LASA2G', 'LASA.LASA2G',variables = list('gmalcoh6','gmalcohn','gmalcohd','gmalcohu','gmvar31','gmvar32','gmvar33','gmvar34','gmvar35','gmvar35p','gmvar41','glphya06','glphya07','glphya08','glphya09','gadl5a','gadl5b','gadl5c','gadl5d','gadl5e','glphya10','glphya11','glphya12','glphya13','glphya14','glphya15','glphya16','glphya17','glphya18','glphya19','glphya20','glphya31','glphya32','glphya33','glphya34','glphya35','glphya36','glphya37','glphya38','gqsleep1','gqsleep2','gqsleep3','gqsleep4','gqsleep5','gcesd11'))
LASA2G <- opal.execute(erasmus_opal,'LASA2G')

opal.assign.table.tibble(erasmus_opal, 'LASA2H', 'LASA.LASA2H',variables = list('HMALCOH6','HMALCOHN','HMALCOHD','HMALCOHW','HMALCOHU','HMVAR31','HMVAR32','HMVAR33','HMVAR34','HMVAR35','HMVAR35P','HMVAR41','HLPHYA06','HLPHYA07','HLPHYA08','HLPHYA09','HADL5A','HADL5B','HADL5C','HADL5D','HLPHYA10','HLPHYA11','HLPHYA12','HLPHYA13','HLPHYA14','HLPHYA15','HLPHYA16','HLPHYA17','HLPHYA18','HLPHYA19','HLPHYA20','HLPHYA31','HLPHYA32','HLPHYA33','HLPHYA34','HLPHYA35','HLPHYA36','HLPHYA37','HLPHYA38','hqsleep1','hqsleep2','hqsleep3','hqsleep4','hqsleep5','hqsleepm','hqsleeph','hcesd11','HQSLEEP1'))
LASA2H <- opal.execute(erasmus_opal,'LASA2H')
```
## Assign participant id as first column of your harmonized dataframes
```{r, echo=FALSE}
lsb_LASA2_0 <- data.frame(id = LASA2B$id)
lsb_LASA2_1 <- data.frame(id = LASA2F$id)
lsb_LASA2_2 <- data.frame(id = LASA2G$id)
lsb_LASA2_3 <- data.frame(id = LASA2H$id)
```
# Table of Contents
1. [Alcohol consumption subdomain](#alcohol-consumption-subdomain)
2. [Tobacco consumption subdomain](#tobacco-consumption-subdomain)
3. [Physical activity subdomain](#physical-activity-subdomain)
4. [Diet and nutrition subdomain](#diet-and-nutrition-subdomain)
5. [Sleep quality subdomain](#sleep-quality-subdomain)

# Alcohol consumption subdomain

### **Variable label**:  Current consumption of alcohol  
**Variable name**: lsb_alc_cur_0  
**Variable description**:  Indicator of whether the participant currently consumes alcohol or has consumed alcohol in the past 12 months.  
**Value type**: integer  
**Variable unit**: N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 |  Does not currently consumes alcohol   
1 |  Currently consumes alcohol  

**Harmonization status**:  complete  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
lsb_LASA2_0$lsb_alc_cur_0 <- recode(as.integer(LASA2B$bmalcohu),'1'=0L, '2'=1L, .default=NA_integer_)
```  
### **Variable label**:  Current consumption of alcohol  
**Variable name**: lsb_alc_cur_1  
**Variable description**:  Indicator of whether the participant currently consumes alcohol or has consumed alcohol in the past 12 months.  
**Value type**: integer  
**Variable unit**: N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 |  Does not currently consumes alcohol   
1 |  Currently consumes alcohol   

**Harmonization status**:  complete  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
lsb_LASA2_1$lsb_alc_cur_1 <- recode(as.integer(LASA2F$fmalcohu),'1'=0L,'2'=1L,.default=NA_integer_)
```  
### **Variable label**:  Current consumption of alcohol  
**Variable name**: lsb_alc_cur_2  
**Variable description**:  Indicator of whether the participant currently consumes alcohol or has consumed alcohol in the past 12 months.  
**Value type**: integer  
**Variable unit**: N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 |  Does not currently consumes alcohol   
1 |  Currently consumes alcohol  

**Harmonization status**:  complete  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
lsb_LASA2_2$lsb_alc_cur_2 <- recode(as.integer(LASA2G$gmalcohu),'1'=0L,'2'=1L,.default=NA_integer_)
```  
### **Variable label**:  Current consumption of alcohol  
**Variable name**: lsb_alc_cur_3  
**Variable description**:  Indicator of whether the participant currently consumes alcohol or has consumed alcohol in the past 12 months.  
**Value type**: integer  
**Variable unit**: N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 |  Does not currently consumes alcohol   
1 |  Currently consumes alcohol  

**Harmonization status**:  complete  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
lsb_LASA2_3$lsb_alc_cur_3 <- recode(as.integer(LASA2H$HMALCOHU),'1'=0L,'2'=1L,.default=NA_integer_)
```  
### **Variable label**:  Current consumption of alcohol  
**Variable name**: lsb_alc_cur_4  
**Variable description**:  Indicator of whether the participant currently consumes alcohol or has consumed alcohol in the past 12 months.  
**Value type**: integer  
**Variable unit**: N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 |  Does not currently consumes alcohol   
1 |  Currently consumes alcohol  

**Harmonization status**:  impossible  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}

```  
### **Variable label**:  Current consumption of alcohol  
**Variable name**: lsb_alc_cur_5  
**Variable description**:  Indicator of whether the participant currently consumes alcohol or has consumed alcohol in the past 12 months.  
**Value type**: integer  
**Variable unit**: N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 |  Does not currently consumes alcohol   
1 |  Currently consumes alcohol  

**Harmonization status**:  impossible  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}

```  
### **Variable label**:  Current consumption of alcohol  
**Variable name**: lsb_alc_cur_6  
**Variable description**:  Indicator of whether the participant currently consumes alcohol or has consumed alcohol in the past 12 months.  
**Value type**: integer  
**Variable unit**: N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 |  Does not currently consumes alcohol   
1 |  Currently consumes alcohol  

**Harmonization status**:  impossible  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}

```  

### **Variable label**:   Ever consumption of alcohol  
**Variable name**: lsb_alc_ever_0    
**Variable description**:  Indicator of whether the participant has ever consumed alcohol.  
**Value type**: integer  
**Variable unit**: N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 |   Never consumed alcohol  
1 |   Ever consumed alcohol  

**Harmonization status**:  complete  
**Harmonization comment**:    see LASA1  
**R script**:  
```{r, echo=TRUE}
lsb_LASA2_0$lsb_alc_ever_0 <- ifelse(as.integer(LASA2B$bmalcuse) == 1, 0L, ifelse((as.integer(LASA2B$bmalcuse)==2 & as.integer(LASA2B$bmalcohu)==1) | as.integer(LASA2B$bmalcohu)==2,1L,NA))
```  
### **Variable label**:   Ever consumption of alcohol  
**Variable name**: lsb_alc_ever_1    
**Variable description**:  Indicator of whether the participant has ever consumed alcohol.  
**Value type**: integer  
**Variable unit**: N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 |   Never consumed alcohol  
1 |   Ever consumed alcohol  

**Harmonization status**:  complete  
**Harmonization comment**:   see LASA1  
**R script**:  
```{r, echo=TRUE}

```  
### **Variable label**:   Ever consumption of alcohol  
**Variable name**: lsb_alc_ever_2    
**Variable description**:  Indicator of whether the participant has ever consumed alcohol.  
**Value type**: integer  
**Variable unit**: N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 |   Never consumed alcohol  
1 |   Ever consumed alcohol  

**Harmonization status**:    complete  
**Harmonization comment**:   see LASA1  
**R script**:  
```{r, echo=TRUE}

```  
### **Variable label**:   Ever consumption of alcohol  
**Variable name**: lsb_alc_ever_3    
**Variable description**:  Indicator of whether the participant has ever consumed alcohol.  
**Value type**: integer  
**Variable unit**: N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 |   Never consumed alcohol  
1 |   Ever consumed alcohol  

**Harmonization status**:    complete  
**Harmonization comment**:   see LASA1  
**R script**:  
```{r, echo=TRUE}

```  
### **Variable label**:   Ever consumption of alcohol  
**Variable name**: lsb_alc_ever_4    
**Variable description**:  Indicator of whether the participant has ever consumed alcohol.  
**Value type**: integer  
**Variable unit**: N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 |   Never consumed alcohol  
1 |   Ever consumed alcohol  

**Harmonization status**:  impossible  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}

```  
### **Variable label**:   Ever consumption of alcohol  
**Variable name**: lsb_alc_ever_5    
**Variable description**:  Indicator of whether the participant has ever consumed alcohol.  
**Value type**: integer  
**Variable unit**: N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 |   Never consumed alcohol  
1 |   Ever consumed alcohol  

**Harmonization status**:  impossible  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}

```  
### **Variable label**:   Ever consumption of alcohol  
**Variable name**: lsb_alc_ever_6    
**Variable description**:  Indicator of whether the participant has ever consumed alcohol.  
**Value type**: integer  
**Variable unit**: N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 |   Never consumed alcohol  
1 |   Ever consumed alcohol  

**Harmonization status**:  impossible  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}

```  

### **Variable label**:   Frequency of binge drinking  
**Variable name**: lsb_alc_binge_0  
**Variable description**:  Frequency of drinking 4 or more drinks in one day.  
**Value type**: integer  
**Variable unit**: N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
1 |  0 to 3 times a month  
2 |  1 to 3 times a week   
3 |  3 times a week or more  

**Harmonization status**:  complete  
**Harmonization comment**:   Alcohol: number of time six glasses or more   
**R script**:  
```{r, echo=TRUE}
lsb_LASA2_0$lsb_alc_binge_0 <- recode(as.integer(LASA2B$bmalcoh6),'1'=3L,'2'=3L,'3'=3L,'4'=2L,'5'=1L,'6'=1L,'-2'=1L, .default=NA_integer_)
```  
### **Variable label**:   Frequency of binge drinking  
**Variable name**: lsb_alc_binge_1  
**Variable description**:  Frequency of drinking 4 or more drinks in one day.  
**Value type**: integer  
**Variable unit**: N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
1 |  0 to 3 times a month  
2 |  1 to 3 times a week   
3 |  3 times a week or more  

**Harmonization status**:  complete  
**Harmonization comment**:   Alcohol: number of time six glasses or more  
**R script**:  
```{r, echo=TRUE}
lsb_LASA2_1$lsb_alc_binge_1 <- recode(as.integer(LASA2F$fmalcoh6),'6'=1L,'5'=1L,'4'=2L,'3'=3L,'2'=3L,'1'=3L,.default=NA_integer_)
```  
### **Variable label**:   Frequency of binge drinking  
**Variable name**: lsb_alc_binge_2  
**Variable description**:  Frequency of drinking 4 or more drinks in one day.  
**Value type**: integer  
**Variable unit**: N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
1 |  0 to 3 times a month  
2 |  1 to 3 times a week   
3 |  3 times a week or more  

**Harmonization status**:  complete  
**Harmonization comment**:   Alcohol: number of time six glasses or more  
**R script**:  
```{r, echo=TRUE}
lsb_LASA2_2$lsb_alc_binge_2 <- recode(as.integer(LASA2G$gmalcoh6),'6'=1L,'5'=1L,'4'=2L,'3'=3L,'2'=3L,'1'=3L,.default=NA_integer_)
```  
### **Variable label**:   Frequency of binge drinking  
**Variable name**: lsb_alc_binge_3  
**Variable description**:  Frequency of drinking 4 or more drinks in one day.  
**Value type**: integer  
**Variable unit**: N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
1 |  0 to 3 times a month  
2 |  1 to 3 times a week   
3 |  3 times a week or more  

**Harmonization status**:  complete  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
lsb_LASA2_3$lsb_alc_binge_3 <- recode(as.integer(LASA2H$HMALCOH6),'6'=1L,'5'=1L,'4'=2L,'3'=3L,'2'=3L,'1'=3L,.default=NA_integer_)
```  
### **Variable label**:   Frequency of binge drinking  
**Variable name**: lsb_alc_binge_4  
**Variable description**:  Frequency of drinking 4 or more drinks in one day.  
**Value type**: integer  
**Variable unit**: N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
1 |  0 to 3 times a month  
2 |  1 to 3 times a week   
3 |  3 times a week or more  

**Harmonization status**:  impossible  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}

```  
### **Variable label**:   Frequency of binge drinking  
**Variable name**: lsb_alc_binge_5  
**Variable description**:  Frequency of drinking 4 or more drinks in one day.  
**Value type**: integer  
**Variable unit**: N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
1 |  0 to 3 times a month  
2 |  1 to 3 times a week   
3 |  3 times a week or more  

**Harmonization status**:  impossible  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}

```  
### **Variable label**:   Frequency of binge drinking  
**Variable name**: lsb_alc_binge_6  
**Variable description**:  Frequency of drinking 4 or more drinks in one day.  
**Value type**: integer  
**Variable unit**: N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
1 |  0 to 3 times a month  
2 |  1 to 3 times a week   
3 |  3 times a week or more  

**Harmonization status**:  impossible  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}

```  

### **Variable label**:   Current quantity of alcohol consumed per week (total)      
**Variable name**: lsb_alc_total_0  
**Variable description**:  Current quantity of wine, beer and liquor consumed per week.    
**Value type**: decimal    
**Variable unit**: drinks/week  
**Category coding**:  N/A  

**Harmonization status**:  impossible  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}

```  
### **Variable label**:   Current quantity of alcohol consumed per week (total)  
**Variable name**: lsb_alc_total_1  
**Variable description**:  Current quantity of wine, beer and liquor consumed per week.    
**Value type**: decimal    
**Variable unit**: drinks/week  
**Category coding**:  N/A  

**Harmonization status**:  impossible  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}

```  
### **Variable label**:   Current quantity of alcohol consumed per week (total)  
**Variable name**: lsb_alc_total_2  
**Variable description**:  Current quantity of wine, beer and liquor consumed per week.    
**Value type**: decimal    
**Variable unit**: drinks/week  
**Category coding**:  N/A  

**Harmonization status**:  impossible  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}

```  
### **Variable label**:   Current quantity of alcohol consumed per week (total)  
**Variable name**: lsb_alc_total_3  
**Variable description**:  Current quantity of wine, beer and liquor consumed per week.    
**Value type**: decimal    
**Variable unit**: drinks/week  
**Category coding**:  N/A  

**Harmonization status**:  impossible  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}

```  

### **Variable label**:   Current quantity of wine consumed per week  
**Variable name**: lsb_alc_wine_0  
**Variable description**:  Current quantity of wine consumed per week.    
**Value type**: decimal    
**Variable unit**: drinks/week  
**Category coding**:  N/A  

**Harmonization status**:  impossible  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}

```  
### **Variable label**:   Current quantity of wine consumed per week  
**Variable name**: lsb_alc_wine_1  
**Variable description**:  Current quantity of wine consumed per week.    
**Value type**: decimal    
**Variable unit**: drinks/week  
**Category coding**:  N/A  

**Harmonization status**:  impossible  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}

```  
### **Variable label**:   Current quantity of wine consumed per week  
**Variable name**: lsb_alc_wine_2  
**Variable description**:  Current quantity of wine consumed per week.    
**Value type**: decimal    
**Variable unit**: drinks/week  
**Category coding**:  N/A  

**Harmonization status**:  impossible  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}

```  
### **Variable label**:   Current quantity of wine consumed per week  
**Variable name**: lsb_alc_wine_3  
**Variable description**:  Current quantity of wine consumed per week.    
**Value type**: decimal    
**Variable unit**: drinks/week  
**Category coding**:  N/A  

**Harmonization status**:  impossible  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}

```  

### **Variable label**:   Current quantity of beer consumed per week  
**Variable name**: lsb_alc_beer_0  
**Variable description**:  Current quantity of beer consumed per week.   
**Value type**: decimal    
**Variable unit**: drinks/week  
**Category coding**:  N/A  
 

**Harmonization status**:  impossible  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}

```  
### **Variable label**:   Current quantity of beer consumed per week  
**Variable name**: lsb_alc_beer_1  
**Variable description**:  Current quantity of beer consumed per week.    
**Value type**: decimal    
**Variable unit**: drinks/week  
**Category coding**:  N/A  
 

**Harmonization status**:  impossible  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}

```  
### **Variable label**:   Current quantity of beer consumed per week  
**Variable name**: lsb_alc_beer_2  
**Variable description**:  Current quantity of beer consumed per week.    
**Value type**: decimal    
**Variable unit**: drinks/week  
**Category coding**:  N/A  
 

**Harmonization status**:  impossible  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}

```  
### **Variable label**:   Current quantity of beer consumed per week  
**Variable name**: lsb_alc_beer_3  
**Variable description**:  Current quantity of beer consumed per week.    
**Value type**: decimal    
**Variable unit**: drinks/week  
**Category coding**:  N/A  
 

**Harmonization status**:  impossible  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}

```  

### **Variable label**:   Current quantity of liquor consumed per week  
**Variable name**: lsb_alc_liq_0  
**Variable description**:  Current quantity of liquor consumed per week.    
**Value type**: decimal    
**Variable unit**: drinks/week  
**Category coding**:  N/A  
 

**Harmonization status**:  impossible  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}

```  
### **Variable label**:   Current quantity of liquor consumed per week  
**Variable name**: lsb_alc_liq_1  
**Variable description**:  Current quantity of liquor consumed per week.   
**Value type**: decimal    
**Variable unit**: drinks/week  
**Category coding**:  N/A  
 

**Harmonization status**:  impossible  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}

```  
### **Variable label**:   Current quantity of liquor consumed per week  
**Variable name**: lsb_alc_liq_2  
**Variable description**:  Current quantity of liquor consumed per week.    
**Value type**: decimal    
**Variable unit**: drinks/week  
**Category coding**:  N/A  
 

**Harmonization status**:  impossible  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}

```  
### **Variable label**:   Current quantity of liquor consumed per week  
**Variable name**: lsb_alc_liq_3  
**Variable description**:  Current quantity of liquor consumed per week.   
**Value type**: decimal    
**Variable unit**: drinks/week  
**Category coding**:  N/A  
 

**Harmonization status**:  impossible  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}

```  

# Tobacco consumption subdomain

### **Variable label**:  Current tobacco smoking  
**Variable name**:  lsb_smk_cur_0  
**Variable description**:  Indicator of whether the participant currently smokes any tobacco product.  
**Value type**:  integer  
**Variable unit**:  N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 |   Currently does not smoke any tobacco product  
1 |   Currently smokes any tobacco product  

**Harmonization status**:  complete  
**Harmonization comment**:   Only cigarette smoking.  
**R script**:  
```{r, echo=TRUE}
lsb_LASA2_0$lsb_smk_cur_0 <- recode(as.integer(LASA2B$bmvar31),'1'=0L,'2'=1L, .default=NA_integer_)
```  
### **Variable label**:  Current tobacco smoking  
**Variable name**:  lsb_smk_cur_1  
**Variable description**:  Indicator of whether the participant currently smokes any tobacco product.  
**Value type**:  integer  
**Variable unit**:  N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 |   Currently does not smoke any tobacco product  
1 |   Currently smokes any tobacco product  

**Harmonization status**:  complete  
**Harmonization comment**:   Only cigarette smoking.  
**R script**:  
```{r, echo=TRUE}
lsb_LASA2_1$lsb_smk_cur_1 <- recode(as.integer(LASA2F$fmvar31),'1'=0L,'2'=1L,.default=NA_integer_)
```  
### **Variable label**:  Current tobacco smoking  
**Variable name**:  lsb_smk_cur_2  
**Variable description**:  Indicator of whether the participant currently smokes any tobacco product.  
**Value type**:  integer  
**Variable unit**:  N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 |   Currently does not smoke any tobacco product  
1 |   Currently smokes any tobacco product  

**Harmonization status**:  complete  
**Harmonization comment**:   Only cigarette smoking.  
**R script**:  
```{r, echo=TRUE}
lsb_LASA2_2$lsb_smk_cur_2 <- recode(as.integer(LASA2G$gmvar31),'1'=0L,'2'=1L,.default=NA_integer_)
```  
### **Variable label**:  Current tobacco smoking  
**Variable name**:  lsb_smk_cur_3  
**Variable description**:  Indicator of whether the participant currently smokes any tobacco product.  
**Value type**:  integer  
**Variable unit**:  N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 |   Currently does not smoke any tobacco product  
1 |   Currently smokes any tobacco product  

**Harmonization status**:  complete  
**Harmonization comment**:   Only cigarette smoking.  
**R script**:  
```{r, echo=TRUE}
lsb_LASA2_3$lsb_smk_cur_3 <- recode(as.integer(LASA2H$HMVAR31),'1'=0L,'2'=1L,.default=NA_integer_)
```  
### **Variable label**:  Current tobacco smoking  
**Variable name**:  lsb_smk_cur_4  
**Variable description**:  Indicator of whether the participant currently smokes any tobacco product.  
**Value type**:  integer  
**Variable unit**:  N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 |   Currently does not smoke any tobacco product  
1 |   Currently smokes any tobacco product  

**Harmonization status**:  impossible  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}

```  
### **Variable label**:  Current tobacco smoking  
**Variable name**:  lsb_smk_cur_5  
**Variable description**:  Indicator of whether the participant currently smokes any tobacco product.  
**Value type**:  integer  
**Variable unit**:  N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 |   Currently does not smoke any tobacco product  
1 |   Currently smokes any tobacco product  

**Harmonization status**:  impossible  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}

```  
### **Variable label**:  Current tobacco smoking  
**Variable name**:  lsb_smk_cur_6  
**Variable description**:  Indicator of whether the participant currently smokes any tobacco product.  
**Value type**:  integer  
**Variable unit**:  N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 |   Currently does not smoke any tobacco product  
1 |   Currently smokes any tobacco product  

**Harmonization status**:  impossible  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}

```  

### **Variable label**:  Smoking status  
**Variable name**:  lsb_smk_status_0  
**Variable description**:  Smoking status of the participant.  
**Value type**:  integer  
**Variable unit**:  N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 |   Never smoker  
1 |   Former smoker  
2 |   Current smoker  

**Harmonization status**:  complete  
**Harmonization comment**:   Only cigarette smoking.  
**R script**:  
```{r, echo=TRUE}
lsb_LASA2_0$lsb_smk_status_0 <- ifelse(as.integer(LASA2B$bmvar32)==1,0L, ifelse(as.integer(LASA2B$bmvar31)==1 & as.integer(LASA2B$bmvar32)==2, 1L, ifelse(as.integer(LASA2B$bmvar31)==2,2L,NA)))
```  
### **Variable label**:  Smoking status  
**Variable name**:  lsb_smk_status_1  
**Variable description**:  Smoking status of the participant.  
**Value type**:  integer  
**Variable unit**:  N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 |   Never smoker  
1 |   Former smoker  
2 |   Current smoker  

**Harmonization status**:  complete  
**Harmonization comment**:   Only cigarette smoking.  
**R script**:  
```{r, echo=TRUE}
lsb_LASA2_1$lsb_smk_status_1 <- ifelse(as.integer(LASA2F$fmvar32)==1,0L, ifelse(as.integer(LASA2F$fmvar31)==1 & as.integer(LASA2F$fmvar32)==2, 1L, ifelse(as.integer(LASA2F$fmvar31)==2,2L,NA)))
```  
### **Variable label**:  Smoking status  
**Variable name**:  lsb_smk_status_2  
**Variable description**:  Smoking status of the participant.  
**Value type**:  integer  
**Variable unit**:  N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 |   Never smoker  
1 |   Former smoker  
2 |   Current smoker  

**Harmonization status**:  complete  
**Harmonization comment**:   Only cigarette smoking.  
**R script**:  
```{r, echo=TRUE}
lsb_LASA2_2$lsb_smk_status_2 <- ifelse(as.integer(LASA2G$gmvar32)==1,0L, ifelse(as.integer(LASA2G$gmvar31)==1 & as.integer(LASA2G$gmvar32)==2, 1L, ifelse(as.integer(LASA2G$gmvar31)==2,2L,NA)))
```  
### **Variable label**:  Smoking status  
**Variable name**:  lsb_smk_status_3  
**Variable description**:  Smoking status of the participant.  
**Value type**:  integer  
**Variable unit**:  N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 |   Never smoker  
1 |   Former smoker  
2 |   Current smoker  

**Harmonization status**:  complete  
**Harmonization comment**:   Only cigarette smoking.  
**R script**:  
```{r, echo=TRUE}
lsb_LASA2_3$lsb_smk_status_3 <- ifelse(as.integer(LASA2H$HMVAR32)==1,0L, ifelse(as.integer(LASA2H$HMVAR31)==1 & as.integer(LASA2H$HMVAR32)==2, 1L, ifelse(as.integer(LASA2H$HMVAR31)==2,2L,NA)))
```  
### **Variable label**:  Smoking status  
**Variable name**:  lsb_smk_status_4  
**Variable description**:  Smoking status of the participant.  
**Value type**:  integer  
**Variable unit**:  N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 |   Never smoker  
1 |   Former smoker  
2 |   Current smoker  

**Harmonization status**:  impossible  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}

```  
### **Variable label**:  Smoking status  
**Variable name**:  lsb_smk_status_5  
**Variable description**:  Smoking status of the participant.  
**Value type**:  integer  
**Variable unit**:  N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 |   Never smoker  
1 |   Former smoker  
2 |   Current smoker  

**Harmonization status**:  impossible  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}

```  
### **Variable label**:  Smoking status  
**Variable name**:  lsb_smk_status_6  
**Variable description**:  Smoking status of the participant.  
**Value type**:  integer  
**Variable unit**:  N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 |   Never smoker  
1 |   Former smoker  
2 |   Current smoker  

**Harmonization status**:  impossible  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}

```  

### **Variable label**:  Ever tobacco smoking  
**Variable name**:  lsb_smk_ever_0    
**Variable description**:  Indicator of whether the participant has ever smoked any tobacco product.  
**Value type**:  integer  
**Variable unit**:  N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 |   Never smoked tobacco  
1 |   Ever smoked tobacco  

**Harmonization status**:  complete  
**Harmonization comment**:   Only cigarette smoking.  
**R script**:  
```{r, echo=TRUE}
lsb_LASA2_0$lsb_smk_ever_0 <- recode(as.integer(LASA2B$bmvar32), '1'=0L,'2'=1L,'-2'=1L,.default=NA_integer_)
```  
### **Variable label**:  Ever tobacco smoking  
**Variable name**:  lsb_smk_ever_1    
**Variable description**:  Indicator of whether the participant has ever smoked any tobacco product.  
**Value type**:  integer  
**Variable unit**:  N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 |   Never smoked tobacco  
1 |   Ever smoked tobacco  

**Harmonization status**: complete   
**Harmonization comment**:   Only cigarette smoking.  
**R script**:  
```{r, echo=TRUE}
lsb_LASA2_1$lsb_smk_ever_1 <- recode(as.integer(LASA2F$fmvar32), '1'=0L,'2'=1L,'-2'=1L,.default=NA_integer_)
```  
### **Variable label**:  Ever tobacco smoking  
**Variable name**:  lsb_smk_ever_2    
**Variable description**:  Indicator of whether the participant has ever smoked any tobacco product.  
**Value type**:  integer  
**Variable unit**:  N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 |   Never smoked tobacco  
1 |   Ever smoked tobacco  

**Harmonization status**:  complete  
**Harmonization comment**:   Only cigarette smoking.  
**R script**:  
```{r, echo=TRUE}
lsb_LASA2_2$lsb_smk_ever_2 <- recode(as.integer(LASA2G$gmvar32), '1'=0L,'2'=1L,'-2'=1L,.default=NA_integer_)
```  
### **Variable label**:  Ever tobacco smoking  
**Variable name**:  lsb_smk_ever_3    
**Variable description**:  Indicator of whether the participant has ever smoked any tobacco product.  
**Value type**:  integer  
**Variable unit**:  N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 |   Never smoked tobacco  
1 |   Ever smoked tobacco  

**Harmonization status**:  complete  
**Harmonization comment**:   Only cigarette smoking.  
**R script**:  
```{r, echo=TRUE}
lsb_LASA2_3$lsb_smk_ever_3 <- recode(as.integer(LASA2H$HMVAR32), '1'=0L,'2'=1L,'-2'=1L,.default=NA_integer_)
```  
### **Variable label**:  Ever tobacco smoking  
**Variable name**:  lsb_smk_ever_4    
**Variable description**:  Indicator of whether the participant has ever smoked any tobacco product.  
**Value type**:  integer  
**Variable unit**:  N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 |   Never smoked tobacco  
1 |   Ever smoked tobacco  

**Harmonization status**:  impossible  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}

```  
### **Variable label**:  Ever tobacco smoking  
**Variable name**:  lsb_smk_ever_5    
**Variable description**:  Indicator of whether the participant has ever smoked any tobacco product.  
**Value type**:  integer  
**Variable unit**:  N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 |   Never smoked tobacco  
1 |   Ever smoked tobacco  

**Harmonization status**:  impossible  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}

```  
### **Variable label**:  Ever tobacco smoking  
**Variable name**:  lsb_smk_ever_6    
**Variable description**:  Indicator of whether the participant has ever smoked any tobacco product.  
**Value type**:  integer  
**Variable unit**:  N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 |   Never smoked tobacco  
1 |   Ever smoked tobacco  

**Harmonization status**:  impossible  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}

```  

### **Variable label**:  Quantity cigarettes smoked    
**Variable name**:  lsb_cig_qty_0   
**Variable description**:  Current average number of cigarettes smoked per day.  
**Value type**:  integer  
**Variable unit**:  cigarettes/day  
**Category coding**:  

**Harmonization status**:  
**Harmonization comment**:   number of self-rolled cigarretes a week (past and current (self-rolled) cigarette smokers) (question)
**R script**:  
```{r, echo=TRUE}

```  
### **Variable label**:  Quantity cigarettes smoked    
**Variable name**:  lsb_cig_qty_1   
**Variable description**:  Current average number of cigarettes smoked per day.  
**Value type**:  integer  
**Variable unit**:  cigarettes/day  
**Category coding**:  

**Harmonization status**:  
**Harmonization comment**:    number of self-rolled cigarretes a week (past and current (self-rolled) cigarette smokers) (question)  
**R script**:  
```{r, echo=TRUE}

```  
### **Variable label**:  Quantity cigarettes smoked    
**Variable name**:  lsb_cig_qty_2   
**Variable description**:  Current average number of cigarettes smoked per day.  
**Value type**:  integer  
**Variable unit**:  cigarettes/day  
**Category coding**:  

**Harmonization status**:  
**Harmonization comment**:   number of self-rolled cigarretes a week (past and current (self-rolled) cigarette smokers) (question) 
**R script**:  
```{r, echo=TRUE}

```  
### **Variable label**:  Quantity cigarettes smoked    
**Variable name**:  lsb_cig_qty_3   
**Variable description**:  Current average number of cigarettes smoked per day.  
**Value type**:  integer  
**Variable unit**:  cigarettes/day  
**Category coding**:  

**Harmonization status**:  
**Harmonization comment**:   number of self-rolled cigarretes a week (past and current (self-rolled) cigarette smokers) (question) 
**R script**:  
```{r, echo=TRUE}

```  
### **Variable label**:  Quantity cigarettes smoked    
**Variable name**:  lsb_cig_qty_4   
**Variable description**:  Current average number of cigarettes smoked per day.  
**Value type**:  integer  
**Variable unit**:  cigarettes/day  
**Category coding**:  

**Harmonization status**:  impossible  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}

```  
### **Variable label**:  Quantity cigarettes smoked    
**Variable name**:  lsb_cig_qty_5   
**Variable description**:  Current average number of cigarettes smoked per day.  
**Value type**:  integer  
**Variable unit**:  cigarettes/day  
**Category coding**:  

**Harmonization status**:  impossible  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}

```  
### **Variable label**:  Quantity cigarettes smoked    
**Variable name**:  lsb_cig_qty_6   
**Variable description**:  Current average number of cigarettes smoked per day.  
**Value type**:  integer  
**Variable unit**:  cigarettes/day  
**Category coding**:  

**Harmonization status**:  impossible  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}

```  

### **Variable label**:  Smoking initiation age    
**Variable name**:  lsb_smk_start_0    
**Variable description**:  Age at which the participant started smoking any tobacco product.  
**Value type**:  integer  
**Variable unit**:  years  
**Category coding**:  

**Harmonization status**:  complete  
**Harmonization comment**:   Only cigarette smoking.  
**R script**:  
```{r, echo=TRUE}
lsb_LASA2_0$lsb_smk_start_0 <- ifelse(as.integer(LASA2B$bmvar33)<0,NA,as.integer(LASA2B$bmvar33))
```  
### **Variable label**:  Smoking initiation age    
**Variable name**:  lsb_smk_start_1    
**Variable description**:  Age at which the participant started smoking any tobacco product.  
**Value type**:  integer  
**Variable unit**:  years  
**Category coding**:  

**Harmonization status**:  complete  
**Harmonization comment**:   Only cigarette smoking.  
**R script**:  
```{r, echo=TRUE}
lsb_LASA2_1$lsb_smk_start_1 <- ifelse(as.integer(LASA2F$fmvar33)<0,NA,as.integer(LASA2F$fmvar33))
```  
### **Variable label**:  Smoking initiation age    
**Variable name**:  lsb_smk_start_2    
**Variable description**:  Age at which the participant started smoking any tobacco product.  
**Value type**:  integer  
**Variable unit**:  years  
**Category coding**:  

**Harmonization status**:  complete  
**Harmonization comment**:   Only cigarette smoking.  
**R script**:  
```{r, echo=TRUE}
lsb_LASA2_2$lsb_smk_start_2 <- ifelse(as.integer(LASA2G$gmvar33)<0,NA,as.integer(LASA2G$gmvar33))
```  
### **Variable label**:  Smoking initiation age    
**Variable name**:  lsb_smk_start_3    
**Variable description**:  Age at which the participant started smoking any tobacco product.  
**Value type**:  integer  
**Variable unit**:  years  
**Category coding**:  

**Harmonization status**:  complete  
**Harmonization comment**:   Only cigarette smoking.  
**R script**:  
```{r, echo=TRUE}
lsb_LASA2_3$lsb_smk_start_3 <- ifelse(as.integer(LASA2H$HMVAR33)<0,NA,as.integer(LASA2H$HMVAR33))
```  
### **Variable label**:  Smoking initiation age    
**Variable name**:  lsb_smk_start_4    
**Variable description**:  Age at which the participant started smoking any tobacco product.  
**Value type**:  integer  
**Variable unit**:  years  
**Category coding**:  

**Harmonization status**:  impossible  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}

```  
### **Variable label**:  Smoking initiation age    
**Variable name**:  lsb_smk_start_5    
**Variable description**:  Age at which the participant started smoking any tobacco product.  
**Value type**:  integer  
**Variable unit**:  years  
**Category coding**:  

**Harmonization status**:  impossible  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}

```  
### **Variable label**:  Smoking initiation age    
**Variable name**:  lsb_smk_start_6    
**Variable description**:  Age at which the participant started smoking any tobacco product.  
**Value type**:  integer  
**Variable unit**:  years  
**Category coding**:  

**Harmonization status**:  impossible  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}

```  

### **Variable label**:  Smoking cessation age  
**Variable name**:  lsb_smk_stop_0   
**Variable description**:  Age at which the participant last smoked any tobacco product.  
**Value type**:  integer  
**Variable unit**:  years  
**Category coding**:  

**Harmonization status**:  complete  
**Harmonization comment**:   Only cigarette smoking.  
**R script**:  
```{r, echo=TRUE}
lsb_LASA2_0$lsb_smk_stop_0 <- ifelse(as.integer(LASA2B$bmvar34)<0,NA,as.integer(LASA2B$bmvar34))
```  
### **Variable label**:  Smoking cessation age  
**Variable name**:  lsb_smk_stop_1   
**Variable description**:  Age at which the participant last smoked any tobacco product.  
**Value type**:  integer  
**Variable unit**:  years  
**Category coding**:  

**Harmonization status**:  complete  
**Harmonization comment**:   Only cigarette smoking.  
**R script**:  
```{r, echo=TRUE}
lsb_LASA2_1$lsb_smk_stop_1 <- ifelse(as.integer(LASA2F$fmvar34)<0,NA,as.integer(LASA2F$fmvar34))
```  
### **Variable label**:  Smoking cessation age  
**Variable name**:  lsb_smk_stop_2   
**Variable description**:  Age at which the participant last smoked any tobacco product.  
**Value type**:  integer  
**Variable unit**:  years  
**Category coding**:  

**Harmonization status**:  complete  
**Harmonization comment**:   Only cigarette smoking.  
**R script**:  
```{r, echo=TRUE}
lsb_LASA2_2$lsb_smk_stop_2 <- ifelse(as.integer(LASA2G$gmvar34)<0,NA,as.integer(LASA2G$gmvar34))
```  
### **Variable label**:  Smoking cessation age  
**Variable name**:  lsb_smk_stop_3   
**Variable description**:  Age at which the participant last smoked any tobacco product.  
**Value type**:  integer  
**Variable unit**:  years  
**Category coding**:  

**Harmonization status**:  complete  
**Harmonization comment**:   Only cigarette smoking.  
**R script**:  
```{r, echo=TRUE}
lsb_LASA2_3$lsb_smk_stop_3 <- ifelse(as.integer(LASA2H$HMVAR34)<0,NA,as.integer(LASA2H$HMVAR34))
```  
### **Variable label**:  Smoking cessation age  
**Variable name**:  lsb_smk_stop_4   
**Variable description**:  Age at which the participant last smoked any tobacco product.  
**Value type**:  integer  
**Variable unit**:  years  
**Category coding**:  

**Harmonization status**:  impossible  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}

```  
### **Variable label**:  Smoking cessation age  
**Variable name**:  lsb_smk_stop_5   
**Variable description**:  Age at which the participant last smoked any tobacco product.  
**Value type**:  integer  
**Variable unit**:  years  
**Category coding**:  

**Harmonization status**:  impossible  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}

```  
### **Variable label**:  Smoking cessation age  
**Variable name**:  lsb_smk_stop_6   
**Variable description**:  Age at which the participant last smoked any tobacco product.  
**Value type**:  integer  
**Variable unit**:  years  
**Category coding**:  

**Harmonization status**:  impossible  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}

```  

### **Variable label**:  Pack years  
**Variable name**:  lsb_smk_py_0    
**Variable description**:  Number of estimated pack years of the participant.   
**Value type**:  decimal    
**Variable unit**:  pack-years    
**Category coding**:  

**Harmonization status**:    
**Harmonization comment**:   question  
**R script**:  
```{r, echo=TRUE}

```  
### **Variable label**:  Pack years  
**Variable name**:  lsb_smk_py_1    
**Variable description**:  Number of estimated pack years of the participant.     
**Value type**:  decimal    
**Variable unit**:  pack-years    
**Category coding**:  

**Harmonization status**:    
**Harmonization comment**: question    
**R script**:  
```{r, echo=TRUE}

```  
### **Variable label**:  Pack years  
**Variable name**:  lsb_smk_py_2    
**Variable description**:  Number of estimated pack years of the participant.     
**Value type**:  decimal    
**Variable unit**:  pack-years    
**Category coding**:  

**Harmonization status**:    
**Harmonization comment**:   question  
**R script**:  
```{r, echo=TRUE}

```  

# Physical activity subdomain

### **Variable label**: Frequency of walking    
**Variable name**:    lsb_pa_walk_freq_0    
**Variable description**:  Number of times the participant went for a walk in last week.    
**Value type**:  integer  
**Variable unit**:  N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 |  Never  
1 |  Seldom (1-2 days)  
2 |  Sometimes (3-4 days)  
3 |  Often (5-7 days)  

**Harmonization status**:  impossible    
**Harmonization comment**:   study-specific asks for number of times walked outside.  (question)  
**R script**:  
```{r, echo=TRUE}
#lsb_LASA2_0$lsb_pa_walk_freq_0 <- ifelse((as.integer(LASA2B$blphya08)/2)==0,0L,ifelse((as.integer(LASA2B$blphya08)/2)>0 & (as.integer(LASA2B$blphya08)/2)<3,1L, ifelse((as.integer(LASA2B$blphya08)/2)>2 &(as.integer(LASA2B$blphya08)/2)<5,2L, ifelse((as.integer(LASA2B$blphya08)/2)>4 & (as.integer(LASA2B$blphya08)/2)<8,3L,NA))))
```  
### **Variable label**: Frequency of walking    
**Variable name**:    lsb_pa_walk_freq_1    
**Variable description**:  Number of times the participant went for a walk in last week.    
**Value type**:  integer  
**Variable unit**:  N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 |  Never  
1 |  Seldom (1-2 dyas)  
2 |  Sometimes (3-4 days)  
3 |  Often (5-7 days)  

**Harmonization status**:  impossible    
**Harmonization comment**:   study-specific asks for number of times walked outside.   (question)  
**R script**:  
```{r, echo=TRUE}

```  
### **Variable label**: Frequency of walking    
**Variable name**:    lsb_pa_walk_freq_2    
**Variable description**:  Number of times the participant went for a walk in last week.    
**Value type**:  integer  
**Variable unit**:  N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 |  Never  
1 |  Seldom (1-2 dyas)  
2 |  Sometimes (3-4 days)  
3 |  Often (5-7 days)    

**Harmonization status**:  impossible    
**Harmonization comment**:   study-specific asks for number of times walked outside.  (question)  
**R script**:  
```{r, echo=TRUE}

```  
### **Variable label**: Frequency of walking    
**Variable name**:    lsb_pa_walk_freq_3    
**Variable description**:  Number of times the participant went for a walk in last week.    
**Value type**:  integer  
**Variable unit**:  N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 |  Never  
1 |  Seldom (1-2 dyas)  
2 |  Sometimes (3-4 days)  
3 |  Often (5-7 days)    

**Harmonization status**:  impossible    
**Harmonization comment**:   study-specific asks for number of times walked outside.  (question)   
**R script**:  
```{r, echo=TRUE}

```  
### **Variable label**: Frequency of walking    
**Variable name**:    lsb_pa_walk_freq_4    
**Variable description**:  Number of times the participant went for a walk in last week.    
**Value type**:  integer  
**Variable unit**:  N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 |  Never  
1 |  Seldom (1-2 dyas)  
2 |  Sometimes (3-4 days)  
3 |  Often (5-7 days)    

**Harmonization status**:  impossible    
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}

```  
### **Variable label**: Frequency of walking    
**Variable name**:    lsb_pa_walk_freq_5    
**Variable description**:  Number of times the participant went for a walk in last week.    
**Value type**:  integer  
**Variable unit**:  N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 |  Never  
1 |  Seldom (1-2 dyas)  
2 |  Sometimes (3-4 days)  
3 |  Often (5-7 days)    

**Harmonization status**:  impossible    
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}

```  
### **Variable label**: Frequency of walking    
**Variable name**:    lsb_pa_walk_freq_6    
**Variable description**:  Number of times the participant went for a walk in last week.    
**Value type**:  integer  
**Variable unit**:  N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 |  Never  
1 |  Seldom (1-2 dyas)  
2 |  Sometimes (3-4 days)  
3 |  Often (5-7 days)    

**Harmonization status**:  impossible    
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}

```  

### **Variable label**:  Average walking time     
**Variable name**:   lsb_pa_walk_time_0  
**Variable description**:  Average time the participant spends walking per day.    
**Value type**:  integer  
**Variable unit**:  N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 |  Less than 30 minutes  
1 |  30 minutes but less than 1 hour  
2 |  1 hour but less than 2 hours
3 |  2 hours but less than 4 hours  
4 |  4 hours or more  

**Harmonization status**:  complete  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
lsb_LASA2_0$lsb_pa_walk_time_0 <- ifelse(as.integer(LASA2B$blphya09)<30 & as.integer(LASA2B$blphya09)>=0 ,0L, ifelse(as.integer(LASA2B$blphya09)>=30 & as.integer(LASA2B$blphya09)<60,1L, ifelse(as.integer(LASA2B$blphya09)>=60 & as.integer(LASA2B$blphya09)<120,2L, ifelse(as.integer(LASA2B$blphya09)>=120 & as.integer(LASA2B$blphya09)<240,3L, ifelse(as.integer(LASA2B$blphya09)>=240,4L,NA)))))
```  
### **Variable label**:  Average walking time   
**Variable name**:   lsb_pa_walk_time_1  
**Variable description**:  Average time the participant spends walking per day.    
**Value type**:  integer  
**Variable unit**:  N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 |  Less than 30 minutes  
1 |  30 minutes but less than 1 hour  
2 |  1 hour but less than 2 hours
3 |  2 hours but less than 4 hours  
4 |  4 hours or more   

**Harmonization status**:  complete  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
lsb_LASA2_1$lsb_pa_walk_time_1 <- ifelse(as.integer(LASA2F$flphya09)<30 & as.integer(LASA2F$flphya09)>=0 ,0L, ifelse(as.integer(LASA2F$flphya09)>=30 & as.integer(LASA2F$flphya09)<60,1L, ifelse(as.integer(LASA2F$flphya09)>=60 & as.integer(LASA2F$flphya09)<120,2L, ifelse(as.integer(LASA2F$flphya09)>=120 & as.integer(LASA2F$flphya09)<240,3L, ifelse(as.integer(LASA2F$flphya09)>=240,4L,NA)))))
```  
### **Variable label**:  Average walking time    
**Variable name**:   lsb_pa_walk_time_2  
**Variable description**:  Average time the participant spends walking per day.    
**Value type**:  integer  
**Variable unit**:  N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 |  Less than 30 minutes  
1 |  30 minutes but less than 1 hour  
2 |  1 hour but less than 2 hours
3 |  2 hours but less than 4 hours  
4 |  4 hours or more   

**Harmonization status**:  complete  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
lsb_LASA2_2$lsb_pa_walk_time_2 <- ifelse(as.integer(LASA2G$glphya09)<30 & as.integer(LASA2G$glphya09)>=0 ,0L, ifelse(as.integer(LASA2G$glphya09)>=30 & as.integer(LASA2G$glphya09)<60,1L, ifelse(as.integer(LASA2G$glphya09)>=60 & as.integer(LASA2G$glphya09)<120,2L, ifelse(as.integer(LASA2G$glphya09)>=120 & as.integer(LASA2G$glphya09)<240,3L, ifelse(as.integer(LASA2G$glphya09)>=240,4L,NA)))))
```  
### **Variable label**:  Average walking time     
**Variable name**:   lsb_pa_walk_time_3  
**Variable description**:  Average time the participant spends walking per day.    
**Value type**:  integer  
**Variable unit**:  N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 |  Less than 30 minutes  
1 |  30 minutes but less than 1 hour  
2 |  1 hour but less than 2 hours
3 |  2 hours but less than 4 hours  
4 |  4 hours or more   

**Harmonization status**:  complete  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
lsb_LASA2_3$lsb_pa_walk_time_3 <- ifelse(as.integer(LASA2H$HLPHYA09)<30 & as.integer(LASA2H$HLPHYA09)>=0 ,0L, ifelse(as.integer(LASA2H$HLPHYA09)>=30 & as.integer(LASA2H$HLPHYA09)<60,1L, ifelse(as.integer(LASA2H$HLPHYA09)>=60 & as.integer(LASA2H$HLPHYA09)<120,2L, ifelse(as.integer(LASA2H$HLPHYA09)>=120 & as.integer(LASA2H$HLPHYA09)<240,3L, ifelse(as.integer(LASA2H$HLPHYA09)>=240,4L,NA)))))
```  
### **Variable label**:  Average walking time    
**Variable name**:   lsb_pa_walk_time_4  
**Variable description**:  Average time the participant spends walking per day.    
**Value type**:  integer  
**Variable unit**:  N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 |  Less than 30 minutes  
1 |  30 minutes but less than 1 hour  
2 |  1 hour but less than 2 hours
3 |  2 hours but less than 4 hours  
4 |  4 hours or more     

**Harmonization status**:  impossible  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}

```  
### **Variable label**:  Average walking time     
**Variable name**:   lsb_pa_walk_time_5  
**Variable description**:  Average time the participant spends walking per day.    
**Value type**:  integer  
**Variable unit**:  N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 |  Less than 30 minutes  
1 |  30 minutes but less than 1 hour  
2 |  1 hour but less than 2 hours
3 |  2 hours but less than 4 hours  
4 |  4 hours or more     

**Harmonization status**:  impossible  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}

```  
### **Variable label**:  Average walking time     
**Variable name**:   lsb_pa_walk_time_6  
**Variable description**:  Average time the participant spends walking per day.    
**Value type**:  integer  
**Variable unit**:  N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 |  Less than 30 minutes  
1 |  30 minutes but less than 1 hour  
2 |  1 hour but less than 2 hours
3 |  2 hours but less than 4 hours  
4 |  4 hours or more    

**Harmonization status**:  impossible  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}

```  

### **Variable label**:  Average walking time for transportation  
**Variable name**:  lsb_pa_walk_trans_0    
**Variable description**:  Minutes per week the participant spent on walking for transportation (utilitarian walking) in the last week.  
**Value type**:  integer  
**Variable unit**:  minutes/week  
**Category coding**:  N/A  

**Harmonization status**:  impossible  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}

```  
### **Variable label**:  Average walking time for transportation    
**Variable name**:  lsb_pa_walk_trans_1    
**Variable description**: Minutes per week the participant spent on walking for transportation (utilitarian walking) in the last week.    
**Value type**:  integer  
**Variable unit**:  minutes/week  
**Category coding**:  N/A  

**Harmonization status**:  impossible  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}

```   
### **Variable label**:  Average walking time for transportation    
**Variable name**:  lsb_pa_walk_trans_2    
**Variable description**:  Minutes per week the participant spent on walking for transportation (utilitarian walking) in the last week.  
**Value type**:  integer  
**Variable unit**:  minutes/week  
**Category coding**:  N/A  

**Harmonization status**:  impossible  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}

```   
### **Variable label**:  Average walking for transportation    
**Variable name**:  lsb_pa_walk_trans_4    
**Variable description**:  Minutes per week the participant spent on walking for transportation (utilitarian walking) in the last week.    
**Value type**:  integer  
**Variable unit**:  minutes/week  
**Category coding**:  N/A  

**Harmonization status**:  impossible  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}

```   

### **Variable label**:  Average walking time for leisure  
**Variable name**:  lsb_pa_walk_leis_0    
**Variable description**:  Minutes per week the participant spent on walking for leisure in the last week.  
**Value type**:  integer  
**Variable unit**:  minutes/week  
**Category coding**:  N/A  

**Harmonization status**:  impossible  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}

```  
### **Variable label**:  Average walking time for leisure  
**Variable name**:  lsb_pa_walk_leis_2    
**Variable description**:  Minutes per week the participant spent on walking for leisure in the last week.  
**Value type**:  integer  
**Variable unit**:  minutes/week  
**Category coding**:  N/A  

**Harmonization status**:  impossible  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}

```   
### **Variable label**:  Average walking time for leisure  
**Variable name**:  lsb_pa_walk_leis_3    
**Variable description**:  Minutes per week the participant spent on walking for leisure in the last week.  
**Value type**:  integer  
**Variable unit**:  minutes/week  
**Category coding**:  N/A  

**Harmonization status**:  impossible  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}

```   
### **Variable label**:  Average walking for leisure  
**Variable name**:  lsb_pa_walk_leis_4    
**Variable description**:  Minutes per week the participant spent on walking for leisure in the last week.  
**Value type**:  integer  
**Variable unit**:  minutes/week  
**Category coding**:  N/A  

**Harmonization status**:  impossible  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}

```    

### **Variable label**:  Average cycling time    
**Variable name**:  lsb_pa_cycle_0  
**Variable description**:  Average minutes per week the participant spent on cycling in the last week.  
**Value type**:  integer  
**Variable unit**:  minutes per week  
**Category coding**:  N/A  

**Harmonization status**:  
**Harmonization comment**:    
**R script**:  
```{r, echo=TRUE}
#This is where the R-script will be written

```  
### **Variable label**:  Average cycling time    
**Variable name**:  lsb_pa_cycle_1  
**Variable description**:  Average minutes per week the participant spent on cycling in the last week.    
**Value type**:  integer  
**Variable unit**:  minutes per week  
**Category coding**:  N/A  

**Harmonization status**:  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
#This is where the R-script will be written

```  
### **Variable label**:  Average cycling time    
**Variable name**:  lsb_pa_cycle_2  
**Variable description**:  Average minutes per week the participant spent on cycling in the last week.    
**Value type**:  integer  
**Variable unit**:  minutes per week  
**Category coding**:  N/A  

**Harmonization status**:  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
#This is where the R-script will be written

```  
### **Variable label**:  Average cycling time    
**Variable name**:  lsb_pa_cycle_3  
**Variable description**:  Average minutes per week the participant spent on cycling in the last week.    
**Value type**:  integer  
**Variable unit**:  minutes per week  
**Category coding**:  N/A  

**Harmonization status**:  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
#This is where the R-script will be written

```  
### **Variable label**:  Average cycling time    
**Variable name**:  lsb_pa_cycle_4  
**Variable description**:  Average minutes per week the participant spent on cycling in the last week.    
**Value type**:  integer  
**Variable unit**:  minutes per week  
**Category coding**:  N/A  

**Harmonization status**:  impossible  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}

```  
### **Variable label**:  Average cycling time    
**Variable name**:  lsb_pa_cycle_5  
**Variable description**:  Average minutes per week the participant spent on cycling in the last week.    
**Value type**:  integer  
**Variable unit**:  minutes per week  
**Category coding**:  N/A  

**Harmonization status**:  impossible  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}

```   
### **Variable label**:  Average cycling time    
**Variable name**:  lsb_pa_cycle_6  
**Variable description**:  Average minutes per week the participant spent on cycling in the last week.    
**Value type**:  integer  
**Variable unit**:  minutes per week  
**Category coding**:  N/A  

**Harmonization status**:  impossible  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}

```    

### **Variable label**:  Gardening   
**Variable name**:  lsb_pa_garden_0  
**Variable description**:  Indicator of whether the participant does any gardening activities.  
**Value type**:  integer  
**Variable unit**:  N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 |   Does not do any gardening activities  
1 |   Does any gardeing activities  

**Harmonization status**:  complete   
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
lsb_LASA2_0$lsb_pa_garden_0 <- ifelse(as.integer(LASA2B$blphya17)==2,1L, ifelse(as.integer(LASA2B$blphya17)==1, 0L, ifelse(as.integer(LASA2B$blphya17)==-2 & as.integer(LASA2B$blphya15)==-2 & as.integer(LASA2B$blphya14)==1,0L,NA)))
```  
### **Variable label**:  Gardening    
**Variable name**:  lsb_pa_garden_1  
**Variable description**:  Indicator of whether the participant does any gardening activities.  
**Value type**:  integer  
**Variable unit**:  N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 |   Does not do any gardening activities  
1 |   Does any gardeing activities  

**Harmonization status**:  complete  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
lsb_LASA2_1$lsb_pa_garden_1 <- ifelse(as.integer(LASA2F$flphya17)==2, 1L, ifelse(as.integer(LASA2F$flphya17)==1, 0L, ifelse(as.integer(LASA2F$flphya17)==-2 & as.integer(LASA2F$flphya15)==-2 & as.integer(LASA2F$flphya14)==1,0L,NA)))
```  
### **Variable label**:  Gardening    
**Variable name**:  lsb_pa_garden_2  
**Variable description**:  Indicator of whether the participant does any gardening activities.  
**Value type**:  integer  
**Variable unit**:  N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 |   Does not do any gardening activities  
1 |   Does any gardeing activities  

**Harmonization status**:  complete  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
lsb_LASA2_2$lsb_pa_garden_2 <- ifelse(as.integer(LASA2G$glphya17)==2, 1L, ifelse(as.integer(LASA2G$glphya17)==1, 0L, ifelse(as.integer(LASA2G$glphya17)==-2 & as.integer(LASA2G$glphya15)==-2 & as.integer(LASA2G$glphya14)==1,0L,NA)))
```  
### **Variable label**:  Gardening    
**Variable name**:  lsb_pa_garden_3  
**Variable description**:  Indicator of whether the participant does any gardening activities.  
**Value type**:  integer  
**Variable unit**:  N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 |   Does not do any gardening activities  
1 |   Does any gardeing activities  

**Harmonization status**:  complete  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
lsb_LASA2_3$lsb_pa_garden_3 <- ifelse(as.integer(LASA2H$HLPHYA17)==2, 1L, ifelse(as.integer(LASA2H$HLPHYA17)==1, 0L, ifelse(as.integer(LASA2H$HLPHYA17)==-2 & as.integer(LASA2H$HLPHYA15)==-2 & as.integer(LASA2H$HLPHYA14)==1,0L,NA)))
```  
### **Variable label**:  Gardening    
**Variable name**:  lsb_pa_garden_4  
**Variable description**:  Indicator of whether the participant does any gardening activities.  
**Value type**:  integer  
**Variable unit**:  N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 |   Does not do any gardening activities  
1 |   Does any gardeing activities  

**Harmonization status**:  impossible  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}

```  
### **Variable label**:  Gardening    
**Variable name**:  lsb_pa_garden_5  
**Variable description**:  Indicator of whether the participant does any gardening activities.  
**Value type**:  integer  
**Variable unit**:  N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 |   Does not do any gardening activities  
1 |   Does any gardeing activities  

**Harmonization status**:  impossible  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}

```  
### **Variable label**:  Gardening    
**Variable name**:  lsb_pa_garden_6  
**Variable description**:  Indicator of whether the participant does any gardening activities.  
**Value type**:  integer  
**Variable unit**:  N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 |   Does not do any gardening activities  
1 |   Does any gardeing activities  

**Harmonization status**:  impossible  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}

```  
### **Variable label**:  Average gardening time    
**Variable name**:  lsb_pa_garden_time_0    
**Variable description**:  Average minutes per week the participant spent on gardening activities in the last week.    
**Value type**:  integer  
**Variable unit**:  minutes/week  
**Category coding**:  N/A  

**Harmonization status**:  complete  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
lsb_LASA2_0$lsb_pa_garden_time_0 <- ifelse(as.integer(LASA2B$blphya19)==-2 & as.integer(LASA2B$blphya17)==-2 & as.integer(LASA2B$blphya14)==1,0L, ifelse(as.integer(LASA2B$blphya19)<0, NA,as.integer(LASA2B$blphya19)/2))
```  
### **Variable label**:  Average gardening time    
**Variable name**:  lsb_pa_garden_time_1    
**Variable description**:  Average minutes per week the participant spent on gardening activities in the last week.       
**Value type**:  integer  
**Variable unit**:  minutes/week    
**Category coding**:  N/A  

**Harmonization status**:  complete  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
lsb_LASA2_1$lsb_pa_garden_time_1 <- ifelse(as.integer(LASA2F$flphya19)==-2 & as.integer(LASA2F$flphya17)==-2 & as.integer(LASA2F$flphya14)==1,0L, ifelse(as.integer(LASA2F$flphya19)<0, NA,as.integer(LASA2F$flphya19)/2))
```  
### **Variable label**:  Average gardening time    
**Variable name**:  lsb_pa_garden_time_2    
**Variable description**:  Average minutes per week the participant spent on gardening activities in the last week.       
**Value type**:  integer  
**Variable unit**:  minutes/week    
**Category coding**:  N/A  

**Harmonization status**:  complete  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
lsb_LASA2_2$lsb_pa_garden_time_2 <- ifelse(as.integer(LASA2G$glphya19)==-2 & as.integer(LASA2G$glphya17)==-2 & as.integer(LASA2G$glphya14)==1,0L, ifelse(as.integer(LASA2G$glphya19)<0, NA,as.integer(LASA2G$glphya19)/2))
```  
### **Variable label**:  Average gardening time    
**Variable name**:  lsb_pa_garden_time_3    
**Variable description**:  Average minutes per week the participant spent on gardening activities in the last week.       
**Value type**:  integer  
**Variable unit**:  minutes/week    
**Category coding**:  N/A  

**Harmonization status**:  complete  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
lsb_LASA2_3$lsb_pa_garden_time_3 <- ifelse(as.integer(LASA2H$HLPHYA19)==-2 & as.integer(LASA2H$HLPHYA17)==-2 & as.integer(LASA2H$HLPHYA14)==1,0L, ifelse(as.integer(LASA2H$HLPHYA19)<0, NA,as.integer(LASA2H$HLPHYA19)/2))
```  
### **Variable label**:  Average gardening time    
**Variable name**:  lsb_pa_garden_time_4    
**Variable description**:  Average minutes per week the participant spent on gardening activities in the last week.       
**Value type**:  integer  
**Variable unit**:  minutes/week    
**Category coding**:  N/A  

**Harmonization status**:  impossible  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}

```   
### **Variable label**:  Average gardening time    
**Variable name**:  lsb_pa_garden_time_5    
**Variable description**:  Average minutes per week the participant spent on gardening activities in the last week.       
**Value type**:  integer  
**Variable unit**:  minutes/week    
**Category coding**:  N/A  

**Harmonization status**:  impossible  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}

```    
### **Variable label**:  Average gardening time    
**Variable name**:  lsb_pa_garden_time_6    
**Variable description**:  Average minutes per week the participant spent on gardening activities in the last week.       
**Value type**:  integer  
**Variable unit**:  minutes/week    
**Category coding**:  N/A  

**Harmonization status**:  impossible  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}

```  

### **Variable label**:  Household activities  
**Variable name**:  lsb_pa_house_0  
**Variable description**:  Indicator of whether the participant does any household activities (light, moderate or vigorous).     
**Value type**:  integer  
**Variable unit**:  N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 |   Does not do any household activities  
1 |   Does any household activities  

**Harmonization status**:  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
#This is where the R-script will be written

```  
### **Variable label**:  Household activities  
**Variable name**:  lsb_pa_house_1  
**Variable description**:  Indicator of whether the participant does any household activities (light, moderate or vigorous).     
**Value type**:  integer  
**Variable unit**:  N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 |   Does not do any household activities  
1 |   Does any household activities  

**Harmonization status**:  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
#This is where the R-script will be written

```  
### **Variable label**:  Household activities  
**Variable name**:  lsb_pa_house_2  
**Variable description**:  Indicator of whether the participant does any household activities (light, moderate or vigorous).     
**Value type**:  integer  
**Variable unit**:  N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 |   Does not do any household activities  
1 |   Does any household activities  

**Harmonization status**:  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
#This is where the R-script will be written

```  
### **Variable label**:  Household activities  
**Variable name**:  lsb_pa_house_3  
**Variable description**:  Indicator of whether the participant does any household activities (light, moderate or vigorous).     
**Value type**:  integer  
**Variable unit**:  N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 |   Does not do any household activities  
1 |   Does any household activities  

**Harmonization status**:  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
#This is where the R-script will be written

```  
### **Variable label**:  Household activities  
**Variable name**:  lsb_pa_house_4  
**Variable description**:  Indicator of whether the participant does any household activities (light, moderate or vigorous).     
**Value type**:  integer  
**Variable unit**:  N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 |   Does not do any household activities  
1 |   Does any household activities  

**Harmonization status**:  impossible  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}

```    
### **Variable label**:  Household activities  
**Variable name**:  lsb_pa_house_5  
**Variable description**:  Indicator of whether the participant does any household activities (light, moderate or vigorous).     
**Value type**:  integer  
**Variable unit**:  N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 |   Does not do any household activities  
1 |   Does any household activities  

**Harmonization status**:  impossible  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}

```   
### **Variable label**:  Household activities  
**Variable name**:  lsb_pa_house_6  
**Variable description**:  Indicator of whether the participant does any household activities (light, moderate or vigorous).     
**Value type**:  integer  
**Variable unit**:  N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 |   Does not do any household activities  
1 |   Does any household activities  

**Harmonization status**:  impossible  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}

```  

### **Variable label**:  Average household activities time      
**Variable name**:  lsb_pa_house_time_0  
**Variable description**:  Average minutes per week the participant spent doing household activities in last week.  
**Value type**:  integer  
**Variable unit**:  minutes per week  
**Category coding**:  N/A  

**Harmonization status**:  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
#This is where the R-script will be written

```  
### **Variable label**:  Average household activities time      
**Variable name**:  lsb_pa_house_time_1  
**Variable description**:  Average minutes per week the participant spent doing household activities in last week.  
**Value type**:  integer  
**Variable unit**:  minutes per week  
**Category coding**:  N/A  

**Harmonization status**:  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
#This is where the R-script will be written

```  
### **Variable label**:  Average household activities time      
**Variable name**:  lsb_pa_house_time_2  
**Variable description**:  Average minutes per week the participant spent doing household activities in last week.  
**Value type**:  integer  
**Variable unit**:  minutes per week  
**Category coding**:  N/A  

**Harmonization status**:  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
#This is where the R-script will be written

```  
### **Variable label**:  Average household activities time      
**Variable name**:  lsb_pa_house_time_3  
**Variable description**:  Average minutes per week the participant spent doing household activities in last week.  
**Value type**:  integer  
**Variable unit**:  minutes per week  
**Category coding**:  N/A  

**Harmonization status**:  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
#This is where the R-script will be written

```  
### **Variable label**:  Average household activities time      
**Variable name**:  lsb_pa_house_time_4  
**Variable description**:  Average minutes per week the participant spent doing household activities in last week.  
**Value type**:  integer  
**Variable unit**:  minutes per week  
**Category coding**:  N/A  

**Harmonization status**:  impossible  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}

```  
### **Variable label**:  Average household activities time      
**Variable name**:  lsb_pa_house_time_5  
**Variable description**:  Average minutes per week the participant spent doing household activities in last week.  
**Value type**:  integer  
**Variable unit**:  minutes per week  
**Category coding**:  N/A  

**Harmonization status**:  impossible  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}

```   
### **Variable label**:  Average household activities time      
**Variable name**:  lsb_pa_house_time_6  
**Variable description**:  Average minutes per week the participant spent doing household activities in last week.  
**Value type**:  integer  
**Variable unit**:  minutes per week  
**Category coding**:  N/A  

**Harmonization status**:  impossible  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}

```   
### **Variable label**: Sports or exercise      
**Variable name**:  lsb_pa_sport_0  
**Variable description**:  Indicator of whether the participant does any sports or exercise.  
**Value type**:  integer  
**Variable unit**:  N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 |  Does not do any sports or exercise   
1 |  Does any sports or exercise

**Harmonization status**:  impossible    
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}

```   
### **Variable label**: Sports or exercise      
**Variable name**:  lsb_pa_sport_1  
**Variable description**:  Indicator of whether the participant does any sports or exercise.  
**Value type**:  integer  
**Variable unit**:  N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 |  Does not do any sports or exercise   
1 |  Does any sports or exercise

**Harmonization status**:  impossible  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}

```   
### **Variable label**: Sports or exercise      
**Variable name**:  lsb_pa_sport_2  
**Variable description**:  Indicator of whether the participant does any sports or exercise.  
**Value type**:  integer  
**Variable unit**:  N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 |  Does not do any sports or exercise   
1 |  Does any sports or exercise

**Harmonization status**:  impossible  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}

```   
### **Variable label**: Sports or exercise      
**Variable name**:  lsb_pa_sport_3  
**Variable description**:  Indicator of whether the participant does any sports or exercise.  
**Value type**:  integer  
**Variable unit**:  N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 |  Does not do any sports or exercise   
1 |  Does any sports or exercise

**Harmonization status**:  impossible  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}

```   
### **Variable label**: Sports or exercise      
**Variable name**:  lsb_pa_sport_4  
**Variable description**:  Indicator of whether the participant does any sports or exercise.  
**Value type**:  integer  
**Variable unit**:  N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 |  Does not do any sports or exercise   
1 |  Does any sports or exercise

**Harmonization status**:  impossible  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}

```   
### **Variable label**: Sports or exercise      
**Variable name**:  lsb_pa_sport_5  
**Variable description**:  Indicator of whether the participant does any sports or exercise.  
**Value type**:  integer  
**Variable unit**:  N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 |  Does not do any sports or exercise   
1 |  Does any sports or exercise

**Harmonization status**:  impossible  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}

```     
### **Variable label**: Sports or exercise      
**Variable name**:  lsb_pa_sport_6  
**Variable description**:  Indicator of whether the participant does any sports or exercise.  
**Value type**:  integer  
**Variable unit**:  N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 |  Does not do any sports or exercise   
1 |  Does any sports or exercise

**Harmonization status**:  impossible  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}

```    

### **Variable label**:  Average sports or exercise time       
**Variable name**:  lsb_pa_sport_time_0  
**Variable description**:  Average time a week the participant spent on sports or exercise.    
**Value type**: integer  
**Variable unit**:  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 |  never   
1 |  less than 1 hour a week   
2 |  between 1 and 2 hours a week   
3 |  more than 2 hours a week  

**Harmonization status**:  impossible  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}

```  
### **Variable label**:  Average sports or exercise time       
**Variable name**:  lsb_pa_sport_time_1  
**Variable description**:  Average time a week the participant spent on sports or exercise.    
**Value type**: integer    
**Variable unit**:  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 |  never   
1 |  less than 1 hour a week   
2 |  between 1 and 2 hours a week   
3 |  more than 2 hours a week   

**Harmonization status**:  impossible  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}

```  
### **Variable label**:  Average sports or exercise time       
**Variable name**:  lsb_pa_sport_time_2  
**Variable description**:  Average time a week the participant spent on sports or exercise.    
**Value type**: integer   
**Variable unit**:  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 |  never   
1 |  less than 1 hour a week   
2 |  between 1 and 2 hours a week   
3 |  more than 2 hours a week    

**Harmonization status**:  impossible  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}

```  
### **Variable label**:  Average sports or exercise time       
**Variable name**:  lsb_pa_sport_time_3  
**Variable description**:  Average time a week the participant spent on sports or exercise.    
**Value type**: integer    
**Variable unit**:  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 |  never   
1 |  less than 1 hour a week   
2 |  between 1 and 2 hours a week   
3 |  more than 2 hours a week    

**Harmonization status**:  impossible  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}

```  
### **Variable label**:  Average sports or exercise time       
**Variable name**:  lsb_pa_sport_time_4  
**Variable description**:  Average time a week the participant spent on sports or exercise.    
**Value type**: integer   
**Variable unit**:  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 |  never   
1 |  less than 1 hour a week   
2 |  between 1 and 2 hours a week   
3 |  more than 2 hours a week    

**Harmonization status**:  impossible  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}

```    
### **Variable label**:  Average sports or exercise time       
**Variable name**:  lsb_pa_sport_time_5  
**Variable description**:  Average time a week the participant spent on sports or exercise.    
**Value type**: integer   
**Variable unit**:  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 |  never   
1 |  less than 1 hour a week   
2 |  between 1 and 2 hours a week   
3 |  more than 2 hours a week    

**Harmonization status**:  impossible  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}

```  
### **Variable label**:  Average sports or exercise time       
**Variable name**:  lsb_pa_sport_time_6  
**Variable description**:  Average time a week the participant spent on sports or exercise.    
**Value type**: integer   
**Variable unit**:  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 |  never   
1 |  less than 1 hour a week   
2 |  between 1 and 2 hours a week   
3 |  more than 2 hours a week    

**Harmonization status**:  impossible  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}

```    

# Diet and nutrition subdomain

### **Variable label**:  Daily vegetable consumption  
**Variable name**:  lsb_veg_0    
**Variable description**:  Indicator of whether the participant currently consumes vegetables on a daily basis.   
**Value type**:  integer  
**Variable unit**:  N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 |   Does not consume vegetables on a daily basis  
1 |   Consumes vegetables on a daily basis  

**Harmonization status**:  impossible  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}

```  
### **Variable label**:  Daily vegetable consumption  
**Variable name**:  lsb_veg_1    
**Variable description**:  Indicator of whether the participant currently consumes vegetables on a daily basis.   
**Value type**:  integer  
**Variable unit**:  N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 |   Does not consume vegetables on a daily basis  
1 |   Consumes vegetables on a daily basis  

**Harmonization status**:  impossible  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}

```  
### **Variable label**:  Daily vegetable consumption  
**Variable name**:  lsb_veg_2    
**Variable description**:  Indicator of whether the participant currently consumes vegetables on a daily basis.   
**Value type**:  integer  
**Variable unit**:  N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 |   Does not consume vegetables on a daily basis  
1 |   Consumes vegetables on a daily basis  

**Harmonization status**:  impossible  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}

```  

### **Variable label**:  Daily fruit consumption  
**Variable name**:  lsb_fruit_0  
**Variable description**:  Indicator of whether the participant currently consumes fruit on a daily basis.   
**Value type**:  integer  
**Variable unit**:  N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 |   Does not consume fruit on a daily basis
1 |   Consumes fruit on a daily basis  

**Harmonization status**:  impossible  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}

```  
### **Variable label**:  Daily fruit consumption  
**Variable name**:  lsb_fruit_1  
**Variable description**:  Indicator of whether the participant currently consumes fruit on a daily basis.   
**Value type**:  integer  
**Variable unit**:  N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 |   Does not consume fruit on a daily basis
1 |   Consumes fruit on a daily basis  

**Harmonization status**:  impossible  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}

```  
### **Variable label**:  Daily fruit consumption  
**Variable name**:  lsb_fruit_2  
**Variable description**:  Indicator of whether the participant currently consumes fruit on a daily basis.   
**Value type**:  integer  
**Variable unit**:  N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 |   Does not consume fruit on a daily basis
1 |   Consumes fruit on a daily basis  

**Harmonization status**:  impossible  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}

```  

### **Variable label**:  Daily water consumption  
**Variable name**:  lsb_water_0    
**Variable description**:  Indicator of whether the participant drinks water on a daily basis.   
**Value type**:  integer  
**Variable unit**:  N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 |   Does not drinks water on a daily basis
1 |   Drinks water on a daily basis

**Harmonization status**:  impossible  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}

```  
### **Variable label**:  Daily water consumption  
**Variable name**:  lsb_water_1    
**Variable description**:  Indicator of whether the participant drinks water on a daily basis.   
**Value type**:  integer  
**Variable unit**:  N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 |   Does not drinks water on a daily basis
1 |   Drinks water on a daily basis

**Harmonization status**:  impossible  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}

```   
### **Variable label**:  Daily water consumption  
**Variable name**:  lsb_water_2    
**Variable description**:  Indicator of whether the participant drinks water on a daily basis.   
**Value type**:  integer  
**Variable unit**:  N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 |   Does not drinks water on a daily basis
1 |   Drinks water on a daily basis

**Harmonization status**:  impossible  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}

```   
### **Variable label**:  Daily water consumption  
**Variable name**:  lsb_water_4    
**Variable description**:  Indicator of whether the participant drinks water on a daily basis.   
**Value type**:  integer  
**Variable unit**:  N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 |   Does not drinks water on a daily basis
1 |   Drinks water on a daily basis

**Harmonization status**:  impossible  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}

```   

### **Variable label**:  Quantity daily coffee  
**Variable name**:  lsb_coffee_qty_0  
**Variable description**:  Current quantity of coffee the participant consumes per day.   
**Value type**:  integer  
**Variable unit**:  cups/day  
**Category coding**:  N/A  

**Harmonization status**:  impossible  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}

```  
### **Variable label**:  Quantity daily coffee  
**Variable name**:  lsb_coffee_qty_1  
**Variable description**:  Current quantity of coffee the participant consumes per day.   
**Value type**:  integer  
**Variable unit**:  cups/day 
**Category coding**:  N/A  

**Harmonization status**:  impossible  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}

```    
### **Variable label**:  Quantity daily coffee  
**Variable name**:  lsb_coffee_qty_2  
**Variable description**:  Current quantity of coffee the participant consumes per day.   
**Value type**:  integer  
**Variable unit**:  cups/day  
**Category coding**:  N/A  

**Harmonization status**:  impossible  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}

```  
### **Variable label**:  Quantity daily coffee  
**Variable name**:  lsb_coffee_qty_3  
**Variable description**:  Current quantity of coffee the participant consumes per day.   
**Value type**:  integer  
**Variable unit**:  cups/day 
**Category coding**:  N/A  

**Harmonization status**:  impossible  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}

```  
### **Variable label**:  Quantity daily coffee  
**Variable name**:  lsb_coffee_qty_4  
**Variable description**:  Current quantity of coffee the participant consumes per day.   
**Value type**:  integer  
**Variable unit**:  cups/day  
**Category coding**:  N/A  

**Harmonization status**:  impossible  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}

```  

# Sleep quality subdomain

### **Variable label**:  Average sleep hours  
**Variable name**:  lsb_sleep_hours_0  
**Variable description**:  Average number of hours the participant sleeps per night.  
**Value type**:  integer  
**Variable unit**:  hours/night  
**Category coding**:  N/A  

**Harmonization status**:  complete  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
lsb_LASA2_0$lsb_sleep_hours_0 <- ifelse(as.integer(LASA2B$bqsleep1)<0,NA, as.integer(LASA2B$bqsleep1))
```  
### **Variable label**:  Average sleep hours  
**Variable name**:  lsb_sleep_hours_1  
**Variable description**:  Average number of hours the participant sleeps per night.  
**Value type**:  integer  
**Variable unit**:  hours/night   
**Category coding**:  N/A  

**Harmonization status**:  complete  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
lsb_LASA2_1$lsb_sleep_hours_1 <- ifelse(as.integer(LASA2F$fqsleep1)<0,NA, as.integer(LASA2F$fqsleep1))
```  
### **Variable label**:  Average sleep hours  
**Variable name**:  lsb_sleep_hours_2  
**Variable description**:  Average number of hours the participant sleeps per night.  
**Value type**:  integer  
**Variable unit**:  hours/night 
**Category coding**:  N/A  

**Harmonization status**:  complete  
**Harmonization comment**:   redo
**R script**:  
```{r, echo=TRUE}
lsb_LASA2_2$lsb_sleep_hours_2 <- ifelse(as.integer(LASA2G$gqsleep1)<0,NA, (as.integer(LASA2G$gqsleep1)/60))
```  
### **Variable label**:  Average sleep hours  
**Variable name**:  lsb_sleep_hours_3  
**Variable description**:  Average number of hours the participant sleeps per night.  
**Value type**:  integer  
**Variable unit**:  hours/night
**Category coding**:  N/A  

**Harmonization status**:  complete  
**Harmonization comment**:   redo
**R script**:  
```{r, echo=TRUE}
lsb_LASA2_3$lsb_sleep_hours_3 <- ifelse(as.integer(LASA2H$hqsleep1)<0,NA, (as.integer(LASA2H$hqsleep1)/60))
```  
### **Variable label**:  Average sleep hours  
**Variable name**:  lsb_sleep_hours_4    
**Variable description**:  Average number of hours the participant sleeps per night.  
**Value type**:  integer  
**Variable unit**:  hours/night   
**Category coding**:  N/A  

**Harmonization status**:  impossible  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}

```  
### **Variable label**:  Average sleep hours  
**Variable name**:  lsb_sleep_hours_5  
**Variable description**:  Average number of hours the participant sleeps per night.  
**Value type**:  integer  
**Variable unit**:  hours/night    
**Category coding**:  N/A  

**Harmonization status**:  impossible  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}

```  

### **Variable label**:  Difficulty falling a sleep  
**Variable name**:  lsb_sleep_diff_0  
**Variable description**:  Indicator of whether the participant ever has any diffulty falling a sleep.  
**Value type**:  integer  
**Variable unit**:  N/A  
**Category coding**:    

**Code** | **Category Label**  
------------- | -------------  
0 |  Never has difficulty falling asleep
1 |  Sometimes has difficulty falling asleep

**Harmonization status**:  complete    
**Harmonization comment**:   question  
**R script**:  
```{r, echo=TRUE}
lsb_LASA2_0$lsb_sleep_diff_0 <- recode(as.integer(LASA2B$bqsleep2),'1'=0L,'2'=1L,'3'=1L,'4'=1L,.default=NA_integer_)
```  
### **Variable label**:  Difficulty falling a sleep  
**Variable name**:  lsb_sleep_diff_1  
**Variable description**:  Indicator of whether the participant ever has any diffulty falling a sleep.  
**Value type**:  integer  
**Variable unit**:  N/A  
**Category coding**:    

**Code** | **Category Label**  
------------- | -------------  
0 |  Never has difficulty falling asleep
1 |  Sometimes has difficulty falling asleep

**Harmonization status**:  complete    
**Harmonization comment**:   question  
**R script**:  
```{r, echo=TRUE}
lsb_LASA2_1$lsb_sleep_diff_1 <- recode(as.integer(LASA2F$fqsleep2),'1'=0L,'2'=1L,'3'=1L,'4'=1L,.default=NA_integer_)
```  
### **Variable label**:  Difficulty falling a sleep  
**Variable name**:  lsb_sleep_diff_2    
**Variable description**:  Indicator of whether the participant ever has any diffulty falling a sleep.  
**Value type**:  integer  
**Variable unit**:  N/A  
**Category coding**:    

**Code** | **Category Label**  
------------- | -------------  
0 |  Never has difficulty falling asleep
1 |  Sometimes has difficulty falling asleep

**Harmonization status**:  complete    
**Harmonization comment**:   question  
**R script**:  
```{r, echo=TRUE}
lsb_LASA2_2$lsb_sleep_diff_2 <- recode(as.integer(LASA2G$gqsleep2),'1'=0L,'2'=1L,'3'=1L,'4'=1L,.default=NA_integer_)
```  
### **Variable label**:  Difficulty falling a sleep  
**Variable name**:  lsb_sleep_diff_3  
**Variable description**:  Indicator of whether the participant ever has any diffulty falling a sleep.  
**Value type**:  integer  
**Variable unit**:  N/A  
**Category coding**:    

**Code** | **Category Label**  
------------- | -------------  
0 |  Never has difficulty falling asleep
1 |  Sometimes has difficulty falling asleep

**Harmonization status**:  complete    
**Harmonization comment**:   question  
**R script**:  
```{r, echo=TRUE}
lsb_LASA2_3$lsb_sleep_diff_3 <- recode(as.integer(LASA2H$hqsleep2),'1'=0L,'2'=1L,'3'=1L,'4'=1L,.default=NA_integer_)
```  
### **Variable label**:  Difficulty falling a sleep  
**Variable name**:  lsb_sleep_diff_4  
**Variable description**:  Indicator of whether the participant ever has any diffulty falling a sleep.  
**Value type**:  integer  
**Variable unit**:  N/A  
**Category coding**:    

**Code** | **Category Label**  
------------- | -------------  
0 |  Never has difficulty falling asleep
1 |  Sometimes has difficulty falling asleep

**Harmonization status**:  impossible  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}

```  
### **Variable label**:  Difficulty falling a sleep  
**Variable name**:  lsb_sleep_diff_5  
**Variable description**:  Indicator of whether the participant ever has any diffulty falling a sleep.  
**Value type**:  integer  
**Variable unit**:  N/A  
**Category coding**:    

**Code** | **Category Label**  
------------- | -------------  
0 |  Never has difficulty falling asleep
1 |  Sometimes has difficulty falling asleep

**Harmonization status**:  impossible  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}

```   

### **Variable label**:  Quality of sleep  
**Variable name**:  lsb_sleep_qlty_0  
**Variable description**:  Indicator of the quality of sleep of the participant.    
**Value type**:  integer  
**Variable unit**:  N/A  
**Category coding**:    

**Code** | **Category Label**  
------------- | -------------  
0 |  Very bad 
1 |  Fairly bad
2 |  Fairly good
3 |  Very good  

**Harmonization status**:  impossible  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}

```  

### **Variable label**:  Quality of sleep  
**Variable name**:  lsb_sleep_qlty_1  
**Variable description**:  Indicator of the quality of sleep of the participant.    
**Value type**:  integer  
**Variable unit**:  N/A  
**Category coding**:    

**Code** | **Category Label**  
------------- | -------------  
0 |  Very bad 
1 |  Fairly bad
2 |  Fairly good
3 |  Very good  

**Harmonization status**:  impossible  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}

```  

### **Variable label**:  Quality of sleep  
**Variable name**:  lsb_sleep_qlty_2  
**Variable description**:  Indicator of the quality of sleep of the participant.    
**Value type**:  integer  
**Variable unit**:  N/A  
**Category coding**:    

**Code** | **Category Label**  
------------- | -------------  
0 |  Very bad 
1 |  Fairly bad
2 |  Fairly good
3 |  Very good  

**Harmonization status**:  impossible  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}

```  
### **Variable label**:  Quality of sleep  
**Variable name**:  lsb_sleep_qlty_3  
**Variable description**:  Indicator of the quality of sleep of the participant.    
**Value type**:  integer  
**Variable unit**:  N/A  
**Category coding**:    

**Code** | **Category Label**  
------------- | -------------  
0 |  Very bad 
1 |  Fairly bad
2 |  Fairly good
3 |  Very good  

**Harmonization status**:  impossible  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}

```   
### **Variable label**:  Quality of sleep  
**Variable name**:  lsb_sleep_qlty_4  
**Variable description**:  Indicator of the quality of sleep of the participant.    
**Value type**:  integer  
**Variable unit**:  N/A  
**Category coding**:    

**Code** | **Category Label**  
------------- | -------------  
0 |  Very bad 
1 |  Fairly bad
2 |  Fairly good
3 |  Very good  

**Harmonization status**:  impossible  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}

```    
### **Variable label**:  Quality of sleep  
**Variable name**:  lsb_sleep_qlty_5  
**Variable description**:  Indicator of the quality of sleep of the participant.    
**Value type**:  integer  
**Variable unit**:  N/A  
**Category coding**:    

**Code** | **Category Label**  
------------- | -------------  
0 |  Very bad 
1 |  Fairly bad
2 |  Fairly good
3 |  Very good  

**Harmonization status**:  impossible  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}

```  



